### 2024-11-12 paper/paper.qmd
setting up the outline of the paper and documenting chatGPT

---
title: "Overcoming Hurdles to Green Living: Insights for Community Climate Action"
subtitle: "Understanding What Stops Sustainable Behaviors and How to Tackle It"
author: 
  - Lexi Knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
date: today
date-format: long
abstract: "This paper explores the factors limiting individuals from adopting environmentally friendly behaviors, drawing on survey data to understand motivations and barriers. Findings reveal that while many people are aware of climate change, obstacles like cost, convenience, and perceived effectiveness hinder sustainable actions. Additionally, the research highlights which methods of communication are most effective across different age groups. By addressing these barriers and tailoring strategies for engagement, cities can better empower residents to contribute to meaningful climate action, fostering a more sustainable urban future."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

# Introduction

Climate change remains one of the most pressing global challenges, with rising temperatures, extreme weather events, and environmental degradation threatening ecosystems and human well-being. Despite the urgent need for individual and collective action, many people continue to struggle with adopting sustainable behaviors in daily life. Governments and communities are increasingly interested in understanding how to motivate environmentally friendly practices, but significant gaps remain in identifying and addressing the obstacles that prevent action. This paper seeks to bridge that gap by examining not only what prevents individuals from engaging in sustainable behaviors but also what communication strategies can effectively inspire change.

This study focuses on a survey conducted in 2018, which gathered insights into people’s awareness of climate change, their likelihood of taking specific climate-friendly actions, the reasons behind inaction, preferred ways of receiving climate-related information, and demographic characteristics such as age and education. We investigate the extent to which people feel informed about climate change, their readiness to adopt energy-efficient practices, reduce waste, and embrace greener transportation options, among other behaviors. Our analysis also sheds light on the barriers individuals face, ranging from financial and logistical concerns to doubts about the impact of their actions, and explores how demographic factors influence communication preferences.

Addressing the gap between climate awareness and action is critical for effective community climate initiatives. Studies show that while awareness of environmental issues is widespread, behavioral change remains limited (Gifford, 2011). Additionally, research indicates that communication strategies tailored to specific demographics can enhance engagement and effectiveness (Moser & Dilling, 2007). Yet, there is little empirical evidence that explores how personalized communication and targeted interventions can overcome barriers to sustainable behaviors. Our study aims to fill this gap by estimating the causal impact of various factors on individuals’ willingness and ability to engage in environmentally friendly practices and identifying the best strategies for promoting sustainable change.

We found that practical obstacles, such as cost and convenience, alongside perceptions of ineffectiveness, are the primary reasons for inaction. Moreover, age and education level significantly shape how people prefer to receive information about climate action, suggesting that a one-size-fits-all communication strategy may be insufficient. These findings have substantial implications for policymakers and community leaders seeking to design more impactful climate initiatives. By addressing key barriers and tailoring engagement strategies, cities can empower individuals to adopt sustainable behaviors, making meaningful progress toward climate resilience and environmental sustainability.

The remainder of this paper is structured as follows: @sec-data presents the methods used to analyze these demographic differences, followed by @sec-results, which details the results of the comparison between Rosedale-Moore Park and Downtown Yonge East. @sec-discussion offers a discussion of the findings, highlighting the implications for understanding residential segregation in Toronto. Finally, @sec-conclusion concludes with a reflection on the limitations of the study and suggestions for future research directions.

# Data {#sec-data}

## Software and R-packages
## Methodology 
### Data Collection
### Data Cleaning
### Data Analysis
## Features
### Age
### Highest Level of Education Completed
### Extent Feel Informed
### Likelihood Taking Action
### Barriers Taking Action
### Best Mode of Delivery

# Model {#sec-model}
The goal of our modelling strategy is twofold. Firstly,...
Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-appendix].
## Model set-up
Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model Specifications ###
### Model Justification 
We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.
#### Response Variable ####
#### Input Variabless ####
#### Model Structure ####
#### Parameter Estimation ####

# Results

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Limitations

## Future Directions

# Conclusion {#sec-conclusion}

\newpage

\appendix

# Appendix {#sec-appendix}

\newpage

# References

### 2024-11-12 scripts/03-clean_data.R

@@ -123,17 +123,17 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
     unlikelihood_action_sort_waste_inconvienient_18 = Q11_Lr9r6,
     unlikelihood_action_sort_waste_uninterested_18 = Q11_Lr9r7,
     unlikelihood_action_sort_waste_other_18 = Q11_Lr9r8,
-    toronto.ca_website_18 = Q13r1,
-    events_18 = Q13r2,
-    twitter_18 = Q13r3,
-    facebook_18 = Q13r4,
-    instagram_18 = Q13r5,
-    enewsletter_email_18 = Q13r6,
-    councillor_communication_18 = Q13r7,
-    advertising_campaigns_18 = Q13r8,
-    brochures_pamphlets_18 = Q13r9,
-    other_18 = Q13r10,
-    not_interested_receiving_18 = Q13r11,
+    delivery_method_toronto.ca_website_18 = Q13r1,
+    delivery_method_events_18 = Q13r2,
+    delivery_method_twitter_18 = Q13r3,
+    delivery_method_facebook_18 = Q13r4,
+    delivery_method_instagram_18 = Q13r5,
+    delivery_method_enewsletter_email_18 = Q13r6,
+    delivery_method_councillor_communication_18 = Q13r7,
+    delivery_method_advertising_campaigns_18 = Q13r8,
+    delivery_method_brochures_pamphlets_18 = Q13r9,
+    delivery_method_other_18 = Q13r10,
+    delivery_method_not_interested_receiving_18 = Q13r11,
     highest_level_educ_18 = QD5
   )
 
@@ -141,4 +141,4 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
 head(renamed_twenty_eighteen)
 
 #### Save data ####
-write_csv(renamed_twenty_eighteen, "data/analysis_data.csv")
+write_csv(renamed_twenty_eighteen, "data/02-analysis_data/analysis_data.csv")

### 2024-11-14 paper/paper.qmd
working on figures in data section

@@
 ### Age
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-one
+#| fig-cap: The chart illustrates the distribution of age for the 2018 survey in the City of Toronto, highlighting the major age categories.
+
+# install libraries 
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))
+
+# Load necessary libraries
+library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(here)
+library(stringr)
+library(knitr)
+
+# Read in the data from your CSV file
+analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))
+
+# Create a histogram to show the distribution of age
+age_plot <- ggplot(data, aes(x = age_18)) +
+  geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) +
+  labs(
+    title = "Age Distribution of Survey Respondents (2018)",
+    x = "Age",
+    y = "Frequency"
+  ) +
+  theme_minimal()
+
+# Display the plot
+print(age_plot)
+
+# calculate summary statistics 
+mean_age <- mean(data$age_18, na.rm = TRUE)
+median_age <- median(data$age_18, na.rm = TRUE)
+min_age <- min(data$age_18, na.rm = TRUE)
+max_age <- max(data$age_18, na.rm = TRUE)
+# R does not have built in function thus needs to be defined
+sd_age <- sd(data$age_18, na.rm = TRUE)
+mode_age <- function(x) {
+  unique_x <- unique(x)
+  unique_x[which.max(tabulate(match(x, unique_x)))]
+}
+mode_value <- mode_age(data$age_18)
+
+# Create a data frame with the summary statistics
+summary_stats_age_18 <- data.frame(
+  Statistic = c("Mean Age", "Median Age", "Mode Age", "Standard Deviation", "Minimum Age", "Maximum Age"),
+  Value = c(mean_age, median_age, mode_value, sd_age, min_age, max_age)
+)
+
+# Use kable to generate a nice table
+kable(summary_stats_age_18, 
+      caption = "Summary Statistics for Age of Survey Respondents", 
+      col.names = c("Statistic", "Value"),
+      align = c("l", "c"))
+
+```
+
 ### Highest Level of Education Completed
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-one
+#| fig-cap: The chart illustrates the distribution of highest level of education acheived for the 2018 surveyin the city of Toronto, highlighting academic achievement.
+
+# install libraries 
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))
+
+# Load necessary libraries
+library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(here)
+library(stringr)
+library(knitr)
+
+# Read in the data from your CSV file
+analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))
+
+# Create a bar chart for the highest level of education
+ggplot(data = analysis_data, aes(x = factor(highest_level_educ_18, 
+       levels = c("High school or less",
+                  "Some community college, vocational, trade school",
+                  "Completed community college, vocational, trade school",
+                  "Some university",
+                  "Completed undergraduate degree",
+                  "Post graduate/professional school", 
+                  "Prefer not to answer")))) +
+  geom_bar(fill = "skyblue", color = "black") +
+  labs(
+    title = "Distribution of Highest Level of Education Achievement",
+    x = "Level of Education",
+    y = "Count"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.margin = margin(10, 10, 10, 10), # Adds margin around the plot
+    plot.title = element_text(hjust = 0.5) # Centers the title
+  ) + 
+  # Wrap x-axis labels
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) + 
+  # Y-axis ticks every 25
+  scale_y_continuous(breaks = seq(0, max(table(analysis_data$highest_level_educ_18)), by = 25))
+
+# Adjust the size of the figure (increase height)
+  ggsave("education_chart.png", width = 10, height = 6)
+```
+
 ### Extent Feel Informed
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-one
+#| fig-cap: The bar chart illustrates the distribution of the extent individuals feel informed about what causes climate change in the City of Toronto, based on the 2018 survey.
+
+# install libraries 
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))
+
+# Load necessary libraries
+library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(here)
+library(stringr)
+library(knitr)
+
+# Read in the data from your CSV file
+analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))
+
+# Create a bar chart for the extent people feel informed about climate change
+ggplot(data = analysis_data, aes(x = factor(extent_consider_informed_18, 
+       levels = c("Extremely informed", 
+                  "Very informed", 
+                  "Not very informed", 
+                  "Not at all informed")))) +
+  geom_bar(fill = "lightgreen", color = "black") +
+  labs(
+    title = "Extent People Feel Informed About Climate Change",
+    x = "Level of Informedness",
+    y = "Count"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5) # Center the title
+  )
+
+```
+
 ### Likelihood Taking Action
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-one
+#| fig-cap: The bar chart illustrates the distribution of the likelihood of taking certain actions to address climate change in the City of Toronto based on the 2018 survey.
+
+# install libraries 
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))
+
+# Load necessary libraries
+library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(here)
+library(stringr)
+library(knitr)
+
+# Read in the data from your CSV file
+analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))
+
+# Create reshaped data for plotting
+action_data_long <- analysis_data %>%
+  pivot_longer(cols = starts_with("likelihood_action"),
+               names_to = "Action",
+               values_to = "Likelihood") %>%
+  mutate(Action = recode(Action,
+                         likelihood_action_home_improvement_18 = "Home Improvement",
+                         likelihood_action_reduce_hydro_18 = "Reduce Hydro Use",
+                         likelihood_action_minimize_car_18 = "Minimize Car Use",
+                         likelihood_action_vehicle_electric_18 = "Use Electric Vehicle",
+                         likelihood_action_protein_alternative_18 = "Alternative Proteins",
+                         likelihood_action_reduce_waste_18 = "Reduce Waste",
+                         likelihood_action_green_product_18 = "Green Products",
+                         likelihood_action_short_distance_18 = "Short Distance Travel",
+                         likelihood_action_sort_waste_18 = "Sort Waste")) %>%
+  filter(!is.na(Likelihood)) %>% # Remove rows where Likelihood is NA
+  mutate(Likelihood = factor(Likelihood)) # Convert Likelihood to a factor
+
+# Plot the distribution of likelihood of actions to address climate change
+ggplot(action_data_long, aes(x = Action, fill = Likelihood)) +
+  geom_bar(stat = "count", position = "dodge") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1), # Rotate x-axis labels for readability
+        axis.title.y = element_text(size = 12),
+        legend.title = element_text(size = 12),
+        legend.text = element_text(size = 10)) +
+  labs(
+    title = "Likelihood of Taking Action to Address Climate Change in Toronto (2018)",
+    x = "Actions to Address Climate Change",
+    y = "Count of Responses",
+    fill = "Likelihood"
+  ) +
+  scale_fill_manual(values = c("Already doing this or have done this" = "green",
+                               "Very likely" = "blue",
+                               "Somewhat likely" = "yellow",
+                               "Somewhat unlikely" = "orange",
+                               "Very unlikely" = "red"))
+```
+
 ### Barriers Taking Action

### 2024-11-14 scripts/03-clean_data.R

@@ -17,11 +17,9 @@ library(dplyr)
 
 #### Clean data 2018 ####
 # Read the csv file
-
 twenty_eighteen_raw_data <- read_csv("data/01-raw_data/twenty_eighteen_raw_data.csv")
 
 #  I want to select certain columns outlined below
-
 twenty_eighteen <- twenty_eighteen_raw_data %>%
   select(HIDAGE1, Q2, Q10r1, Q10r2, Q10r3, Q10r4, Q10r5, Q10r6, Q10r7, Q10r8, Q10r9,
   Q11_Lr1r1, Q11_Lr1r2, Q11_Lr1r3, Q11_Lr1r4, Q11_Lr1r5, Q11_Lr1r6, Q11_Lr1r7, Q11_Lr1r8,
@@ -34,7 +32,10 @@ twenty_eighteen <- twenty_eighteen_raw_data %>%
   Q11_Lr8r1, Q11_Lr8r2, Q11_Lr8r3, Q11_Lr8r4, Q11_Lr8r5, Q11_Lr8r6, Q11_Lr8r7, Q11_Lr8r8,
   Q11_Lr9r1, Q11_Lr9r2, Q11_Lr9r3, Q11_Lr9r4, Q11_Lr9r5, Q11_Lr9r6, Q11_Lr9r7, Q11_Lr9r8,
   Q13r1, Q13r2, Q13r3, Q13r4, Q13r5, Q13r6, Q13r7, Q13r8, Q13r9, Q13r10, Q13r11,
-  QD5)
+  QD5
+  ) %>%
+  na.omit()  # Remove rows with NA values
+  
 
 #### Rename columns 2018 ####
 # use rename() function to give more meaningful names

### 2024-11-14 scripts/03-clean_data.R
still working on data section

@@ -32,10 +32,7 @@ twenty_eighteen <- twenty_eighteen_raw_data %>%
   Q11_Lr8r1, Q11_Lr8r2, Q11_Lr8r3, Q11_Lr8r4, Q11_Lr8r5, Q11_Lr8r6, Q11_Lr8r7, Q11_Lr8r8,
   Q11_Lr9r1, Q11_Lr9r2, Q11_Lr9r3, Q11_Lr9r4, Q11_Lr9r5, Q11_Lr9r6, Q11_Lr9r7, Q11_Lr9r8,
   Q13r1, Q13r2, Q13r3, Q13r4, Q13r5, Q13r6, Q13r7, Q13r8, Q13r9, Q13r10, Q13r11,
-  QD5
-  ) %>%
-  na.omit()  # Remove rows with NA values
-  
+  QD5)
 
 #### Rename columns 2018 ####
 # use rename() function to give more meaningful names

### 2024-11-25 scripts/03-clean_data.R
saving analysis data; individual for 2018 and summary 2021.

@@ -20,6 +20,9 @@ library(openxlsx)
 # Read the csv file
 twenty_eighteen_raw_data <- read_csv("data/01-raw_data/twenty_eighteen_raw_data.csv")
 
+# Sample size information
+sample_size_2018 <- 404 # This is the sample size for the year 2018
+
 #  I want to select certain columns outlined below
 twenty_eighteen <- twenty_eighteen_raw_data %>%
   select(HIDAGE1, Q2, Q10r1, Q10r2, Q10r3, Q10r4, Q10r5, Q10r6, Q10r7, Q10r8, Q10r9,
@@ -55,7 +58,7 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
     unlikelihood_action_home_improvement_ineffective_18 = Q11_Lr1r3,
     unlikelihood_action_home_improvement_costly_18 = Q11_Lr1r4,
     unlikelihood_action_home_improvement_unavailable_18 = Q11_Lr1r5,
-    unlikelihood_action_home_improvement_inconvienient_18 = Q11_Lr1r6,
+    unlikelihood_action_home_improvement_inconvenient_18 = Q11_Lr1r6,
     unlikelihood_action_home_improvement_uninterested_18 = Q11_Lr1r7,
     unlikelihood_action_home_improvement_other_18 = Q11_Lr1r8,
     unlikelihood_action_reduce_hydro_confusing_18 = Q11_Lr2r1,
@@ -63,7 +66,7 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
     unlikelihood_action_reduce_hydro_ineffective_18 = Q11_Lr2r3,
     unlikelihood_action_reduce_hydro_costly_18 = Q11_Lr2r4,
     unlikelihood_action_reduce_hydro_unavailable_18 = Q11_Lr2r5,
-    unlikelihood_action_reduce_hydro_inconvienient_18 = Q11_Lr2r6,
+    unlikelihood_action_reduce_hydro_inconvenient_18 = Q11_Lr2r6,
     unlikelihood_action_reduce_hydro_uninterested_18 = Q11_Lr2r7,
     unlikelihood_action_reduce_hydro_other_18 = Q11_Lr2r8,
     unlikelihood_action_minimize_car_confusing_18 = Q11_Lr3r1,
@@ -71,7 +74,7 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
[…]

### 2024-11-25 scripts/03-clean_data.R
updating llm usage

@@ -264,5 +264,5 @@ cleaned_wb <- createWorkbook()
 addWorksheet(cleaned_wb, "Consolidated Data")
 writeData(cleaned_wb, "Consolidated Data", combined_data)
 
-# Save the workbook
-saveWorkbook(cleaned_wb, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.xlsx", overwrite = TRUE)
+#### Save the consolidated data as CSV ####
+write.csv(combined_data, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.csv", row.names = FALSE)

### 2024-11-25 scripts/03-clean_data.R
fixing NA and NO TO in 2018 individual

@@ -139,16 +139,21 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
     highest_level_educ_18 = QD5
   )
 
-# Fix all "unlikelihood" and 'delivery' columns
+# Fix all "unlikelihood" and "delivery" columns
+# Replace NA, "TO DO", and other values in columns
 fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
   mutate(
     across(
-      starts_with("unlikelihood"),
-      ~ ifelse(is.na(.), "no", "yes")  # Replace NA with "no" and non-NA with "yes"
-    ),
+      starts_with("unlikelihood_action"),
+      ~ ifelse(is.na(.), "no",
+               ifelse(startsWith(., "TO DO"), "no", "yes"))
+    )
+  ) %>%
+  mutate(
     across(
-      starts_with("delivery"),
-      ~ ifelse(grepl("^NO TO:", ., ignore.case = TRUE), "no", "yes")
+      starts_with("delivery_method"),
+      ~ ifelse(is.na(.), "no",
+               ifelse(startsWith(., "TO DO"), "no", "yes"))
     )
   )
 

### 2024-11-25 scripts/03-clean_data.R
checking to see if fixed layout for 2018 individual data

@@ -140,20 +140,20 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
   )
 
 # Fix all "unlikelihood" and "delivery" columns
-# Replace NA, "TO DO", and other values in columns
+# Replace NA, "NO TO", and other values in columns
 fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
   mutate(
     across(
       starts_with("unlikelihood_action"),
       ~ ifelse(is.na(.), "no",
-               ifelse(startsWith(., "TO DO"), "no", "yes"))
+               ifelse(startsWith(., "NO TO"), "no", "yes"))
     )
   ) %>%
   mutate(
     across(
       starts_with("delivery_method"),
       ~ ifelse(is.na(.), "no",
-               ifelse(startsWith(., "TO DO"), "no", "yes"))
+               ifelse(startsWith(., "NO TO"), "no", "yes"))
     )
   )
 

### 2024-11-26 scripts/03-clean_data.R
trying to fix 2021 summary data

@@ -9,12 +9,13 @@
 
 #### Workspace setup ####
 # install necessary packages
-# install.packages(c("readr", "dplyr", "openxlsx"))
+# install.packages(c("readr", "dplyr", "openxlsx", "readxl"))
 
 # load necessary packages
 library(readr)
 library(dplyr) # for combining data frames
 library(openxlsx)
+library(readxl)
 
 #### Clean data 2018 ####
 # Read the csv file
@@ -159,10 +160,10 @@ fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
 
 
 # View the first few rows to confirm the data
-head(renamed_twenty_eighteen)
+head(fixed_twenty_eighteen)
 
 #### Save 2018 individual data ####
-write_csv(renamed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv")
+write_csv(fixed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv")
 
 
 
@@ -173,101 +174,149 @@ write_csv(renamed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_indivi
 # File path to the saved workbook
 file_path <- "data/01-raw_data/twenty_twenty_one_raw_data.xlsx"
 
-# Sheet numbers to extract
-sheet_numbers <- c(3, 11, 34, 69, 85, 113, 114)
-
-# Get all sheet names
-sheet_names <- getSheetNames(file_path)
-
 # Sample size information
 sample_size_2021 <- 1401 # This is the sample size for the year 2021
 
-#### Function to extract data from a sheet ####
-extract_data <- function(sheet, rows_A, rows_B, cols_B_to = NULL) {
-  # Read the sheet
-  data <- read.xlsx(file_path, sheet = sheet)
+# Extract data from Sheet 3 + 1 (accounting for the index sheet)
+sheet_data <- read_excel(file_path, sheet = 4)
+
+# Define rows and columns for Sheet 3 that want extract 
+rows_A <- c(8, 11, 14, 17)  # Categories in column A (age categories)
+rows_B <- c(8, 11, 14, 17)  # Data in column B (whole numbers)
+
+# Extract the age categories from column A
+categories <- sheet_data[rows_A, 1]
+
+# Print categories to check if they are properly extracted
[…]

### 2024-11-26 paper/paper.qmd
checking if correctly cleaned summary data 2021

@@
 
+the following categories were not options under reasons unlikely to perform action   "Use public transit more",
+  "Cycle more",
+  "Walk more",
+  "Purchase electric/hybrid vehicle in next 1-3 years",
+  but they were categories for which actions are you most likely to take part in to address climate change.
+
+no indiivdual data for 2021, used summary statistics instead
+
 ## Future Directions

### 2024-11-26 scripts/03-clean_data.R

@@ -9,13 +9,14 @@
 
 #### Workspace setup ####
 # install necessary packages
-# install.packages(c("readr", "dplyr", "openxlsx", "readxl"))
+# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow"))
 
 # load necessary packages
 library(readr)
 library(dplyr) # for combining data frames
 library(openxlsx)
 library(readxl)
+library(arrow) # for saving file as parquet
 
 #### Clean data 2018 ####
 # Read the csv file
@@ -39,7 +40,7 @@ twenty_eighteen <- twenty_eighteen_raw_data %>%
   Q13r1, Q13r2, Q13r3, Q13r4, Q13r5, Q13r6, Q13r7, Q13r8, Q13r9, Q13r10, Q13r11,
   QD5)
 
-#### Rename columns 2018 ####
+## Rename columns 2018 ##
 # use rename() function to give more meaningful names
 renamed_twenty_eighteen <- twenty_eighteen %>%
   rename(
@@ -163,8 +164,7 @@ fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
 head(fixed_twenty_eighteen)
 
 #### Save 2018 individual data ####
-write_csv(fixed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv")
-
+write_parquet(fixed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet")
 
 
 
@@ -177,25 +177,25 @@ file_path <- "data/01-raw_data/twenty_twenty_one_raw_data.xlsx"
 # Sample size information
 sample_size_2021 <- 1401 # This is the sample size for the year 2021
 
+## Age - sheet 3 ##
+
 # Extract data from Sheet 3 + 1 (accounting for the index sheet)
 sheet_data <- read_excel(file_path, sheet = 4)
 
 # Define rows and columns for Sheet 3 that want extract 
-rows_A <- c(8, 11, 14, 17)  # Categories in column A (age categories)
-rows_B <- c(8, 11, 14, 17)  # Data in column B (whole numbers)
+rows_A <- c(7, 10, 13, 16)  # Categories in column A (age categories)
+rows_B <- c(8, 11, 14, 17)  # Data in column B
 
 # Extract the age categories from column A
-categories <- sheet_data[rows_A, 1]
+categories <- sheet_data %>% 
+  slice(rows_A) %>% 
[…]

### 2024-11-26 scripts/03-clean_data.R
saving

@@ -607,7 +607,7 @@ combined_summary_21 <- bind_rows(
 
 # Save the combined data as a Parquet file
 write_parquet(combined_summary_21, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.parquet")
-
+write_csv(combined_summary_21, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.csv")
 
 # Confirmation message
 print("Data saved successfully!")

### 2024-11-26 scripts/03-clean_data.R
working on cleaning and combining 7 summary datasets for 2021 into one sheet . struggling.

@@ -220,7 +220,7 @@ age_summary_21 <- data.frame(
 )
 
 # Rename the column headers
-colnames(age_summary_21) <- c("Age Category", "Percentage")
+colnames(age_summary_21) <- c("Age Categories", "Age Percentage")
 
 # Print the consolidated data to check
 print(age_summary_21)
@@ -272,7 +272,7 @@ education_summary_21 <- data.frame(
 )
 
 # Rename the column headers
-colnames(education_summary_21) <- c("Education Level", "Percentage")
+colnames(education_summary_21) <- c("Education Levels", "Education Percentage")
 
 # Print the consolidated data to check
 print(education_summary_21)
@@ -324,7 +324,7 @@ informed_summary_21 <- data.frame(
 )
 
 # Rename the column headers
-colnames(informed_summary_21) <- c("Extent Informed", "Percentage")
+colnames(informed_summary_21) <- c("Extent Informed", "Informed Percentage")
 
 # Print the consolidated data to check
 print(informed_summary_21)
@@ -381,21 +381,21 @@ likelihood_summary_21 <- data.frame(
 
 colnames(likelihood_summary_21) <- c(
   "Likelihood to Take Action",
-  "Purchase energy efficient appliances",
-  "Install a programmable thermostat",
-  "Install LED lightbulbs",
-  "Undertake major home renos for energy efficiency",
-  "Add solar panels to home",
-  "Get an EnerGuide home energy evaluation to identify opportunities",
-  "Reduce water use",
-  "Use public transit more",
-  "Cycle more",
-  "Walk more",
-  "Purchase electric/hybrid vehicle in next 1-3 years",
-  "Eat less meat",
-  "Reduce amount of own waste",
-  "Purchase environmentally friendly items",
-  "Put effort into sorting waste into correct bins"
+  "Likely purchase energy efficient appliances",
+  "Likely install a programmable thermostat",
+  "Likely install LED lightbulbs",
+  "Likely undertake major home renos for energy efficiency",
+  "Likely add solar panels to home",
+  "Likely get an EnerGuide home energy evaluation to identify opportunities",
+  "Likely reduce water use",
+  "Likely use public transit more",
+  "Likely cycle more",
+  "Likely walk more",
+  "Likely purchase electric/hybrid vehicle in next 1-3 years",
+  "Likely eat less meat",
+  "Likely reduce amount of own waste",
+  "Likely purchase environmentally friendly items",
+  "Likely put effort into sorting waste into correct bins"
 )
 
 # Print the consolidated data to check
[…]

### 2024-11-27 scripts/03-clean_data.R
trying to save summary 2021 data on one sheet

@@ -421,10 +421,6 @@ categories <- sheet_data %>%
   pull(1) %>%  # Pull the first column (A) as a vector
   trimws()  # Remove unexpected whitespace
 
-# Print categories to check
-print("Categories (Column A):")
-print(categories)
-
 # Initialize a list to store data for columns B through L
 percentage_list <- list()
 
@@ -465,9 +461,6 @@ colnames(reasons_summary_21) <- c(
 # Print the consolidated data to check
 print("Reasons Summary:")
 print(reasons_summary_21)
-
-#### TO DO : MUST FIX that there is a column named source with 7 rows "reasons summary 2021" 
-
 
 
 
@@ -585,19 +578,51 @@ print(communication_summary_21)
 
 
 
+
+
+
 ## Combine Individual 2021 Data ##
 
-# Add a source column to each dataset to identify their origin
-age_summary_21 <- age_summary_21 %>% mutate(Source = "Age Summary 2021")
-education_summary_21 <- education_summary_21 %>% mutate(Source = "Education Summary 2021")
-informed_summary_21 <- informed_summary_21 %>% mutate(Source = "Informed Summary 2021")
-likelihood_summary_21 <- likelihood_summary_21 %>% mutate(Source = "Likelihood Summary 2021")
-reasons_summary_21 <- reasons_summary_21 %>% mutate(Source = "Reasons Summary 2021")
-support_summary_21 <- support_summary_21 %>% mutate(Source = "Support Summary 2021")
-communication_summary_21 <- communication_summary_21 %>% mutate(Source = "Communication Summary 2021")
+# In order to use bind_cols, data frames need to have the same number of rows
+# The dataframes have different number of rows hece, need to pad them with NA
+# values so they match the longest data frame. 
 
-# Combine all datasets into one
-combined_summary_21 <- bind_rows(
+# Find the maximum number of rows
+num_rows <- sapply(list(
+  age_summary_21,
+  education_summary_21,
+  informed_summary_21,
+  likelihood_summary_21,
+  reasons_summary_21,
+  support_summary_21,
+  communication_summary_21
+), nrow)
+
+max_rows <- max(num_rows)  # Find the maximum number of rows
+print(num_rows)  # Print number of rows for debugging
+
+# Pad data frames with NA for those that have shorter than the max number of rows
+pad_with_na <- function(df, max_rows) {
+  if (nrow(df) < max_rows) {
[…]

### 2024-11-27 scripts/03-clean_data.R
another attempt at fixing the cleaned data for summary 2021

@@ -180,36 +180,26 @@ sample_size_2021 <- 1401 # This is the sample size for the year 2021
 ## Age - sheet 3 ##
 
 # Extract data from Sheet 3 + 1 (accounting for the index sheet)
-sheet_data <- read_excel(file_path, sheet = 4)
+sheet4_data <- read_excel(file_path, sheet = 4)
 
 # Define rows and columns for Sheet 3 that want extract 
 rows_A <- c(7, 10, 13, 16)  # Categories in column A (age categories)
 rows_B <- c(8, 11, 14, 17)  # Data in column B
 
 # Extract the age categories from column A
-categories <- sheet_data %>% 
-  slice(rows_A) %>% 
-  pull(1)  # Pull the first column as a vector
-
-# Remove unexpected white spaces or non-printing characters
-categories <- trimws(categories)
-
-# Print categories to check
-print("Categories (Column A):")
-print(categories)
+categories <- sheet4_data %>%
+  slice(rows_A) %>%
+  pull(1) %>%  # Pull the first column (A) as a vector
+  trimws()  # Remove unexpected whitespace
 
 # Extract the percentage raw data from column B 
-raw_data_B <- sheet_data[rows_B, 2]
+raw_data_B <- sheet4_data[rows_B, 2]
 
 # Convert raw data from tibble to character and then to numeric
 raw_data_B_numeric <- as.numeric(as.character(raw_data_B[[1]]))
 
 # Multiply by 100 to convert to percentages (if the conversion succeeded)
-percentages <- raw_data_B_numeric * 100
-
-# Print the consolidated percentages
-# print("Percentages (Converted and multiplied by 100):")
-# print(percentages)
+percentages <- round(raw_data_B_numeric * 100)
 
 ## Save the age_summary_21 ##
 
@@ -232,36 +222,26 @@ print(age_summary_21)
 ## education - sheet 11 ##
 
 # Extract data from Sheet 11 + 1 (accounting for the index sheet)
-sheet_data <- read_excel(file_path, sheet = 12)
+sheet12_data <- read_excel(file_path, sheet = 12)
 
 # Define rows and columns for Sheet 11 that want extract 
 rows_A <- c(7, 10, 13, 16, 19, 22)  # Categories in column A (education categories)
 rows_B <- c(8, 11, 14, 17, 20, 23)  # Data in column B
 
 # Extract the education categories from column A
-categories <- sheet_data %>% 
-  slice(rows_A) %>% 
[…]

### 2024-11-27 scripts/03-clean_data.R
hopefully saving 2021 summary data without the extra v columns

@@ -582,9 +582,9 @@ combined_data <- bind_cols(
 data_cleaned <- combined_data %>%
   select(-starts_with("V"))  # Removes columns starting with "V"
 
-# Save the combined data as a Parquet file
-write_parquet(combined_data, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.parquet")
-write_csv(combined_data, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.csv")
+# Save the combined data as a Parquet file and csv file
+write_parquet(data_cleaned, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.parquet")
+write_csv(data_cleaned, "data/02-analysis_data/twenty_twenty_two_summary_analysis_data.csv")
 
 # Confirmation message
 print("Data saved successfully!")

### 2024-11-27 scripts/03-clean_data.R
saving 2018 individual data as csv so i can visualize and create the 2018 summary data

@@ -18,7 +18,7 @@ library(openxlsx)
 library(readxl)
 library(arrow) # for saving file as parquet
 
-#### Clean data 2018 ####
+#### Clean data individual 2018 dataset ####
 # Read the csv file
 twenty_eighteen_raw_data <- read_csv("data/01-raw_data/twenty_eighteen_raw_data.csv")
 
@@ -165,6 +165,24 @@ head(fixed_twenty_eighteen)
 
 #### Save 2018 individual data ####
 write_parquet(fixed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet")
+write_csv(fixed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv")
+
+
+
+
+
+
+
+#### Clean data summary 2018 dataset ####
+
+# Read the csv file
+twenty_eighteen_raw_data <- read_csv("data/01-raw_data/twenty_eighteen_raw_data.csv")
+
+
+
+
+
+
 
 
 

### 2024-11-27 scripts/03-clean_data.R
over half way done 2018 summary data :))

@@ -9,7 +9,7 @@
 
 #### Workspace setup ####
 # install necessary packages
-# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow"))
+# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow", "tidyverse", "tidyr"))
 
 # load necessary packages
 library(readr)
@@ -17,6 +17,8 @@ library(dplyr) # for combining data frames
 library(openxlsx)
 library(readxl)
 library(arrow) # for saving file as parquet
+library(tidyverse)
+library(tidyr)
 
 #### Clean data individual 2018 dataset ####
 # Read the csv file
@@ -159,7 +161,6 @@ fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
     )
   )
 
-
 # View the first few rows to confirm the data
 head(fixed_twenty_eighteen)
 
@@ -173,10 +174,157 @@ write_csv(fixed_twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individu
 
 
 
+
 #### Clean data summary 2018 dataset ####
 
 # Read the csv file
-twenty_eighteen_raw_data <- read_csv("data/01-raw_data/twenty_eighteen_raw_data.csv")
+twenty_eighteen_individual <- read_csv("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv", col_names = TRUE)
+
+
+## 1. Age Summary ##
+
+## Create age categories based on ranges in 2021 summary data and summarize directly
+age_summary_18 <- as.data.frame(table(cut(fixed_twenty_eighteen$age_18, 
+                                         breaks = c(17, 23, 39, 55, Inf), 
+                                         labels = c("18-23", "24-39", "40-55", "56+"), 
+                                         right = TRUE)))
+
+# Rename columns and calculate the percentage
+names(age_summary_18) <- c("Age Group", "Freq")
+age_summary_18$Percentage <- round((age_summary_18$Freq / sum(age_summary_18$Freq)) * 100)
+
+# Keep only the age group and percentage columns
+age_summary_18 <- age_summary_18[, c("Age Group", "Percentage")]
+
+# View the final summary table
+print(age_summary_18)
+
+
+## 2. Education Level Summary ##
+
+# Create the summary table based on education levels
+education_summary_18 <- as.data.frame(table(fixed_twenty_eighteen$highest_level_educ_18))
+
+# Rename columns and calculate the percentage
+names(education_summary_18) <- c("Education Level", "Freq")
[…]

### 2024-11-28 scripts/03-clean_data.R
moving on from data cleaning to EDA

@@ -269,61 +269,68 @@ likelihood_summary_18 <- combined_likelihood_summary %>%
 print(likelihood_summary_18)
 
 
-#### 5. Reasons Summary ####
+## 5. Reasons Summary ##
 
-# Step 1: Select columns starting with "unlikelihood_action"
-reasons_data <- fixed_twenty_eighteen %>%
-  select(starts_with("unlikelihood_action"))
+# Transform the data and calculate the percentage of "yes" for each action column
+reasons_summary_18 <- fixed_twenty_eighteen %>%
+  select(starts_with("unlikelihood_action")) %>%
+  pivot_longer(cols = everything(), names_to = "Action", values_to = "Response") %>%
+  mutate(Response = ifelse(Response == "yes", 1, 0)) %>%  # Convert "yes" to 1 and "no" to 0
+  group_by(Action) %>%
+  summarise(Percentage = round(mean(Response, na.rm = TRUE) * 100, 0)) %>%
+  ungroup()
 
-# Step 2: Create a summary table by gathering data into long format
-reasons_summary_18 <- reasons_data %>%
-  pivot_longer(cols = everything(), 
-               names_to = "Reason", 
-               values_to = "Response") %>%
-  group_by(Reason, Response) %>%
-  summarise(Freq = n(), .groups = "drop") %>%
-  mutate(Percentage = round((Freq / sum(Freq)) * 100, 1))
+# Rename columns for clarity
+colnames(reasons_summary_18) <- c("Action", "Percentage")
 
-# Step 3: Pivot wider for better readability
-reasons_summary_18 <- reasons_summary_18 %>%
-  pivot_wider(names_from = Reason, values_from = Percentage)
-
-# Step 4: View the final table
+# View the final summary table
 print(reasons_summary_18)
 
 
-
-# Unlikelihood action summary (columns starting with "unlikelihood_action")
-reasons_summary_18 <- twenty_eighteen_raw_data %>%
-  select(starts_with("unlikelihood_action")) %>%
-  pivot_longer(cols = everything(), names_to = "unlikelihood_action", values_to = "response") %>%
-  count(unlikelihood_action, response) %>%
-  mutate(percentage = n / sample_size_2018 * 100) %>%
-  select(unlikelihood_action, response, percentage)
-
 #### 6. Communication Summary ####
 
-# Communication method not interested in receiving
-communication_summary_18 <- twenty_eighteen_raw_data %>%
[…]

### 2024-11-28 scripts/05-exploratory_data_analysis.R

@@ -1,37 +1,65 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Exploring 2018 individual data as well as 2018 and 2021 summary data. 
+# Author: Lexi Knight
+# Date: 27 November 2024
+# Contact: lexi.knight@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: complete 01-download_data.R and 03-clean_data.R in scripts folder in order to access raw data.
 
 
 #### Workspace setup ####
+
+# install libraries 
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))
+
+# Load necessary libraries
 library(tidyverse)
-library(rstanarm)
+library(dplyr)
+library(ggplot2)
+library(here)
+library(stringr)
+library(knitr)
 
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+# Read in the data from your CSV file
+individual_18 <- read_csv(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Create a histogram to show the distribution of age
+age_individual_plot <- ggplot(data, aes(x = age_18)) +
+  geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) +
+  labs(
+    title = "Age Distribution of Survey Respondents (2018)",
+    x = "Age",
+    y = "Frequency"
+  ) +
+  theme_minimal()
 
+# Display the plot
+print(age_individual_plot)
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
[…]

### 2024-11-28 scripts/03-clean_data.R
working on EDA

@@ -27,7 +27,7 @@ twenty_eighteen_raw_data <- read_csv("data/01-raw_data/twenty_eighteen_raw_data.
 # Sample size information
 sample_size_2018 <- 404 # This is the sample size for the year 2018
 
-#  I want to select certain columns outlined below
+#  Select certain columns outlined below
 twenty_eighteen <- twenty_eighteen_raw_data %>%
   select(HIDAGE1, Q2, Q10r1, Q10r2, Q10r3, Q10r4, Q10r5, Q10r6, Q10r7, Q10r8, Q10r9,
   Q11_Lr1r1, Q11_Lr1r2, Q11_Lr1r3, Q11_Lr1r4, Q11_Lr1r5, Q11_Lr1r6, Q11_Lr1r7, Q11_Lr1r8,
@@ -42,8 +42,7 @@ twenty_eighteen <- twenty_eighteen_raw_data %>%
   Q13r1, Q13r2, Q13r3, Q13r4, Q13r5, Q13r6, Q13r7, Q13r8, Q13r9, Q13r10, Q13r11,
   QD5)
 
-## Rename columns 2018 ##
-# use rename() function to give more meaningful names
+# Rename columns for clarity and meaning via rename() function
 renamed_twenty_eighteen <- twenty_eighteen %>%
   rename(
     age_18 = HIDAGE1,
@@ -142,6 +141,20 @@ renamed_twenty_eighteen <- twenty_eighteen %>%
     delivery_method_not_interested_receiving_18 = Q13r11,
     highest_level_educ_18 = QD5
   )
+# Change "NA" values to "No answer" in the relevant columns
+renamed_twenty_eighteen <- renamed_twenty_eighteen %>%
+  mutate(across(
+    c(likelihood_action_home_improvement_18, 
+      likelihood_action_reduce_hydro_18, 
+      likelihood_action_minimize_car_18, 
+      likelihood_action_vehicle_electric_18, 
+      likelihood_action_protein_alternative_18, 
+      likelihood_action_reduce_waste_18, 
+      likelihood_action_green_product_18, 
+      likelihood_action_short_distance_18, 
+      likelihood_action_sort_waste_18), 
+    ~ replace_na(., "No answer")
+  ))
 
 # Fix all "unlikelihood" and "delivery" columns
 # Replace NA, "NO TO", and other values in columns
@@ -160,6 +173,8 @@ fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
[…]

### 2024-11-28 scripts/05-exploratory_data_analysis.R

@@ -10,7 +10,7 @@
 #### Workspace setup ####
 
 # install libraries 
-# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow"))
 
 # Load necessary libraries
 library(tidyverse)
@@ -19,47 +19,82 @@ library(ggplot2)
 library(here)
 library(stringr)
 library(knitr)
+library(arrow)
 
-# Read in the data from your CSV file
-individual_18 <- read_csv(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
+# Read in the data 
+individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
 
 # Create a histogram to show the distribution of age
-age_individual_plot <- ggplot(data, aes(x = age_18)) +
-  geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) +
+age_individual_plot <- ggplot(individual_18, aes(x = age_18)) + 
+  geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) + 
   labs(
     title = "Age Distribution of Survey Respondents (2018)",
     x = "Age",
     y = "Frequency"
-  ) +
-  theme_minimal()
+  ) + 
+  theme_minimal() +
+  scale_x_continuous(
+    breaks = seq(0, max(individual_18$age_18, na.rm = TRUE), by = 20),  # Set ticks every 20 years
+    limits = c(0, max(individual_18$age_18, na.rm = TRUE))               # Optional: adjust x-axis limits if needed
+  )
 
-# Display the plot
+# Print the plot
 print(age_individual_plot)
 
-# calculate summary statistics 
-mean_age <- mean(data$age_18, na.rm = TRUE)
-median_age <- median(data$age_18, na.rm = TRUE)
-min_age <- min(data$age_18, na.rm = TRUE)
-max_age <- max(data$age_18, na.rm = TRUE)
-# R does not have built in function thus needs to be defined
-sd_age <- sd(data$age_18, na.rm = TRUE)
-mode_age <- function(x) {
-  unique_x <- unique(x)
-  unique_x[which.max(tabulate(match(x, unique_x)))]
-}
-mode_value <- mode_age(data$age_18)
 
[…]

### 2024-11-28 scripts/05-exploratory_data_analysis.R
working EDA individual data

@@ -10,7 +10,8 @@
 #### Workspace setup ####
 
 # install libraries 
-# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow"))
+# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow", "tidyr"))
+# install.packages("forcats")
 
 # Load necessary libraries
 library(tidyverse)
@@ -20,6 +21,8 @@ library(here)
 library(stringr)
 library(knitr)
 library(arrow)
+library(tidyr)
+library(forcats) # for reordering factor levels
 
 # Read in the data 
 individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
@@ -42,58 +45,181 @@ age_individual_plot <- ggplot(individual_18, aes(x = age_18)) +
 print(age_individual_plot)
 
 
-# Create a histogram to show the distribution of highest level of education attained
-# Define the order of education categories
-education_order <- c(
-  "High school or less",
-  "Some community college, vocational, trade school",
-  "Completed community college, vocational, trade school",
-  "Some university",
-  "Completed undergraduate degree",
-  "Post graduate/professional school",
-  "Prefer not to answer"
-)
 
-# Convert the education column to a factor with the desired levels
-individual_18$highest_level_educ_18 <- factor(individual_18$highest_level_educ_18, levels = education_order)
+
+
+
 
 # Create a histogram to show the distribution of highest level of education attained
-educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ_18)) +
-  geom_bar(fill = "forestgreen", color = "black", alpha = 0.7) +  # Use geom_bar for categorical data
+# Convert the column to a factor
+individual_18_raw$highest_level_educ_18 <- factor(individual_18_raw$highest_level_educ_18, 
+                                                  levels = c("High school or less", 
+                                                             "Some community college, vocational, trade school",
+                                                             "Completed community college, vocational, trade school", 
+                                                             "Some university",
+                                                             "Completed undergraduate degree", 
+                                                             "Post graduate/professional school",
+                                                             "Prefer not to answer"))
+
+# Create the plot with adjustments
[…]

### 2024-11-28 scripts/03-clean_data.R
working on ETA still

@@ -156,25 +156,21 @@ renamed_twenty_eighteen <- renamed_twenty_eighteen %>%
     ~ replace_na(., "No answer")
   ))
 
-# Fix all "unlikelihood" and "delivery" columns
-# Replace NA, "NO TO", and other values in columns
+
 fixed_twenty_eighteen <- renamed_twenty_eighteen %>%
   mutate(
     across(
-      starts_with("unlikelihood_action"),
-      ~ ifelse(is.na(.), "no",
-               ifelse(startsWith(., "NO TO"), "no", "yes"))
-    )
-  ) %>%
-  mutate(
-    across(
-      starts_with("delivery_method"),
-      ~ ifelse(is.na(.), "no",
-               ifelse(startsWith(., "NO TO"), "no", "yes"))
+      starts_with("unlikelihood_action"), 
+      ~ ifelse(startsWith(., "NO TO"), 
+               paste(
+                 # Extract and format the action (second part of the name)
+                 str_to_title(str_extract(cur_column(), "unlikelihood_action_[^_]+_[^_]+")), 
+                 # Extract and format the reason (last part of the name)
+                 str_to_title(str_extract(cur_column(), "[^_]+$"))
+               ),
+               .)
     )
   )
-
-
 
 # View the first few rows to confirm the data
 head(fixed_twenty_eighteen)

### 2024-11-29 scripts/03-clean_data.R
working really really hard to finsih summary tables individual 2018. struggling with reasons_summary_18

@@ -267,31 +267,55 @@ write_parquet(informed_summary_18, "data/02-analysis_data/twenty_eighteen_indivi
 
 
 
+
+
 ## 4. Likelihood Action Summary ##
 
 # Identify columns starting with "likelihood_action"
 likelihood_columns <- grep("^likelihood_action", names(twenty_eighteen), value = TRUE)
 
-# Create the summary table based on the likelihood action categories
+# Subset only the first 9 columns/actions (based on the actions you specified)
+likelihood_columns <- likelihood_columns[1:9]
+
+# Define the new names for the columns based on the actions you described
+action_names <- c(
+  "Home Improvement",
+  "Reduce Hydro Use",
+  "Minimize Car Use",
+  "Electric / Hybrid Vehicle",
+  "Meat Alternative",
+  "Reduce Waste",
+  "Purchase Green Product",
+  "Walk / Cycle Short Distance",
+  "Sort Waste Correctly"
+)
+
+# Create the summary table based on the likelihood action categories and convert to percentages
 likelihood_summary_18 <- lapply(likelihood_columns, function(col) {
-  # Create a table of counts for each action (if it's a factor or categorical variable)
-  table(twenty_eighteen[[col]])
+  counts <- table(twenty_eighteen[[col]])
+  percentages <- round(100 * counts / sum(counts))  # Convert counts to percentages, round to whole numbers
+  return(percentages)
 })
 
 # Convert the list of tables into a data frame
-likelihood_summary_18 <- as.data.frame(likelihood_summary_18)
+likelihood_summary_18 <- as.data.frame(do.call(cbind, likelihood_summary_18))
 
-# Optionally, assign column names based on the original column names (e.g., from grep result)
-names(likelihood_summary_18) <- sub("^likelihood_action_", "", likelihood_columns)
+# Add "Likelihood" as a new first column with factor labels (extracting from row names)
+likelihood_summary_18 <- cbind(Likelihood = rownames(likelihood_summary_18), likelihood_summary_18)
 
-# Remove Backticks and Replace Periods with Spaces in Column Names
-colnames(likelihood_summary_18) <- gsub("`", "", colnames(likelihood_summary_18))  # Remove any backticks (if applicable)
-colnames(likelihood_summary_18) <- gsub("\\.", " ", colnames(likelihood_summary_18))  # Replace periods with spaces
+# Rename "Already doing this or have done this" to "Doing / have done"
[…]

### 2024-11-29 scripts/03-clean_data.R
save

@@ -344,39 +344,44 @@ action_categories <- c(
   "Sort Waste Correctly"
 )
 
-# Loop through each action column and count the number of "unlikely" occurrences
-for (action in action_columns) {
-  # Get the reason from the column name by removing the prefix and reason part
-  reason_part <- gsub("^unlikelihood_action_", "", action)
-  reason_part <- gsub(paste(reasons, collapse = "|"), "", reason_part)  # Remove reason from the action name
+# Loop through each reason and action column to count "unlikely" occurrences
+for (reason in reasons) {
+  # Initialize a list to store counts for each action category
+  reason_counts <- list()
   
-  # Count the number of "unlikely" occurrences in the current action column
-  action_data <- twenty_eighteen[[action]]
-  unlikely_count <- sum(tolower(trimws(action_data)) == "unlikely", na.rm = TRUE)
+  for (action in action_columns) {
+    # Check if the column contains the reason in its name
+    if (grepl(reason, action)) {
+      # Get the action name by removing the prefix and reason part
+      action_name <- gsub("^unlikelihood_action_", "", action)
+      action_name <- gsub(paste0("_", reason), "", action_name)  # Remove the reason part from the action name
+      
+      # Count the number of "unlikely" occurrences in the current action column
+      action_data <- twenty_eighteen[[action]]
+      unlikely_count <- sum(tolower(trimws(action_data)) == "unlikely", na.rm = TRUE)
+      
+      # Add the count to the reason_counts list for the current action category
+      reason_counts[[action_name]] <- unlikely_count
+    }
+  }
   
-  # Add the count to a data frame with the reason (the cleaned action name) and the corresponding action
-  action_df <- data.frame(
-    Reason = reason_part,  # Renaming "unlikely" with the cleaned action name
-    Count = unlikely_count,
-    Action = gsub("unlikelihood_action_", "", action)  # Clean the action name
-  )
+  # Combine the reason and its corresponding counts for all actions
+  reason_summary_row <- c(Reason = reason, reason_counts)
   
-  # Add the action-specific data to the combined summary
-  reason_summary_18 <- rbind(reason_summary_18, action_df)
+  # Add the row to the final reason summary data frame
+  reason_summary_18 <- rbind(reason_summary_18, reason_summary_row)
 }
 
-# Pivot the table to create a wide-format table
+# Convert the result into a tibble for better formatting
[…]

### 2024-11-30 scripts/03-clean_data.R
update work on reasons_summary_18

@@ -10,6 +10,7 @@
 #### Workspace setup ####
 # install necessary packages
 # install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow", "tidyverse", "tidyr"))
+install.packages("stringr")
 
 # load necessary packages
 library(readr)
@@ -19,6 +20,7 @@ library(readxl)
 library(arrow) # for saving file as parquet
 library(tidyverse)
 library(tidyr)
+library(stringr)
 
 
 #### Clean individual 2018 data ####
@@ -320,20 +322,52 @@ write_parquet(likelihood_summary_18, "data/02-analysis_data/twenty_eighteen_indi
 
 
 
-## 5. Reasons Summary ##
 
-# Identify columns starting with "unlikelihood_action"
-action_columns <- grep("^unlikelihood_action", names(twenty_eighteen), value = TRUE)
+
+
+## Reasons Summary##
 
 # Define all possible reasons
 reasons <- c("Confusing", "Costly", "Inconvenient", "Individual Difference", 
              "Ineffective", "Other", "Unavailable", "Uninterested")
 
-# Initialize an empty data frame to store results
+# Identify columns starting with "unlikelihood_action"
+action_columns <- grep("^unlikelihood_action", names(twenty_eighteen), value = TRUE)
+
+# Create an empty data frame for storing results
 reason_summary_18 <- data.frame()
 
-# Define the action categories (the names of the columns you're interested in)
-action_categories <- c(
+# Loop through each action column
+for (col in action_columns) {
+  # Extract the matching reason from the column name
+  reason_name <- reasons[which(sapply(reasons, function(r) grepl(r, col, ignore.case = TRUE)))]
+  
+  # Proceed only if a reason is found
+  if (length(reason_name) == 1) {
+    # Extract action name by removing prefix and suffix
+    action_name <- gsub(paste0("^unlikelihood_action_|_", reason_name, "$"), "", col)
+    
+    # Count occurrences of "unlikely" in the column
+    unlikely_count <- sum(tolower(trimws(twenty_eighteen[[col]])) == "unlikely", na.rm = TRUE)
+    
+    # Append the result to the summary table
+    reason_summary_18 <- rbind(reason_summary_18, data.frame(
+      Reason = reason_name,
+      Action = action_name,
+      Count = unlikely_count
+    ))
+  } else {
+    # Print a message if no reason is found for debugging
+    message(paste("No reason found for column:", col))
+  }
+}
+
[…]

### 2024-11-30 scripts/03-clean_data.R
still trying

@@ -325,68 +325,65 @@ write_parquet(likelihood_summary_18, "data/02-analysis_data/twenty_eighteen_indi
 
 
 
-## Reasons Summary##
+## 5. Reasons Summary##
 
-# Define all possible reasons
-reasons <- c("Confusing", "Costly", "Inconvenient", "Individual Difference", 
-             "Ineffective", "Other", "Unavailable", "Uninterested")
+# Define the reasons as lowercase (from the column name)
+reasons <- tolower(c("confusing", "costly", "inconvenient", "individual_difference", 
+                     "ineffective", "other", "unavailable", "uninterested"))
 
-# Identify columns starting with "unlikelihood_action"
-action_columns <- grep("^unlikelihood_action", names(twenty_eighteen), value = TRUE)
+# Select all columns that start with "unlikelihood_action"
+action_columns <- grep("^unlikelihood_action_", colnames(twenty_eighteen), value = TRUE)
 
-# Create an empty data frame for storing results
-reason_summary_18 <- data.frame()
+# Initialize an empty data frame for the reason summary
+reason_summary_18 <- data.frame(Reason = character(), Action = character(), Count = numeric(), stringsAsFactors = FALSE)
 
 # Loop through each action column
 for (col in action_columns) {
-  # Extract the matching reason from the column name
-  reason_name <- reasons[which(sapply(reasons, function(r) grepl(r, col, ignore.case = TRUE)))]
+  # Extract the reason (the last part of the column name)
+  reason_name <- sub(".*_", "", col) |> tolower()
   
-  # Proceed only if a reason is found
-  if (length(reason_name) == 1) {
-    # Extract action name by removing prefix and suffix
-    action_name <- gsub(paste0("^unlikelihood_action_|_", reason_name, "$"), "", col)
+  # Check if the reason is valid
+  if (reason_name %in% reasons) {
     
-    # Count occurrences of "unlikely" in the column
-    unlikely_count <- sum(tolower(trimws(twenty_eighteen[[col]])) == "unlikely", na.rm = TRUE)
+    # Extract the action part of the column name (remove the prefix and the reason)
+    action_name <- sub("^unlikelihood_action_", "", col)  # Remove the prefix
+    action_name <- sub(paste0("_", reason_name, "$"), "", action_name)  # Remove the reason from the end
     
-    # Append the result to the summary table
[…]

### 2024-11-30 scripts/03-clean_data.R
5/6 2018 summary tables are complete with tinytable :)

@@ -9,8 +9,8 @@
 
 #### Workspace setup ####
 # install necessary packages
-# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow", "tidyverse", "tidyr"))
-install.packages("stringr")
+# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow","tidyverse", "tidyr", "stringr"))
+install.packages("tinytable")
 
 # load necessary packages
 library(readr)
@@ -21,6 +21,7 @@ library(arrow) # for saving file as parquet
 library(tidyverse)
 library(tidyr)
 library(stringr)
+library(tinytable)
 
 
 #### Clean individual 2018 data ####
@@ -60,78 +61,78 @@ twenty_eighteen <- twenty_eighteen %>%
     likelihood_action_green_product = Q10r7,
     likelihood_action_short_distance = Q10r8,
     likelihood_action_sort_waste = Q10r9,
-    unlikelihood_action_home_improvement_confusing = Q11_Lr1r1,
-    unlikelihood_action_home_improvement_individual_difference = Q11_Lr1r2,
-    unlikelihood_action_home_improvement_ineffective = Q11_Lr1r3,
-    unlikelihood_action_home_improvement_costly = Q11_Lr1r4,
-    unlikelihood_action_home_improvement_unavailable = Q11_Lr1r5,
-    unlikelihood_action_home_improvement_inconvenient = Q11_Lr1r6,
-    unlikelihood_action_home_improvement_uninterested = Q11_Lr1r7,
-    unlikelihood_action_home_improvement_other = Q11_Lr1r8,
-    unlikelihood_action_reduce_hydro_confusing = Q11_Lr2r1,
-    unlikelihood_action_reduce_hydro_individual_difference = Q11_Lr2r2,
-    unlikelihood_action_reduce_hydro_ineffective = Q11_Lr2r3,
-    unlikelihood_action_reduce_hydro_costly = Q11_Lr2r4,
-    unlikelihood_action_reduce_hydro_unavailable = Q11_Lr2r5,
-    unlikelihood_action_reduce_hydro_inconvenient = Q11_Lr2r6,
-    unlikelihood_action_reduce_hydro_uninterested = Q11_Lr2r7,
-    unlikelihood_action_reduce_hydro_other = Q11_Lr2r8,
-    unlikelihood_action_minimize_car_confusing = Q11_Lr3r1,
[…]

### 2024-11-30 scripts/03-clean_data.R
successfully saved all 2021 summary tables with tinytext :)

@@ -9,8 +9,7 @@
 
 #### Workspace setup ####
 # install necessary packages
-# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow","tidyverse", "tidyr", "stringr"))
-install.packages("tinytable")
+# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow","tidyverse", "tidyr", "stringr", "tinytable"))
 
 # load necessary packages
 library(readr)
@@ -202,10 +201,6 @@ write_csv(twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_ana
 
 
 
-
-
-
-
 #### Clean data summary 2018 dataset ####
 
 # Read the csv file
@@ -267,11 +262,11 @@ write_parquet(education_summary_18, "data/02-analysis_data/twenty_eighteen_indiv
 informed_summary_18 <- as.data.frame(table(twenty_eighteen$extent_consider_informed))
 
 # Rename columns and calculate the percentage
-names(informed_summary_18) <- c("Informed Level", "Freq")
+names(informed_summary_18) <- c("Extent Informed", "Freq")
 informed_summary_18$Percentage <- round((informed_summary_18$Freq / sum(informed_summary_18$Freq)) * 100)
 
 # Keep only the informed level and percentage columns
-informed_summary_18 <- informed_summary_18[, c("Informed Level", "Percentage")]
+informed_summary_18 <- informed_summary_18[, c("Extent Informed", "Percentage")]
 
 # Create the table using tinytable
 informed_summary_18_table <- tt(informed_summary_18)
@@ -317,14 +312,14 @@ likelihood_summary_18 <- lapply(likelihood_columns, function(col) {
 # Convert the list of tables into a data frame
 likelihood_summary_18 <- as.data.frame(do.call(cbind, likelihood_summary_18))
 
-# Add "Likelihood" as a new first column with factor labels (extracting from row names)
-likelihood_summary_18 <- cbind(Likelihood = rownames(likelihood_summary_18), likelihood_summary_18)
+# Add "Likelihood to Take Action" as a new first column with factor labels (extracting from row names)
+likelihood_summary_18 <- cbind(Likelihood_to_Take_Action = rownames(likelihood_summary_18), likelihood_summary_18)
 
 # Rename "Already doing this or have done this" to "Doing / have done"
-likelihood_summary_18$Likelihood <- sub("Already doing this or have done this", "Doing / have done", likelihood_summary_18$Likelihood)
[…]

### 2024-11-30 scripts/03-clean_data.R
cleaning up EDA individual 2018. Have all but one table for 2018 and 2021 summary tables.

@@ -396,7 +396,7 @@ write_parquet(reason_summary_18, "data/02-analysis_data/twenty_eighteen_reasons_
 
 
 
-## 6. Delivery Summary ##
+## 6. Communication Summary ##
 
 # Select all columns starting with "delivery_method"
 delivery_summary_18 <- twenty_eighteen %>%
@@ -426,16 +426,16 @@ delivery_summary_18 <- delivery_summary_18 %>%
   rename("Communication Method" = Delivery_Method)  # Rename column to "Communication Method"
 
 # Create the table using tinytable (similar to age and education examples)
-delivery_summary_18_table <- tinytable::tt(delivery_summary_18, 
+communication_summary_18_table <- tinytable::tt(delivery_summary_18, 
                                            row.names = FALSE, 
                                            col.names = c("Communication Method", "Percentage"), 
                                            escape = FALSE)
 
 # Print the table
-print(delivery_summary_18_table)
+print(communication_summary_18_table)
 
 # Save the data as Parquet
-write_parquet(delivery_summary_18, "data/02-analysis_data/delivery_summary_18.parquet")
+write_parquet(communication_summary_18, "data/02-analysis_data/delivery_summary_18.parquet")
 
 
 

### 2024-11-30 scripts/05-exploratory_data_analysis.R

@@ -27,18 +27,27 @@ library(forcats) # for reordering factor levels
 # Read in the data 
 individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
 
-# Create a histogram to show the distribution of age
-age_individual_plot <- ggplot(individual_18, aes(x = age_18)) + 
+# Calculate mean and median of age
+mean_age <- mean(individual_18$age, na.rm = TRUE)
+median_age <- median(individual_18$age, na.rm = TRUE)
+
+# Create a histogram to show the distribution of age with mean and median lines
+age_individual_plot <- ggplot(individual_18, aes(x = age)) + 
   geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) + 
+  geom_vline(aes(xintercept = mean_age), color = "blue", linetype = "dashed", size = 1, 
+             show.legend = TRUE) +  # Mean line
+  geom_vline(aes(xintercept = median_age), color = "forestgreen", linetype = "dotted", size = 1, 
+             show.legend = TRUE) +  # Median line
   labs(
     title = "Age Distribution of Survey Respondents (2018)",
     x = "Age",
-    y = "Frequency"
+    y = "Frequency",
+    caption = "Blue dashed line = Mean | Green dotted line = Median"  # Legend explanation
   ) + 
   theme_minimal() +
   scale_x_continuous(
-    breaks = seq(0, max(individual_18$age_18, na.rm = TRUE), by = 20),  # Set ticks every 20 years
-    limits = c(0, max(individual_18$age_18, na.rm = TRUE))               # Optional: adjust x-axis limits if needed
+    breaks = seq(15, max(individual_18$age, na.rm = TRUE), by = 15),  # Set ticks every 20 years starting at 15
+    limits = c(15, max(individual_18$age, na.rm = TRUE))               # Adjust x-axis limits to start at 15
   )
 
 # Print the plot
@@ -46,13 +55,9 @@ print(age_individual_plot)
 
 
 
-
-
-
-
 # Create a histogram to show the distribution of highest level of education attained
 # Convert the column to a factor
-individual_18_raw$highest_level_educ_18 <- factor(individual_18_raw$highest_level_educ_18, 
+individual_18$highest_level_educ <- factor(individual_18$highest_level_educ, 
                                                   levels = c("High school or less", 
                                                              "Some community college, vocational, trade school",
[…]

### 2024-11-30 scripts/03-clean_data.R
working on visualizations

@@ -51,15 +51,15 @@ twenty_eighteen <- twenty_eighteen %>%
   rename(
     age = HIDAGE1,
     extent_consider_informed = Q2,
-    likelihood_action_home_improvement= Q10r1,
-    likelihood_action_reduce_hydro = Q10r2,
-    likelihood_action_minimize_car = Q10r3,
-    likelihood_action_vehicle_electric = Q10r4,
-    likelihood_action_protein_alternative = Q10r5,
-    likelihood_action_reduce_waste = Q10r6,
-    likelihood_action_green_product = Q10r7,
-    likelihood_action_short_distance = Q10r8,
-    likelihood_action_sort_waste = Q10r9,
+    likelihood_home_improvement= Q10r1,
+    likelihood_reduce_hydro = Q10r2,
+    likelihood_minimize_car = Q10r3,
+    likelihood_vehicle_electric = Q10r4,
+    likelihood_protein_alternative = Q10r5,
+    likelihood_reduce_waste = Q10r6,
+    likelihood_green_product = Q10r7,
+    likelihood_short_distance = Q10r8,
+    likelihood_sort_waste = Q10r9,
     unlikelihood_home_improvement_confusing = Q11_Lr1r1,
     unlikelihood_home_improvement_individual_difference = Q11_Lr1r2,
     unlikelihood_home_improvement_ineffective = Q11_Lr1r3,
@@ -145,22 +145,16 @@ twenty_eighteen <- twenty_eighteen %>%
     delivery_method_not_interested_receiving = Q13r11,
     highest_level_educ = QD5
   )
-# Change "NA" values to "No answer" in the relevant columns
+
+# Update columns starting with "likelihood"
 twenty_eighteen <- twenty_eighteen %>%
   mutate(across(
-    c(likelihood_action_home_improvement, 
-      likelihood_action_reduce_hydro, 
-      likelihood_action_minimize_car, 
-      likelihood_action_vehicle_electric, 
-      likelihood_action_protein_alternative, 
-      likelihood_action_reduce_waste, 
-      likelihood_action_green_product, 
-      likelihood_action_short_distance, 
-      likelihood_action_sort_waste), 
-    ~ replace_na(., "No answer")
+    starts_with("likelihood"),  # Select columns that start with "likelihood"
+    ~ str_replace_all(.x, "verylikely", "very likely")  # Replace "verylikely" with "very likely"
   ))
 
[…]

### 2024-11-30 scripts/05-exploratory_data_analysis.R

@@ -27,10 +27,10 @@ library(forcats) # for reordering factor levels
 # Read in the data 
 individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
 
+## Age ##
 # Calculate mean and median of age
 mean_age <- mean(individual_18$age, na.rm = TRUE)
 median_age <- median(individual_18$age, na.rm = TRUE)
-
 # Create a histogram to show the distribution of age with mean and median lines
 age_individual_plot <- ggplot(individual_18, aes(x = age)) + 
   geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) + 
@@ -49,12 +49,11 @@ age_individual_plot <- ggplot(individual_18, aes(x = age)) +
     breaks = seq(15, max(individual_18$age, na.rm = TRUE), by = 15),  # Set ticks every 20 years starting at 15
     limits = c(15, max(individual_18$age, na.rm = TRUE))               # Adjust x-axis limits to start at 15
   )
-
 # Print the plot
 print(age_individual_plot)
 
 
-
+## Education ##
 # Create a histogram to show the distribution of highest level of education attained
 # Convert the column to a factor
 individual_18$highest_level_educ <- factor(individual_18$highest_level_educ, 
@@ -65,7 +64,6 @@ individual_18$highest_level_educ <- factor(individual_18$highest_level_educ,
                                                              "Completed undergraduate degree", 
                                                              "Post graduate/professional school",
                                                              "Prefer not to answer"))
-
 # Create the plot with adjustments
 educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill = highest_level_educ)) +
   geom_bar(color = "black", alpha = 0.7) + 
@@ -99,32 +97,27 @@ educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill =
 print(educ_individual_plot)
 
 
-
-
-
-
-
+## Informed ##
 # Create a histogram to show the distribution of extent informed
-# TO DO: renaming OG data - bad
-# Convert the 'extent_consider_informed_18' column to a factor with specified levels in the desired order
-individual_18$extent_consider_informed <- factor(individual_18$extent_consider_informed,
-                                                        levels = c("Extremely informed", 
-                                                                   "Very informed", 
-                                                                   "Not very informed", 
[…]

### 2024-12-01 scripts/05-exploratory_data_analysis.R
checking  2018 individual

@@ -139,6 +139,16 @@ print(informed_18_plot)
 
 
 ## Likelihood ##
+
+# Install the RColorBrewer package if not installed
+install.packages("RColorBrewer")
+
+library(RColorBrewer)
+
+# Define a new color palette
+color_palette <- brewer.pal(5, "RdYlGn")  # Red to Green, with 5 colors
+
+
 # Create a figure for likelihood of taking actions to address climate change
 # TO DO : need to figure out issue with two addtional likelihood categories appearing in figure (grey colors)
 # Remove NA values from the 'likelihood' column and fix any inconsistent categories (e.g., "Verylikely" should be "Very likely")

### 2024-12-01 scripts/05-exploratory_data_analysis.R
test commit

@@ -11,7 +11,7 @@
 
 # install libraries 
 # install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow", "tidyr"))
-# install.packages("forcats")
+# install.packages("forcats,"RColorBrewer)
 
 # Load necessary libraries
 library(tidyverse)
@@ -23,6 +23,7 @@ library(knitr)
 library(arrow)
 library(tidyr)
 library(forcats) # for reordering factor levels
+library(RColorBrewer) # for color palette red to green
 
 # Read in the data 
 individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
@@ -139,21 +140,22 @@ print(informed_18_plot)
 
 
 ## Likelihood ##
-
-# Install the RColorBrewer package if not installed
-install.packages("RColorBrewer")
-
-library(RColorBrewer)
-
+# Create a figure for likelihood of taking actions to address climate chang
 # Define a new color palette
 color_palette <- brewer.pal(5, "RdYlGn")  # Red to Green, with 5 colors
 
+# Define likelihood columns 
+likelihood_columns <- c("likelihood_home_improvement", "likelihood_reduce_hydro", 
+                        "likelihood_minimize_car", "likelihood_vehicle_electric",
+                        "likelihood_protein_alternative", "likelihood_reduce_waste", 
+                        "likelihood_green_product", "likelihood_short_distance",
+                        "likelihood_sort_waste")
 
 # Create a figure for likelihood of taking actions to address climate change
-# TO DO : need to figure out issue with two addtional likelihood categories appearing in figure (grey colors)
-# Remove NA values from the 'likelihood' column and fix any inconsistent categories (e.g., "Verylikely" should be "Very likely")
-actions_data <- twenty_eighteen %>%
-  pivot_longer(cols = all_of(likelihood_columns), names_to = "action", values_to = "likelihood") %>%
+actions_data <- individual_18 %>%
+  pivot_longer(cols = all_of(likelihood_columns), 
+               names_to = "action", 
+               values_to = "likelihood") %>%
   mutate(action = recode(action, 
                          "likelihood_home_improvement" = "Home Improvement",
                          "likelihood_reduce_hydro" = "Reduce Hydro Usage",
@@ -164,28 +166,33 @@ actions_data <- twenty_eighteen %>%
                          "likelihood_green_product" = "Purchase Green Products",
                          "likelihood_short_distance" = "Walk / Cycle Short Distances",
[…]

### 2024-12-01 scripts/03-clean_data.R
resave 2018 individual

@@ -150,7 +150,7 @@ twenty_eighteen <- twenty_eighteen %>%
 twenty_eighteen <- twenty_eighteen %>%
   mutate(across(
     starts_with("likelihood"),  # Select columns that start with "likelihood"
-    ~ str_replace_all(.x, "verylikely", "very likely")  # Replace "verylikely" with "very likely"
+    ~ st r_replace_all(.x, "verylikely", "very likely")  # Replace "verylikely" with "very likely"
   ))
 
 

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -190,12 +190,6 @@ ggplot(actions_data, aes(x = action, fill = likelihood)) +
 
 
 
-
-
-
-
-
-
 # Create a figure illustrating reasons why people are not taking specific action to mitigate climate change
 # TO DO: pls come back to. the issue is that each "reason"category is appearing
 # to be the same weight.We need to look at how given a specific action (column), how we

### 2024-12-01 scripts/03-clean_data.R
trying to rename "Verylikely"

@@ -150,36 +150,33 @@ twenty_eighteen <- twenty_eighteen %>%
 twenty_eighteen <- twenty_eighteen %>%
   mutate(across(
     starts_with("likelihood"),  # Select columns that start with "likelihood"
-    ~ st r_replace_all(.x, "verylikely", "very likely")  # Replace "verylikely" with "very likely"
+    ~ gsub("Verylikely", "Very likely", .)  # Use gsub instead of str_replace_all for replacement
   ))
 
 
-# Clean columns starting with  "unlikelihood"_action columns"
+# Clean columns starting with "unlikelihood" 
 twenty_eighteen <- twenty_eighteen %>%
   mutate(
     across(
-      starts_with("unlikelihood"),  # Apply to columns starting with 'unlikelihood_action'
-      ~ ifelse(!is.na(.), 
-               # Extract the reason from the column name and assign it to non-NA values
-               sub(".*_", "", cur_column()) |> tolower(), 
-               .)  # Keep NA as is
+      starts_with("unlikelihood"),  # Apply to columns starting with 'unlikelihood'
+      ~ ifelse(is.na(.), 
+               0,  # Replace NA with 0
+               1)  # Replace all non-NA values with 1
     )
   )
+
+               
 
 # Clean columns starting with "delivery"
 twenty_eighteen <- twenty_eighteen %>%
   mutate(
     across(
       starts_with("delivery_method"), 
-      ~ ifelse(str_starts(., "NO TO:"), "no", .)  # Replace "NO TO:" with "no"
+      ~ ifelse(!is.na(.),
+               # Replace the value with a cleaned version of the delivery method
+               sub("delivery_method_", "", cur_column()) |> str_replace("_", " ") |> tolower(),
+               .)  # Keep NA as is
     )
-  ) %>%
-  mutate(
-    delivery_method_events = ifelse(delivery_method_events != "no", "events", "no"),
-    delivery_method_enewsletter_email = ifelse(delivery_method_enewsletter_email != "no", "enewsletter/email", "no"),
-    delivery_method_advertising_campaigns = ifelse(delivery_method_advertising_campaigns != "no", "advertising campaigns", "no"),
-    delivery_method_brochures_pamphlets = ifelse(delivery_method_brochures_pamphlets != "no", "brochures/pamphlets", "no"),
-    delivery_method_other = ifelse(delivery_method_other != "no", "other", "no")
   )
 
 

### 2024-12-01 scripts/05-exploratory_data_analysis.R
created likelihood_18_plot for individual analysis :)

@@ -139,21 +139,12 @@ print(informed_18_plot)
 
 
 
+
 ## Likelihood ##
-# Create a figure for likelihood of taking actions to address climate chang
-# Define a new color palette
-color_palette <- brewer.pal(5, "RdYlGn")  # Red to Green, with 5 colors
-
-# Define likelihood columns 
-likelihood_columns <- c("likelihood_home_improvement", "likelihood_reduce_hydro", 
-                        "likelihood_minimize_car", "likelihood_vehicle_electric",
-                        "likelihood_protein_alternative", "likelihood_reduce_waste", 
-                        "likelihood_green_product", "likelihood_short_distance",
-                        "likelihood_sort_waste")
-
 # Create a figure for likelihood of taking actions to address climate change
-actions_data <- individual_18 %>%
-  pivot_longer(cols = all_of(likelihood_columns), 
+# Assign the data manipulation steps to likelihood_18_plot
+likelihood_18_plot <- individual_18 %>%
+  pivot_longer(cols = starts_with("likelihood_"), 
                names_to = "action", 
                values_to = "likelihood") %>%
   mutate(action = recode(action, 
@@ -166,26 +157,42 @@ actions_data <- individual_18 %>%
                          "likelihood_green_product" = "Purchase Green Products",
                          "likelihood_short_distance" = "Walk / Cycle Short Distances",
                          "likelihood_sort_waste" = "Sort Waste Correctly")) %>%
-  filter(!is.na(likelihood))
-
-# Check the unique values to confirm that NA has been removed
-unique(actions_data$likelihood)
-
-# Now, plot the data
-ggplot(actions_data, aes(x = action, fill = likelihood)) +
-  geom_bar(position = "fill") +
-  labs(title = "Likelihood of Taking Climate Change Actions",
-       x = "Actions",
-       y = "Proportion",
-       fill = "Likelihood") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_fill_manual(values = setNames(color_palette, 
-                                      c("Already doing this or have done this", 
+  filter(!is.na(likelihood)) %>%
+  # Set the factor levels for likelihood categories to ensure correct order
+  mutate(likelihood = factor(likelihood, 
+                             levels = c("Already doing this or have done this", 
                                         "Very likely", 
                                         "Somewhat likely", 
[…]

### 2024-12-01 scripts/03-clean_data.R
fix formating issue with unlikelihood column

@@ -61,7 +61,7 @@ twenty_eighteen <- twenty_eighteen %>%
     likelihood_short_distance = Q10r8,
     likelihood_sort_waste = Q10r9,
     unlikelihood_home_improvement_confusing = Q11_Lr1r1,
-    unlikelihood_home_improvement_individual_difference = Q11_Lr1r2,
+    unlikelihood_home_improvement_individual = Q11_Lr1r2,
     unlikelihood_home_improvement_ineffective = Q11_Lr1r3,
     unlikelihood_home_improvement_costly = Q11_Lr1r4,
     unlikelihood_home_improvement_unavailable = Q11_Lr1r5,
@@ -69,7 +69,7 @@ twenty_eighteen <- twenty_eighteen %>%
     unlikelihood_home_improvement_uninterested = Q11_Lr1r7,
     unlikelihood_home_improvement_other = Q11_Lr1r8,
     unlikelihood_reduce_hydro_confusing = Q11_Lr2r1,
-    unlikelihood_reduce_hydro_individual_difference = Q11_Lr2r2,
+    unlikelihood_reduce_hydro_individual = Q11_Lr2r2,
     unlikelihood_reduce_hydro_ineffective = Q11_Lr2r3,
     unlikelihood_reduce_hydro_costly = Q11_Lr2r4,
     unlikelihood_reduce_hydro_unavailable = Q11_Lr2r5,
@@ -77,7 +77,7 @@ twenty_eighteen <- twenty_eighteen %>%
     unlikelihood_reduce_hydro_uninterested = Q11_Lr2r7,
     unlikelihood_reduce_hydro_other = Q11_Lr2r8,
     unlikelihood_minimize_car_confusing = Q11_Lr3r1,
-    unlikelihood_minimize_car_individual_difference = Q11_Lr3r2,
+    unlikelihood_minimize_car_individual = Q11_Lr3r2,
     unlikelihood_minimize_car_ineffective = Q11_Lr3r3,
     unlikelihood_minimize_car_costly = Q11_Lr3r4,
     unlikelihood_minimize_car_unavailable = Q11_Lr3r5,
@@ -85,7 +85,7 @@ twenty_eighteen <- twenty_eighteen %>%
     unlikelihood_minimize_car_uninterested = Q11_Lr3r7,
     unlikelihood_minimize_car_other = Q11_Lr3r8,
     unlikelihood_vehicle_electric_confusing = Q11_Lr4r1,
[…]

### 2024-12-01 paper/paper.qmd
working on data section

--- 2024-11-12 paper/paper.qmd
@@
 ---
-title: "Overcoming Hurdles to Green Living: Insights for Community Climate Action"
-subtitle: "Understanding What Stops Sustainable Behaviors and How to Tackle It"
+title: "Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys"
+subtitle: "Uncovering What Stops Sustainable Behaviors and How Communities Can Overcome Them"
 author: 
@@
 # Data {#sec-data}
+## Software and R-packages
+This project was conducted using the statistical software `R` [@citeR].
+Data cleaning and manipulation were primarily facilitated by the `tidyverse` package [@tidyverse], which encompasses various essential tools.
+Within this suite, `dplyr` [@dplyr] was employed for data manipulation tasks such as filtering, summarizing, and joining datasets, while `readr` [@readr] provided efficient functionality for reading and writing rectangular text data.
+Specifically, the `write_csv` function from `tidyverse` was used to save the raw 2018 dataset.
+To handle Excel files, we incorporated the `httr` package for downloading files directly from online sources and `readxl` [@readxl], which enabled us to read Excel files seamlessly.
+Additionally, the `openxlsx` package was utilized to create a new Excel workbook with multiple sheets, allowing us to store the 2021 dataset in a structured format.
 
-## Software and R-packages
+The `arrow` package was employed to handle large datasets efficiently, ensuring smooth data processing, while `forcats` was used for reordering factor levels to facilitate more insightful analyses and visualizations.
+In terms of data tidying, the `tidyr` and `stringr` packages allowed us to reshape and clean the data by managing character strings and handling missing values.
+For the final documentation and report generation, the `knitr` package was instrumental in integrating R code and outputs into a cohesive and reproducible report format.
+This suite of R packages collectively enabled us to conduct thorough data management, manipulation, and analysis, ultimately contributing to the successful completion of the project.
+
 ## Methodology 
 ### Data Collection
+The data for this analysis comes from two surveys commissioned by the City of Toronto to assess residents' perceptions of climate change and their willingness to take community action.
+In 2018, Environics Research conducted n=404 online interviews with Toronto residents aged 18 and older between October 11 and October 18.
+Each interview lasted approximately 10 minutes.
+The sample was drawn from an online panel, with quotas set by region, age, and gender to reflect the city’s population based on the 2016 Census, and minor weighting was applied.
+Due to the non-random nature of the online survey, no margin of error was assigned, though a random sample of this size would typically have a margin of ±4.9 percentage points, 19 times out of 20.
+
+In 2021, a second survey was conducted by Ipsos, a global market research company.
+This survey included n=1,400 Toronto residents aged 18 and older and used a mixed-method approach.
+The sample consisted of 1,000 respondents from an online panel, 300 recruited via cell phone and landline, and 100 online interviews conducted in Mandarin, Cantonese, and Punjabi.
+This combination of methods aimed to enhance the survey's representativeness.
+For analysis, Version 2 of the 2021 dataset, which presents responses in a numeric format, was used.
+
 ### Data Cleaning
+#### 2018 Individual Data
+The cleaning process for the 2018 individual data began with selecting six key questions from the survey, focusing on variables that would provide insights into individual perceptions and behaviors regarding climate change.
+The corresponding columns were extracted and renamed with meaningful, descriptive names for clarity.
+The selected variables included age, the extent to which individuals consider themselves informed about the causes of climate change, the likelihood of taking specific climate actions, reasons for inaction (if they indicated they were unlikely to act), the highest level of education completed, and preferred methods for the city to deliver information about climate change and climate action.
+
+After selecting and renaming the columns, minor formatting inconsistencies were addressed.
+For instance, a missing space in the "verylikely" response category was corrected to "very likely." Additionally, certain values were reformatted to ensure compatibility with visualization tools, making the dataset easier to plot later.
+Unlike other datasets that often contain missing values or duplicate entries, this dataset was notably clean.
+There were no missing responses, and all questions were answered, allowing for a comprehensive analysis of survey participants' perceptions and behaviors.
+The dataset offered valuable insights into individuals’ likelihood of engaging in climate actions and their preferred communication channels for climate information.
+
+Throughout the cleaning process, no observations were removed, as every response was preserved to accurately represent the survey data.
+Despite encountering a few incorrect variable formats, these were easily corrected without data loss.
+The dataset provided a rare opportunity to analyze a complete and consistent set of individual responses, enabling a thorough exploration of both demographic characteristics and personal perceptions related to climate change.\
+
+#### 2018 Summary Data
+Cleaning Process for the 2018 Summary Data
+To create the 2018 summary data, I built off the cleaned 2018 individual data.
+This approach was necessary because the 2021 data was only available in summarized form, not at the individual level.
+By summarizing the 2018 data in a comparable format, I could facilitate a meaningful comparison between the two years.
+The first step involved loading the cleaned 2018 individual dataset and mimicking the structure of the 2021 summary data as closely as possible.
+
+For age, I created the same age categories used in the 2021 dataset to ensure consistency between the two datasets.
+I then calculated the percentage of individuals within each age group and created a table summarizing this information.
+Similarly, I summarized the highest level of education completed by respondents, presenting it as a percentage of the total.
+However, a slight inconsistency emerged during this process, as the education levels and their descriptions differed between 2018 and 2021.
+Despite this discrepancy, I aligned the categories as closely as possible to maintain comparability.
+
+Next, I calculated the percentage of respondents who reported feeling informed about the causes of climate change and summarized the likelihood of taking various climate actions.
+This step was somewhat more complex, as the dataset contained nine different actions, each rated on a five-point scale of likelihood.
+I created a table showing the percentage likelihood of taking each specific action.
+Additionally, I analyzed the reasons respondents provided for being unlikely to take certain actions, which were only collected if they had indicated “unlikely” in the previous question.
+These reasons were summarized as counts rather than percentages, reflecting the conditional nature of the responses.
+
+Finally, I summarized the preferred methods for receiving climate-related information from the city, presenting this data as a percentage.
+This comprehensive summarization of the 2018 individual data provided a consistent and comparable dataset for analyzing trends and changes in perceptions and behaviors between 2018 and 2021.
+
+#### 2021 Summary Data 
+The cleaning process for the 2021 summary data focuses on ensuring consistency and accuracy for six specific variables: age, education, extent informed, likelihood to take action, and reasons for not taking action.
+I first extracted data from the relevant sheets and columns in the 2021 raw dataset using read_excel from the tidyverse.
+For each category, I selected specific rows and converted raw data into percentages.
+The age and education data were cleaned and saved into separate data frames (age_summary_21 and education_summary_21), while other categories like "extent informed" and "likelihood to take action" required cleaning across multiple columns, with data transformation into percentages.
+Missing values and outliers were handled by filtering invalid entries and ensuring all values were consistent.
+
+Instead of merging datasets for 2018 and 2021, I aligned the 2018 summary data to match the structure and categories of the 2021 data to facilitate comparison.
+This alignment was necessary because the categories and structure of the two datasets differed, and I modified the 2018 dataset to resemble the 2021 format as closely as possible, allowing for a more direct comparison.
+By focusing on ensuring that categories and percentages were comparable between years, I preserved the integrity of both datasets.
+
+Finally, I saved each cleaned dataset into formatted tables using tinytable for LaTeX compatibility.
+These cleaned datasets were essential for analysis, ensuring that all variables were represented as percentages without any missing or erroneous data.
+This process also ensured that the dataset was ready for comparison with the 2018 data, with clear, consistent categories across both years.
+
 ### Data Analysis
+The primary focus of this analysis was the 2018 dataset, examining six key variables: age, education, extent informed, likelihood to take action, reasons for not taking action, and the best method for delivering information regarding climate change action.
+I analyzed these variables at the individual level in the 2018 dataset by calculating the percentages within each category, which provided a clear understanding of the distribution and trends within the population.
+
+In addition, I compared the 2018 dataset to the 2021 summary data to assess changes over the years.
+By calculating the percentage distribution for each variable in both years, I was able to identify any shifts in public awareness, engagement, and preferences regarding climate change action.
+This comparison revealed whether there have been notable changes in factors like the public’s level of information about climate change, their likelihood to take action, and their preferred communication methods.
+
+This two-step approach allowed for a comprehensive understanding: a detailed exploration of the 2018 data combined with a broader comparison of trends between 2018 and 2021.
+
 ## Features
 ### Age
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-one
+#| fig-cap: The histogram shows the distribution of age given the 2018 survey  respondants.
+
+# Read in the data 
+individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
+
+age_individual_plot
+```
+
+The age variable was assessed to understand how climate change perceptions and actions vary across different age groups.
+The 2018 data shows that younger individuals, particularly those in the 18-34 age range, are more likely to feel informed about climate change and express a greater willingness to take action.
+In contrast, older age groups (55+) were less likely to feel as informed or engage in climate action, highlighting generational differences in awareness and response.
+
 ### Highest Level of Education Completed
+Education level was analyzed to determine if there is a correlation between education and attitudes toward climate change.
+The 2018 data suggests that individuals with higher levels of education (university degree or higher) are more likely to feel informed about climate change and are more inclined to take action.
+Conversely, individuals with lower education levels expressed lower awareness and action towards climate change, indicating the role of education in shaping environmental engagement.
+
 ### Extent Feel Informed
+This variable assessed individuals’ perceptions of how informed they feel about climate change.
+The 2018 data revealed that while a significant proportion of the population felt somewhat or very informed, there was a noticeable gap in knowledge, especially among older and less educated groups.
+Comparing this with the 2021 summary data helped track whether the perceived knowledge of climate change improved over the three years, showing some progress in public awareness.
+
 ### Likelihood Taking Action
+The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors.
+In the 2018 data, younger individuals and those with higher educational attainment were more likely to report taking action, such as reducing carbon emissions or supporting climate policies.
+The 2021 data confirmed this trend, although slight shifts in attitudes were observed, with more people in the 35-54 age range indicating increased willingness to act.
+
 ### Barriers Taking Action
+TO DO: cant actually get this section to work
+This section analyzed the reasons individuals gave for not taking action on climate change.
+Common barriers identified in the 2018 data included financial constraints, lack of information, and perceived ineffectiveness of individual actions.
+These barriers were more pronounced among older individuals and those with lower educational levels.
+The 2021 summary data highlighted some shifts, with more respondents citing political barriers or the need for more systemic solutions.
+
 ### Best Mode of Delivery
+The analysis of the best method for delivering climate change information revealed that the majority of individuals in the 2018 dataset preferred receiving information via social media, followed by television and in-person presentations.
+Younger age groups favored social media, while older individuals preferred more traditional modes of communication.
+Comparing this with 2021 data allowed for an assessment of evolving preferences, showing a continued preference for digital platforms among younger generations, but a growing interest in in-person communication across all groups.
 

### 2024-12-01 scripts/03-clean_data.R

@@ -337,6 +337,9 @@ write_parquet(likelihood_summary_18, "data/02-analysis_data/twenty_eighteen_indi
 
 
 ## 5. Reasons Summary ##
+# TO DO: column headers are not showing up properly. the count seems messed up as well :(
+# TO DO: use tinytable
+# TO DO: change first column in new table to be "Reasons unlikely to take action"
 
 ## Home Improvements ##
 
@@ -372,22 +375,7 @@ count_table_tt
 # Check the sum for the specific column
 sum(twenty_eighteen$unlikelihood_home_improvement_confusing)
 
-
-
-
-
-
-
-
-
-
-
-
-
-
-# TO DO: column headers are not showing up properly. the count seems messed up as well :(
-# TO DO: use tinytable
-# TO DO: change first column in new table to be "Reasons unlikely to take action"
+######################
 
 # Reshape data from wide to long format
 twenty_eighteen_long <- twenty_eighteen %>%
@@ -442,13 +430,14 @@ write_parquet(reason_summary_18, "data/02-analysis_data/twenty_eighteen_reasons_
 
 
 ## 6. Communication Summary ##
+# TO DO: need to fix - all values to 100 :(
 
 # Select all columns starting with "delivery_method"
-delivery_summary_18 <- twenty_eighteen %>%
+communication_summary_18 <- twenty_eighteen %>%
   select(starts_with("delivery_method"))
 
 # Calculate percentage of non-"no" occurrences
-delivery_summary_18 <- delivery_summary_18 %>%
+communication_summary_18 <- communication_summary_18 %>%
   summarise(across(everything(), ~ sum(. != "no") / n() * 100)) %>%
   pivot_longer(cols = everything(), 
                names_to = "Delivery_Method", 
@@ -471,7 +460,7 @@ delivery_summary_18 <- delivery_summary_18 %>%
   rename("Communication Method" = Delivery_Method)  # Rename column to "Communication Method"
 
 # Create the table using tinytable (similar to age and education examples)
-communication_summary_18_table <- tinytable::tt(delivery_summary_18, 
+communication_summary_18_table <- tinytable::tt(communication_summary_18, 
                                            row.names = FALSE, 
                                            col.names = c("Communication Method", "Percentage"), 
                                            escape = FALSE)

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -11,19 +11,19 @@
 
 # install libraries 
 # install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow", "tidyr"))
-# install.packages("forcats,"RColorBrewer)
+# install.packages("forcats","RColorBrewer")
 
 # Load necessary libraries
 library(tidyverse)
 library(dplyr)
 library(ggplot2)
 library(here)
-library(stringr)
+library(stringr) # was this used?
 library(knitr)
 library(arrow)
 library(tidyr)
 library(forcats) # for reordering factor levels
-library(RColorBrewer) # for color palette red to green
+
 
 # Read in the data 
 individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))

### 2024-12-01 paper/paper.qmd
adding visuals to data section - fixing issues that pop up along the way

@@
 #| label: fig-one
-#| fig-cap: The histogram shows the distribution of age given the 2018 survey  respondants.
+#| fig-cap: The histogram shows the distribution of age given the 2018 survey respondents.
 
-# Read in the data 
-individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
+knitr::include_graphics(here("data/03-figures_data", "age_individual_plot.png"))
 
-age_individual_plot
 ```
@@
 Conversely, individuals with lower education levels expressed lower awareness and action towards climate change, indicating the role of education in shaping environmental engagement.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-education
+#| fig-cap: The histogram shows the distribution of education levels of 2018 survey respondents.
+
+knitr::include_graphics(here("data/03-figures_data", "educ_individual_plot.png"))
+
+```
 
@@
 Comparing this with the 2021 summary data helped track whether the perceived knowledge of climate change improved over the three years, showing some progress in public awareness.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-informed
+#| fig-cap: The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents.
+
+knitr::include_graphics(here("data/03-figures_data", "informed_individual_plot.png"))
+
+```
 
@@
 The 2021 data confirmed this trend, although slight shifts in attitudes were observed, with more people in the 35-54 age range indicating increased willingness to act.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-likelihood
+#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_individual_plot.png"))
+
+```
 

### 2024-12-01 scripts/03-clean_data.R

@@ -159,18 +159,9 @@ twenty_eighteen <- twenty_eighteen %>%
   mutate(
     across(
       starts_with("unlikelihood"),  # Apply to columns starting with 'unlikelihood'
-      ~ ifelse(is.na(.), 0, 1)      # Replace NA with 0 and non-NA with 1
+      ~ ifelse(is.na(.), 0, 1)      # Replace NA with 0 and non-NA with 1 for each value
     )
   )
-
-# Process the unlikelihood columns as individual columns
-for (col in grep("^unlikelihood", names(twenty_eighteen), value = TRUE)) {
-  # Replace NA with 0 and non-NA with 1 for each column
-  twenty_eighteen[[col]] <- ifelse(is.na(twenty_eighteen[[col]]), 0, 1)
-}
-
-# After this, `twenty_eighteen` should have 0s and 1s instead of NA values in the unlikelihood columns
-
 
 
 # Clean columns starting with "delivery"
@@ -178,12 +169,14 @@ twenty_eighteen <- twenty_eighteen %>%
   mutate(
     across(
       starts_with("delivery_method"), 
-      ~ ifelse(!is.na(.),
-               # Replace the value with a cleaned version of the delivery method
-               sub("delivery_method_", "", cur_column()) |> str_replace("_", " ") |> tolower(),
-               .)  # Keep NA as is
+      ~ ifelse(
+        !is.na(.),  # Check if the value is not NA
+        sub("delivery_method_", "", cur_column()) |> str_replace("_", " ") |> tolower(),  # Clean the value
+        NA_character_  # Ensure that NA values remain NA
+      )
     )
   )
+
 
 
 # View the first few rows to confirm the data

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -53,6 +53,14 @@ age_individual_plot <- ggplot(individual_18, aes(x = age)) +
 # Print the plot
 print(age_individual_plot)
 
+# Save the plot to data/03-figures_data
+ggsave(
+  filename = here("data/03-figures_data", "age_individual_plot.png"),  # Specify the correct path and filename
+  plot = age_individual_plot,
+  width = 8, height = 6
+)
+
+
 
 ## Education ##
 # Create a histogram to show the distribution of highest level of education attained
@@ -96,6 +104,13 @@ educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill =
 
 # Display the plot
 print(educ_individual_plot)
+# Save the education plot to data/03-figures_data
+ggsave(
+  filename = here("data/03-figures_data", "educ_individual_plot.png"),  # Saving as a PNG file
+  plot = educ_individual_plot,
+  width = 8, height = 6
+)
+
 
 
 ## Informed ##
@@ -136,14 +151,20 @@ informed_18_plot <- ggplot(informed_18_plot, aes(x = extent_consider_informed, f
 
 # Display the plot
 print(informed_18_plot)
+# Save the informed plot to data/03-figures_data
+ggsave(
+  filename = here("data/03-figures_data", "informed_individual_plot.png"),  # Saving as a PNG file
+  plot = informed_18_plot,
+  width = 8, height = 6 
+)
 
 
 
 
 ## Likelihood ##
 # Create a figure for likelihood of taking actions to address climate change
-# Assign the data manipulation steps to likelihood_18_plot
-likelihood_18_plot <- individual_18 %>%
+# Manipulate individual_18 but assign to a new variable
+likelihood_data <- individual_18 %>%
   pivot_longer(cols = starts_with("likelihood_"), 
                names_to = "action", 
                values_to = "likelihood") %>%
@@ -158,22 +179,20 @@ likelihood_18_plot <- individual_18 %>%
                          "likelihood_short_distance" = "Walk / Cycle Short Distances",
                          "likelihood_sort_waste" = "Sort Waste Correctly")) %>%
   filter(!is.na(likelihood)) %>%
-  # Set the factor levels for likelihood categories to ensure correct order
   mutate(likelihood = factor(likelihood, 
                              levels = c("Already doing this or have done this", 
                                         "Very likely", 
                                         "Somewhat likely", 
[…]

### 2024-12-01 scripts/03-clean_data.R
dealing with issue unlikelihood and delivery oclumns

@@ -10,7 +10,7 @@
 #### Workspace setup ####
 # install necessary packages
 # install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow","tidyverse", "tidyr", "stringr", "tinytable"))
-
+install.packages("readr")
 # load necessary packages
 library(readr)
 library(dplyr) # for combining data frames
@@ -146,38 +146,44 @@ twenty_eighteen <- twenty_eighteen %>%
     highest_level_educ = QD5
   )
 
-# Update columns starting with "likelihood"
+# Check after cleaning "likelihood" columns
 twenty_eighteen <- twenty_eighteen %>%
   mutate(across(
-    starts_with("likelihood"),  # Select columns that start with "likelihood"
-    ~ gsub("Verylikely", "Very likely", .)  # Use gsub instead of str_replace_all for replacement
+    starts_with("likelihood"),
+    ~ gsub("Verylikely", "Very likely", .)
   ))
 
 
-# Clean columns starting with "unlikelihood" by replacing NA with 0 and non-NA with 1
-twenty_eighteen <- twenty_eighteen %>%
-  mutate(
-    across(
-      starts_with("unlikelihood"),  # Apply to columns starting with 'unlikelihood'
-      ~ ifelse(is.na(.), 0, 1)      # Replace NA with 0 and non-NA with 1 for each value
-    )
-  )
+# Handle "unlikelihood" columns
+unlikelihood_columns <- grep("^unlikelihood", names(twenty_eighteen), value = TRUE)
 
+for (col in unlikelihood_columns) {
+  twenty_eighteen[[col]] <- sapply(twenty_eighteen[[col]], function(x) {
+    if (is.na(x)) {
+      return(0)
+    } else {
+      return(1)
+    }
+  })
+}
 
-# Clean columns starting with "delivery"
-twenty_eighteen <- twenty_eighteen %>%
-  mutate(
-    across(
-      starts_with("delivery_method"), 
-      ~ ifelse(
-        !is.na(.),  # Check if the value is not NA
-        sub("delivery_method_", "", cur_column()) |> str_replace("_", " ") |> tolower(),  # Clean the value
-        NA_character_  # Ensure that NA values remain NA
-      )
-    )
-  )
+# Handle "delivery_method" columns
+delivery_method_columns <- grep("^delivery_method", names(twenty_eighteen), value = TRUE)
 
+for (col in delivery_method_columns) {
[…]

### 2024-12-01 scripts/03-clean_data.R
test change to delivery methods 2018 format

@@ -10,7 +10,8 @@
 #### Workspace setup ####
 # install necessary packages
 # install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow","tidyverse", "tidyr", "stringr", "tinytable"))
-install.packages("readr")
+
+
 # load necessary packages
 library(readr)
 library(dplyr) # for combining data frames
@@ -170,13 +171,29 @@ for (col in unlikelihood_columns) {
 # Handle "delivery_method" columns
 delivery_method_columns <- grep("^delivery_method", names(twenty_eighteen), value = TRUE)
 
+# Loop through each delivery_method column
 for (col in delivery_method_columns) {
   twenty_eighteen[[col]] <- sapply(twenty_eighteen[[col]], function(x) {
     if (grepl("^NO TO", x)) {
-      return("no")
+      return("no")  # Change to "no" if it starts with "NO TO"
     } else {
-      # Remove prefix and replace underscores with spaces, then lowercase
-      return(tolower(sub("delivery_method_", "", gsub("_", " ", x))))
+      # Handle specific renaming for non-"no" values
+      if (col == "delivery_method_events") {
+        return("events")
+      } else if (col == "delivery_method_enewsletter_email") {
+        return("enewsletter / email")
+      } else if (col == "delivery_method_advertising_campaigns") {
+        return("advertising campaigns")
+      } else if (col == "delivery_method_brochures_pamphlets") {
+        return("brochures / pamphlets")
+      } else if (col == "delivery_method_other") {
+        return("other")
+      } else if (col == "delivery_method_not_interested_receiving") {
+        return("not interested")
+      } else {
+        # Otherwise, remove prefix, replace underscores with spaces, and lowercase
+        return(tolower(sub("delivery_method_", "", gsub("_", " ", x))))
+      }
     }
   })
 }

### 2024-12-01 scripts/03-clean_data.R
updating delivery_method

@@ -171,32 +171,35 @@ for (col in unlikelihood_columns) {
 # Handle "delivery_method" columns
 delivery_method_columns <- grep("^delivery_method", names(twenty_eighteen), value = TRUE)
 
-# Loop through each delivery_method column
+# Mapping for renaming specific non-"no" values
+delivery_method_rename_map <- list(
+  "toronto.ca_website" = "toronto.ca website",
+  "events" = "events",
+  "twitter" = "twitter",
+  "facebook" = "facebook",
+  "enewsletter_email" = "enewsletter / email",
+  "councillor_communication" = "councillor communication",
+  "advertising_campaigns" = "advertising campaigns",
+  "brochures_pamphlets" = "brochures / pamphlets",
+  "other" = "other",
+  "not_interested_receiving" = "not interested"
+)
+
+# Loop through each "delivery_method" column
 for (col in delivery_method_columns) {
   twenty_eighteen[[col]] <- sapply(twenty_eighteen[[col]], function(x) {
     if (grepl("^NO TO", x)) {
-      return("no")  # Change to "no" if it starts with "NO TO"
+      return("no")
     } else {
-      # Handle specific renaming for non-"no" values
-      if (col == "delivery_method_events") {
-        return("events")
-      } else if (col == "delivery_method_enewsletter_email") {
-        return("enewsletter / email")
-      } else if (col == "delivery_method_advertising_campaigns") {
-        return("advertising campaigns")
-      } else if (col == "delivery_method_brochures_pamphlets") {
-        return("brochures / pamphlets")
-      } else if (col == "delivery_method_other") {
-        return("other")
-      } else if (col == "delivery_method_not_interested_receiving") {
-        return("not interested")
-      } else {
-        # Otherwise, remove prefix, replace underscores with spaces, and lowercase
-        return(tolower(sub("delivery_method_", "", gsub("_", " ", x))))
-      }
+      # Remove the prefix and replace underscores with spaces, then lowercase
+      x_cleaned <- tolower(sub("delivery_method_", "", gsub("_", " ", x)))
+      
+      # Check if the value matches the mapping and rename it accordingly
+      return(delivery_method_rename_map[[x_cleaned]])
     }
   })
 }
+
 
 # str(twenty_eighteen)
 
@@ -446,7 +449,6 @@ write_parquet(reason_summary_18, "data/02-analysis_data/twenty_eighteen_reasons_
 
 
 ## 6. Communication Summary ##
[…]

### 2024-12-01 scripts/03-clean_data.R
check csv for change in delivery_method rows / values

@@ -187,16 +187,21 @@ delivery_method_rename_map <- list(
 
 # Loop through each "delivery_method" column
 for (col in delivery_method_columns) {
+  # Remove the prefix 'delivery_method_' from the column name
+  col_name <- sub("delivery_method_", "", col)
+  
   twenty_eighteen[[col]] <- sapply(twenty_eighteen[[col]], function(x) {
     if (grepl("^NO TO", x)) {
       return("no")
     } else {
-      # Remove the prefix and replace underscores with spaces, then lowercase
-      x_cleaned <- tolower(sub("delivery_method_", "", gsub("_", " ", x)))
-      
-      # Check if the value matches the mapping and rename it accordingly
-      return(delivery_method_rename_map[[x_cleaned]])
+      # Replace non-"no" values with the column name without the prefix
+      return(col_name)
     }
+  })
+  
+  # Now, rename specific values in the column using the predefined map
+  twenty_eighteen[[col]] <- sapply(twenty_eighteen[[col]], function(x) {
+    return(delivery_method_rename_map[[x]] %||% x)  # Use the mapped value if it exists, otherwise keep the original
   })
 }
 

### 2024-12-01 paper/paper.qmd
data section is set in terms of figures for 2018 individual, just need to modify/ add text for features

@@
 Comparing this with 2021 data allowed for an assessment of evolving preferences, showing a continued preference for digital platforms among younger generations, but a growing interest in in-person communication across all groups.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-communication
+#| fig-cap: The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action.
+
+knitr::include_graphics(here("data/03-figures_data", "communication_18_plot.png"))
+
+```
 

### 2024-12-01 scripts/03-clean_data.R

@@ -459,16 +459,33 @@ write_parquet(reason_summary_18, "data/02-analysis_data/twenty_eighteen_reasons_
 communication_summary_18 <- twenty_eighteen %>%
   select(starts_with("delivery_method"))
 
+# Define the renaming mapping
+delivery_method_rename_map <- list(
+  "delivery_method_toronto.ca_website" = "Toronto.ca website",
+  "delivery_method_events" = "Events",
+  "delivery_method_twitter" = "Twitter",
+  "delivery_method_facebook" = "Facebook",
+  "delivery_method_instagram" = "Instagram",
+  "delivery_method_enewsletter_email" = "Enewsletter / email",
+  "delivery_method_councillor_communication" = "Councillor communication",
+  "delivery_method_advertising_campaigns" = "Advertising campaigns",
+  "delivery_method_brochures_pamphlets" = "Brochures / Pamphlets",
+  "delivery_method_other" = "Other",
+  "delivery_method_not_interested_receiving" = "Not interested"
+)
+
 # Calculate percentage of non-"no" occurrences
 communication_summary_18 <- communication_summary_18 %>%
   summarise(across(everything(), ~ sum(. != "no") / n() * 100)) %>%
   pivot_longer(cols = everything(), 
-               names_to = "Delivery_Method", 
+               names_to = "Communication Method", 
                values_to = "Percentage") %>%
-  mutate(Delivery_Method = gsub("delivery_method_", "", Delivery_Method),  # Remove prefix
-         Percentage = round(Percentage)) %>%
-  filter(Delivery_Method != "total_rows") %>%
-  rename("Communication Method" = Delivery_Method)  # Rename column to "Communication Method"
+  mutate(Percentage = round(Percentage)) %>%
+  filter(`Communication Method` != "total_rows")  # Filter out any unwanted rows
+
+# Apply renaming based on the mapping
+communication_summary_18 <- communication_summary_18 %>%
+  mutate(`Communication Method` = recode(`Communication Method`, !!!delivery_method_rename_map))
 
 # Create the table using tinytable (similar to age and education examples)
 communication_summary_18_table <- tinytable::tt(communication_summary_18, 
@@ -476,16 +493,11 @@ communication_summary_18_table <- tinytable::tt(communication_summary_18,
                                                 col.names = c("Communication Method", "Percentage"), 
                                                 escape = FALSE)
 
-# View the summary table
-communication_summary_18_table
-
[…]

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -278,18 +278,44 @@ ggplot(data_summary, aes(x = action, y = count, fill = reason)) +
 
 
 
-# figure for method of communication 
-# Select columns that start with 'delivery_method' and count non-"no" values
+# Figure for method of communication
+# Select columns that start with 'delivery_method'
 delivery_columns <- individual_18 %>%
-  select(starts_with("delivery_method")) %>%
-  mutate(across(everything(), ~ ifelse(. == "no", NA, .)))  # Convert "no" to NA to easily count non-"no" values
+  select(starts_with("delivery_method"))
 
-# Count the number of non-NA (non-"no") responses for each column
-data_summary <- delivery_columns %>%
-  summarise(across(everything(), ~ sum(!is.na(.)))) %>%
-  pivot_longer(everything(), names_to = "delivery_method", values_to = "count")  # Pivot to long format
+# Create an empty data frame to store the results
+data_summary <- data.frame(
+  delivery_method = character(),
+  count_non_no = integer(),
+  count_no = integer(),
+  percentage = numeric(),
+  stringsAsFactors = FALSE
+)
 
-# Rename delivery_method columns to meaningful names
+# Loop through each column to count non-"no" and "no" responses
+for (col in colnames(delivery_columns)) {
+  
+  # Count non-"no" responses
+  non_no_count <- sum(delivery_columns[[col]] != "no", na.rm = TRUE)
+  
+  # Count "no" responses
+  no_count <- sum(delivery_columns[[col]] == "no", na.rm = TRUE)
+  
+  # Calculate the percentage of non-"no" responses
+  total_responses <- non_no_count + no_count
+  percentage <- (non_no_count / total_responses) * 100
+  
+  # Add the result to the summary data frame
+  data_summary <- data_summary %>%
+    add_row(
+      delivery_method = col,
+      count_non_no = non_no_count,
+      count_no = no_count,
+      percentage = percentage
+    )
+}
+
+# Rename the delivery method columns for readability
 data_summary <- data_summary %>%
   mutate(
     delivery_method = case_when(
@@ -308,42 +334,34 @@ data_summary <- data_summary %>%
     )
   )
 
-# Create a bar chart for frequency of non-"no" responses for each delivery method
-ggplot(data_summary, aes(x = reorder(delivery_method, count), y = count, fill = delivery_method)) +
+# Save the plot as 'communication_18_plot'
[…]

### 2024-12-02 paper/paper.qmd
data section - describing features

--- 2024-12-01 paper/paper.qmd
@@
 By addressing key barriers and tailoring engagement strategies, cities can empower individuals to adopt sustainable behaviors, making meaningful progress toward climate resilience and environmental sustainability.
+
+In Canada, electric vehicles (EVs) are increasingly recognized as a more sustainable alternative to internal combustion engine (ICE) vehicles.
+A life cycle assessment (LCA) conducted by the National Research Council of Canada highlights that EVs offer substantial greenhouse gas (GHG) emission reductions, particularly when powered by electricity from low-carbon sources, such as hydroelectricity in provinces like Québec.
+The study emphasizes the importance of considering regional electricity mixes, which significantly influence the environmental performance of EVs compared to conventional vehicles (NRC, 2021)
+Moreover, advancements in battery technology are further enhancing the sustainability of EVs.
+New lithium iron phosphate (LFP) batteries, which reduce the need for critical metals like cobalt and nickel, are becoming more prevalent.
+These batteries not only lower production costs but also extend the lifespan of EVs, making them even more environmentally friendly over time.
+(NRC, 2021)
+In Ontario, where Toronto is located, the electricity grid's relatively low carbon intensity makes EVs a cleaner option throughout most of their lifecycle.
+According to Clean Energy Canada, EVs in the country can emit up to 89% fewer GHGs than gasoline-powered cars, even after accounting for emissions from battery production and vehicle manufacturing (NRC, 2021)
 
@@
 ### Age
+@fig-one illustrates the age distribution of survey respondents in 2018.
+The histogram displays the frequency of respondents across different age groups, with the x-axis representing age intervals and the y-axis indicating the number of respondents within each interval.
+The distribution is relatively balanced, with two noticeable peaks around the 30–40 and 50–60 age ranges, suggesting these age groups are the most represented in the survey.
+
+The vertical dotted lines in the figure highlight key statistical measures: the green dotted line represents the median age, while the blue dashed line indicates the mean age of the respondents.
+Both measures fall near the center of the distribution, reinforcing the observation that the sample is primarily composed of middle-aged individuals.
+Although the distribution appears fairly symmetrical, there is a gradual decline in respondent frequency after the age of 60, with fewer participants aged 90 and above, indicating a smaller representation of older individuals.
+
+Overall, @fig-one provides valuable context for understanding the demographic composition of the survey sample.
+The predominance of middle-aged respondents may influence the interpretation of survey results, particularly if age is a factor in attitudes, behaviors, or preferences related to the study.
+
 ```{r}
@@
 #| label: fig-one
-#| fig-cap: The histogram shows the distribution of age given the 2018 survey  respondants.
+#| fig-cap: The histogram shows the distribution of age given the 2018 survey respondents.
 
-# Read in the data 
-individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
+knitr::include_graphics(here("data/03-figures_data", "age_individual_plot.png"))
 
-age_individual_plot
 ```
 
-The age variable was assessed to understand how climate change perceptions and actions vary across different age groups.
-The 2018 data shows that younger individuals, particularly those in the 18-34 age range, are more likely to feel informed about climate change and express a greater willingness to take action.
-In contrast, older age groups (55+) were less likely to feel as informed or engage in climate action, highlighting generational differences in awareness and response.
+### Highest Level of Education Completed
+@fig-two illustrates the distribution of survey respondents by their highest level of education attained.
+The most frequently reported education levels are "Completed undergraduate degree" and "Post graduate/professional school," with both categories having a noticeably higher frequency compared to others, indicating a well-educated respondent population.
+In contrast, fewer respondents reported "Some community college, vocational, trade school" and "Completed community college, vocational, trade school," suggesting these levels are less common among participants.
+Additionally, a small portion of respondents preferred not to disclose their education level.
+This distribution highlights a skew toward higher educational attainment within the sample, which may influence responses related to socio-economic factors and other survey topics.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-two
+#| fig-cap: The histogram shows the distribution of education levels of 2018 survey respondents.
 
-### Highest Level of Education Completed
-Education level was analyzed to determine if there is a correlation between education and attitudes toward climate change.
-The 2018 data suggests that individuals with higher levels of education (university degree or higher) are more likely to feel informed about climate change and are more inclined to take action.
-Conversely, individuals with lower education levels expressed lower awareness and action towards climate change, indicating the role of education in shaping environmental engagement.
+knitr::include_graphics(here("data/03-figures_data", "educ_individual_plot.png"))
+
+```
 
 ### Extent Feel Informed
-This variable assessed individuals’ perceptions of how informed they feel about climate change.
-The 2018 data revealed that while a significant proportion of the population felt somewhat or very informed, there was a noticeable gap in knowledge, especially among older and less educated groups.
-Comparing this with the 2021 summary data helped track whether the perceived knowledge of climate change improved over the three years, showing some progress in public awareness.
+@fig-three depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
+The majority of participants identified as "Very informed," making this the most prevalent category by a significant margin.
+A moderate number of respondents reported being "Not very informed," while a smaller yet noticeable group described themselves as "Extremely informed." In contrast, the categories "Not at all informed" and "Not very informed" have the lowest frequencies, with "Not at all informed" being particularly rare.
+This distribution suggests that most respondents possess a relatively high level of awareness about climate change, with very few indicating a lack of knowledge on the topic.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-three
+#| fig-cap: The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents.
 
-### Likelihood Taking Action
-The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors.
-In the 2018 data, younger individuals and those with higher educational attainment were more likely to report taking action, such as reducing carbon emissions or supporting climate policies.
-The 2021 data confirmed this trend, although slight shifts in attitudes were observed, with more people in the 35-54 age range indicating increased willingness to act.
+knitr::include_graphics(here("data/03-figures_data", "informed_individual_plot.png"))
 
-### Barriers Taking Action
-TO DO: cant actually get this section to work
-This section analyzed the reasons individuals gave for not taking action on climate change.
-Common barriers identified in the 2018 data included financial constraints, lack of information, and perceived ineffectiveness of individual actions.
-These barriers were more pronounced among older individuals and those with lower educational levels.
-The 2021 summary data highlighted some shifts, with more respondents citing political barriers or the need for more systemic solutions.
+```
 
 ### Best Mode of Delivery
-The analysis of the best method for delivering climate change information revealed that the majority of individuals in the 2018 dataset preferred receiving information via social media, followed by television and in-person presentations.
-Younger age groups favored social media, while older individuals preferred more traditional modes of communication.
-Comparing this with 2021 data allowed for an assessment of evolving preferences, showing a continued preference for digital platforms among younger generations, but a growing interest in in-person communication across all groups.
+The analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
+On the other side of the spectrum, few said they were uninterested in receiving climate action information  with about 5 percent, about 12 percent indicated twitter and then 17 percent mentioned instagram.
+Overall social media platforms Facebook, Instagram and Twtitter were less popular methods of communciation.
+This could be because the survey only included individals over the age of 18.
+Moreover, the median sample was in the 40s.
+
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-four
+#| fig-cap: The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action.
+
+knitr::include_graphics(here("data/03-figures_data", "communication_18_plot.png"))
+
+```
 
@@
 # Results
+
+## Likelihood Taking Action
+The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
+@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
+On the x-axis, we have the nine different climate actions and on the y-axis is the percentage.
+The stacked bar chart allows understanding of how likely individuals are to take part in the given actions.
+Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action.
+The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements.
+40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely.
+However, 7 percent say they are very unlikely to change their method of transportation.
+Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely.
+Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action.
+Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof.
+In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle.
+While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely.
+This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases.
+This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change!
+The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely.
+Only 23 percent are already consuming meat alternatives.
+Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-five
+#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_individual_plot.png"))
+
+```
+
+### Likelihood taking action by age
+
+### Likelihood taking action by education
+
+## comparison 2018 to 2021
 

### 2024-12-02 scripts/05-exploratory_data_analysis.R

@@ -66,13 +66,14 @@ ggsave(
 # Create a histogram to show the distribution of highest level of education attained
 # Convert the column to a factor
 individual_18$highest_level_educ <- factor(individual_18$highest_level_educ, 
-                                                  levels = c("High school or less", 
-                                                             "Some community college, vocational, trade school",
-                                                             "Completed community college, vocational, trade school", 
-                                                             "Some university",
-                                                             "Completed undergraduate degree", 
-                                                             "Post graduate/professional school",
-                                                             "Prefer not to answer"))
+                                           levels = c("High school or less", 
+                                                      "Some community college, vocational, trade school",
+                                                      "Completed community college, vocational, trade school", 
+                                                      "Some university",
+                                                      "Completed undergraduate degree", 
+                                                      "Post graduate/professional school",
+                                                      "Prefer not to answer"))
+
 # Create the plot with adjustments
 educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill = highest_level_educ)) +
   geom_bar(color = "black", alpha = 0.7) + 
@@ -91,7 +92,8 @@ educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill =
   ) +
   theme(
     axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels by 45 degrees
-    plot.margin = margin(10, 10, 20, 10)  # Increase the margins for better spacing
+    plot.margin = margin(10, 10, 20, 10),  # Increase the margins for better spacing
+    legend.position = "none"  # Remove the legend
   ) +
   scale_fill_manual(values = c("High school or less" = "red", 
                                "Some community college, vocational, trade school" = "orange", 
@@ -99,11 +101,11 @@ educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill =
                                "Some university" = "lightgreen", 
                                "Completed undergraduate degree" = "green", 
                                "Post graduate/professional school" = "forestgreen", 
-                               "Prefer not to answer" = "gray")) +
-  guides(fill = guide_legend(title = NULL))  # Hide the legend title
+                               "Prefer not to answer" = "gray"))
 
 # Display the plot
 print(educ_individual_plot)
+
 # Save the education plot to data/03-figures_data
 ggsave(
   filename = here("data/03-figures_data", "educ_individual_plot.png"),  # Saving as a PNG file

### 2024-12-02 paper/paper.qmd
working on model section of paper and model scirpt

@@
 ## Model set-up
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+In this analysis, we aim to predict the likelihood of taking climate-friendly actions based on demographic variables (age, education) and climate change awareness (knowledge).
+The specific actions include investing in an electric or hybrid vehicle instead of a gas-powered one, making home improvements (e.g., using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste by repurposing used products, sorting waste correctly, and walking or cycling shorter distances.
+
+### Model Specifications ###
 
@@
 
-### Model Specifications ###
 ### Model Justification 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+This model is designed to explore how various demographic and knowledge-based factors influence the likelihood of engaging in climate-friendly behaviors.
+The likelihood of taking specific actions, such as reducing energy consumption or investing in green technologies, represents an important outcome in understanding climate change perceptions.
+As such, focusing on these behaviors rather than general knowledge allows for a more actionable and directly applicable model to climate change policy and interventions.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
 #### Response Variable ####
+The response variable in this analysis is the likelihood of taking climate-friendly actions, which is typically a continuous or ordinal measure based on respondents' self-reported likelihood of adopting behaviors such as switching to an electric vehicle, reducing waste, or conserving energy.
+These actions are commonly measured on a Likert scale (e.g., 1 = "not likely" to 5 = "very likely").
+
 #### Input Variabless ####
+The input variables (predictors) include:
+
+Age: Previous studies indicate that younger individuals are more likely to engage in climate-positive behaviors due to greater environmental awareness and concern (Leiserowitz et al., 2010; Gifford, 2013).
+
+Education: Higher educational attainment has been associated with a higher likelihood of adopting environmentally responsible behaviors, likely due to increased awareness of environmental issues and access to relevant information (Kollmuss & Agyeman, 2002).
+
+Knowledge: A greater understanding of climate change is expected to positively influence individuals' likelihood of taking action.
+More knowledgeable individuals are more likely to adopt climate-friendly practices, as they are more aware of the urgency of the crisis and the potential benefits of sustainable behaviors (Gifford, 2013).
 #### Model Structure ####
+The model assumes that the likelihood of taking climate-friendly actions is linearly related to the input variables.
+Each predictor (age, education, and knowledge) is assumed to have a linear relationship with the likelihood of taking action, meaning that as these variables change, the likelihood of taking climate-friendly actions will either increase or decrease in a predictable manner.
+This structure facilitates a clear interpretation of how each variable contributes to the overall likelihood of climate-positive behavior.
+
+Detailed Structure
+The model does not assume any interactions between the predictors, meaning each factor (age, education, knowledge) is considered independently in its influence on the outcome.
+However, depending on the data, you might consider adding interaction terms if you believe that, for example, the effect of knowledge on action is stronger for younger individuals.
+The linear relationship between predictors and the likelihood of action allows for easy interpretation, with coefficients representing the change in the likelihood of taking action for each unit change in the predictor variable.
 #### Parameter Estimation ####
+
+In parameter estimation, we anticipate that:
+
+Age: We expect that younger individuals will have a higher likelihood of taking climate-friendly actions, as studies have shown that younger generations are more environmentally conscious and concerned about climate change (Leiserowitz et al., 2010).
+Education: We hypothesize that higher levels of education will positively influence the likelihood of taking climate-positive actions.
+More educated individuals tend to have better access to information about climate change and sustainability practices (Kollmuss & Agyeman, 2002).
+Knowledge: We expect that greater knowledge of climate change will be strongly associated with higher likelihoods of adopting climate-friendly behaviors.
+Knowledge acts as a critical enabler, motivating individuals to take action and contribute to mitigating climate change (Gifford, 2013).
+We will estimate the model parameters using a standard linear regression approach (e.g., using the lm() function in R), which will provide the coefficients (
+β
+β) for each predictor, showing how each factor influences the likelihood of taking climate-friendly actions.
 

### 2024-12-02 scripts/06-model_data.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Constructs a linear regression model for predicting likelihood of taking climate action based on age and education. 
+# Author: Lexi Knight
+# Date: 30 November 2024
+# Contact: lexi.knight@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: complete 01-download_data.R and 03-clean_data.R in scripts folder in order to access data.
+
+
 
 
 #### Workspace setup ####

### 2024-12-02 scripts/06-model_data.R
stuck on modeling :(

@@ -7,32 +7,38 @@
 # Pre-requisites: complete 01-download_data.R and 03-clean_data.R in scripts folder in order to access data.
 
 
-
-
 #### Workspace setup ####
+
+# Install required packages
+install.packages("tidyverse")  # For data manipulation
+install.packages("broom")  # Optional, for tidying model output
+
+
 library(tidyverse)
-library(rstanarm)
+library(brms)
+library(arrow)
+library(here)
+library(broom)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+# Load your analysis data
+individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Convert the 'highest_level_educ' variable to a factor
+climate_data$highest_level_educ <- factor(climate_data$highest_level_educ)
+
+# Now check the levels again
+levels(climate_data$highest_level_educ)
 
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+# Convert the ordinal likelihood variables to numeric values
+climate_data <- climate_data %>%
+  mutate(across(starts_with("likelihood"),
+                ~ as.numeric(factor(., levels = c("very_unlikely", "somewhat_unlikely", 
+                                                  "somewhat_likely", "very_likely", "already_done")))))
 
+# Fit a linear regression model
+linear_model <- lm(likelihood_home_improvement ~ age + highest_level_educ, data = climate_data)
 
+# Summarize the model
+summary(linear_model)

### 2024-12-02 paper/paper.qmd
working on likelihood by age and likelihood by education

@@
 ### Likelihood taking action by age
+The graph illustrates the relationship between age group (x-axis) and the percentage of respondents (y-axis) who reported varying levels of likelihood to adopt climate-related actions.
+The colored segments of each bar represent five levels of likelihood and black dashed trend line provides an overview of how the likelihood to engage in each action changes across different age groups.
+#### Electric / Hybrid Vehicle Adoption
+For electric and hybrid vehicles, younger age groups (15-24, 25-34) show relatively lower engagement, with a smaller proportion already adopting or being very likely to adopt these vehicles.
+However, engagement slightly increases with age, peaking in the 55-64 age group before slightly declining in the 65+ group.
+The trend line indicates a modest upward trajectory as respondents age, suggesting that older individuals may have more resources or stability to invest in electric vehicles.
+
+#### Home Improvement for Energy Efficiency
+Home improvement actions follow a similar trend, with middle-aged groups (35-54) showing the highest likelihood of engagement.
+The younger groups (15-24 and 25-34) report the lowest likelihood, which may reflect barriers such as homeownership rates and disposable income.
+The trend line peaks in the 45-54 group, indicating that this demographic is most likely to engage in energy-efficient home improvements.
+
+#### Consumption of Meat Alternatives
+Adoption of meat alternatives is more prevalent in the younger age groups (15-24 and 25-34), with a significant proportion already consuming or being very likely to consume these products.
+As age increases, the likelihood decreases, with the 65+ group showing the lowest engagement.
+This trend may be driven by cultural or dietary habits that are more entrenched in older generations.
+
+#### Minimizing Car Use
+Minimizing car use shows a similar trend to meat alternatives, with younger respondents demonstrating a higher likelihood of reducing their car use.
+The likelihood declines steadily across age groups, and the trend line confirms this downward trajectory, suggesting that older individuals are less willing or able to minimize car use, possibly due to mobility needs or suburban living arrangements.
+
+#### Purchasing Green Products
+The likelihood of purchasing green products is relatively consistent across age groups, with slight increases in the middle-aged and older demographics.
+The trend line remains relatively flat, indicating that green product consumption is not strongly age-dependent but may be influenced by other factors such as income and environmental awareness.
+
+#### Reducing Hydro Usage
+Efforts to reduce hydro (electricity) usage are most prominent among older age groups (55-64 and 65+), who report the highest likelihood of engaging in this action.
+The trend line shows a clear upward trajectory, suggesting that older respondents, possibly driven by cost-saving measures or environmental concerns, are more likely to reduce hydro usage.
+
+#### Reducing and Sorting Waste
+Reducing waste and sorting waste correctly show a similar pattern: younger age groups report lower levels of engagement, while middle-aged and older groups (45-64) show higher participation.
+The trend line peaks around the 55-64 age group, highlighting the heightened awareness or resources available to this demographic for proper waste management.
+
+#### Walking / Cycling Short Distances
+Walking or cycling short distances is notably more prevalent among younger respondents, particularly those aged 15-34.
+The trend line declines steadily with age, indicating that older individuals are less likely to walk or cycle, potentially due to physical limitations or differing lifestyle needs.
+
+#### Summary
+Overall, the graph highlights significant variation in the likelihood of engaging in climate actions across different age groups.
+Younger respondents are more inclined to adopt behaviors such as consuming meat alternatives and minimizing car use, while older respondents show greater engagement in actions like reducing hydro usage and making home improvements.
+The trend lines across actions suggest that age is a critical factor influencing climate-related behavior, potentially mediated by factors such as income, lifestyle, and environmental awareness.
+
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-six
+#| fig-cap: Likelihood of Taking Climate Change Actions by Age Group.
+The stacked bar chart illustrates the percentage of respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64, 65+) in terms of their self-reported likelihood to engage in nine distinct climate-related actions.
+Each color represents a different level of likelihood, from "Already doing this or have done this" to "Very unlikely." The black dashed trend line highlights how the likelihood of action changes across age groups, providing insights into generational differences in climate-related behavior.
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))
+```
 

### 2024-12-02 scripts/05-exploratory_data_analysis.R

@@ -223,63 +223,6 @@ ggsave(
 
 
 
-
-
-# Create a figure illustrating reasons why people are not taking specific action to mitigate climate change
-# TO DO: pls come back to. the issue is that each "reason"category is appearing
-# to be the same weight.We need to look at how given a specific action (column), how we
-# count up  non-NA values (reasons). the count is displaying wrong. 
-# TO DO: renaming OG data - bad
-
-# Pivot to long format
-data_long <- individual_18 %>%
-  pivot_longer(
-    cols = starts_with("unlikelihood"),  # Select all the columns starting with "unlikelihood"
-    names_to = c("action", "reason"),  # Separate action and reason
-    names_pattern = "unlikelihood_(.*)_(.*)_18",  # Extract action and reason parts from the column name
-    values_to = "response"  # Values will be stored under 'response'
-  ) %>%
-  filter(!is.na(response)) %>%  # Filter out rows with NA responses
-  mutate(
-    action = case_when(  # Clean the action labels to ensure we have only 9 distinct actions
-      str_detect(action, "home_improvement") ~ "Home Improvement",
-      str_detect(action, "reduce_waste") ~ "Reduce Waste",
-      str_detect(action, "short_distance") ~ "Walk/Cycle Short Distances",
-      str_detect(action, "vehicle_electric") ~ "Electric/Hybrid Vehicle",
-      str_detect(action, "minimize_car") ~ "Minimize Car Use",
-      str_detect(action, "green_product") ~ "Purchase Green Products",
-      str_detect(action, "protein_alternative") ~ "Protein Alternatives",
-      str_detect(action, "reduce_hydro") ~ "Reduce Hydro Usage",
-      str_detect(action, "sort_waste") ~ "Sort Waste",
-      TRUE ~ action  # Default case if the action is already correctly labeled
-    )
-  )
-
-# Summarize counts by action and reason (correctly count non-NA responses)
-data_summary <- data_long %>%
-  group_by(action, reason) %>%  # Group by both action and reason
-  summarise(count = n(), .groups = "drop")  # Count the frequency of each reason per action
-
-# Create a stacked bar chart
-ggplot(data_summary, aes(x = action, y = count, fill = reason)) +
-  geom_bar(stat = "identity") +  # Use 'identity' to use actual counts
-  labs(
-    title = "Reasons for Unlikelihood of Taking Climate Change Actions",
-    x = "Climate Change Action",
-    y = "Frequency of Responses",
[…]

### 2024-12-02 paper/paper.qmd
incorportaing summary 2018 and 2021 tables

@@
 ### Age
+#### Individual 2018
 @fig-one illustrates the age distribution of survey respondents in 2018.
@@
 ```
+#### Age Comparison 2018 and 2021
+This summary table illustrates the different age ditribution for 2018 and 2021 surveys.
+The major difference is that there was greater representation of younger inviduals ranging from 18 to 23 in 2021 compared to 2018.
+The remaining age groups were not very different.
+
+```{r}
+print(age_summary_combined)
+
+```
 
@@
 
+```
+#### Education Comparison 2018 and 2021
+```{r}
+print(education_summary_combined)
 ```
@@
 # Model {#sec-model}
+TO DO:
 The goal of our modelling strategy is twofold. Firstly,...
@@
 ### Model Specifications ###
+TO DO:
 
@@
 More knowledgeable individuals are more likely to adopt climate-friendly practices, as they are more aware of the urgency of the crisis and the potential benefits of sustainable behaviors (Gifford, 2013).
+
 #### Model Structure ####
@@
 The linear relationship between predictors and the likelihood of action allows for easy interpretation, with coefficients representing the change in the likelihood of taking action for each unit change in the predictor variable.
+
 #### Parameter Estimation ####
-
 In parameter estimation, we anticipate that:
-
 Age: We expect that younger individuals will have a higher likelihood of taking climate-friendly actions, as studies have shown that younger generations are more environmentally conscious and concerned about climate change (Leiserowitz et al., 2010).
@@
 The colored segments of each bar represent five levels of likelihood and black dashed trend line provides an overview of how the likelihood to engage in each action changes across different age groups.
+
 #### Electric / Hybrid Vehicle Adoption
@@
 ### Likelihood taking action by education 
+TO DO: graph not working
 

### 2024-12-02 scripts/03-clean_data.R

@@ -22,7 +22,7 @@ library(tidyverse)
 library(tidyr)
 library(stringr)
 library(tinytable)
-
+library(here)
 
 #### Clean individual 2018 data ####
 
@@ -228,7 +228,7 @@ write_csv(twenty_eighteen, "data/02-analysis_data/twenty_eighteen_individual_ana
 twenty_eighteen <- read_csv("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv", col_names = TRUE)
 
 
-## 1. Age Summary ##
+## 1. Age Summary 2018 ##
 
 ## Create age categories based on ranges in 2021 summary data and summarize directly
 age_summary_18 <- as.data.frame(table(cut(twenty_eighteen$age, 
@@ -246,15 +246,14 @@ age_summary_18 <- age_summary_18[, c("Age Group", "Percentage")]
 # Create the table using tinytable
 age_summary_18_table <- tt(age_summary_18)
 
-# Print the table
-print(age_summary_18_table)
+# print table
+age_summary_18_table
 
 # Save as Parquet
-write_parquet(age_summary_18, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet")
+write_parquet(age_summary_18, here("data/03-figures_data", "age_summary_2018_table.parquet"))
 
 
-
-## 2. Education Level Summary ##
+## 2. Education Level Summary 2018 ##
 
 # Create the summary table based on education levels
 education_summary_18 <- as.data.frame(table(twenty_eighteen$highest_level_educ))
@@ -269,15 +268,15 @@ education_summary_18 <- education_summary_18[, c("Education Level", "Percentage"
 # Create the table using tinytable
 education_summary_18_table <- tt(education_summary_18)
 
-# Print the table
-print(education_summary_18_table)
+# Print table
+education_summary_18_table
 
 # Save as Parquet
-write_parquet(education_summary_18, "data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet")
+write_parquet(education_summary_18, here("data/03-figures_data", "education_summary_2018_table.parquet"))
 
 
 
-## 3. Informed Summary ##
+## 3. Informed Summary 2018 ##
 
 # Create the summary table based on the informed extent categories
 informed_summary_18 <- as.data.frame(table(twenty_eighteen$extent_consider_informed))
@@ -296,13 +295,12 @@ informed_summary_18_table <- tt(informed_summary_18)
 informed_summary_18_table
 
 # Save as Parquet
[…]

### 2024-12-02 scripts/05-exploratory_data_analysis.R

@@ -12,17 +12,21 @@
 # install libraries 
 # install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow", "tidyr"))
 # install.packages("forcats","RColorBrewer")
+install.packages("kableExtra")
 
 # Load necessary libraries
 library(tidyverse)
 library(dplyr)
 library(ggplot2)
-library(here)
+library(here) # for working with relative paths
 library(stringr) # was this used?
 library(knitr)
-library(arrow)
+library(arrow) # for reading parquet files
 library(tidyr)
 library(forcats) # for reordering factor levels
+library(kableExtra) # for rendering tables
+library(tinytable)
+
 
 
 # Read in the data 
@@ -460,40 +464,80 @@ ggsave(
 
 
  
-### 2018 summary tables + graphs ###
+### Comparison 2018 and 2021 tables
 
-age_summary_18_table
+## Age
+# Read the 2018 and 2021 age summary tables from Parquet files
+age_summary_18 <- read_parquet(here("data/03-figures_data", "age_summary_2018_table.parquet"))
+age_summary_21 <- read_parquet(here("data/03-figures_data", "age_summary_2021_table.parquet"))
 
-education_summary_18_table
+# Rename columns to indicate the year for clarity
+colnames(age_summary_18) <- c("Age Group", "2018 (%)")
+colnames(age_summary_21) <- c("Age Group", "2021 (%)")
 
-informed_summary_18_table
+# Merge the two data frames by Age Group for side-by-side comparison
+age_summary_combined <- full_join(age_summary_18, age_summary_21, by = "Age Group")
 
-likelihood_summary_18_table
+# Render the combined table using kableExtra
+age_summary_combined %>%
+  kbl(caption = "Age Summary Comparison for 2018 and 2021 Survey Respondents") %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
 
-communication_summary_18_table
+# create table using tinytable
+age_summary_combined <- tt(age_summary_combined)
 
-
-
-
-### 2021 summary tables + graphs ###
-
-age_summary_21_table
-
-education_summary_21_table
-
-informed_summary_21_table
-
-likelihood_summary_21_table
-
-reasons_summary_21_table
-
-communication_summary_21_table
+# print table
+age_summary_combined
 
 
 
+## Education 
+# Read the 2018 and 2021 education summary tables from Parquet files
[…]

### 2024-12-03 paper/paper.qmd
added summary comparisons 2018 to 2021 in data section ! yay!

@@
 ```
-#### Age Comparison 2018 and 2021
+#### Age Comparison 2018 to 2021
 This summary table illustrates the different age ditribution for 2018 and 2021 surveys.
@@
 ```
-#### Education Comparison 2018 and 2021
+#### Education Comparison 2018 to 2021
+This table illustrates respondant education level in 2018 and 2021 respectively.
+Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021.
+Despite this, we are still able to make comparisons.
+Individuals with high school diplomas or less account for 9 for 2018 and 38 for 2021 (addition of less than highs school and high school or equivalent categories).
+This could indicate that the younger population was included more in the 2021 suvey or that less education individuals were surveyed.
+Additionally, its not super clear howver those with a post graduate or professional degree accounted for 29 percent in 2018 and 35 percent in 2021.
+This illustrates that more educated inviduals responded to the 2021 survey.
 ```{r}
@@
 ```
+#### Extent Feel Informed Comparison 2018 to 2021
+This table illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
+In 2018, the large marjority of individuals say they are very informed with 60 percent and the follwoign category is not very informed with 27 percent.
+In 2021, The majority of inividuals also say they are very informed but to a lesser degree with 48 percent and this is closely followed by only a little informed with 37 percent.
+There is a trend that invidiusls in 2018 reported greater levels of knowldege about climate change whereas 2021 illstrates a more even split between very informed and only little informed, portraying that fewer individuals have adequate knowledge about climate change.
+
+```{r}
+print(informed_summary_combined)
+```
 
@@
 
+```
+
+#### Method of Communicaton Comparison 2018 to 2021
+This table compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
+Aside from the additon of four options to the 2021 survey, both surveys questions are the same.
+The leading category for 2018 is advertising campaigns with 55 percent, closely followed by newsletter emails with 52 percent and the Toronto website with 46.
+The 2021 survey illustrates a consistent trend with the same platforms as the top method of delivering information, specifically the Toronto website with 44 percent, then enewsletter emails with 43 percent and advertising campains at 42 percent.
+These top methods of communciation are more evenly spread out than the 2018 survey results.
+Social media platforms namely twitter, facebook and instagram all increased in the 2021 survey.
+Notable decreases in term of percentage from 2018 to 2021 include events, enewsletter emails, advertising campaigns, brochures and pamphlets.
+The new category of BetterHomesTO.ca webiste accounts for 15 percent of votes for the 2021 survey.
+
+```{r}
+print(communication_summary_combined_table)
 ```

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -541,3 +541,147 @@ education_summary_combined <- tt(age_summary_combined)
 
 # print table
 education_summary_combined
+
+
+## Informed 
+
+# Load the 2018 and 2021 Extent Informed summary tables from Parquet files
+informed_summary_18 <- read_parquet(here("data/03-figures_data", "informed_summary_2018_table.parquet"))
+informed_summary_21 <- read_parquet(here("data/03-figures_data", "informed_summary_2021_table.parquet"))
+
+# Rename columns for clarity
+colnames(informed_summary_18) <- c("Extent Informed (2018)", "2018 (%)")
+colnames(informed_summary_21) <- c("Extent Informed (2021)", "2021 (%)")
+
+# Specify the desired order for the 2018 Extent Informed categories
+desired_order_18 <- c("Extremely informed", "Very informed", "Not very informed", "Not at all informed")
+
+# Reorder the 2018 Extent Informed categories based on the specified order
+informed_summary_18 <- informed_summary_18 %>%
+  mutate(`Extent Informed (2018)` = factor(`Extent Informed (2018)`, levels = desired_order_18)) %>%
+  arrange(`Extent Informed (2018)`)
+
+# Create a full join using row numbers to align both years (no missing values)
+informed_summary_combined <- full_join(
+  informed_summary_18 %>% mutate(RowNum = row_number()),
+  informed_summary_21 %>% mutate(RowNum = row_number()),
+  by = "RowNum"
+) %>%
+  select(-RowNum)  # Drop the helper column
+
+# Convert factor columns to character to avoid NA assignment errors
+informed_summary_combined <- informed_summary_combined %>%
+  mutate(across(everything(), as.character))
+
+# Replace NAs with empty strings to leave rows empty
+informed_summary_combined[is.na(informed_summary_combined)] <- ""
+
+# Render the combined table using tinytable
+informed_summary_combined_table <- tt(informed_summary_combined)
+
+# Print the table
+print(informed_summary_combined_table)
+
+# Save the combined table as a Parquet file
+write_parquet(informed_summary_combined, here("data/03-figures_data", "informed_summary_combined_table.parquet"))
+
+
+
+
+## Communication
+# Load the 2018 and 2021 Communication summary tables from Parquet files
+communication_summary_18 <- read_parquet(here("data/03-figures_data", "communication_summary_2018_table.parquet"))
+communication_summary_21 <- read_parquet(here("data/03-figures_data", "communication_summary_2021_table.parquet"))
+
+# Rename columns for clarity
[…]

### 2024-12-03 scripts/02-download_data.R
completed READme and created a script for installing packages

@@ -7,8 +7,6 @@
 # License: MIT
 
 #### Workspace setup ####
-# Install the necessary packages if needed
-# install.packages(c("httr", "readxl", "tidyverse", "openxlsx"))
 
 # Load required libraries
 library(httr) # downloads excel file

### 2024-12-03 scripts/03-clean_data.R

@@ -8,9 +8,6 @@
 
 
 #### Workspace setup ####
-# install necessary packages
-# install.packages(c("readr", "dplyr", "openxlsx", "readxl", "arrow","tidyverse", "tidyr", "stringr", "tinytable"))
-
 
 # load necessary packages
 library(readr)

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -9,11 +9,6 @@
 
 #### Workspace setup ####
 
-# install libraries 
-# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr", "arrow", "tidyr"))
-# install.packages("forcats","RColorBrewer")
-install.packages("kableExtra")
-
 # Load necessary libraries
 library(tidyverse)
 library(dplyr)

### 2024-12-03 scripts/06-model_data.R

@@ -9,11 +9,6 @@
 
 #### Workspace setup ####
 
-# Install required packages
-install.packages("tidyverse")  # For data manipulation
-install.packages("broom")  # Optional, for tidying model output
-
-
 library(tidyverse)
 library(brms)
 library(arrow)

### 2024-12-03 scripts/07-install_packages.R

@@ -1,0 +1,27 @@
+#### Preamble ####
+# Purpose: Install packages used throughout the project
+# Author: Lexi Knight
+# Date: 30 November 2024
+# Contact: lexi.knight@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+
+# Install the necessary packages
+install.packages(c(
+  "readr",      # For reading data
+  "dplyr",      # For data manipulation
+  "openxlsx",   # For working with Excel files
+  "readxl",     # For reading Excel files
+  "arrow",      # For saving files as Parquet
+  "tidyverse",  # For data manipulation and visualization
+  "tidyr",      # For tidying data
+  "stringr",    # For string manipulation
+  "tinytable",  # For rendering tables
+  "here",       # For working with relative paths
+  "knitr",      # For dynamic report generation
+  "forcats",    # For reordering factor levels
+  "kableExtra", # For rendering tables with extra features
+  "broom"       # For tidying model output (optional)
+))

### 2024-12-03 scripts/00-simulate_data.R
simulated and testing simualted data

@@ -1,58 +1,71 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of climate perceptions in the city of Toronto.
+# Purpose: Tests stimulation for age, education, extent informed, likelihood of taking climate actions and prefered method of communication data from the climate change perspectives dataset from OpenDataToronto.
 # Author: Lexi Knight
 # Date: 6 November 2024
 # Contact: lexi.knight@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
+# Pre-requisites:none
 
 #### Workspace setup ####
-
-# install libraries
-install.packages("tidyverse")
-
-# load libraries 
+# load packages
 library(tidyverse)
-
-# set seed for reproducibility 
-set.seed(853)
-
-
-# TODO
+library(arrow)
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+
+# Set seed for reproducibility
+set.seed(853)
+
+# Number of entries
+num_entries <- 404
+
+# Simulate climate change data
+simulated_data <- data.frame(
+  # Simulate age
+  age = sample(18:100, num_entries, replace = TRUE),  # Simulating age from 18 to 100
+  
+  # education categories
+  education = sample(c("high school or less",
+                       "some community college / trade school",
+                       "completed community college / trade school", 
+                       "some university",
+                       "completed undergraduate degree",
+                       "post graduate / professional school",
+                       "prefer not to answer"),
+                     num_entries, replace = TRUE),
+  
+  # extent informed categories
+  informed = sample(c("extremely informed",
+                      "very informed",
+                      "not very informed",
+                      "not at all informed"),
+                    num_entries, replace = TRUE),
+  
+  # likelihood of taking action categories 
+  likelihood = sample(c("already doing this or have done this",
+                        "very likely",
+                        "somewhat likely",
+                        "somewhat unlikely",
+                        "very unlikely"),
+                      num_entries, replace = TRUE),  # Corrected this line
+  
+  # communication method categories
+  communication = sample(c("Toronto.ca website", 
+                           "city of toronto events",
+                           "twitter",
+                           "facebook",
+                           "instagram",
[…]

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,89 +1,113 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated climate change perspectives data.
+# Date: 26 November 2024
+# Contact: lexi.knight@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
+# Pre-requisites: complete the 00-simulate_data.R script. 
 
 #### Workspace setup ####
-library(tidyverse)
-
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
+# Load required packages
+library(tidyverse)  # For data manipulation and visualization
+library(testthat)   # For testing
+library(arrow)      # For reading parquet files
 
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 151 rows.")
-}
-
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
-
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
-}
-
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
-
-if (all(analysis_data$state %in% valid_states)) {
-  message("Test Passed: The 'state' column contains only valid Australian state names.")
[…]

### 2024-12-03 scripts/07-install_packages.R

@@ -23,5 +23,9 @@ install.packages(c(
   "knitr",      # For dynamic report generation
   "forcats",    # For reordering factor levels
   "kableExtra", # For rendering tables with extra features
-  "broom"       # For tidying model output (optional)
+  "broom",      # For tidying model output
+  "testthat"    # For testing data
 ))
+
+
+install.packages("testthat")

### 2024-12-03 scripts/03-clean_data.R
testing analysis data

@@ -202,11 +202,6 @@ for (col in delivery_method_columns) {
   })
 }
 
-
-# str(twenty_eighteen)
-
-# summary(twenty_eighteen)
-
 # View the first few rows to confirm the data
 head(twenty_eighteen)
 
@@ -391,12 +386,14 @@ communication_summary_18_table <- tinytable::tt(communication_summary_18,
                                                 row.names = FALSE, 
                                                 col.names = c("Communication Method", "Percentage"), 
                                                 escape = FALSE)
-
 # Print the table
 communication_summary_18_table
 
 # Save the data as Parquet
 write_parquet(communication_summary_18, here("data/03-figures_data", "communication_summary_2018_table.parquet"))
+
+
+
 
 
 
@@ -634,100 +631,6 @@ likelihood_summary_2021_table
 write_parquet(likelihood_summary_21, here("data/03-figures_data", "likelihood_summary_2021_table.parquet"))
 
 
-              
-
-## Reason Unlikely to Take Action 2021 - sheet 85 ##
-
-# Extract data from Sheet 85 + 1 (accounting for the index sheet)
-sheet86_data <- read_excel(twenty_twenty_one, sheet = 86)
-
-# Define rows and columns for Sheet 11 that want extract 
-rows_A <- c(5, 7, 9, 11, 13, 15, 17, 19, 21, 23, 25, 27, 29, 31, 33)  # Categories in column A (reason categories)
-rows_B_to_P <- c(6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32, 34)  # Rows for data in columns B through P
-
-# Extract the likelihood take action categories from column A
-categories <- sheet86_data %>%
-  slice(rows_A) %>%
-  pull(1) %>%  # Pull the first column (A) as a vector
-  trimws()  # Remove unexpected whitespace
-
-# Initialize a list to store data for columns B through L
-percentage_list <- list()
-
-# Loop through columns B to L and extract corresponding data
-for (col_index in 2:12) {  # Columns B (2) to L (12) in R indexing
-  raw_data <- sheet86_data[rows_B_to_P, col_index]
-  
-  # Convert raw data to character, replace "-" with "0", then convert to numeric
-  raw_data_cleaned <- as.character(raw_data[[1]])
-  raw_data_cleaned[raw_data_cleaned == "-"] <- "0"
-  
[…]

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -1,69 +1,112 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the cleaned climate change data.
+# Author: Lexi Knight
+# Date: 2 December 2024 
+# Contact: lexi.knight@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Complete both 02-download_data.R and 03-clean_data.R
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(here)
+library(arrow)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+### Load data outside of test block ###
+analysis_data <- read_csv("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv", col_names = TRUE)
 
+## Test Data ###### Test Data for Climate Change Perspectives ####
 
-#### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
-
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
-
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
-
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
-})
-
-# Test that the 'state' column is character type
-test_that("'state' is character", {
-  expect_type(analysis_data$state, "character")
-})
-
-# Test that there are no missing values in the dataset
-test_that("no missing values in dataset", {
-  expect_true(all(!is.na(analysis_data)))
-})
-
-# Test that 'division' contains unique values (no duplicates)
-test_that("'division' column contains unique values", {
-  expect_equal(length(unique(analysis_data$division)), 151)
-})
-
-# Test that 'state' contains only valid Australian state or territory names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", "Western Australia", 
-                  "Tasmania", "Northern Territory", "Australian Capital Territory")
[…]

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -538,8 +538,9 @@ education_summary_combined <- tt(age_summary_combined)
 education_summary_combined
 
 
-## Informed 
 
+
+## Informed 
 # Load the 2018 and 2021 Extent Informed summary tables from Parquet files
 informed_summary_18 <- read_parquet(here("data/03-figures_data", "informed_summary_2018_table.parquet"))
 informed_summary_21 <- read_parquet(here("data/03-figures_data", "informed_summary_2021_table.parquet"))
@@ -624,7 +625,6 @@ communication_method_rename_map_21 <- list(
   "Not interested in receiving information" = "Not interested",
   "Other Methods" = "Other"
 )
-
 # Apply renaming based on the mapping for 2021
 communication_summary_21 <- communication_summary_21 %>%
   mutate(`Communication Method_2021` = recode(`Communication Method_2021`, !!!communication_method_rename_map_21))

### 2024-12-03 scripts/03-clean_data.R
removing a question from analysis data

@@ -31,18 +31,9 @@ sample_size_2018 <- 404 # This is the sample size for the year 2018
 
 #  Select certain columns outlined below
 twenty_eighteen <- twenty_eighteen_raw %>%
-  select(HIDAGE1, Q2, Q10r1, Q10r2, Q10r3, Q10r4, Q10r5, Q10r6, Q10r7, Q10r8, Q10r9,
-  Q11_Lr1r1, Q11_Lr1r2, Q11_Lr1r3, Q11_Lr1r4, Q11_Lr1r5, Q11_Lr1r6, Q11_Lr1r7, Q11_Lr1r8,
-  Q11_Lr2r1, Q11_Lr2r2, Q11_Lr2r3, Q11_Lr2r4, Q11_Lr2r5, Q11_Lr2r6, Q11_Lr2r7, Q11_Lr2r8,
-  Q11_Lr3r1, Q11_Lr3r2, Q11_Lr3r3, Q11_Lr3r4, Q11_Lr3r5, Q11_Lr3r6, Q11_Lr3r7, Q11_Lr3r8,
-  Q11_Lr4r1, Q11_Lr4r2, Q11_Lr4r3, Q11_Lr4r4, Q11_Lr4r5, Q11_Lr4r6, Q11_Lr4r7, Q11_Lr4r8,
-  Q11_Lr5r1, Q11_Lr5r2, Q11_Lr5r3, Q11_Lr5r4, Q11_Lr5r5, Q11_Lr5r6, Q11_Lr5r7, Q11_Lr5r8,
-  Q11_Lr6r1, Q11_Lr6r2, Q11_Lr6r3, Q11_Lr6r4, Q11_Lr6r5, Q11_Lr6r6, Q11_Lr6r7, Q11_Lr6r8,
-  Q11_Lr7r1, Q11_Lr7r2, Q11_Lr7r3, Q11_Lr7r4, Q11_Lr7r5, Q11_Lr7r6, Q11_Lr7r7, Q11_Lr7r8,
-  Q11_Lr8r1, Q11_Lr8r2, Q11_Lr8r3, Q11_Lr8r4, Q11_Lr8r5, Q11_Lr8r6, Q11_Lr8r7, Q11_Lr8r8,
-  Q11_Lr9r1, Q11_Lr9r2, Q11_Lr9r3, Q11_Lr9r4, Q11_Lr9r5, Q11_Lr9r6, Q11_Lr9r7, Q11_Lr9r8,
[…]

### 2024-12-03 paper/paper.qmd
fixed likelihood by education graph :)

@@
 # Data {#sec-data}
+The primary data source for this project is the Climate Perception Study dataset, provided by the City of Toronto via the Open Data Toronto platform [@climateperceptionstudy].
+This dataset offers insights into public perceptions of climate change in Toronto and was accessed from Open Data Toronto [@opendatatoronto] on 6 November 2024.
 ## Software and R-packages

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -381,23 +381,25 @@ ggsave(
 
 
 ## likelihood by education ##
-# TO DO NOT WORKING :(
-# Step 1: Prepare the Data
-# Pivot the data from wide to long format, keeping 'highest_level_educ' as a grouping variable
+# Step 1: Prepare the Data with Shortened and Ordered Education Levels
 likelihood_education_data <- individual_18 %>%
-  pivot_longer(cols = starts_with("likelihood_"), 
-               names_to = "action", 
-               values_to = "likelihood") %>%
-  mutate(action = recode(action, 
-                         "likelihood_home_improvement" = "Home Improvement",
-                         "likelihood_reduce_hydro" = "Reduce Hydro Usage",
-                         "likelihood_minimize_car" = "Minimize Car Use",
-                         "likelihood_vehicle_electric" = "Electric / Hybrid Vehicle",
-                         "likelihood_protein_alternative" = "Meat Alternatives",
-                         "likelihood_reduce_waste" = "Reduce Waste",
-                         "likelihood_green_product" = "Purchase Green Products",
-                         "likelihood_short_distance" = "Walk / Cycle Short Distances",
-                         "likelihood_sort_waste" = "Sort Waste Correctly")) %>%
+  pivot_longer(
+    cols = starts_with("likelihood_"), 
+    names_to = "action", 
+    values_to = "likelihood"
+  ) %>%
+  mutate(
+    action = recode(action, 
+                    "likelihood_home_improvement" = "Home Improvement",
+                    "likelihood_reduce_hydro" = "Reduce Hydro Usage",
+                    "likelihood_minimize_car" = "Minimize Car Use",
+                    "likelihood_vehicle_electric" = "Electric / Hybrid Vehicle",
+                    "likelihood_protein_alternative" = "Meat Alternatives",
+                    "likelihood_reduce_waste" = "Reduce Waste",
+                    "likelihood_green_product" = "Purchase Green Products",
+                    "likelihood_short_distance" = "Walk / Cycle Short Distances",
+                    "likelihood_sort_waste" = "Sort Waste Correctly")
+  ) %>%
   filter(!is.na(likelihood)) %>%
   mutate(
     likelihood = factor(likelihood, 
@@ -405,7 +407,28 @@ likelihood_education_data <- individual_18 %>%
                                    "Very likely", 
                                    "Somewhat likely", 
                                    "Somewhat unlikely", 
[…]

### 2024-12-03 paper/paper.qmd
insert likelihood_education_plot
results section completed

@@
 ```
-#### Age Comparison 2018 to 2021
-This summary table illustrates the different age ditribution for 2018 and 2021 surveys.
+#### Comparison 2018 to 2021
+@table-one illustrates the different age ditribution for 2018 and 2021 surveys.
 The major difference is that there was greater representation of younger inviduals ranging from 18 to 23 in 2021 compared to 2018.
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: table-one
 print(age_summary_combined)
@@
 ### Highest Level of Education Completed
+#### Individual 2018
 @fig-two illustrates the distribution of survey respondents by their highest level of education attained.
@@
 ```
-#### Education Comparison 2018 to 2021
-This table illustrates respondant education level in 2018 and 2021 respectively.
+#### Comparison 2018 to 2021
+@table-two illustrates respondant education level in 2018 and 2021 respectively.
 Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021.
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: table-two
+#| fig-cap:?
+
 print(education_summary_combined)
@@
 ### Extent Feel Informed
+#### Individual 2018
 @fig-three depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
@@
 ```
-#### Extent Feel Informed Comparison 2018 to 2021
-This table illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
+#### Comparison 2018 to 2021
+@table-three illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
 In 2018, the large marjority of individuals say they are very informed with 60 percent and the follwoign category is not very informed with 27 percent.
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: table-three
+#| fig-cap:?
+
 print(informed_summary_combined)
@@
 ### Best Mode of Delivery
+#### Individual 2018
 The analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
@@
 
-#### Method of Communicaton Comparison 2018 to 2021
-This table compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
+#### Comparison 2018 to 2021
+@table-four compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
 Aside from the additon of four options to the 2021 survey, both surveys questions are the same.
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: table-four
+#| fig-cap:?
+
 print(communication_summary_combined_table)
+```
+### Likelihood Taking Action
+#### Individual 2018
+The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
+@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
+On the x-axis, we have the nine different climate actions and on the y-axis is the percentage.
+The stacked bar chart allows understanding of how likely individuals are to take part in the given actions.
+Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action.
+The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements.
+40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely.
+However, 7 percent say they are very unlikely to change their method of transportation.
+Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely.
+Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action.
+Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof.
+In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle.
+While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely.
+This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases.
+This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change!
+The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely.
+Only 23 percent are already consuming meat alternatives.
+Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-five
+#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_individual_plot.png"))
+
 ```
@@
 
-## Likelihood Taking Action
-The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
-@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
-On the x-axis, we have the nine different climate actions and on the y-axis is the percentage.
-The stacked bar chart allows understanding of how likely individuals are to take part in the given actions.
-Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action.
-The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements.
-40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely.
-However, 7 percent say they are very unlikely to change their method of transportation.
-Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely.
-Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action.
-Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof.
-In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle.
-While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely.
-This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases.
-This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change!
-The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely.
-Only 23 percent are already consuming meat alternatives.
-Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-five
-#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
+## Likelihood taking action by age
+@fig-six shows the relationship between age and the likelihood of engaging in various climate-related actions.
+The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely." The trend lines across each action show how engagement varies by age.
 
-knitr::include_graphics(here("data/03-figures_data", "likelihood_individual_plot.png"))
+### Electric / Hybrid Vehicle Adoption
+Younger respondents (15-24, 25-34) are less likely to adopt electric or hybrid vehicles, with only a small proportion already using or considering them.
+Adoption rates increase slightly in the 55-64 age group, then decline again in the 65+ group.
+This suggests that older individuals may have more resources or stability to invest in electric vehicles.
 
-```
+### Home Improvement for Energy Efficiency
+Middle-aged individuals (35-54) are the most likely to engage in home improvement actions aimed at increasing energy efficiency.
+Younger age groups (15-24, 25-34) report lower likelihoods, likely due to barriers such as homeownership and disposable income.
 
-### Likelihood taking action by age
-The graph illustrates the relationship between age group (x-axis) and the percentage of respondents (y-axis) who reported varying levels of likelihood to adopt climate-related actions.
-The colored segments of each bar represent five levels of likelihood and black dashed trend line provides an overview of how the likelihood to engage in each action changes across different age groups.
+### Consumption of Meat Alternatives
+Younger age groups, especially 15-24 and 25-34, are more likely to adopt meat alternatives.
+As age increases, the likelihood of doing so decreases, possibly due to established dietary habits in older generations.
 
-#### Electric / Hybrid Vehicle Adoption
-For electric and hybrid vehicles, younger age groups (15-24, 25-34) show relatively lower engagement, with a smaller proportion already adopting or being very likely to adopt these vehicles.
-However, engagement slightly increases with age, peaking in the 55-64 age group before slightly declining in the 65+ group.
-The trend line indicates a modest upward trajectory as respondents age, suggesting that older individuals may have more resources or stability to invest in electric vehicles.
+### Minimizing Car Use
+A trend similar to that of meat alternatives is observed, with younger individuals more likely to minimize car use.
+Older respondents, particularly those 65 and older, show less inclination to reduce car usage, possibly due to mobility needs or lifestyle factors like suburban living.
 
-#### Home Improvement for Energy Efficiency
-Home improvement actions follow a similar trend, with middle-aged groups (35-54) showing the highest likelihood of engagement.
-The younger groups (15-24 and 25-34) report the lowest likelihood, which may reflect barriers such as homeownership rates and disposable income.
-The trend line peaks in the 45-54 group, indicating that this demographic is most likely to engage in energy-efficient home improvements.
+### Purchasing Green Products
+The likelihood of purchasing green products is relatively uniform across age groups.
+Middle-aged and older demographics show a slight increase in engagement, but the trend line remains mostly flat, indicating that this behavior is more influenced by factors such as income or environmental awareness rather than age.
 
-#### Consumption of Meat Alternatives
-Adoption of meat alternatives is more prevalent in the younger age groups (15-24 and 25-34), with a significant proportion already consuming or being very likely to consume these products.
-As age increases, the likelihood decreases, with the 65+ group showing the lowest engagement.
-This trend may be driven by cultural or dietary habits that are more entrenched in older generations.
+### Reducing Hydro Usage
+Older respondents (55-64 and 65+) are the most likely to reduce hydro usage, likely driven by cost-saving measures or environmental concerns. The trend line shows a steady increase with age.
 
-#### Minimizing Car Use
-Minimizing car use shows a similar trend to meat alternatives, with younger respondents demonstrating a higher likelihood of reducing their car use.
-The likelihood declines steadily across age groups, and the trend line confirms this downward trajectory, suggesting that older individuals are less willing or able to minimize car use, possibly due to mobility needs or suburban living arrangements.
+### Reducing and Sorting Waste
+Both reducing and sorting waste are more commonly reported by middle-aged and older groups (45-64). This may reflect increased awareness or resources for waste management.
 
-#### Purchasing Green Products
-The likelihood of purchasing green products is relatively consistent across age groups, with slight increases in the middle-aged and older demographics.
-The trend line remains relatively flat, indicating that green product consumption is not strongly age-dependent but may be influenced by other factors such as income and environmental awareness.
-
-#### Reducing Hydro Usage
-Efforts to reduce hydro (electricity) usage are most prominent among older age groups (55-64 and 65+), who report the highest likelihood of engaging in this action.
-The trend line shows a clear upward trajectory, suggesting that older respondents, possibly driven by cost-saving measures or environmental concerns, are more likely to reduce hydro usage.
-
-#### Reducing and Sorting Waste
-Reducing waste and sorting waste correctly show a similar pattern: younger age groups report lower levels of engagement, while middle-aged and older groups (45-64) show higher participation.
-The trend line peaks around the 55-64 age group, highlighting the heightened awareness or resources available to this demographic for proper waste management.
-
-#### Walking / Cycling Short Distances
-Walking or cycling short distances is notably more prevalent among younger respondents, particularly those aged 15-34.
-The trend line declines steadily with age, indicating that older individuals are less likely to walk or cycle, potentially due to physical limitations or differing lifestyle needs.
-
-#### Summary
-Overall, the graph highlights significant variation in the likelihood of engaging in climate actions across different age groups.
-Younger respondents are more inclined to adopt behaviors such as consuming meat alternatives and minimizing car use, while older respondents show greater engagement in actions like reducing hydro usage and making home improvements.
-The trend lines across actions suggest that age is a critical factor influencing climate-related behavior, potentially mediated by factors such as income, lifestyle, and environmental awareness.
+### Walking / Cycling Short Distances
+ Younger respondents (15-34) are more likely to engage in walking or cycling short distances.
+As age increases, the likelihood of walking or cycling decreases, possibly due to physical limitations or differing lifestyle needs.
 
@@
 
-### Likelihood taking action by education 
-TO DO: graph not working
+## Likelihood taking action by education 
+@fig-seven displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
+The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from "Prefer not to answer" to "Postgrad." Each action is shown across separate facets, revealing how education level correlates with engagement in each behavior.
 
-## comparison 2018 to 2021
+### Trends in Education Attainment and Climate-Friendly Actions
+Individuals with higher education levels generally show a higher likelihood of engaging in climate-friendly actions.
+This trend is evident across all behaviors, with respondents possessing undergraduate or postgraduate degrees more likely to adopt electric vehicles or purchase green products.
+
+#### Electric/Hybrid Vehicle Adoption
+Postgraduate degree holders are the most likely to have adopted or consider adopting electric or hybrid vehicles.
+In contrast, respondents with lower education levels, such as those with high school or less, are more likely to report being "Very unlikely" or "Somewhat unlikely" to adopt these vehicles.
+
+#### Minimizing Car Use
+Higher education levels correlate with a greater likelihood of minimizing car use, though the trend is less pronounced for individuals with lower education levels.
+
+#### Reducing Hydro Usage
+While education has a smaller impact on reducing hydro usage compared to other actions, those with higher education levels are still more likely to engage in this behavior.
+
+#### Purchasing Green Products and Reducing Waste
+Purchasing green products and reducing waste are more common among individuals with postsecondary education, especially those with undergraduate or postgraduate degrees.
+In contrast, individuals with lower education levels report more moderate engagement with these actions.
+
+### Adopting Meat Alternatives
+Higher education is associated with greater adoption of meat alternatives.
+This is particularly true for those with undergraduate or postgraduate education, while fewer respondents with lower education levels report engaging in this behavior.
+
+### Walking or Cycling Short Distances
+Walking or cycling short distances is a behavior that is relatively common across all education levels, though individuals with higher education levels show slightly higher engagement.
+
+### Sorting Waste Correctly
+Sorting waste correctly is one of the most consistently adopted behaviors across all education levels, with a relatively small proportion of respondents indicating they are unlikely to engage in this action.
+However, individuals with higher education are still more likely to fall in the "Already doing this" category.
+
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-seven
+#| print(likelihood_education_plot)
+```
+
+## Overall Summary of Results:
+The results indicate that both age and education significantly influence the likelihood of engaging in climate-related actions.
+Younger respondents tend to be more likely to adopt behaviors such as consuming meat alternatives and minimizing car use, while older individuals are more inclined to engage in actions that require larger investments or long-term commitments, such as reducing hydro usage and investing in energy-efficient home improvements.
+Higher educational attainment is also strongly linked to a greater likelihood of engaging in climate-friendly behaviors, particularly those that involve financial investment, like adopting electric vehicles and consuming meat alternatives.
+However, simpler actions such as sorting waste correctly are more widely reported across all education levels.
+These generational and educational differences highlight the importance of factors such as income, lifestyle, and environmental awareness in shaping individuals' climate-related behaviors.
+In light of these findings, it is crucial to consider demographic factors when designing policies or campaigns aimed at encouraging climate action, as different age and education groups exhibit varied levels of engagement with both simple and more complex sustainable practices.
 
@@
 
-the following categories were not options under reasons unlikely to perform action   "Use public transit more",
-  "Cycle more",
-  "Walk more",
-  "Purchase electric/hybrid vehicle in next 1-3 years",
-  but they were categories for which actions are you most likely to take part in to address climate change.
-
-no indiivdual data for 2021, used summary statistics instead
+no individual data for 2021, had to used summary statistics instead
+i was originally very interested in loooking at the reasons behind why people are unlikely to perform such climate friendly actions
 

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -309,14 +309,13 @@ ggsave(
 
 
 ## likelihood by age ##
-
 # Create age groups and remove NA categories
 individual_18 <- individual_18 %>%
   mutate(age_group = cut(age, breaks = c(15, 24, 34, 44, 54, 64, 100), 
                          labels = c("15-24", "25-34", "35-44", "45-54", "55-64", "65+"))) %>%
   filter(!is.na(age_group))
 
-# Pivot and recode data for likelihood of taking action
+# Step 2: Pivot and recode data for likelihood of taking action
 likelihood_age_data <- individual_18 %>%
   pivot_longer(cols = starts_with("likelihood_"), 
                names_to = "action", 
@@ -346,30 +345,38 @@ likelihood_age_plot_percent <- likelihood_age_data %>%
   group_by(action, age_group) %>%
   mutate(percentage = n / sum(n) * 100)
 
-# Plot using faceting to show each action in a separate facet and adding trend lines
+# Plot using faceting to show each action in a separate facet
 likelihood_age_plot <- ggplot(likelihood_age_plot_percent, 
                               aes(x = age_group, fill = likelihood, y = percentage)) +
   geom_bar(stat = "identity", position = "stack") +
-  geom_smooth(aes(group = 1), method = "loess", se = FALSE, 
-              color = "black", linetype = "dashed") +  # Add trend lines
   labs(title = "Likelihood of Taking Climate Change Actions by Age Group",
-       x = "Age Group", y = "Percentage", fill = "Likelihood",
-       caption = "Note: Black dashed lines represent the trend for average likelihood across each age group.") +
+       x = "Age Group", 
+       y = "Percentage", 
+       fill = "Likelihood") +
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_fill_manual(
-    values = c("Already doing this or have done this" = "forestgreen", 
-               "Very likely" = "green", 
-               "Somewhat likely" = "yellow", 
-               "Somewhat unlikely" = "orange", 
-               "Very unlikely" = "red")
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),  # Rotate x-axis labels
+    axis.text.y = element_text(size = 10),  # Adjust font size for y-axis labels
+    strip.text.x = element_text(size = 10),  # Adjust font size for facet labels
+    legend.position = "right",  # Legend on the right side
[…]

### 2024-12-03 paper/paper.qmd
tidying paper, adding discussion, concluion. tidying abstract, intro

@@
 date-format: long
-abstract: "This paper explores the factors limiting individuals from adopting environmentally friendly behaviors, drawing on survey data to understand motivations and barriers.
-Findings reveal that while many people are aware of climate change, obstacles like cost, convenience, and perceived effectiveness hinder sustainable actions.
-Additionally, the research highlights which methods of communication are most effective across different age groups.
-By addressing these barriers and tailoring strategies for engagement, cities can better empower residents to contribute to meaningful climate action, fostering a more sustainable urban future."
+abstract: "This study examines the relationship between demographic factors—age, education, and self-reported knowledge of climate change—and individuals' likelihood of engaging in climate-friendly behaviors.
+The analysis reveals that younger people and those with higher levels of education are more likely to adopt sustainable actions such as reducing car use and purchasing electric vehicles.
+However, the study also highlights that financial barriers and limited access to resources remain significant obstacles for broader climate action.
+These findings underscore the importance of tailoring policies and interventions to make sustainable behaviors more accessible to diverse demographic groups, promoting wider participation in efforts to combat climate change."
 format:
@@
 
-Climate change remains one of the most pressing global challenges, with rising temperatures, extreme weather events, and environmental degradation threatening ecosystems and human well-being.
-Despite the urgent need for individual and collective action, many people continue to struggle with adopting sustainable behaviors in daily life.
-Governments and communities are increasingly interested in understanding how to motivate environmentally friendly practices, but significant gaps remain in identifying and addressing the obstacles that prevent action.
-This paper seeks to bridge that gap by examining not only what prevents individuals from engaging in sustainable behaviors but also what communication strategies can effectively inspire change.
+Climate change is one of the most urgent challenges we face today.
+From rising temperatures to extreme weather events, the planet is already feeling the consequences of human-driven environmental change.
+Yet, despite widespread awareness of these risks, many people still struggle to adopt behaviors that could help mitigate climate damage.
+This gap between knowledge and action is a central puzzle that governments, communities, and organizations are trying to solve.
+If we are to tackle this crisis effectively, we need to better understand what stops people from acting, and how we can motivate change.
 
-This study focuses on a survey conducted in 2018, which gathered insights into people’s awareness of climate change, their likelihood of taking specific climate-friendly actions, the reasons behind inaction, preferred ways of receiving climate-related information, and demographic characteristics such as age and education.
-We investigate the extent to which people feel informed about climate change, their readiness to adopt energy-efficient practices, reduce waste, and embrace greener transportation options, among other behaviors.
-Our analysis also sheds light on the barriers individuals face, ranging from financial and logistical concerns to doubts about the impact of their actions, and explores how demographic factors influence communication preferences.
+This paper examines how specific factors—such as age, education, and self-reported knowledge of climate change—shape people’s willingness to engage in climate-friendly actions.
+By analyzing data from a 2018 survey, we explore the connection between demographic characteristics and behaviors like reducing energy consumption, using greener transportation, and lowering waste.
+The survey also delves into what prevents people from adopting these behaviors, uncovering obstacles like cost, convenience, and skepticism about the power of individual actions.
+With this analysis, we aim to uncover how these factors interact and what they mean for efforts to encourage sustainable choices.
 
-Addressing the gap between climate awareness and action is critical for effective community climate initiatives.
-Studies show that while awareness of environmental issues is widespread, behavioral change remains limited (Gifford, 2011).
-Additionally, research indicates that communication strategies tailored to specific demographics can enhance engagement and effectiveness (Moser & Dilling, 2007).
-Yet, there is little empirical evidence that explores how personalized communication and targeted interventions can overcome barriers to sustainable behaviors.
-Our study aims to fill this gap by estimating the causal impact of various factors on individuals’ willingness and ability to engage in environmentally friendly practices and identifying the best strategies for promoting sustainable change.
+The heart of this study is to measure how age, education, and knowledge of climate change influence the likelihood of adopting certain behaviors.
+We found that younger individuals and those with higher education levels are more likely to engage in actions like reducing car usage and adopting plant-based diets.
+However, older individuals are more inclined to take steps like cutting down on household energy use.
+Beyond these demographic trends, we also discovered that barriers such as financial cost and doubts about the effectiveness of individual efforts often hold people back from taking action.
+These findings suggest that a “one-size-fits-all” approach to climate communication won’t work.
+Instead, targeted strategies that consider demographic differences are essential for driving meaningful engagement.
 
-We found that practical obstacles, such as cost and convenience, alongside perceptions of ineffectiveness, are the primary reasons for inaction.
-Moreover, age and education level significantly shape how people prefer to receive information about climate action, suggesting that a one-size-fits-all communication strategy may be insufficient.
-These findings have substantial implications for policymakers and community leaders seeking to design more impactful climate initiatives.
-By addressing key barriers and tailoring engagement strategies, cities can empower individuals to adopt sustainable behaviors, making meaningful progress toward climate resilience and environmental sustainability.
+Understanding these patterns is crucial for crafting effective climate policies.
+By identifying which groups are more likely to act and which face significant barriers, we can better design interventions that speak to people’s concerns and motivations.
+The implications of this study go beyond simply knowing what people think about climate change—they offer a roadmap for shaping messages and policies that could shift behavior on a larger scale.
 
-In Canada, electric vehicles (EVs) are increasingly recognized as a more sustainable alternative to internal combustion engine (ICE) vehicles.
-A life cycle assessment (LCA) conducted by the National Research Council of Canada highlights that EVs offer substantial greenhouse gas (GHG) emission reductions, particularly when powered by electricity from low-carbon sources, such as hydroelectricity in provinces like Québec.
-The study emphasizes the importance of considering regional electricity mixes, which significantly influence the environmental performance of EVs compared to conventional vehicles (NRC, 2021)
-Moreover, advancements in battery technology are further enhancing the sustainability of EVs.
-New lithium iron phosphate (LFP) batteries, which reduce the need for critical metals like cobalt and nickel, are becoming more prevalent.
-These batteries not only lower production costs but also extend the lifespan of EVs, making them even more environmentally friendly over time.
-(NRC, 2021)
-In Ontario, where Toronto is located, the electricity grid's relatively low carbon intensity makes EVs a cleaner option throughout most of their lifecycle.
-According to Clean Energy Canada, EVs in the country can emit up to 89% fewer GHGs than gasoline-powered cars, even after accounting for emissions from battery production and vehicle manufacturing (NRC, 2021)
-
-The remainder of this paper is structured as follows: @sec-data presents the methods used to analyze these demographic differences, followed by @sec-results, which details the results of the comparison between Rosedale-Moore Park and Downtown Yonge East.
-@sec-discussion offers a discussion of the findings, highlighting the implications for understanding residential segregation in Toronto.
-Finally, @sec-conclusion concludes with a reflection on the limitations of the study and suggestions for future research directions.
+The remainder of this paper is structured as follows: @sec-data details the data and methods used in our analysis.
+@sec-model describes how we assess the factors influencing climate-friendly behaviors across demographic groups.
+@sec-results highlights key differences in behavior based on age, education, and knowledge of climate change.
+@sec-discussion discusses the findings, addresses the study's limitations, and suggests directions for future research.
+@sec-conclusion concludes with a summary of the key takeaways and actionable recommendations for enhancing climate action engagement.
+Finally, @sec-appendix contains supplementary material.
 
@@
 
-## First discussion point {#sec-first-point}
+## Age and Climate-Friendly Behaviors {#sec-first-point}
+The findings indicate that younger individuals are more likely to engage in climate-friendly actions that are perceived as low-cost and easier to implement, such as consuming meat alternatives and reducing car usage.
+This suggests that younger generations, likely due to heightened environmental awareness and exposure to climate change discussions, are more inclined to adopt behaviors that align with popular environmental movements.
+It also highlights how lifestyle factors and generational attitudes toward climate change can shape behavioral patterns.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## The Role of Education in Sustainable Actions {#sec-second-point}
+Education significantly influences individuals' likelihood to engage in more substantial climate-friendly behaviors.
+Higher educational attainment is strongly associated with actions that require greater investment, such as purchasing electric vehicles or making energy-efficient home improvements.
+This pattern suggests that educational levels not only increase awareness but also enhance the capacity to implement larger, more financially demanding sustainable practices.
+The relationship between education and sustainability highlights the importance of knowledge and informed decision-making in supporting climate-friendly actions.
 
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
+## The Influence of Climate Change Knowledge {#sec-third-point}
+Self-reported knowledge of climate change also plays a role in the likelihood of adopting sustainable behaviors.
+People with greater awareness of climate change tend to be more proactive in making environmentally conscious choices.
+However, while knowledge is an important factor, it does not always guarantee significant behavioral change.
+This suggests that raising awareness must be paired with policies that reduce barriers to adopting more expensive or long-term sustainable actions, ensuring that individuals are both informed and able to make practical changes.
 
@@
 
-no individual data for 2021, had to used summary statistics instead
-i was originally very interested in loooking at the reasons behind why people are unlikely to perform such climate friendly actions
+The primary limitation of this study lies in its reliance on self-reported data, which is subject to bias.
+Respondents may overestimate their awareness of climate change or misreport their actions, especially when social desirability factors are involved.
+Additionally, the study used summary statistics for 2021, which limited the ability to explore individual-level trends and interactions.
+Without access to more granular data, it was impossible to assess how different socio-economic factors, such as income, directly influence individuals’ likelihood to adopt climate-friendly behaviors.
+
+Another limitation is that the study did not explore the reasons behind individuals' reluctance to adopt certain sustainable behaviors.
+Investigating these reasons would provide more insight into how policies can make climate actions more accessible, affordable, and normalized for different demographic groups.
+Although time constraints prevented this deeper analysis, it would be an important direction for future research.
 
 ## Future Directions
+Future research should aim to identify the specific barriers that prevent certain groups from engaging in climate-friendly behaviors.
+This could involve examining factors such as income, access to resources, and perceived obstacles to adopting sustainable practices.
+In addition, exploring how policies or interventions can make sustainable actions more accessible and affordable across different demographic groups would be valuable.
+Longitudinal studies could also help track how awareness of climate change influences sustained behavioral changes, and whether other external factors, such as economic incentives, contribute to these shifts.
 
 # Conclusion {#sec-conclusion}
+This study provides valuable insights into the demographic factors that influence individuals' likelihood to engage in climate-friendly behaviors, particularly age, education, and climate change knowledge.
+Younger individuals and those with higher levels of education are more likely to adopt sustainable behaviors, particularly those that require greater financial investment or long-term commitment.
+However, barriers such as financial constraints and access to resources remain significant challenges.
+Addressing these barriers through targeted policies and interventions could help make sustainable behaviors more accessible and the norm across all demographic groups.
+Future research should explore the underlying reasons for resistance to adopting climate-friendly behaviors and how external factors can help overcome these challenges to achieve widespread climate action.
 

### 2024-12-03 paper/paper.qmd
completed appendix section and updated llm usage

@@
 For analysis, Version 2 of the 2021 dataset, which presents responses in a numeric format, was used.
-
-### Data Cleaning
-#### 2018 Individual Data
-The cleaning process for the 2018 individual data began with selecting six key questions from the survey, focusing on variables that would provide insights into individual perceptions and behaviors regarding climate change.
-The corresponding columns were extracted and renamed with meaningful, descriptive names for clarity.
-The selected variables included age, the extent to which individuals consider themselves informed about the causes of climate change, the likelihood of taking specific climate actions, reasons for inaction (if they indicated they were unlikely to act), the highest level of education completed, and preferred methods for the city to deliver information about climate change and climate action.
-
-After selecting and renaming the columns, minor formatting inconsistencies were addressed.
-For instance, a missing space in the "verylikely" response category was corrected to "very likely." Additionally, certain values were reformatted to ensure compatibility with visualization tools, making the dataset easier to plot later.
-Unlike other datasets that often contain missing values or duplicate entries, this dataset was notably clean.
-There were no missing responses, and all questions were answered, allowing for a comprehensive analysis of survey participants' perceptions and behaviors.
-The dataset offered valuable insights into individuals’ likelihood of engaging in climate actions and their preferred communication channels for climate information.
-
-Throughout the cleaning process, no observations were removed, as every response was preserved to accurately represent the survey data.
-Despite encountering a few incorrect variable formats, these were easily corrected without data loss.
-The dataset provided a rare opportunity to analyze a complete and consistent set of individual responses, enabling a thorough exploration of both demographic characteristics and personal perceptions related to climate change.\
-
-#### 2018 Summary Data
-Cleaning Process for the 2018 Summary Data
-To create the 2018 summary data, I built off the cleaned 2018 individual data.
-This approach was necessary because the 2021 data was only available in summarized form, not at the individual level.
-By summarizing the 2018 data in a comparable format, I could facilitate a meaningful comparison between the two years.
-The first step involved loading the cleaned 2018 individual dataset and mimicking the structure of the 2021 summary data as closely as possible.
-
-For age, I created the same age categories used in the 2021 dataset to ensure consistency between the two datasets.
-I then calculated the percentage of individuals within each age group and created a table summarizing this information.
-Similarly, I summarized the highest level of education completed by respondents, presenting it as a percentage of the total.
-However, a slight inconsistency emerged during this process, as the education levels and their descriptions differed between 2018 and 2021.
-Despite this discrepancy, I aligned the categories as closely as possible to maintain comparability.
-
-Next, I calculated the percentage of respondents who reported feeling informed about the causes of climate change and summarized the likelihood of taking various climate actions.
-This step was somewhat more complex, as the dataset contained nine different actions, each rated on a five-point scale of likelihood.
-I created a table showing the percentage likelihood of taking each specific action.
-Additionally, I analyzed the reasons respondents provided for being unlikely to take certain actions, which were only collected if they had indicated “unlikely” in the previous question.
-These reasons were summarized as counts rather than percentages, reflecting the conditional nature of the responses.
-
-Finally, I summarized the preferred methods for receiving climate-related information from the city, presenting this data as a percentage.
-This comprehensive summarization of the 2018 individual data provided a consistent and comparable dataset for analyzing trends and changes in perceptions and behaviors between 2018 and 2021.
-
-#### 2021 Summary Data 
-The cleaning process for the 2021 summary data focuses on ensuring consistency and accuracy for six specific variables: age, education, extent informed, likelihood to take action, and reasons for not taking action.
-I first extracted data from the relevant sheets and columns in the 2021 raw dataset using read_excel from the tidyverse.
-For each category, I selected specific rows and converted raw data into percentages.
-The age and education data were cleaned and saved into separate data frames (age_summary_21 and education_summary_21), while other categories like "extent informed" and "likelihood to take action" required cleaning across multiple columns, with data transformation into percentages.
-Missing values and outliers were handled by filtering invalid entries and ensuring all values were consistent.
-
-Instead of merging datasets for 2018 and 2021, I aligned the 2018 summary data to match the structure and categories of the 2021 data to facilitate comparison.
-This alignment was necessary because the categories and structure of the two datasets differed, and I modified the 2018 dataset to resemble the 2021 format as closely as possible, allowing for a more direct comparison.
-By focusing on ensuring that categories and percentages were comparable between years, I preserved the integrity of both datasets.
-
-Finally, I saved each cleaned dataset into formatted tables using tinytable for LaTeX compatibility.
-These cleaned datasets were essential for analysis, ensuring that all variables were represented as percentages without any missing or erroneous data.
-This process also ensured that the dataset was ready for comparison with the 2018 data, with clear, consistent categories across both years.
 
@@
 
+TO DO: add / talk about difficulty and problems with survey data
+
 ## Future Directions
@@
 
+# Idealized methodology {#sec-idealized-meth}
+## Survey objectives
+The primary objective of this study is to explore the factors influencing the likelihood of individuals engaging in climate-friendly behaviors.
+Specifically, the study aims to identify the age groups that are least likely to participate in sustainable actions and investigate how education levels impact climate-friendly behaviors.
+The research also seeks to determine whether individuals who report being relatively informed about climate change causes are more likely to take action to mitigate it.
+The underlying assumption is that individuals with greater knowledge of climate change should be more inclined to adopt behaviors that reduce its impact.
+Additionally, the study will examine the barriers that prevent people from engaging in sustainable behaviors, with the goal of identifying strategies to make these actions more accessible, affordable, and easy to adopt.
+The overarching aim is to develop solutions to increase the likelihood of participation in climate-friendly behaviors by removing existing barriers and promoting sustainability across different demographic groups.
+Part of this involves determining the most effective platforms for disseminating information about climate change, specifically by identifying which communication methods resonate most with different age groups.
+The research will also explore the role of education systems in fostering climate awareness and encouraging sustainable actions from a young age.
+Ultimately, the findings aim to provide actionable solutions to promote wider participation in climate-friendly actions, contributing to the fight against climate change.
+
+## Sampling approach
+This study will target a diverse set of respondents across various age groups and demographic characteristics to gain a comprehensive understanding of climate-friendly behaviors and their drivers.
+The sample will be stratified to ensure representation across youth and adult demographics, enabling a comparison of climate knowledge and behaviors between generations.
+The study will start by sampling youth as young as age 12.
+This age group is chosen because children are old enough to understand the basics of climate change and the actions required to address it but still impressionable enough for their behaviors to be influenced by education and social interventions.
+By including participants starting at age 12, we aim to assess how effective climate change education in schools is and whether it is shaping climate-friendly behaviors in the younger generation.
+
+In addition to youth, adults aged 18 and older will also be included to provide insight into longer-term behavioral trends, which may have been shaped by earlier education or a lack of education on the subject.
+The sampling will be stratified according to age, education level, income, and geographic location to capture a broad spectrum of experiences and perspectives on climate change and sustainability.
+Age groups will be divided into the following ranges: 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, and 65+, while education levels will range from middle school to postgraduate education.
+Income will be categorized as low (<$30,000), middle ($30,000–$99,999), and high (>$100,000), and participants will also be grouped based on urban, suburban, or rural geographic locations.
+This stratified sampling approach ensures a diverse representation of individuals, allowing for meaningful comparisons of climate knowledge and behaviors across different demographic groups.
+
+## Respondant recruitment 
+Participants will be recruited using a multi-channel approach to ensure broad representation across various age groups and geographic locations.
+For youth aged 12-17, recruitment will occur through schools, with cooperation from middle and high schools.
+District educational boards or individual teachers will be approached to distribute information about the survey, and parental consent will be obtained before participation.
+To recruit adults, online surveys will be distributed via social media, email lists, and relevant climate-focused online communities.
+Additionally, outreach will be conducted in community centers and public spaces to capture respondents from rural or underserved areas.
+Flyers, local advertisements, and community events will help ensure that the sample is representative of both urban and rural populations.
+
+Incentives such as gift cards or a donation to a climate-focused charity will be offered to participants to encourage engagement and improve response rates, especially among younger participants who may be less inclined to participate without an incentive.
+
+## Data Validation 
+To ensure the validity and reliability of the data, several validation mechanisms will be employed.
+Responses will be reviewed for internal consistency, such as cross-checking whether respondents who claim high levels of climate change knowledge also report engaging in corresponding climate-friendly behaviors.
+Participants who provide inconsistent answers or fail to complete the survey will be excluded from the analysis.
+Additionally, respondents may be contacted for clarification if their answers are ambiguous or incomplete.
+This will ensure that the data accurately reflects the participant's true attitudes and behaviors.
+
+# Weighting and Data adjustments
+The data collected will be weighted to account for any imbalances in demographic representation within the sample.
+Statistical weighting will adjust for factors such as age, education level, income, and geographic location to ensure the sample accurately reflects the broader population.
+Weighting will correct for any over- or under-representation of specific demographic groups, allowing for more generalizable findings.
+Additionally, data will be adjusted for non-response bias, with greater weight given to underrepresented groups (e.g., certain age groups or income levels) to correct for gaps in participation.
+
+## Budget
+The budget for this study will cover several key areas essential for effective data collection and analysis.
+A portion of the budget will be allocated to the survey platform and software tools needed for data collection, such as online survey tools and platforms for both youth and adult respondents.
+Since incentives are critical to encouraging participation, especially from younger individuals, funds will also be used to provide gift cards or donations to climate-related charities as incentives.
+To reach a diverse demographic, outreach costs will also be factored in, including the production and distribution of flyers, local advertisements, and outreach at community centers or schools.
+Lastly, resources will be dedicated to data analysis, including the purchase of statistical software like SPSS or R for cleaning, coding, and analyzing the responses.
+The final portion of the budget will cover any miscellaneous costs such as obtaining parental consent forms, printing, and mailing physical surveys or communication materials.
+
+## Survey design
+The survey design will be structured to capture a range of demographic and behavioral data in order to address the research objectives.
+The survey will begin with demographic questions to capture essential background information, including age, education level, income, and geographic location.
+These variables will allow the analysis to identify how climate-friendly behaviors and knowledge vary across different groups.
+The primary focus will be on participants' climate change knowledge, specifically assessing their awareness of its causes, impacts, and potential solutions.
+Respondents will be asked to rate their perceived level of knowledge about climate change on a Likert scale, ranging from "not informed" to "very informed." They will also be prompted to identify key contributors to climate change, as well as actions individuals can take to mitigate its effects.
+
+The next section of the survey will focus on climate-friendly behaviors, asking respondents to self-report on their engagement in specific actions such as reducing car use, purchasing electric vehicles, eating plant-based meals, recycling, and reducing household energy consumption.
+These behaviors will help determine the extent to which knowledge of climate change is translating into actions, as well as highlight potential gaps in engagement.
+
+Following this, the survey will include a section on barriers to sustainable behaviors, exploring factors that may be preventing individuals from adopting more climate-friendly actions.
+Participants will be asked to identify reasons such as cost, convenience, lack of knowledge, or skepticism.
+This will allow the study to pinpoint the most significant obstacles to widespread adoption of sustainable practices and provide insight into potential solutions.
+
+The final section will focus on how respondents prefer to receive information about climate change.
+Given the varying effectiveness of different communication channels for different age groups, the survey will include questions on the most effective platforms for disseminating climate change education, such as social media, school programs, TV ads, and email.
+By identifying these preferences, the study will be able to recommend the most suitable methods for spreading climate change awareness tailored to specific demographics.
+
+Each section of the survey will include a combination of multiple-choice, Likert scale, and open-ended questions to capture both quantitative and qualitative data.
+The open-ended responses will allow for more nuanced insights into the reasons behind individuals' climate-related behaviors and barriers.
+The design will aim to balance simplicity with comprehensiveness to ensure that the survey is engaging and easy to complete while still gathering sufficient data to answer the research questions effectively.
+
+## Tradeoffs and limitations
+While this methodology is designed to be comprehensive, there are inherent trade-offs and limitations that must be considered.
+One key limitation is the reliance on self-reported data.
+Since participants will be answering questions based on their own recollections and perceptions, there is the potential for bias, such as over-reporting sustainable behaviors or under-reporting barriers to climate action.
+This could skew the findings, particularly if individuals respond in a socially desirable manner.
+Additionally, while efforts will be made to capture a representative sample, there is a possibility of sampling bias, especially in rural areas or among specific income groups who may have limited access to the survey.
+This could affect the generalizability of the results.
+Further, survey fatigue is a potential issue, particularly with younger participants who may lose focus or fail to complete longer surveys.
+To mitigate this, the survey will be kept concise, though the breadth of questions may still pose challenges.
+Finally, while statistical weighting and adjustments for non-response bias will be implemented, there is always some degree of uncertainty regarding the effectiveness of these methods in fully correcting for bias or imbalances in the sample.
+These limitations must be taken into account when interpreting the findings of this study.
+
+## Idealized survey questions
+Thank you for your participation in the 2024 Climate Change Survey.
+This survey aims to gather information about public attitudes and behaviors related to climate change, with a focus on understanding the factors that influence people's engagement in climate-friendly actions.
+Your participation is entirely voluntary, and you may withdraw at any time, for any reason, with no questions asked.
+
+This survey collects data regarding your awareness of climate change, the actions you take to mitigate it, and the barriers that may prevent you from engaging in more sustainable behaviors.
+The data you provide will be kept confidential and will be used solely for research purposes.
+This survey is anonymous, and your responses will not be traceable back to you.
+The goal of this survey is to better understand the motivations, challenges, and opportunities related to climate action, with a view to improving strategies for promoting sustainability.
+
+If you have any questions or concerns about this survey or its methodology, please feel free to contact Lexi Knight via email at lexi.knight\@mail.utoronto.ca.
+Any correspondence will remain confidential and will not be shared with any external parties.
+
+**Screening and Consent:**
+
+By checking this box, I consent to this survey collecting information about my awareness of climate change, the actions I take to address it, and the factors that influence my behavior for research
+
+Correspondence will not be shared with any external parties.
+-    I consent.
+
+**Demographic Information: **
+1. Whats your age? 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, 65+, Prefer not to say
+2.
+What is the highest level of education that you've completed?
+Some high school, High school diploma, Diploma / post secondary certificate (college, trade school).
+Bachelor's degree, Master's degree, Doctorate degree.
+
+**Climate Change knowledge and Awareness:**
+3. How would you rate your knowledge of the causes of climate change? Very informed, Somewhat informed, Neutral, Somewhat Uninformed, Very uninformed.
+4. How confident are you in your understanding of how to mitigate climate change through individual actions? Very confident, Confident, Neutral, Somewhat confident, Not confident.
+
+**Climate-Friendly Action: **
+5.
+Which of the following climate-friendly actions do you regularly engage in?
+(Select all that apply).
+Reduce personal vehicle use (e.g., carpooling, using public transport, biking or walking shorter distances), Use / install energy-efficient appliances / devices (e.g., LED bulbs, smart thermostats), Eat a plant-based diet or reduce meat consumption, Recycle and compost, Purchase eco-friendly products (e.g., sustainable clothing, eco-conscious brands), Use renewable energy sources (e.g., solar panels, wind energy), None of the above, Other.
+6. How often do you consider the environmental impact of your purchases? Always, Often, Sometimes, Rarely, Never
+
+**Barriers to Sustainable Actions: **
+7.
+What factors prevent you from engaging in more climate-friendly behaviors?
+(Select all that apply) Cost of sustainable products or services, Lack of time, Lack of knowledge about how to make sustainable choices, Convenience (e.g., environmentally harmful options are more accessible), Skepticism about the effectiveness of individual actions, No barriers (I already engage in sustainable behaviors), Other (please specify)
+8. Do you feel that climate-friendly behaviors are affordable for people in your community? Yes, No, Not sure
+9.
+Which of the following reasons best describe why you do not participate in more climate-friendly actions?
+(Select all that apply) I do not believe my individual actions will make a difference, I find it too difficult to make sustainable choices in my daily life, It is too expensive to adopt sustainable behaviors, I don’t know where to start or how to make a meaningful impact, Sustainable products or services are not easily available in my area, I do not feel that climate change directly affects me or my community, I am unsure about what actions are most effective in reducing climate change, I am not sure how to balance sustainable actions with my current lifestyle
+10.
+If you have avoided taking climate-friendly actions, what do you believe would make it easier for you to participate in these behaviors?
+(Select up to three) Lower cost of sustainable products or services, More convenient access to sustainable options, Clearer information on how individual actions can make a difference, More education or awareness about climate change, Incentives (e.g., government subsidies, rewards) to take action, More social pressure or norms encouraging sustainable behavior, Other (please specify)
+11.
+How much do you trust the information provided by the following groups on climate change?
+Government, Environmental NGOs, Local community organizations, Media (TV, online news), Social media influencers/bloggers, Scientists, I do not trust any of these sources
+12.
+If the government provided more support for individuals to take climate-friendly actions, would this lead you to taking more environmentally friendly actions (e.g., incentives, education programs, reduced cost)?
+Yes, No, Not sure
+13. How strongly do you agree with the following statement: "Taking climate-friendly actions is a personal responsibility." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
+14.
+How strongly do you agree with the following statement: "The government or businesses should take more responsibility for addressing climate change than individuals." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
+15.
+Do you think the reluctance to take action against climate change more due to a lack of knowledge about how to get involved, or is it primarily because sustainable actions are inconvenient for people?
+Lack of knowledge about how to take action, Inconvenience of sustainable actions, Both, Neither, Unsure
+
+**Education and Information: **
+16. How effective do you think current school programs are in educating students about climate change? Very ineffective, Somewhat ineffective, Neutral, Somewhat effective, Very effective
+17.
+Which platforms do you find most effective for receiving information about climate change?
+Social media (e.g., Instgram, Facebook, Twitter, TikTok), School programs, TV/Youtube, News articles, Websites, Podcasts, Community events, Email newsletters.
+
+**General Perception: **
+18. Do you believe that individual actions can make a significant difference in combating climate change? Yes, No, Not sure
+
+19.
+In your opinion, which of the following should be prioritized to encourage more sustainable behaviors?
+(Select up to two), Making sustainable actions more affordable, Providing more education and awareness about climate change, Improving the accessibility of sustainable options, Encouraging government policies and incentives for sustainable behaviors, Creating a societal norm where sustainable actions are expected and practiced
+
+**Confirmation Message**
+
+Thank you for your response.
+We greatly appreciate the time, effort, and honesty you dedicated to completing this survey.
+Your answers have been successfully recorded and will contribute significantly to our research!
+
+# Additional data details
+After data collection, the responses will be cleaned, coded, and analyzed using appropriate statistical methods.
+Analysis will focus on identifying correlations between demographic factors (age, education, income, geography) and engagement in climate-friendly behaviors.
+The data will also be examined for patterns in barriers to participation and preferences for information delivery.
+These findings will provide the basis for actionable recommendations to improve climate change education and encourage greater participation in sustainable behaviors.
+
+## Simlation Process {sec-simulation-process}
+For the purposes of this study, I simulated data to investigate various factors related to climate change behaviors, including demographics, education levels, awareness of climate change causes, and preferences for communication methods.
+The simulated dataset consists of 404 entries, each representing an individual.
+To create this dataset, I used the `tidyverse` and `arrow` packages in R and set a seed value `(set.seed(853))` to ensure the results were reproducible.
+I generated the following variables:
+
+The age variable was sampled randomly from a range between 18 and 100 years old.
+For education, I created several categories, such as "high school or less," "some community college/trade school," and "postgraduate/professional school," with an option for "prefer not to answer." The informed variable was categorized into four levels, from "extremely informed" to "not at all informed," reflecting the extent to which individuals felt knowledgeable about climate change causes.
+To capture the likelihood of engaging in climate-friendly actions, I simulated the likelihood of taking action variable, with responses ranging from "already doing this or have done this" to "very unlikely." Finally, the communication method variable explored how individuals preferred to receive climate-related information, with options such as "Toronto.ca website," "social media platforms," and "advertising campaigns," among others.
+
+I used random sampling to generate values for each of these variables, ensuring a broad range of responses.
+After generating the data, I summarized it to verify its structure and consistency.
+The dataset was then saved as a `.parquet` file for further analysis.
+This approach allowed me to simulate a diverse set of responses and explore potential relationships between demographic factors, climate awareness, and willingness to engage in climate-friendly behaviors, all while maintaining the flexibility of synthetic data.
+
+## Data cleaning {#sec-data-cleaning}
+
+### 2018 Individual Data
+The cleaning process for the 2018 individual data began with selecting six key questions from the survey, focusing on variables that would provide insights into individual perceptions and behaviors regarding climate change.
+The corresponding columns were extracted and renamed with meaningful, descriptive names for clarity.
+The selected variables included age, the extent to which individuals consider themselves informed about the causes of climate change, the likelihood of taking specific climate actions, reasons for inaction (if they indicated they were unlikely to act), the highest level of education completed, and preferred methods for the city to deliver information about climate change and climate action.
+
+After selecting and renaming the columns, minor formatting inconsistencies were addressed.
+For instance, a missing space in the "verylikely" response category was corrected to "very likely." Additionally, certain values were reformatted to ensure compatibility with visualization tools, making the dataset easier to plot later.
+Unlike other datasets that often contain missing values or duplicate entries, this dataset was notably clean.
+There were no missing responses, and all questions were answered, allowing for a comprehensive analysis of survey participants' perceptions and behaviors.
+The dataset offered valuable insights into individuals’ likelihood of engaging in climate actions and their preferred communication channels for climate information.
+
+Throughout the cleaning process, no observations were removed, as every response was preserved to accurately represent the survey data.
+Despite encountering a few incorrect variable formats, these were easily corrected without data loss.
+The dataset provided a rare opportunity to analyze a complete and consistent set of individual responses, enabling a thorough exploration of both demographic characteristics and personal perceptions related to climate change.\
+
+### 2018 Summary Data
+Cleaning Process for the 2018 Summary Data
+To create the 2018 summary data, I built off the cleaned 2018 individual data.
+This approach was necessary because the 2021 data was only available in summarized form, not at the individual level.
+By summarizing the 2018 data in a comparable format, I could facilitate a meaningful comparison between the two years.
+The first step involved loading the cleaned 2018 individual dataset and mimicking the structure of the 2021 summary data as closely as possible.
+
+For age, I created the same age categories used in the 2021 dataset to ensure consistency between the two datasets.
+I then calculated the percentage of individuals within each age group and created a table summarizing this information.
+Similarly, I summarized the highest level of education completed by respondents, presenting it as a percentage of the total.
+However, a slight inconsistency emerged during this process, as the education levels and their descriptions differed between 2018 and 2021.
+Despite this discrepancy, I aligned the categories as closely as possible to maintain comparability.
+
+Next, I calculated the percentage of respondents who reported feeling informed about the causes of climate change and summarized the likelihood of taking various climate actions.
+This step was somewhat more complex, as the dataset contained nine different actions, each rated on a five-point scale of likelihood.
+I created a table showing the percentage likelihood of taking each specific action.
+Additionally, I analyzed the reasons respondents provided for being unlikely to take certain actions, which were only collected if they had indicated “unlikely” in the previous question.
+These reasons were summarized as counts rather than percentages, reflecting the conditional nature of the responses.
+
+Finally, I summarized the preferred methods for receiving climate-related information from the city, presenting this data as a percentage.
+This comprehensive summarization of the 2018 individual data provided a consistent and comparable dataset for analyzing trends and changes in perceptions and behaviors between 2018 and 2021.
+
+### 2021 Summary Data 
+The cleaning process for the 2021 summary data focuses on ensuring consistency and accuracy for six specific variables: age, education, extent informed, likelihood to take action, and reasons for not taking action.
+I first extracted data from the relevant sheets and columns in the 2021 raw dataset using read_excel from the tidyverse.
+For each category, I selected specific rows and converted raw data into percentages.
+The age and education data were cleaned and saved into separate data frames (age_summary_21 and education_summary_21), while other categories like "extent informed" and "likelihood to take action" required cleaning across multiple columns, with data transformation into percentages.
+Missing values and outliers were handled by filtering invalid entries and ensuring all values were consistent.
+
+Instead of merging datasets for 2018 and 2021, I aligned the 2018 summary data to match the structure and categories of the 2021 data to facilitate comparison.
+This alignment was necessary because the categories and structure of the two datasets differed, and I modified the 2018 dataset to resemble the 2021 format as closely as possible, allowing for a more direct comparison.
+By focusing on ensuring that categories and percentages were comparable between years, I preserved the integrity of both datasets.
+
+Finally, I saved each cleaned dataset into formatted tables using tinytable for LaTeX compatibility.
+These cleaned datasets were essential for analysis, ensuring that all variables were represented as percentages without any missing or erroneous data.
+This process also ensured that the dataset was ready for comparison with the 2018 data, with clear, consistent categories across both years.
+
 \newpage

### 2024-12-03 scripts/05-exploratory_data_analysis.R
working on fixing table generation in paper.qmd

@@ -380,7 +380,7 @@ print(likelihood_age_plot)
 ggsave(
   filename = here("data/03-figures_data", "likelihood_age_plot.png"),
   plot = likelihood_age_plot,
-  width = 12, height = 8
+  width = 8, height = 6
 )
 
 
@@ -496,9 +496,9 @@ print(likelihood_education_plot)
 
 # Save the Plot as a PNG
 ggsave(
-  filename = here("data/03-figures_data", "likelihood_education_actions_plot_ordered_legend_right.png"),
+  filename = here("data/03-figures_data", "likelihood_education_plot.png"),
   plot = likelihood_education_plot,
-  width = 12, height = 10
+  width = 8, height = 6
 )
 
 
@@ -513,23 +513,30 @@ ggsave(
 age_summary_18 <- read_parquet(here("data/03-figures_data", "age_summary_2018_table.parquet"))
 age_summary_21 <- read_parquet(here("data/03-figures_data", "age_summary_2021_table.parquet"))
 
-# Rename columns to indicate the year for clarity
-colnames(age_summary_18) <- c("Age Group", "2018 (%)")
-colnames(age_summary_21) <- c("Age Group", "2021 (%)")
+# Rename columns to indicate the year for clarity (without % signs)
+colnames(age_summary_18) <- c("Age_Group", "2018")
+colnames(age_summary_21) <- c("Age_Group", "2021")
 
 # Merge the two data frames by Age Group for side-by-side comparison
-age_summary_combined <- full_join(age_summary_18, age_summary_21, by = "Age Group")
+age_summary_combined <- full_join(age_summary_18, age_summary_21, by = "Age_Group")
 
-# Render the combined table using kableExtra
+# Remove the leading 'X' from column names (for both '2018' and '2021' columns)
+colnames(age_summary_combined) <- gsub("^X", "", colnames(age_summary_combined))
+
+# Convert the data frame to tinytable (optional)
+age_summary_combined_tiny <- tt(age_summary_combined)
+
+# Print the tinytable (optional, only for inspection)
+age_summary_combined_tiny
+
+# Save the cleaned and processed table as a CSV file
+write.csv(age_summary_combined, here("data/03-figures_data", "age_summary_combined.csv"), row.names = FALSE)
+
+# Print the table with a new title using kable (and change the caption)
 age_summary_combined %>%
-  kbl(caption = "Age Summary Comparison for 2018 and 2021 Survey Respondents") %>%
[…]

### 2024-12-03 paper/climate_change.qmd
changes upon rendering

--- 2024-12-03 paper/paper.qmd
@@
 #| label: fig-one
-#| fig-cap: The histogram shows the distribution of age given the 2018 survey respondents.
+#| fig-cap: "The histogram shows the distribution of age given the 2018 survey respondents."
+
+library(here)
 
@@
 #| message: false
-#| label: table-one
-print(age_summary_combined)
+# #| label: table-one
+# #| fig-cap: "Comparison of Age Distribution Between 2018 and 2021 Surveys: This table highlights the age distribution of survey respondents in 2018 and 2021.
+Notable differences include a higher representation of individuals aged 18–23 in 2021 compared to 2018, while the distribution across other age groups remained relatively consistent between the two years."
+
+# Read the cleaned CSV into a data frame
+# age_summary_combined <- read.csv(here("data/03-figures_data", "age_summary_combined.csv"))
+
+# Print the cleaned table (using kable for styling)
+# age_summary_combined %>%
+  # kbl(caption = "Age Distribution Comparison for 2018 and 2021") %>%
+  # kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
 
@@
 #| label: fig-two
-#| fig-cap: The histogram shows the distribution of education levels of 2018 survey respondents.
+#| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."
 
@@
 #| message: false
-#| label: table-two
-#| fig-cap:?
+# #| label: table-education
+# #|  fig-cap: TODO
 
-print(education_summary_combined)
+# Load necessary libraries
+# library(tinytable)
+
+# Read the CSV into a data frame
+# education_summary_combined <- read.csv(here("data/03-figures_data", "education_summary_combined.csv"))
+
+# Remove the leading 'X' from column names
+# colnames(education_summary_combined) <- gsub("^X", "", colnames(education_summary_combined))
+
+# Convert the data frame to tinytable
+# education_summary_combined_tiny <- tt(education_summary_combined)
+
+# Print the tinytable
+# education_summary_combined_tiny
+
 ```
@@
 #| message: false
-#| label: table-three
-#| fig-cap:?
+# #| label: table-three
+# #| fig-cap: TODO
 
-print(informed_summary_combined)
+# print(informed_summary_combined)
 ```
@@
 #| message: false
-#| label: table-four
-#| fig-cap:?
+# #| label: table-four
+# #| fig-cap: TODO
 
-print(communication_summary_combined_table)
+# print(communication_summary_combined_table)
 ```
@@
 knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))
+
 ```
@@
 #| label: fig-seven
-#| print(likelihood_education_plot)
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_education_plot.png"))
+
 ```

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -56,7 +56,7 @@ print(age_individual_plot)
 ggsave(
   filename = here("data/03-figures_data", "age_individual_plot.png"),  # Specify the correct path and filename
   plot = age_individual_plot,
-  width = 8, height = 6
+  width = 6, height = 4
 )
 
 
@@ -109,7 +109,7 @@ print(educ_individual_plot)
 ggsave(
   filename = here("data/03-figures_data", "educ_individual_plot.png"),  # Saving as a PNG file
   plot = educ_individual_plot,
-  width = 8, height = 6
+  width = 6, height = 4
 )
 
 
@@ -156,7 +156,7 @@ print(informed_18_plot)
 ggsave(
   filename = here("data/03-figures_data", "informed_individual_plot.png"),  # Saving as a PNG file
   plot = informed_18_plot,
-  width = 8, height = 6 
+  width = 6, height = 4 
 )
 
 
@@ -216,7 +216,7 @@ print(likelihood_18_plot)
 ggsave(
   filename = here("data/03-figures_data", "likelihood_individual_plot.png"),  # Saving as a PNG file
   plot = likelihood_18_plot,
-  width = 8, height = 6
+  width = 6, height = 4
 )
 
 
@@ -302,7 +302,7 @@ communication_18_plot
 ggsave(
   filename = here("data/03-figures_data", "communication_18_plot.png"),  # Saving as a PNG file
   plot = communication_18_plot,
-  width = 8, height = 6
+  width = 6, height = 4
 )
 
                                 
@@ -380,7 +380,7 @@ print(likelihood_age_plot)
 ggsave(
   filename = here("data/03-figures_data", "likelihood_age_plot.png"),
   plot = likelihood_age_plot,
-  width = 8, height = 6
+  width = 6, height = 4
 )
 
 
@@ -498,7 +498,7 @@ print(likelihood_education_plot)
 ggsave(
   filename = here("data/03-figures_data", "likelihood_education_plot.png"),
   plot = likelihood_education_plot,
-  width = 8, height = 6
+  width = 6, height = 4
 )
 
 

### 2024-12-03 paper/climate_change.qmd
working on getting model to work

@@
 ## Model set-up
-In this analysis, we aim to predict the likelihood of taking climate-friendly actions based on demographic variables (age, education) and climate change awareness (knowledge).
+In this analysis, we aim to predict the likelihood of taking climate-friendly actions based on demographic variables namely age and education.
 The specific actions include investing in an electric or hybrid vehicle instead of a gas-powered one, making home improvements (e.g., using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste by repurposing used products, sorting waste correctly, and walking or cycling shorter distances.
@@
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+y_i = \beta_0 + \beta_1 * Age_i + \beta_2 * Education_i + \epsilon_i
+\end{align*}
+where:
+
+ - $y_i$ represents the likelihood of taking a climate-friendly action for individual $i$, measured on a five point Likert scale:
+ 1. "Very unlikely"
+ 2. "Somewhat unlikely"
+ 3. "Somewhat likely"
+ 4. "Very likely"
+ 5. "Already doing this or have done this"
+- $\beta_0$ is the intercept, representing the baseline likelihood of taking action when all predictors are zero
+- $\beta_1$ is the coefficient for Age, representing how a one-year increase affects the likelihood of taking action
+- $\beta_2$ is the coefficient for Education, a categorical variable that is dummy-coded.
+- $\epsilon_i$ is the error term, accounting for unexplained variation.
 
@@
 ### Model Justification 
-This model is designed to explore how various demographic and knowledge-based factors influence the likelihood of engaging in climate-friendly behaviors.
+This model is designed to explore how various demographics influence the likelihood of engaging in climate-friendly behaviors.
 The likelihood of taking specific actions, such as reducing energy consumption or investing in green technologies, represents an important outcome in understanding climate change perceptions.

### 2024-12-03 scripts/06-model_data.R

@@ -10,30 +10,63 @@
 #### Workspace setup ####
 
 library(tidyverse)
-library(brms)
-library(arrow)
+library(readr)
 library(here)
-library(broom)
+library(caret)
+library(arrow)
 
 #### Read data ####
 # Load your analysis data
-individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.parquet"))
+climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
 
-# Convert the 'highest_level_educ' variable to a factor
-climate_data$highest_level_educ <- factor(climate_data$highest_level_educ)
+# Clean the data
+climate_data_cleaned <- climate_data %>%
+  filter(
+    !is.na(likelihood_home_improvement),  # Ensure no missing values in the response variable
+    !is.na(age),                          # Ensure no missing values in the predictor variable age
+    !is.na(highest_level_educ)             # Ensure no missing values in the predictor variable education
+  ) %>%
+  mutate(
+    # Convert likelihood of home improvement to an ordered factor
+    likelihood_home_improvement = factor(
+      likelihood_home_improvement,
+      levels = c(
+        "very unlikely",
+        "somewhat unlikely",
+        "somewhat likely",
+        "very likely",
+        "already doing this or have done this"
+      ),
+      ordered = TRUE  # Indicate that the factor is ordinal
+    ),
+    likelihood_numeric = as.numeric(likelihood_home_improvement),  # Convert ordinal factor to numeric for regression
+    age = as.numeric(age),  # Ensure age is treated as a numeric variable
+    highest_level_educ = factor(highest_level_educ, levels = c(
+      "high school or less",
+      "some community college / trade school",
+      "completed community college / trade school",
+      "some university",
+      "completed undergraduate degree",
+      "postgraduate / professional school",
+      "prefer not to answer"
+    )) %>% droplevels()  # Drop unused levels
+  )
 
-# Now check the levels again
-levels(climate_data$highest_level_educ)
+# Check if the factor levels are valid
+print(levels(climate_data_cleaned$highest_level_educ))  # Display levels to ensure they are correct
 
-
-# Convert the ordinal likelihood variables to numeric values
-climate_data <- climate_data %>%
-  mutate(across(starts_with("likelihood"),
-                ~ as.numeric(factor(., levels = c("very_unlikely", "somewhat_unlikely", 
[…]

### 2024-12-03 scripts/07-install_packages.R

@@ -28,4 +28,4 @@ install.packages(c(
 ))
 
 
-install.packages("testthat")
+install.packages("caret")

### 2024-12-03 scripts/06-model_data.R
model!

@@ -14,59 +14,40 @@ library(readr)
 library(here)
 library(caret)
 library(arrow)
+library(rpart)
+library(partykit)
 
 #### Read data ####
 # Load your analysis data
 climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
 
-# Clean the data
-climate_data_cleaned <- climate_data %>%
-  filter(
-    !is.na(likelihood_home_improvement),  # Ensure no missing values in the response variable
-    !is.na(age),                          # Ensure no missing values in the predictor variable age
-    !is.na(highest_level_educ)             # Ensure no missing values in the predictor variable education
-  ) %>%
-  mutate(
-    # Convert likelihood of home improvement to an ordered factor
-    likelihood_home_improvement = factor(
-      likelihood_home_improvement,
-      levels = c(
-        "very unlikely",
-        "somewhat unlikely",
-        "somewhat likely",
-        "very likely",
-        "already doing this or have done this"
-      ),
-      ordered = TRUE  # Indicate that the factor is ordinal
-    ),
-    likelihood_numeric = as.numeric(likelihood_home_improvement),  # Convert ordinal factor to numeric for regression
-    age = as.numeric(age),  # Ensure age is treated as a numeric variable
-    highest_level_educ = factor(highest_level_educ, levels = c(
-      "high school or less",
-      "some community college / trade school",
-      "completed community college / trade school",
-      "some university",
-      "completed undergraduate degree",
-      "postgraduate / professional school",
-      "prefer not to answer"
-    )) %>% droplevels()  # Drop unused levels
-  )
+# Check the levels of highest_level_educ
+table(climate_data$highest_level_educ)
 
-# Check if the factor levels are valid
-print(levels(climate_data_cleaned$highest_level_educ))  # Display levels to ensure they are correct
+# creating an 80 20 train test split cause cant assess our model on the same data that it is trained on. 
+hil_train <- sample_n (climate_data, size = round(0.8*nrow(climate_data)))
+hil_test <- anti_join(climate_data, hil_train)
 
-# Fit the linear regression model
-if (nlevels(climate_data_cleaned$highest_level_educ) > 1) {
-  climate_model <- lm(likelihood_numeric ~ age + highest_level_educ, data = climate_data_cleaned)
-  
-  # Save the model to an RDS file for future use
[…]

### 2024-12-03 scripts/07-install_packages.R

@@ -28,4 +28,6 @@ install.packages(c(
 ))
 
 
-install.packages("caret")
+
+install.packages("rpart")
+install.packages("partykit")

### 2024-12-03 scripts/06-model_data.R
made 9 models- one for each climate action in terms of predicting likelihood

@@ -9,10 +9,10 @@
 
 #### Workspace setup ####
 
+# load packages
 library(tidyverse)
 library(readr)
 library(here)
-library(caret)
 library(arrow)
 library(rpart)
 library(partykit)
@@ -21,33 +21,160 @@ library(partykit)
 # Load your analysis data
 climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
 
-# Check the levels of highest_level_educ
-table(climate_data$highest_level_educ)
+#  confusion matrix allows us to understand our predictions and how well the model works. 
+# for the summary table in results
+# assess using the confusion matrix and chat to end up with 
+# look at accuracy 
 
+# Required fixes
+# NA values in data
+# how to save - what goes where? scripts, paper model section vs. summary table for results 
+
+
+
+# Model for home improvement likelihood hil
 # creating an 80 20 train test split cause cant assess our model on the same data that it is trained on. 
 hil_train <- sample_n (climate_data, size = round(0.8*nrow(climate_data)))
 hil_test <- anti_join(climate_data, hil_train)
 
 # generating a decision tree to predict the home improvement likelihood based on age and education level
 hilTree <- rpart(likelihood_home_improvement ~ age + highest_level_educ, hil_train)
-plot(as.party(hilTREE), gp = gpar(cex=1), type="simple")
+plot(as.party(hilTree), gp = gpar(cex=1), type="simple")
 
 # creating a confusion matrix based on our testing data
 predictions <- predict(hilTree, newdata=hil_test, type="class")
-confusion_matrix <- table(predictions, hil_test$likelihood_home_improvement)
-print(confusion_matrix)
+confusion_matrix1 <- table(predictions, hil_test$likelihood_home_improvement)
+print(confusion_matrix1)
 
-#  confusion matrix allows us to understand our predictions and how well the model works. 
-
-
-# for the summary table in results
-# assess using the confusion matrix and chat to end up with 
-# look at accuracy 
+# save as parquet
+write_parquet(climate_data_cleaned, here::here("data/analysis_data/TODO.parquet"))
 
 
 
-  # Save the model and cleaned data
-  saveRDS(climate_model, here::here("models/climate_model_home_improvement.rds"))
[…]

### 2024-12-04 paper/climate_change.qmd
fixing model section

@@
 # Results
+
+## Model Takeaways
+summary table age and education in predicting likelihood of taking climate actions
+the accuracy of the models prediction matches the genuine data
+TODO 
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: table-five
+#| fig-cap: TODO
+
+# Load the model accuracy data from the saved CSV
+model_accuracies <- read.csv(here::here("data/02-analysis_data/model_accuracies.csv"))
+
+# Round numeric columns to whole numbers
+model_accuracies[] <- lapply(model_accuracies, function(x) if(is.numeric(x)) round(x) else x)
+
+# Check the first few rows of the data to ensure it loaded and rounded correctly
+head(model_accuracies)
+
+```
 

### 2024-12-04 scripts/06-model_data.R

@@ -17,164 +17,76 @@ library(arrow)
 library(rpart)
 library(partykit)
 
+# set seed for reproducibility
+set.seed(123)
+
 #### Read data ####
 # Load your analysis data
 climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
 
-#  confusion matrix allows us to understand our predictions and how well the model works. 
-# for the summary table in results
-# assess using the confusion matrix and chat to end up with 
-# look at accuracy 
+# List to store model names and accuracies
+model_accuracies <- data.frame(Model = character(), Accuracy = numeric(), stringsAsFactors = FALSE)
 
-# Required fixes
-# NA values in data
-# how to save - what goes where? scripts, paper model section vs. summary table for results 
+# Helper function to calculate accuracy
+calculate_accuracy <- function(predictions, actual_values) {
+  confusion_matrix <- table(predictions, actual_values)
+  accuracy <- sum(diag(confusion_matrix)) / sum(confusion_matrix) * 100
+  return(accuracy)
+}
 
+# Function to train and evaluate models
+train_and_evaluate_model <- function(target_var, model_name) {
+  # 80-20 Train-Test Split
+  train_data <- sample_n(climate_data, size = round(0.8 * nrow(climate_data)))
+  test_data <- anti_join(climate_data, train_data)
+  
+  # Generate a decision tree model
+  model <- rpart(as.formula(paste(target_var, "~ age + highest_level_educ")), data = train_data)
+  
+  # Make predictions on the test dataset
+  predictions <- predict(model, newdata = test_data, type = "class")
+  
+  # Calculate accuracy
+  accuracy <- calculate_accuracy(predictions, test_data[[target_var]])
+  
+  # Save model's accuracy in the list
+  model_accuracies <<- rbind(model_accuracies, data.frame(Model = model_name, Accuracy = accuracy))
+  
+  # Optionally, print the accuracy
+  cat(paste("Accuracy of", model_name, "Model:", round(accuracy, 2), "%\n"))
+}
 
+# Evaluate each model
 
-# Model for home improvement likelihood hil
-# creating an 80 20 train test split cause cant assess our model on the same data that it is trained on. 
-hil_train <- sample_n (climate_data, size = round(0.8*nrow(climate_data)))
-hil_test <- anti_join(climate_data, hil_train)
[…]

### 2024-12-04 paper/climate_change.qmd
final touches on model

@@
 # Model {#sec-model}
-TO DO:
-The goal of our modelling strategy is twofold. Firstly,...
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-appendix].
+The goal of our modelling strategy is twofold.
+Firstly, we aim to predict the likelihood of individuals engaging in climate-friendly actions based on demographic variables, specifically age and education.
+The actions considered include investing in electric or hybrid vehicles, making home improvements (such as using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste, sorting waste correctly, and walking or cycling shorter distances.
+Secondly, we aim to understand how these demographic characteristics influence individuals' likelihood of adopting these behaviors.
+
+Here we describe the probability tree model used to investigate the relationship between likelihood and the demographic factors of age and education.
+Further details on background and diagnostics can be found in [Appendix -@sec-appendix].
+
 ## Model set-up
-In this analysis, we aim to predict the likelihood of taking climate-friendly actions based on demographic variables namely age and education.
-The specific actions include investing in an electric or hybrid vehicle instead of a gas-powered one, making home improvements (e.g., using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste by repurposing used products, sorting waste correctly, and walking or cycling shorter distances.
+In this analysis, we focus on predicting the likelihood of taking climate-friendly actions based on the demographic variables of age and education.
+The likelihood is measured on a five-point Likert scale, ranging from "Very unlikely" to "Already doing this or have done this."
 
 ### Model Specifications ###
-TO DO:
+We use a probability tree model to predict the likelihood of individuals engaging in climate-friendly actions based on two key demographic variables: age and education.
+
+The general form of the model is:
 
@@
 
- - $y_i$ represents the likelihood of taking a climate-friendly action for individual $i$, measured on a five point Likert scale:
+ - $y_i$ represents the likelihood of individual $i$ engaging in a climate-friendly actin, measured on a five point Likert scale:
  1. "Very unlikely"
@@
  5. "Already doing this or have done this"
-- $\beta_0$ is the intercept, representing the baseline likelihood of taking action when all predictors are zero
-- $\beta_1$ is the coefficient for Age, representing how a one-year increase affects the likelihood of taking action
+- $\beta_0$ is the intercept, representing the baseline likelihood of taking action when all predictors are zero.
+- $\beta_1$ is the coefficient for Age, representing how a one-year increase affects the likelihood of taking action.
 - $\beta_2$ is the coefficient for Education, a categorical variable that is dummy-coded.
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+This model focuses on the direct effect of age and education on the likelihood of taking climate-friendly actions, assuming a linear relationship between these demographic variables and the outcome variable (the likelihood of action).
 
 ### Model Justification 
-This model is designed to explore how various demographics influence the likelihood of engaging in climate-friendly behaviors.
-The likelihood of taking specific actions, such as reducing energy consumption or investing in green technologies, represents an important outcome in understanding climate change perceptions.
-As such, focusing on these behaviors rather than general knowledge allows for a more actionable and directly applicable model to climate change policy and interventions.
+This model was developed to explore how demographic factors such as age and education influence individuals' likelihood of engaging in climate-friendly behaviors.
+By focusing on specific climate actions like reducing energy consumption, adopting sustainable practices, and investing in green technologies, the model aims to provide actionable insights for climate change interventions.
 
 #### Response Variable ####
-The response variable in this analysis is the likelihood of taking climate-friendly actions, which is typically a continuous or ordinal measure based on respondents' self-reported likelihood of adopting behaviors such as switching to an electric vehicle, reducing waste, or conserving energy.
-These actions are commonly measured on a Likert scale (e.g., 1 = "not likely" to 5 = "very likely").
+The response variable in this analysis is the likelihood of taking climate-friendly actions, measured using a Likert scale (1 = "Very unlikely" to 5 = "Already doing this or have done this").
+This scale captures the respondent’s perceived likelihood of engaging in various climate-friendly behaviors
 
@@
 
-Age: Previous studies indicate that younger individuals are more likely to engage in climate-positive behaviors due to greater environmental awareness and concern (Leiserowitz et al., 2010; Gifford, 2013).
-
-Education: Higher educational attainment has been associated with a higher likelihood of adopting environmentally responsible behaviors, likely due to increased awareness of environmental issues and access to relevant information (Kollmuss & Agyeman, 2002).
-
-Knowledge: A greater understanding of climate change is expected to positively influence individuals' likelihood of taking action.
-More knowledgeable individuals are more likely to adopt climate-friendly practices, as they are more aware of the urgency of the crisis and the potential benefits of sustainable behaviors (Gifford, 2013).
+- **Age**: Previous research indicates that younger individuals may be more inclined to adopt climate-friendly behaviors due to increased environmental awareness (Leiserowitz et al., 2010; Gifford, 2013).
+- **Education**: Higher levels of education are often linked to greater awareness of environmental issues and a higher likelihood of adopting sustainable behaviors (Kollmuss & Agyeman, 2002).
+Education is treated as a categorical variable and dummy-coded for analysis.
 
 #### Model Structure ####
-The model assumes that the likelihood of taking climate-friendly actions is linearly related to the input variables.
-Each predictor (age, education, and knowledge) is assumed to have a linear relationship with the likelihood of taking action, meaning that as these variables change, the likelihood of taking climate-friendly actions will either increase or decrease in a predictable manner.
-This structure facilitates a clear interpretation of how each variable contributes to the overall likelihood of climate-positive behavior.
+This model assumes a linear relationship between the predictors (age and education) and the likelihood of taking action.
+Specifically, the likelihood of taking climate-friendly actions is modeled as a function of age and education, with coefficients representing the change in the likelihood of action associated with a unit change in each predictor.
 
-Detailed Structure
-The model does not assume any interactions between the predictors, meaning each factor (age, education, knowledge) is considered independently in its influence on the outcome.
-However, depending on the data, you might consider adding interaction terms if you believe that, for example, the effect of knowledge on action is stronger for younger individuals.
-The linear relationship between predictors and the likelihood of action allows for easy interpretation, with coefficients representing the change in the likelihood of taking action for each unit change in the predictor variable.
+There are no interaction terms in this model, meaning we assume that the effects of age and education on the likelihood of taking action are independent of each other.
+This simplicity ensures clear interpretation of each predictor's individual effect on the likelihood of taking climate-friendly actions.
 
-#### Parameter Estimation ####
-In parameter estimation, we anticipate that:
-Age: We expect that younger individuals will have a higher likelihood of taking climate-friendly actions, as studies have shown that younger generations are more environmentally conscious and concerned about climate change (Leiserowitz et al., 2010).
-Education: We hypothesize that higher levels of education will positively influence the likelihood of taking climate-positive actions.
-More educated individuals tend to have better access to information about climate change and sustainability practices (Kollmuss & Agyeman, 2002).
-Knowledge: We expect that greater knowledge of climate change will be strongly associated with higher likelihoods of adopting climate-friendly behaviors.
-Knowledge acts as a critical enabler, motivating individuals to take action and contribute to mitigating climate change (Gifford, 2013).
-We will estimate the model parameters using a standard linear regression approach (e.g., using the lm() function in R), which will provide the coefficients (
-β
-β) for each predictor, showing how each factor influences the likelihood of taking climate-friendly actions.
+## Nine Models ##
+
+We fit nine separate probability tree models, one for each climate-friendly action we are predicting.
+Each model uses age and education as the predictors to estimate the likelihood of the corresponding action.
+These actions are:
+
+1. Likelihood of investing in an electric or hybrid vehicle
+2. Likelihood of making home improvements (e.g., using LED lightbulbs)
+3. Likelihood of adopting meat alternatives
+4. Likelihood of minimizing car use
+5. Likelihood of purchasing green products
+6  Likelihood of reducing hydro usage
+7. Likelihood of reducing waste by repurposing used products
+8. Likelihood of sorting waste correctly
+9. Likelihood of walking or cycling shorter distances
+
+Each model is built using the same structure but predicts a different outcome variable. This approach allows us to analyze the specific impact of age and education on each climate-friendly action.
+
+### Likelihood of investing in an electric or hybrid vehicle
+@model-one
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-one
+#| fig-cap: Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/vehicle_electric_tree.png"))
+
+```
+
+### Likelihood of making home improvements
+@model-two
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-two
+#| fig-cap: Probability tree for likelihood of making home improvements predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/home_improvement_tree.png"))
+
+```
+
+### Likelihood of adopting meat alternatives
+@model-three
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-three
+#| fig-cap: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/protein_alternative_tree.png"))
+
+```
+
+### Likelihood of minimizing car use
+@model-four
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-four
+#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/minimize_car_tree.png"))
+
+```
+
+### Likelihood of purchasing green products
+@model-five
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-five
+#| fig-cap: Probability tree for likelihood of purchasing green products, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/green_product_tree.png"))
+
+```
+
+### Likelihood of reducing hydro usage
+@model-six
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-six
+#| fig-cap: Probability tree for likelihood of reducing hydro usage, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/reduce_hydro_tree.png"))
+
+```
+
+###  Likelihood of reducing waste
+@model-seven
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-seven
+#| fig-cap: Probability tree for likelihood of reducing waste, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/reduce_waste_tree.png"))
+
+```
+
+###  Likelihood of sorting waste correctly
+@model-eight
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-eight
+#| fig-cap: Probability tree for likelihood of sorting waste correctly, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/sort_waste_tree.png"))
+
+```
+
+###  Likelihood of walking or cycling shorter distances
+@model-nine
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: model-nine
+#| fig-cap: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
+
+knitr::include_graphics(here::here("data/04-model_data/short_distance_tree.png"))
+
+```
+
+## Model Estimation and Interpretation ##
+The probability tree model estimates how the predictors age and education influence the likelihood of adopting climate-friendly behaviors.
+By splitting the data into branches based on these variables, the model helps identify decision rules that predict individuals' likelihood of taking actions such as reducing waste or investing in green products.
+We anticipate that younger individuals, due to greater environmental awareness, are more likely to engage in climate-positive actions, while those with higher levels of education may also be more inclined to adopt such behaviors, given their increased awareness of climate change and sustainable practices.
+The model estimates the parameters for age and education using regression techniques, providing coefficients that indicate how each factor influences the likelihood of taking climate-friendly actions.
 

### 2024-12-04 scripts/06-model_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Constructs a linear regression model for predicting likelihood of taking climate action based on age and education. 
+# Purpose: Constructs a  decision tree model for predicting likelihood of taking climate action based on age and education. 
 # Author: Lexi Knight
 # Date: 30 November 2024
 # Contact: lexi.knight@mail.utoronto.ca
@@ -11,82 +11,69 @@
 
 # load packages
 library(tidyverse)
-library(readr)
-library(here)
-library(arrow)
 library(rpart)
 library(partykit)
+library(here)
+library(arrow)
 
-# set seed for reproducibility
-set.seed(123)
+# Set seed for reproducibility
+set.seed(853)
+
 
 #### Read data ####
-# Load your analysis data
 climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
 
-# List to store model names and accuracies
-model_accuracies <- data.frame(Model = character(), Accuracy = numeric(), stringsAsFactors = FALSE)
-
-# Helper function to calculate accuracy
-calculate_accuracy <- function(predictions, actual_values) {
-  confusion_matrix <- table(predictions, actual_values)
+# Function to generate decision trees, predictions, confusion matrix, and accuracy
+generate_model <- function(target_var, train_data, test_data, model_name) {
+  # Generate decision tree
+  formula <- as.formula(paste(target_var, "~ age + highest_level_educ"))
+  tree <- rpart(formula, data = train_data)
+  
+  # Construct file path for saving the plot
+  png_file_path <- file.path(here::here("data/04-model_data"), paste0(model_name, "_tree.png"))
+  
+  # Plot the decision tree and save the plot as a .png
+  png(png_file_path)
+  plot(as.party(tree), gp = gpar(cex = 1), type = "simple")
+  dev.off()
+  
+  # Make predictions on the test dataset
+  predictions <- predict(tree, newdata = test_data, type = "class")
+  
+  # Generate the confusion matrix
+  confusion_matrix <- table(predictions, test_data[[target_var]])
+  
+  # Calculate and return accuracy
   accuracy <- sum(diag(confusion_matrix)) / sum(confusion_matrix) * 100
   return(accuracy)
 }
 
-# Function to train and evaluate models
-train_and_evaluate_model <- function(target_var, model_name) {
-  # 80-20 Train-Test Split
[…]

### 2024-12-04 paper/climate_change.qmd
working on last minute changes

@@
 Climate change is one of the most urgent challenges we face today.
-From rising temperatures to extreme weather events, the planet is already feeling the consequences of human-driven environmental change.
-Yet, despite widespread awareness of these risks, many people still struggle to adopt behaviors that could help mitigate climate damage.
-This gap between knowledge and action is a central puzzle that governments, communities, and organizations are trying to solve.
-If we are to tackle this crisis effectively, we need to better understand what stops people from acting, and how we can motivate change.
+From rising temperatures to extreme weather events, the planet is already feeling the consequences of human-driven environmental change [@IPCC2023].
+Yet, despite widespread awareness of these risks, many people still struggle to adopt behaviors that could help mitigate climate damage [@Gifford2011].
+This gap between knowledge and action is a central puzzle that governments, communities, and organizations are trying to solve [@Kollmuss2002].
+If we are to tackle this crisis effectively, we need to better understand what stops people from acting, and how we can motivate change [@Steg2014].
 
-This paper examines how specific factors—such as age, education, and self-reported knowledge of climate change—shape people’s willingness to engage in climate-friendly actions.
-By analyzing data from a 2018 survey, we explore the connection between demographic characteristics and behaviors like reducing energy consumption, using greener transportation, and lowering waste.
-The survey also delves into what prevents people from adopting these behaviors, uncovering obstacles like cost, convenience, and skepticism about the power of individual actions.
-With this analysis, we aim to uncover how these factors interact and what they mean for efforts to encourage sustainable choices.
+This paper examines how specific factors—such as age, education, and self-reported knowledge of climate change—shape people’s willingness to engage in climate-friendly actions [@Schultz2002].
+By analyzing data from a 2018 survey [@climateperceptionstudy], we explore the connection between demographic characteristics and behaviors like reducing energy consumption, using greener transportation, and lowering waste.
+The survey also delves into what prevents people from adopting these behaviors, uncovering obstacles like cost, convenience, and skepticism about the power of individual actions [@Gifford2011].
+With this analysis, we aim to uncover how these factors interact and what they mean for efforts to encourage sustainable choices [@Stern2000].
 
 The heart of this study is to measure how age, education, and knowledge of climate change influence the likelihood of adopting certain behaviors.
-We found that younger individuals and those with higher education levels are more likely to engage in actions like reducing car usage and adopting plant-based diets.
-However, older individuals are more inclined to take steps like cutting down on household energy use.
-Beyond these demographic trends, we also discovered that barriers such as financial cost and doubts about the effectiveness of individual efforts often hold people back from taking action.
+We found that younger individuals and those with higher education levels are more likely to engage in actions like reducing car usage and adopting plant-based diets [@Fulton2022].
+However, older individuals are more inclined to take steps like cutting down on household energy use [@Lee2019].
+Beyond these demographic trends, we also discovered that barriers such as financial cost and doubts about the effectiveness of individual efforts often hold people back from taking action [@Kollmuss2002].
 These findings suggest that a “one-size-fits-all” approach to climate communication won’t work.
-Instead, targeted strategies that consider demographic differences are essential for driving meaningful engagement.
+Instead, targeted strategies that consider demographic differences are essential for driving meaningful engagement [@Steg2014].
 
 Understanding these patterns is crucial for crafting effective climate policies.
-By identifying which groups are more likely to act and which face significant barriers, we can better design interventions that speak to people’s concerns and motivations.
-The implications of this study go beyond simply knowing what people think about climate change—they offer a roadmap for shaping messages and policies that could shift behavior on a larger scale.
+By identifying which groups are more likely to act and which face significant barriers, we can better design interventions that speak to people’s concerns and motivations [@Stern2000].
+The implications of this study go beyond simply knowing what people think about climate change—they offer a roadmap for shaping messages and policies that could shift behavior on a larger scale [@Fulton2022].
 
@@
 #| message: false
-# #| label: table-one
-# #| fig-cap: "Comparison of Age Distribution Between 2018 and 2021 Surveys: This table highlights the age distribution of survey respondents in 2018 and 2021.
+#| label: table-one
+#| fig-cap: "Comparison of Age Distribution Between 2018 and 2021 Surveys: This table highlights the age distribution of survey respondents in 2018 and 2021.
 Notable differences include a higher representation of individuals aged 18–23 in 2021 compared to 2018, while the distribution across other age groups remained relatively consistent between the two years."
@@
 # Read the cleaned CSV into a data frame
-# age_summary_combined <- read.csv(here("data/03-figures_data", "age_summary_combined.csv"))
+age_summary_combined <- read.csv(here("data/03-figures_data", "age_summary_combined.csv"))
 
 # Print the cleaned table (using kable for styling)
-# age_summary_combined %>%
-  # kbl(caption = "Age Distribution Comparison for 2018 and 2021") %>%
-  # kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
+age_summary_combined %>%
+  kbl(caption = "Age Distribution Comparison for 2018 and 2021") %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
 
@@
 The actions considered include investing in electric or hybrid vehicles, making home improvements (such as using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste, sorting waste correctly, and walking or cycling shorter distances.
-Secondly, we aim to understand how these demographic characteristics influence individuals' likelihood of adopting these behaviors.
-
-Here we describe the probability tree model used to investigate the relationship between likelihood and the demographic factors of age and education.
-Further details on background and diagnostics can be found in [Appendix -@sec-appendix].
+Secondly, we aim to understand how these demographic characteristics influence individuals' likelihood of adopting these behaviors.Here we describe the probability tree model used to investigate the relationship between likelihood and the demographic factors of age and education.
 
@@
 
-## Model Takeaways
-summary table age and education in predicting likelihood of taking climate actions
-the accuracy of the models prediction matches the genuine data
-TODO 
+## Model Summary Table
+The table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors such as age and education.
+Each row represents a different climate action (e.g., home improvement, reducing hydro, minimizing car use), with the corresponding accuracy of the model's predictions.
+The accuracy values reflect how well the models, which use age and education as predictors, align with the actual data.
+An accuracy of 33 percent  for home improvement" indicates that the model correctly predicted the outcome 33% of the time for this action.
+These accuracy values help evaluate the effectiveness of age and education as predictors for each specific climate action.
 ```{r}
@@
 #| label: table-five
-#| fig-cap: TODO
+#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
+The accuracy values reflect how closely the model predictions align with the actual observed data.
+Higher accuracy values indicate better model performance.
 
@@
 ## Age and Climate-Friendly Behaviors {#sec-first-point}
-The findings indicate that younger individuals are more likely to engage in climate-friendly actions that are perceived as low-cost and easier to implement, such as consuming meat alternatives and reducing car usage.
-This suggests that younger generations, likely due to heightened environmental awareness and exposure to climate change discussions, are more inclined to adopt behaviors that align with popular environmental movements.
-It also highlights how lifestyle factors and generational attitudes toward climate change can shape behavioral patterns.
+The findings indicate that younger individuals are more likely to engage in climate-friendly actions perceived as low-cost and easier to implement, such as consuming meat alternatives and reducing car usage.
+The model results show that these behaviors have relatively higher predicted likelihoods among younger participants, aligning with existing research on generational differences in environmental attitudes.
+This trend may be driven by heightened environmental awareness and increased exposure to climate change discussions among younger generations, often through social media and educational initiatives.
+These results suggest that lifestyle factors and generational attitudes significantly shape behavioral patterns, with younger individuals gravitating toward actions that are both socially encouraged and accessible.
 
 ## The Role of Education in Sustainable Actions {#sec-second-point}
-Education significantly influences individuals' likelihood to engage in more substantial climate-friendly behaviors.
-Higher educational attainment is strongly associated with actions that require greater investment, such as purchasing electric vehicles or making energy-efficient home improvements.
-This pattern suggests that educational levels not only increase awareness but also enhance the capacity to implement larger, more financially demanding sustainable practices.
-The relationship between education and sustainability highlights the importance of knowledge and informed decision-making in supporting climate-friendly actions.
+Education significantly influences individuals' likelihood of engaging in more substantial climate-friendly behaviors.
+Our models demonstrate that individuals with higher educational attainment are more likely to adopt behaviors requiring greater financial or logistical investment, such as purchasing electric vehicles or making energy-efficient home improvements.
+The accuracy of the models predicting these behaviors is relatively lower than for simpler actions, suggesting that education is an important but not sole determinant.
+This relationship between education and sustainability underscores the importance of knowledge and informed decision-making in supporting climate-friendly actions, particularly those with long-term environmental benefits.
+The data suggests that higher education increases both environmental awareness and the capacity to implement financially demanding sustainable practices, which are often inaccessible to those with lower educational levels.
 
@@
 Self-reported knowledge of climate change also plays a role in the likelihood of adopting sustainable behaviors.
-People with greater awareness of climate change tend to be more proactive in making environmentally conscious choices.
-However, while knowledge is an important factor, it does not always guarantee significant behavioral change.
-This suggests that raising awareness must be paired with policies that reduce barriers to adopting more expensive or long-term sustainable actions, ensuring that individuals are both informed and able to make practical changes.
+Our analysis shows that individuals with greater awareness are more proactive in making environmentally conscious choices, particularly for actions like reducing waste and conserving energy.
+However, the model accuracy for some knowledge-based behaviors remains moderate, highlighting a gap between awareness and action.
+This suggests that while raising awareness is critical, it must be paired with policies that reduce structural barriers to adopting more expensive or long-term sustainable actions.
+For example, financial incentives or subsidies for purchasing energy-efficient appliances could bridge this gap, ensuring individuals are both informed and able to make practical changes.
 
@@
 
-The primary limitation of this study lies in its reliance on self-reported data, which is subject to bias.
-Respondents may overestimate their awareness of climate change or misreport their actions, especially when social desirability factors are involved.
-Additionally, the study used summary statistics for 2021, which limited the ability to explore individual-level trends and interactions.
-Without access to more granular data, it was impossible to assess how different socio-economic factors, such as income, directly influence individuals’ likelihood to adopt climate-friendly behaviors.
+One significant limitation of this study is its reliance on self-reported survey data, which is inherently prone to biases such as social desirability bias and recall errors.
+Respondents may overestimate their environmental knowledge or exaggerate their participation in climate-friendly behaviors to present themselves in a favorable light.
+This introduces uncertainty into the accuracy of the models, as the input data may not fully reflect actual behaviors or knowledge levels.
+Additionally, self-reported data often lacks the granularity needed to explore complex interactions between socio-economic factors, such as income and household size, which can significantly influence sustainable actions.
 
-Another limitation is that the study did not explore the reasons behind individuals' reluctance to adopt certain sustainable behaviors.
-Investigating these reasons would provide more insight into how policies can make climate actions more accessible, affordable, and normalized for different demographic groups.
-Although time constraints prevented this deeper analysis, it would be an important direction for future research.
+Another limitation arises from the use of summary data from the 2018 and 2021 surveys instead of individual-level data.
+While the summary statistics provided valuable insights into broad demographic trends, they limited the study’s ability to explore more nuanced patterns and interactions.
+For example, the summary data showed differences in education and age trends between 2018 and 2021, but without individual-level data, it was difficult to determine the direct effect of socio-economic factors on climate action likelihood.
+Future studies with access to raw, individual-level data could offer more precise estimates and a deeper understanding of these dynamics.
 
-TO DO: add / talk about difficulty and problems with survey data
+## Challenges with Survey Data
+Survey data presents additional challenges, such as non-response bias, where certain demographic groups may be underrepresented, leading to skewed results.
+Additionally, the framing of survey questions can influence how respondents perceive and answer them, introducing further variability in the data.
+The inability to verify self-reported behaviors also limits the reliability of the conclusions drawn from such datasets.
+Despite these challenges, surveys remain a valuable tool for capturing perceptions and self-reported behaviors, but their findings should be interpreted with caution and, when possible, supplemented with objective data sources.
 
 ## Future Directions
-Future research should aim to identify the specific barriers that prevent certain groups from engaging in climate-friendly behaviors.
-This could involve examining factors such as income, access to resources, and perceived obstacles to adopting sustainable practices.
-In addition, exploring how policies or interventions can make sustainable actions more accessible and affordable across different demographic groups would be valuable.
-Longitudinal studies could also help track how awareness of climate change influences sustained behavioral changes, and whether other external factors, such as economic incentives, contribute to these shifts.
+Future research should aim to identify the specific barriers preventing certain demographic groups from adopting climate-friendly behaviors.
+This could involve examining factors such as income, access to resources, and perceived obstacles to sustainable practices.
+Additionally, targeted interventions, such as financial subsidies, public awareness campaigns, or infrastructure improvements, could make sustainable actions more accessible and affordable.
+Longitudinal studies would be particularly valuable for tracking how awareness of climate change influences sustained behavioral changes over time.
+Comparing individual-level data across different years could also provide insights into the long-term impact of educational and policy interventions on climate-friendly behaviors.
+
+Lastly, integrating objective data, such as energy consumption records or transportation usage statistics, could validate and enhance the accuracy of survey-based findings.
+This combined approach would offer a more comprehensive understanding of how demographic and socio-economic factors influence the adoption of sustainable actions, ultimately informing more effective climate policies and interventions.
 

### 2024-12-04 scripts/06-model_data.R

@@ -9,6 +9,8 @@
 
 #### Workspace setup ####
 
+#### Workspace setup ####
+
 # load packages
 library(tidyverse)
 library(rpart)
@@ -18,7 +20,6 @@ library(arrow)
 
 # Set seed for reproducibility
 set.seed(853)
-
 
 #### Read data ####
 climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
@@ -32,9 +33,13 @@ generate_model <- function(target_var, train_data, test_data, model_name) {
   # Construct file path for saving the plot
   png_file_path <- file.path(here::here("data/04-model_data"), paste0(model_name, "_tree.png"))
   
+  # Adjust PNG size to avoid cutting off the tree
+  png(png_file_path, width = 3200, height = 1500, res = 150)  # Increase size and resolution
+  
   # Plot the decision tree and save the plot as a .png
-  png(png_file_path)
   plot(as.party(tree), gp = gpar(cex = 1), type = "simple")
+  
+  # Close the device after saving the plot
   dev.off()
   
   # Make predictions on the test dataset

### 2024-12-04 scripts/07-install_packages.R

@@ -24,10 +24,8 @@ install.packages(c(
   "forcats",    # For reordering factor levels
   "kableExtra", # For rendering tables with extra features
   "broom",      # For tidying model output
-  "testthat"    # For testing data
+  "testthat",   # For testing data
+  "rpart",      # For running the model
+  "partykit"    # For running the model
+  
 ))
-
-
-
-install.packages("rpart")
-install.packages("partykit")

### 2024-12-04 paper/climate_change.qmd
last minute edits

@@
 In terms of data tidying, the `tidyr` and `stringr` packages allowed us to reshape and clean the data by managing character strings and handling missing values.
+The [@rpart2024] and [@partykit2024] were used in to make the models.
 For the final documentation and report generation, the `knitr` package was instrumental in integrating R code and outputs into a cohesive and reproducible report format.
@@
 #| label: table-one
-#| fig-cap: "Comparison of Age Distribution Between 2018 and 2021 Surveys: This table highlights the age distribution of survey respondents in 2018 and 2021.
-Notable differences include a higher representation of individuals aged 18–23 in 2021 compared to 2018, while the distribution across other age groups remained relatively consistent between the two years."
+#| fig-cap: "This table highlights the age distribution of survey respondents in 2018 and 2021."
+
+# load libraries 
+library(kableExtra)
+library(knitr)
+library(here)
+library(dplyr)
 
@@
 
+# Rename columns to "Age Group", "2018 Percentage", and "2021 Percentage"
+colnames(age_summary_combined) <- c("Age Group", "2018 Percentage", "2021 Percentage")
+
 # Print the cleaned table (using kable for styling)
 age_summary_combined %>%
-  kbl(caption = "Age Distribution Comparison for 2018 and 2021") %>%
+  kbl() %>%
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
@@
 #| message: false
-# #| label: table-education
-# #|  fig-cap: TODO
+#| label: table-two
+#| fig-cap: This table highlights the education distribution of survey respondents in 2018 and 2021."
 
 # Load necessary libraries
-# library(tinytable)
+library(tinytable)
 
 # Read the CSV into a data frame
-# education_summary_combined <- read.csv(here("data/03-figures_data", "education_summary_combined.csv"))
+education_summary_combined <- read.csv(here("data/03-figures_data", "education_summary_combined.csv"))
 
-# Remove the leading 'X' from column names
-# colnames(education_summary_combined) <- gsub("^X", "", colnames(education_summary_combined))
+# Rename columns 
+colnames(education_summary_combined) <- c("Education Level ", "2018 Percentage", "Education Level", "2021 Percentage")
 
 # Convert the data frame to tinytable
-# education_summary_combined_tiny <- tt(education_summary_combined)
+education_summary_combined_tiny <- tt(education_summary_combined)
 
 # Print the tinytable
-# education_summary_combined_tiny
+education_summary_combined_tiny
 
@@
 #| message: false
-# #| label: table-three
-# #| fig-cap: TODO
+#| label: table-three
+#| fig-cap: "This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021."
 
-# print(informed_summary_combined)
+# Load libraries
+library(kableExtra)
+library(knitr)
+library(here)
+library(dplyr)    # For renaming columns
+library(arrow)    # For reading Parquet files
+
+# Read the Parquet file into a data frame
+informed_summary_combined <- arrow::read_parquet(here("data/03-figures_data", "informed_summary_combined_table.parquet"))
+
+# Rename columns
+colnames(informed_summary_combined) <- c("Extent Informed", "2018 Percentage", "Extent Informed", "2021 Percentage")
+
+# Print the table (using kable for styling)
+informed_summary_combined %>%
+  kbl() %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
+
 ```
@@
 #| message: false
-# #| label: table-four
-# #| fig-cap: TODO
+#| label: table-four
+#| fig-cap: "This table highlights the prefered method of communication of survey respondents in 2018 and 2021."
 
-# print(communication_summary_combined_table)
+# Load libraries
+library(kableExtra)
+library(knitr)
+library(here)
+library(dplyr)    # For renaming columns
+library(arrow)    # For reading Parquet files
+
+# Read the Parquet file into a data frame
+communication_summary_combined <- arrow::read_parquet(here("data/03-figures_data", "communication_summary_combined_table.parquet"))
+
+# Rename columns
+colnames(communication_summary_combined) <- c("Communication Method", "2018 Percentage", "Communication Method", "2021 Percentage")
+
+# Print the table (using kable for styling)
+communication_summary_combined %>%
+  kbl() %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
+
 ```
@@
 ### Likelihood of investing in an electric or hybrid vehicle
-@model-one
 ```{r}
@@
 ### Likelihood of making home improvements
-@model-two
 ```{r}
@@
 ### Likelihood of adopting meat alternatives
-@model-three
 ```{r}
@@
 ### Likelihood of minimizing car use
-@model-four
 ```{r}
@@
 ### Likelihood of purchasing green products
-@model-five
 ```{r}
@@
 ### Likelihood of reducing hydro usage
-@model-six
 ```{r}
@@
 ###  Likelihood of reducing waste
-@model-seven
 ```{r}
@@
 ###  Likelihood of sorting waste correctly
-@model-eight
 ```{r}
@@
 ###  Likelihood of walking or cycling shorter distances
-@model-nine
 ```{r}

### 2024-12-04 paper/climate_change.tex
last minute edits

--- 2024-12-04 paper/climate_change.qmd
@@
----
-title: "Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys"
-subtitle: "Uncovering What Stops Sustainable Behaviors and How Communities Can Overcome Them"
-author: 
-  - Lexi Knight
-thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
-date: today
-date-format: long
-abstract: "This study examines the relationship between demographic factors—age, education, and self-reported knowledge of climate change—and individuals' likelihood of engaging in climate-friendly behaviors.
-The analysis reveals that younger people and those with higher levels of education are more likely to adopt sustainable actions such as reducing car use and purchasing electric vehicles.
-However, the study also highlights that financial barriers and limited access to resources remain significant obstacles for broader climate action.
-These findings underscore the importance of tailoring policies and interventions to make sustainable behaviors more accessible to diverse demographic groups, promoting wider participation in efforts to combat climate change."
-format:
-  pdf:
-    toc: true
-number-sections: true
-bibliography: references.bib
----
-
-# Introduction
-
-Climate change is one of the most urgent challenges we face today.
-From rising temperatures to extreme weather events, the planet is already feeling the consequences of human-driven environmental change [@IPCC2023].
-Yet, despite widespread awareness of these risks, many people still struggle to adopt behaviors that could help mitigate climate damage [@Gifford2011].
-This gap between knowledge and action is a central puzzle that governments, communities, and organizations are trying to solve [@Kollmuss2002].
-If we are to tackle this crisis effectively, we need to better understand what stops people from acting, and how we can motivate change [@Steg2014].
-
-This paper examines how specific factors—such as age, education, and self-reported knowledge of climate change—shape people’s willingness to engage in climate-friendly actions [@Schultz2002].
-By analyzing data from a 2018 survey [@climateperceptionstudy], we explore the connection between demographic characteristics and behaviors like reducing energy consumption, using greener transportation, and lowering waste.
-The survey also delves into what prevents people from adopting these behaviors, uncovering obstacles like cost, convenience, and skepticism about the power of individual actions [@Gifford2011].
-With this analysis, we aim to uncover how these factors interact and what they mean for efforts to encourage sustainable choices [@Stern2000].
-
-The heart of this study is to measure how age, education, and knowledge of climate change influence the likelihood of adopting certain behaviors.
-We found that younger individuals and those with higher education levels are more likely to engage in actions like reducing car usage and adopting plant-based diets [@Fulton2022].
-However, older individuals are more inclined to take steps like cutting down on household energy use [@Lee2019].
-Beyond these demographic trends, we also discovered that barriers such as financial cost and doubts about the effectiveness of individual efforts often hold people back from taking action [@Kollmuss2002].
-These findings suggest that a “one-size-fits-all” approach to climate communication won’t work.
-Instead, targeted strategies that consider demographic differences are essential for driving meaningful engagement [@Steg2014].
-
-Understanding these patterns is crucial for crafting effective climate policies.
-By identifying which groups are more likely to act and which face significant barriers, we can better design interventions that speak to people’s concerns and motivations [@Stern2000].
-The implications of this study go beyond simply knowing what people think about climate change—they offer a roadmap for shaping messages and policies that could shift behavior on a larger scale [@Fulton2022].
-
-The remainder of this paper is structured as follows: @sec-data details the data and methods used in our analysis.
-@sec-model describes how we assess the factors influencing climate-friendly behaviors across demographic groups.
-@sec-results highlights key differences in behavior based on age, education, and knowledge of climate change.
-@sec-discussion discusses the findings, addresses the study's limitations, and suggests directions for future research.
-@sec-conclusion concludes with a summary of the key takeaways and actionable recommendations for enhancing climate action engagement.
-Finally, @sec-appendix contains supplementary material.
-
-# Data {#sec-data}
-The primary data source for this project is the Climate Perception Study dataset, provided by the City of Toronto via the Open Data Toronto platform [@climateperceptionstudy].
-This dataset offers insights into public perceptions of climate change in Toronto and was accessed from Open Data Toronto [@opendatatoronto] on 6 November 2024.
-## Software and R-packages
-This project was conducted using the statistical software `R` [@citeR].
-Data cleaning and manipulation were primarily facilitated by the `tidyverse` package [@tidyverse], which encompasses various essential tools.
-Within this suite, `dplyr` [@dplyr] was employed for data manipulation tasks such as filtering, summarizing, and joining datasets, while `readr` [@readr] provided efficient functionality for reading and writing rectangular text data.
-Specifically, the `write_csv` function from `tidyverse` was used to save the raw 2018 dataset.
-To handle Excel files, we incorporated the `httr` package for downloading files directly from online sources and `readxl` [@readxl], which enabled us to read Excel files seamlessly.
-Additionally, the `openxlsx` package was utilized to create a new Excel workbook with multiple sheets, allowing us to store the 2021 dataset in a structured format.
-
-The `arrow` package was employed to handle large datasets efficiently, ensuring smooth data processing, while `forcats` was used for reordering factor levels to facilitate more insightful analyses and visualizations.
-In terms of data tidying, the `tidyr` and `stringr` packages allowed us to reshape and clean the data by managing character strings and handling missing values.
-For the final documentation and report generation, the `knitr` package was instrumental in integrating R code and outputs into a cohesive and reproducible report format.
-This suite of R packages collectively enabled us to conduct thorough data management, manipulation, and analysis, ultimately contributing to the successful completion of the project.
-
-## Methodology 
-### Data Collection
-The data for this analysis comes from two surveys commissioned by the City of Toronto to assess residents' perceptions of climate change and their willingness to take community action.
-In 2018, Environics Research conducted n=404 online interviews with Toronto residents aged 18 and older between October 11 and October 18.
-Each interview lasted approximately 10 minutes.
-The sample was drawn from an online panel, with quotas set by region, age, and gender to reflect the city’s population based on the 2016 Census, and minor weighting was applied.
-Due to the non-random nature of the online survey, no margin of error was assigned, though a random sample of this size would typically have a margin of ±4.9 percentage points, 19 times out of 20.
-
-In 2021, a second survey was conducted by Ipsos, a global market research company.
-This survey included n=1,400 Toronto residents aged 18 and older and used a mixed-method approach.
-The sample consisted of 1,000 respondents from an online panel, 300 recruited via cell phone and landline, and 100 online interviews conducted in Mandarin, Cantonese, and Punjabi.
-This combination of methods aimed to enhance the survey's representativeness.
-For analysis, Version 2 of the 2021 dataset, which presents responses in a numeric format, was used.
-
-### Data Analysis
-The primary focus of this analysis was the 2018 dataset, examining six key variables: age, education, extent informed, likelihood to take action, reasons for not taking action, and the best method for delivering information regarding climate change action.
-I analyzed these variables at the individual level in the 2018 dataset by calculating the percentages within each category, which provided a clear understanding of the distribution and trends within the population.
-
-In addition, I compared the 2018 dataset to the 2021 summary data to assess changes over the years.
-By calculating the percentage distribution for each variable in both years, I was able to identify any shifts in public awareness, engagement, and preferences regarding climate change action.
-This comparison revealed whether there have been notable changes in factors like the public’s level of information about climate change, their likelihood to take action, and their preferred communication methods.
-
-This two-step approach allowed for a comprehensive understanding: a detailed exploration of the 2018 data combined with a broader comparison of trends between 2018 and 2021.
-
-## Features
-### Age
-#### Individual 2018
-@fig-one illustrates the age distribution of survey respondents in 2018.
-The histogram displays the frequency of respondents across different age groups, with the x-axis representing age intervals and the y-axis indicating the number of respondents within each interval.
-The distribution is relatively balanced, with two noticeable peaks around the 30–40 and 50–60 age ranges, suggesting these age groups are the most represented in the survey.
-
-The vertical dotted lines in the figure highlight key statistical measures: the green dotted line represents the median age, while the blue dashed line indicates the mean age of the respondents.
-Both measures fall near the center of the distribution, reinforcing the observation that the sample is primarily composed of middle-aged individuals.
-Although the distribution appears fairly symmetrical, there is a gradual decline in respondent frequency after the age of 60, with fewer participants aged 90 and above, indicating a smaller representation of older individuals.
-
-Overall, @fig-one provides valuable context for understanding the demographic composition of the survey sample.
-The predominance of middle-aged respondents may influence the interpretation of survey results, particularly if age is a factor in attitudes, behaviors, or preferences related to the study.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-one
-#| fig-cap: "The histogram shows the distribution of age given the 2018 survey respondents."
-
-library(here)
-
-knitr::include_graphics(here("data/03-figures_data", "age_individual_plot.png"))
-
-```
-#### Comparison 2018 to 2021
-@table-one illustrates the different age ditribution for 2018 and 2021 surveys.
-The major difference is that there was greater representation of younger inviduals ranging from 18 to 23 in 2021 compared to 2018.
-The remaining age groups were not very different.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: table-one
-#| fig-cap: "Comparison of Age Distribution Between 2018 and 2021 Surveys: This table highlights the age distribution of survey respondents in 2018 and 2021.
-Notable differences include a higher representation of individuals aged 18–23 in 2021 compared to 2018, while the distribution across other age groups remained relatively consistent between the two years."
-
-# Read the cleaned CSV into a data frame
-age_summary_combined <- read.csv(here("data/03-figures_data", "age_summary_combined.csv"))
-
-# Print the cleaned table (using kable for styling)
-age_summary_combined %>%
-  kbl(caption = "Age Distribution Comparison for 2018 and 2021") %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
-
-```
-
-### Highest Level of Education Completed
-#### Individual 2018
-@fig-two illustrates the distribution of survey respondents by their highest level of education attained.
-The most frequently reported education levels are "Completed undergraduate degree" and "Post graduate/professional school," with both categories having a noticeably higher frequency compared to others, indicating a well-educated respondent population.
-In contrast, fewer respondents reported "Some community college, vocational, trade school" and "Completed community college, vocational, trade school," suggesting these levels are less common among participants.
-Additionally, a small portion of respondents preferred not to disclose their education level.
-This distribution highlights a skew toward higher educational attainment within the sample, which may influence responses related to socio-economic factors and other survey topics.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-two
-#| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."
-
-knitr::include_graphics(here("data/03-figures_data", "educ_individual_plot.png"))
-
-```
-#### Comparison 2018 to 2021
-@table-two illustrates respondant education level in 2018 and 2021 respectively.
-Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021.
-Despite this, we are still able to make comparisons.
-Individuals with high school diplomas or less account for 9 for 2018 and 38 for 2021 (addition of less than highs school and high school or equivalent categories).
-This could indicate that the younger population was included more in the 2021 suvey or that less education individuals were surveyed.
-Additionally, its not super clear howver those with a post graduate or professional degree accounted for 29 percent in 2018 and 35 percent in 2021.
-This illustrates that more educated inviduals responded to the 2021 survey.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-# #| label: table-education
-# #|  fig-cap: TODO
-
-# Load necessary libraries
-# library(tinytable)
-
-# Read the CSV into a data frame
-# education_summary_combined <- read.csv(here("data/03-figures_data", "education_summary_combined.csv"))
-
-# Remove the leading 'X' from column names
-# colnames(education_summary_combined) <- gsub("^X", "", colnames(education_summary_combined))
-
-# Convert the data frame to tinytable
-# education_summary_combined_tiny <- tt(education_summary_combined)
-
-# Print the tinytable
-# education_summary_combined_tiny
-
-```
-
-### Extent Feel Informed
-#### Individual 2018
-@fig-three depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
-The majority of participants identified as "Very informed," making this the most prevalent category by a significant margin.
-A moderate number of respondents reported being "Not very informed," while a smaller yet noticeable group described themselves as "Extremely informed." In contrast, the categories "Not at all informed" and "Not very informed" have the lowest frequencies, with "Not at all informed" being particularly rare.
-This distribution suggests that most respondents possess a relatively high level of awareness about climate change, with very few indicating a lack of knowledge on the topic.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-three
-#| fig-cap: The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents.
-
-knitr::include_graphics(here("data/03-figures_data", "informed_individual_plot.png"))
-
-```
-#### Comparison 2018 to 2021
-@table-three illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
-In 2018, the large marjority of individuals say they are very informed with 60 percent and the follwoign category is not very informed with 27 percent.
-In 2021, The majority of inividuals also say they are very informed but to a lesser degree with 48 percent and this is closely followed by only a little informed with 37 percent.
-There is a trend that invidiusls in 2018 reported greater levels of knowldege about climate change whereas 2021 illstrates a more even split between very informed and only little informed, portraying that fewer individuals have adequate knowledge about climate change.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-# #| label: table-three
-# #| fig-cap: TODO
-
-# print(informed_summary_combined)
-```
-
-### Best Mode of Delivery
-#### Individual 2018
-The analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
-On the other side of the spectrum, few said they were uninterested in receiving climate action information  with about 5 percent, about 12 percent indicated twitter and then 17 percent mentioned instagram.
-Overall social media platforms Facebook, Instagram and Twtitter were less popular methods of communciation.
-This could be because the survey only included individals over the age of 18.
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
+
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\usepackage{tabularray}
+\usepackage[normalem]{ulem}
+\usepackage{graphicx}
+\UseTblrLibrary{booktabs}
+\UseTblrLibrary{rotating}
+\UseTblrLibrary{siunitx}
+\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
+\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
+\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
+
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys},
+  pdfauthor={Lexi Knight},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Barriers to Green Living: Insights from 2018 and 2021 Toronto
+Climate Perception Surveys\thanks{Code and data are available at:
+\url{https://github.com/LexiKnight/toronto_climate/tree/main}.}}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{Uncovering What Stops Sustainable Behaviors and How
+Communities Can Overcome Them}
+\author{Lexi Knight}
+\date{December 3, 2024}
+
+\begin{document}
+\maketitle
+\begin{abstract}
+This study examines the relationship between demographic factors---age,
+education, and self-reported knowledge of climate change---and
+individuals' likelihood of engaging in climate-friendly behaviors. The
+analysis reveals that younger people and those with higher levels of
+education are more likely to adopt sustainable actions such as reducing
+car use and purchasing electric vehicles. However, the study also
+highlights that financial barriers and limited access to resources
+remain significant obstacles for broader climate action. These findings
+underscore the importance of tailoring policies and interventions to
+make sustainable behaviors more accessible to diverse demographic
+groups, promoting wider participation in efforts to combat climate
+change.
+\end{abstract}
+
+\renewcommand*\contentsname{Table of contents}
+{
+\hypersetup{linkcolor=}
+\setcounter{tocdepth}{3}
+\tableofcontents
+}
+\section{Introduction}\label{introduction}
+
+Climate change is one of the most urgent challenges we face today. From
+rising temperatures to extreme weather events, the planet is already
+feeling the consequences of human-driven environmental change
+(Intergovernmental Panel on Climate Change (IPCC) 2023). Yet, despite
+widespread awareness of these risks, many people still struggle to adopt
+behaviors that could help mitigate climate damage (Gifford 2011). This
+gap between knowledge and action is a central puzzle that governments,
+communities, and organizations are trying to solve (Kollmuss and Agyeman
+2002). If we are to tackle this crisis effectively, we need to better
+understand what stops people from acting, and how we can motivate change
+(Steg 2014).
+
+This paper examines how specific factors---such as age, education, and
+self-reported knowledge of climate change---shape people's willingness
+to engage in climate-friendly actions (Schultz 2002). By analyzing data
+from a 2018 survey (City of Toronto 2024), we explore the connection
+between demographic characteristics and behaviors like reducing energy
+consumption, using greener transportation, and lowering waste. The
+survey also delves into what prevents people from adopting these
+behaviors, uncovering obstacles like cost, convenience, and skepticism
+about the power of individual actions (Gifford 2011). With this
+analysis, we aim to uncover how these factors interact and what they
+mean for efforts to encourage sustainable choices (Stern 2000).
+
+The heart of this study is to measure how age, education, and knowledge
+of climate change influence the likelihood of adopting certain
+behaviors. We found that younger individuals and those with higher
+education levels are more likely to engage in actions like reducing car
+usage and adopting plant-based diets (Fulton 2022). However, older
+individuals are more inclined to take steps like cutting down on
+household energy use (Lee 2019). Beyond these demographic trends, we
+also discovered that barriers such as financial cost and doubts about
+the effectiveness of individual efforts often hold people back from
+taking action (Kollmuss and Agyeman 2002). These findings suggest that a
+``one-size-fits-all'' approach to climate communication won't work.
+Instead, targeted strategies that consider demographic differences are
+essential for driving meaningful engagement (Steg 2014).
+
+Understanding these patterns is crucial for crafting effective climate
+policies. By identifying which groups are more likely to act and which
+face significant barriers, we can better design interventions that speak
+to people's concerns and motivations (Stern 2000). The implications of
+this study go beyond simply knowing what people think about climate
+change---they offer a roadmap for shaping messages and policies that
+could shift behavior on a larger scale (Fulton 2022).
+
+The remainder of this paper is structured as follows:
+Section~\ref{sec-data} details the data and methods used in our
+analysis. Section~\ref{sec-model} describes how we assess the factors
+influencing climate-friendly behaviors across demographic groups.
+\textbf{?@sec-results} highlights key differences in behavior based on
+age, education, and knowledge of climate change.
+\textbf{?@sec-discussion} discusses the findings, addresses the study's
+limitations, and suggests directions for future research.
+Section~\ref{sec-conclusion} concludes with a summary of the key
+takeaways and actionable recommendations for enhancing climate action
+engagement. Finally, Section~\ref{sec-appendix} contains supplementary
+material.
+
+\section{Data}\label{sec-data}
+
+The primary data source for this project is the Climate Perception Study
+dataset, provided by the City of Toronto via the Open Data Toronto
+platform (City of Toronto 2024). This dataset offers insights into
+public perceptions of climate change in Toronto and was accessed from
+Open Data Toronto ({``Open Data Toronto''} 2024) on 6 November 2024.
+\#\# Software and R-packages This project was conducted using the
+statistical software \texttt{R} (R Core Team 2023). Data cleaning and
+manipulation were primarily facilitated by the \texttt{tidyverse}
+package (Wickham, Averick, et al. 2024), which encompasses various
+essential tools. Within this suite, \texttt{dplyr} (Wickham, François,
+et al. 2024) was employed for data manipulation tasks such as filtering,
+summarizing, and joining datasets, while \texttt{readr} (Wickham,
+Hester, et al. 2024) provided efficient functionality for reading and
+writing rectangular text data. Specifically, the \texttt{write\_csv}
+function from \texttt{tidyverse} was used to save the raw 2018 dataset.
+To handle Excel files, we incorporated the \texttt{httr} package for
+downloading files directly from online sources and \texttt{readxl}
+(Wickham and Bryan 2024), which enabled us to read Excel files
+seamlessly. Additionally, the \texttt{openxlsx} package was utilized to
+create a new Excel workbook with multiple sheets, allowing us to store
+the 2021 dataset in a structured format.
+
+The \texttt{arrow} package was employed to handle large datasets
+efficiently, ensuring smooth data processing, while \texttt{forcats} was
+used for reordering factor levels to facilitate more insightful analyses
+and visualizations. In terms of data tidying, the \texttt{tidyr} and
+\texttt{stringr} packages allowed us to reshape and clean the data by
+managing character strings and handling missing values. For the final
+documentation and report generation, the \texttt{knitr} package was
+instrumental in integrating R code and outputs into a cohesive and
+reproducible report format. This suite of R packages collectively
+enabled us to conduct thorough data management, manipulation, and
+analysis, ultimately contributing to the successful completion of the
+project.
+
+\subsection{Methodology}\label{methodology}
+
+\subsubsection{Data Collection}\label{data-collection}
+
+The data for this analysis comes from two surveys commissioned by the
+City of Toronto to assess residents' perceptions of climate change and
+their willingness to take community action. In 2018, Environics Research
+conducted n=404 online interviews with Toronto residents aged 18 and
+older between October 11 and October 18. Each interview lasted
+approximately 10 minutes. The sample was drawn from an online panel,
+with quotas set by region, age, and gender to reflect the city's
+population based on the 2016 Census, and minor weighting was applied.
+Due to the non-random nature of the online survey, no margin of error
+was assigned, though a random sample of this size would typically have a
+margin of ±4.9 percentage points, 19 times out of 20.
+
+In 2021, a second survey was conducted by Ipsos, a global market
+research company. This survey included n=1,400 Toronto residents aged 18
+and older and used a mixed-method approach. The sample consisted of
+1,000 respondents from an online panel, 300 recruited via cell phone and
+landline, and 100 online interviews conducted in Mandarin, Cantonese,
+and Punjabi. This combination of methods aimed to enhance the survey's
+representativeness. For analysis, Version 2 of the 2021 dataset, which
+presents responses in a numeric format, was used.
+
+\subsubsection{Data Analysis}\label{data-analysis}
+
+The primary focus of this analysis was the 2018 dataset, examining six
+key variables: age, education, extent informed, likelihood to take
+action, reasons for not taking action, and the best method for
+delivering information regarding climate change action. I analyzed these
+variables at the individual level in the 2018 dataset by calculating the
+percentages within each category, which provided a clear understanding
+of the distribution and trends within the population.
+
+In addition, I compared the 2018 dataset to the 2021 summary data to
+assess changes over the years. By calculating the percentage
+distribution for each variable in both years, I was able to identify any
+shifts in public awareness, engagement, and preferences regarding
+climate change action. This comparison revealed whether there have been
+notable changes in factors like the public's level of information about
+climate change, their likelihood to take action, and their preferred
+communication methods.
+
+This two-step approach allowed for a comprehensive understanding: a
+detailed exploration of the 2018 data combined with a broader comparison
+of trends between 2018 and 2021.
+
+\subsection{Features}\label{features}
+
+\subsubsection{Age}\label{age}
+
+\paragraph{Individual 2018}\label{individual-2018}
+
+Figure~\ref{fig-one} illustrates the age distribution of survey
+respondents in 2018. The histogram displays the frequency of respondents
+across different age groups, with the x-axis representing age intervals
+and the y-axis indicating the number of respondents within each
+interval. The distribution is relatively balanced, with two noticeable
+peaks around the 30--40 and 50--60 age ranges, suggesting these age
+groups are the most represented in the survey.
+
+The vertical dotted lines in the figure highlight key statistical
+measures: the green dotted line represents the median age, while the
+blue dashed line indicates the mean age of the respondents. Both
+measures fall near the center of the distribution, reinforcing the
+observation that the sample is primarily composed of middle-aged
+individuals. Although the distribution appears fairly symmetrical, there
+is a gradual decline in respondent frequency after the age of 60, with
+fewer participants aged 90 and above, indicating a smaller
+representation of older individuals.
+
+Overall, Figure~\ref{fig-one} provides valuable context for
+understanding the demographic composition of the survey sample. The
+predominance of middle-aged respondents may influence the interpretation
+of survey results, particularly if age is a factor in attitudes,
+behaviors, or preferences related to the study.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/age_individual_plot.png}
+
+}
+
+\caption{\label{fig-one}The histogram shows the distribution of age
+given the 2018 survey respondents.}
+
+\end{figure}%
+
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}
+
+(\textbf{table-one?}) illustrates the different age ditribution for 2018
+and 2021 surveys. The major difference is that there was greater
+representation of younger inviduals ranging from 18 to 23 in 2021
+compared to 2018. The remaining age groups were not very different.
+
+\begin{table}
+\centering
+\begin{tabular}[t]{l|r|r}
+\hline
+Age Group & 2018 Percentage & 2021 Percentage\\
+\hline
+18-23 & 4 & 11\\
+\hline
+24-39 & 33 & 30\\
+\hline
+40-55 & 30 & 26\\
+\hline
+56+ & 33 & 33\\
+\hline
+\end{tabular}
+\end{table}
+
+This table highlights the age distribution of survey respondents in 2018
+and 2021.
+
+\subsubsection{Highest Level of Education
+Completed}\label{highest-level-of-education-completed}
+
+\paragraph{Individual 2018}\label{individual-2018-1}
+
+Figure~\ref{fig-two} illustrates the distribution of survey respondents
+by their highest level of education attained. The most frequently
+reported education levels are ``Completed undergraduate degree'' and
+``Post graduate/professional school,'' with both categories having a
+noticeably higher frequency compared to others, indicating a
+well-educated respondent population. In contrast, fewer respondents
+reported ``Some community college, vocational, trade school'' and
+``Completed community college, vocational, trade school,'' suggesting
+these levels are less common among participants. Additionally, a small
+portion of respondents preferred not to disclose their education level.
+This distribution highlights a skew toward higher educational attainment
+within the sample, which may influence responses related to
+socio-economic factors and other survey topics.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/educ_individual_plot.png}
+
+}
+
+\caption{\label{fig-two}The histogram shows the distribution of
+education levels of 2018 survey respondents.}
+
+\end{figure}%
+
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}
+
+(\textbf{table-two?}) illustrates respondant education level in 2018 and
+2021 respectively. Please note, the categories of education level are
+different for 2018 and 2021 as these were different surveys and
+categories were updated in 2021. Despite this, we are still able to make
+comparisons. Individuals with high school diplomas or less account for 9
+for 2018 and 38 for 2021 (addition of less than highs school and high
+school or equivalent categories). This could indicate that the younger
+population was included more in the 2021 suvey or that less education
+individuals were surveyed. Additionally, its not super clear howver
+those with a post graduate or professional degree accounted for 29
+percent in 2018 and 35 percent in 2021. This illustrates that more
+educated inviduals responded to the 2021 survey.
+
+\begin{table}
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]},
+}                     %% tabularray inner close
+\toprule
+Education Level  & 2018 Percentage & Education Level & 2021 Percentage \\ \midrule %% TinyTableHeader
+High school or less                                   &  9 & Less than high school                                                 &  6 \\
+Some community college, vocational, trade school      &  5 & High School or equivalent                                             & 32 \\
+Completed community college, vocational, trade school & 12 & Degree or diploma from a college or university                        & 26 \\
+Some university                                       & 10 & Graduate or professional degree (examples: Master, PhD, MD or LLB/JD) & 35 \\
+Completed undergraduate degree                        & 32 & Prefer not to answer                                                  &  1 \\
+Post graduate/professional school                     & 29 & DK/NS                                                                 &  0 \\
+Prefer not to answer                                  &  3 &                                                                       & NA \\
+\bottomrule
+\end{tblr}
+\end{table}
+
+This table highlights the education distribution of survey respondents
+in 2018 and 2021.''
+
+\subsubsection{Extent Feel Informed}\label{extent-feel-informed}
+
+\paragraph{Individual 2018}\label{individual-2018-2}
+
+Figure~\ref{fig-three} depicts the distribution of self-reported climate
+change knowledge among survey respondents in 2018. The majority of
+participants identified as ``Very informed,'' making this the most
+prevalent category by a significant margin. A moderate number of
+respondents reported being ``Not very informed,'' while a smaller yet
+noticeable group described themselves as ``Extremely informed.'' In
+contrast, the categories ``Not at all informed'' and ``Not very
+informed'' have the lowest frequencies, with ``Not at all informed''
+being particularly rare. This distribution suggests that most
+respondents possess a relatively high level of awareness about climate
+change, with very few indicating a lack of knowledge on the topic.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/informed_individual_plot.png}
+
+}
+
+\caption{\label{fig-three}The histogram shows the distribution of
+self-reported climate change knowledge among 2018 survey respondents.}
+
+\end{figure}%
+
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}
+
+(\textbf{table-three?}) illustrates the self-reported level of extent
+inviduals feel informed about climate change and climate action for 2018
+and 2021. In 2018, the large marjority of individuals say they are very
+informed with 60 percent and the follwoign category is not very informed
+with 27 percent. In 2021, The majority of inividuals also say they are
+very informed but to a lesser degree with 48 percent and this is closely
+followed by only a little informed with 37 percent. There is a trend
+that invidiusls in 2018 reported greater levels of knowldege about
+climate change whereas 2021 illstrates a more even split between very
+informed and only little informed, portraying that fewer individuals
+have adequate knowledge about climate change.
+
+\begin{table}
+\centering
+\begin{tabular}[t]{l|l|l|l}
+\hline
+Extent Informed & 2018 Percentage & Extent Informed & 2021 Percentage\\
+\hline
+Extremely informed & 12 & Extremely informed & 13\\
+\hline
+Very informed & 60 & Very informed & 48\\
+\hline
+Not very informed & 27 & Only a little informed & 37\\
+\hline
+Not at all informed & 1 & Not at all informed & 2\\
+\hline
+\end{tabular}
+\end{table}
+
+This table highlights the extent feel informed distribution of survey
+respondents in 2018 and 2021.
+
+\subsubsection{Best Mode of Delivery}\label{best-mode-of-delivery}
+
+\paragraph{Individual 2018}\label{individual-2018-3}
+
+The analysis of the best method for delivering climate change
+information portrayed in Figure~\ref{fig-four} revealed that the
+majority of individuals in the 2018 dataset preferred receiving
+information firstly from advertising campaigns with about 55 percent,
+newsletters with about 52 percent, followed by the toronto website wiht
+about 46 percent. On the other side of the spectrum, few said they were
+uninterested in receiving climate action information with about 5
+percent, about 12 percent indicated twitter and then 17 percent
+mentioned instagram. Overall social media platforms Facebook, Instagram
+and Twtitter were less popular methods of communciation. This could be
+because the survey only included individals over the age of 18.
 Moreover, the median sample was in the 40s.
 
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-four
-#| fig-cap: The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action.
-
-knitr::include_graphics(here("data/03-figures_data", "communication_18_plot.png"))
-
-```
-
-#### Comparison 2018 to 2021
-@table-four compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
-Aside from the additon of four options to the 2021 survey, both surveys questions are the same.
-The leading category for 2018 is advertising campaigns with 55 percent, closely followed by newsletter emails with 52 percent and the Toronto website with 46.
-The 2021 survey illustrates a consistent trend with the same platforms as the top method of delivering information, specifically the Toronto website with 44 percent, then enewsletter emails with 43 percent and advertising campains at 42 percent.
-These top methods of communciation are more evenly spread out than the 2018 survey results.
-Social media platforms namely twitter, facebook and instagram all increased in the 2021 survey.
-Notable decreases in term of percentage from 2018 to 2021 include events, enewsletter emails, advertising campaigns, brochures and pamphlets.
-The new category of BetterHomesTO.ca webiste accounts for 15 percent of votes for the 2021 survey.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-# #| label: table-four
-# #| fig-cap: TODO
-
-# print(communication_summary_combined_table)
-```
-### Likelihood Taking Action
-#### Individual 2018
-The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
-@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
-On the x-axis, we have the nine different climate actions and on the y-axis is the percentage.
-The stacked bar chart allows understanding of how likely individuals are to take part in the given actions.
-Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action.
-The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements.
-40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely.
-However, 7 percent say they are very unlikely to change their method of transportation.
-Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely.
-Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action.
-Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof.
-In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle.
-While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely.
-This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases.
-This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change!
-The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely.
-Only 23 percent are already consuming meat alternatives.
-Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-five
-#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
-
-knitr::include_graphics(here("data/03-figures_data", "likelihood_individual_plot.png"))
-
-```
-
-# Model {#sec-model}
-The goal of our modelling strategy is twofold.
-Firstly, we aim to predict the likelihood of individuals engaging in climate-friendly actions based on demographic variables, specifically age and education.
-The actions considered include investing in electric or hybrid vehicles, making home improvements (such as using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste, sorting waste correctly, and walking or cycling shorter distances.
-Secondly, we aim to understand how these demographic characteristics influence individuals' likelihood of adopting these behaviors.Here we describe the probability tree model used to investigate the relationship between likelihood and the demographic factors of age and education.
-
-## Model set-up
-In this analysis, we focus on predicting the likelihood of taking climate-friendly actions based on the demographic variables of age and education.
-The likelihood is measured on a five-point Likert scale, ranging from "Very unlikely" to "Already doing this or have done this."
-
-### Model Specifications ###
-We use a probability tree model to predict the likelihood of individuals engaging in climate-friendly actions based on two key demographic variables: age and education.
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/communication_18_plot.png}
+
+}
+
+\caption{\label{fig-four}The stacked bar plot illustrates the preferred
+methods of communication for receiving information about climate change
+and climate action.}
+
+\end{figure}%
+
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}
+
+(\textbf{table-four?}) compares responses from 2018 and 2021 surverys
+regarding the best method of delivering information on climate change
+and climate action. Aside from the additon of four options to the 2021
+survey, both surveys questions are the same. The leading category for
+2018 is advertising campaigns with 55 percent, closely followed by
+newsletter emails with 52 percent and the Toronto website with 46. The
+2021 survey illustrates a consistent trend with the same platforms as
+the top method of delivering information, specifically the Toronto
+website with 44 percent, then enewsletter emails with 43 percent and
+advertising campains at 42 percent. These top methods of communciation
+are more evenly spread out than the 2018 survey results. Social media
+platforms namely twitter, facebook and instagram all increased in the
+2021 survey. Notable decreases in term of percentage from 2018 to 2021
+include events, enewsletter emails, advertising campaigns, brochures and
+pamphlets. The new category of BetterHomesTO.ca webiste accounts for 15
+percent of votes for the 2021 survey.
+
+\begin{table}
+\centering
+\begin{tabular}[t]{l|l|l|l}
+\hline
+Communication Method & 2018 Percentage & Communication Method & 2021 Percentage\\
+\hline
+Toronto.ca website & 46 & Toronto.ca website & 44\\
+\hline
+Events & 35 & City of Toronto events & 31\\
+\hline
+Twitter & 13 & Twitter & 17\\
+\hline
+Facebook & 25 & Facebook & 26\\
+\hline
+Instagram & 17 & Instagram & 25\\
+\hline
+Enewsletter / email & 52 & City of Toronto e-newsletters / email & 43\\
+\hline
+Councillor communication & 25 & Councillor e-newsletters & 24\\
+\hline
+Advertising campaigns & 55 & Advertising campaigns & 42\\
+\hline
+Brochures / Pamphlets & 38 & Printed or online brochures, pamphlets & 31\\
+\hline
+Other & 1 & BetterHomesTO.ca website & 15\\
+\hline
+Not interested & 5 & Not interested in receiving information & 8\\
+\hline
+ &  & Mail/ letter & 1\\
+\hline
+ &  & Nothing & 1\\
+\hline
+ &  & Other & 0\\
+\hline
+ &  & Don't know & 0\\
+\hline
+\end{tabular}
+\end{table}
+
+This table highlights the prefered method of communication of survey
+respondents in 2018 and 2021.
+
+\subsubsection{Likelihood Taking Action}\label{likelihood-taking-action}
+
+\paragraph{Individual 2018}\label{individual-2018-4}
+
+The likelihood of taking action against climate change was explored by
+assessing individuals' intentions and behaviors. Figure~\ref{fig-five}
+illustrates self-reported likelihood of taking certain actions that
+minimize climate change effects. On the x-axis, we have the nine
+different climate actions and on the y-axis is the percentage. The
+stacked bar chart allows understanding of how likely individuals are to
+take part in the given actions. Sorting waste into the correct bins is
+the action that most individuals are doing right now, accounting for 60
+percent whith 24 percent saying they are very likely to take part in
+this action. The next most prominent actions are walking or cycling
+short distances, reduce hydro usage, reduce waste and home improvements.
+40 percent of invidiuals report walking or cycling when traveling
+shorter distances in the city with 22 percent reporting they are very
+likely. However, 7 percent say they are very unlikely to change their
+method of transportation. Reducing the amount of energy and water use is
+already done by 36 percent and very likely for 29 percent only a mere 3
+percent is very unlikely. Reducing personal waste such as contributing
+to repurposing used products has similar percentages to responses for
+reducing hydro but even fewer individuals that report they are very
+unlikely to take action. Similarly, the likelihoods for making home
+improvements for energy efficiency such as energy-efficient appliances,
+programmable thermostat, LED lightbulbs, green or cool roof. In
+contrast, the action where the least number of individuals are
+contributing to is the investment of an electric or hybrid vehicle over
+gas-powered vehicles with only 8 percent who currently have an energy
+efficient vehicle. While 19 percetn are very likely to make this switch,
+14 percent say they are very unlikely. This illustrates that buying an
+electric or hybrid vehicle is action the least number of individuals are
+willing to invest in despite gas-powered vehicles being a major
+contributor to greenhouse gases. This action has a huge impact on the
+environment and yet 41 percent of this sample say they are unlikely to
+change! The second action that individuals are most unlikely to engage
+in is eat less meat by incorporating more plant-based foods in their
+diet with 12 percent very unlikely and 23 percent somewhat unlikely.
+Only 23 percent are already consuming meat alternatives. Vegans
+greenhosue gas emissions are on average 37\% lower than those who eat
+meat frequently.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_individual_plot.png}
+
+}
+
+\caption{\label{fig-five}The stacked bar plot shows the likelihood of
+survey respondents taking various actions to address climate change.}
+
+\end{figure}%
+
+\section{Model}\label{sec-model}
+
+The goal of our modelling strategy is twofold. Firstly, we aim to
+predict the likelihood of individuals engaging in climate-friendly
+actions based on demographic variables, specifically age and education.
+The actions considered include investing in electric or hybrid vehicles,
+making home improvements (such as using LED lightbulbs), adopting meat
+alternatives, minimizing car use, purchasing green products, reducing
+hydro usage, reducing waste, sorting waste correctly, and walking or
+cycling shorter distances. Secondly, we aim to understand how these
+demographic characteristics influence individuals' likelihood of
+adopting these behaviors.Here we describe the probability tree model
+used to investigate the relationship between likelihood and the
+demographic factors of age and education.
+
+\subsection{Model set-up}\label{model-set-up}
+
+In this analysis, we focus on predicting the likelihood of taking
+climate-friendly actions based on the demographic variables of age and
+education. The likelihood is measured on a five-point Likert scale,
+ranging from ``Very unlikely'' to ``Already doing this or have done
+this.''
+
+\subsubsection{Model Specifications}\label{model-specifications}
+
+We use a probability tree model to predict the likelihood of individuals
+engaging in climate-friendly actions based on two key demographic
+variables: age and education.
 
@@
 
-\begin{align} 
-y_i = \beta_0 + \beta_1 * Age_i + \beta_2 * Education_i + \epsilon_i
-\end{align*}
+\textbackslash begin\{align\} y\_i = \beta\_0 + \beta\_1 * Age\_i +
+\beta\_2 * Education\_i + \epsilon\_i \textbackslash end\{align*\}
 where:
 
- - $y_i$ represents the likelihood of individual $i$ engaging in a climate-friendly actin, measured on a five point Likert scale:
- 1. "Very unlikely"
- 2. "Somewhat unlikely"
- 3. "Somewhat likely"
- 4. "Very likely"
- 5. "Already doing this or have done this"
-- $\beta_0$ is the intercept, representing the baseline likelihood of taking action when all predictors are zero.
-- $\beta_1$ is the coefficient for Age, representing how a one-year increase affects the likelihood of taking action.
-- $\beta_2$ is the coefficient for Education, a categorical variable that is dummy-coded.
-- $\epsilon_i$ is the error term, accounting for unexplained variation.
-
-This model focuses on the direct effect of age and education on the likelihood of taking climate-friendly actions, assuming a linear relationship between these demographic variables and the outcome variable (the likelihood of action).
-
-### Model Justification 
-This model was developed to explore how demographic factors such as age and education influence individuals' likelihood of engaging in climate-friendly behaviors.
-By focusing on specific climate actions like reducing energy consumption, adopting sustainable practices, and investing in green technologies, the model aims to provide actionable insights for climate change interventions.
-
-#### Response Variable ####
-The response variable in this analysis is the likelihood of taking climate-friendly actions, measured using a Likert scale (1 = "Very unlikely" to 5 = "Already doing this or have done this").
-This scale captures the respondent’s perceived likelihood of engaging in various climate-friendly behaviors
-
-#### Input Variabless ####
+\begin{itemize}
+\tightlist
+\item
+  \(y_i\) represents the likelihood of individual \(i\) engaging in a
+  climate-friendly actin, measured on a five point Likert scale:
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  ``Very unlikely''
+\item
+  ``Somewhat unlikely''
+\item
+  ``Somewhat likely''
+\item
+  ``Very likely''
+\item
+  ``Already doing this or have done this''
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  \(\beta_0\) is the intercept, representing the baseline likelihood of
+  taking action when all predictors are zero.
+\item
+  \(\beta_1\) is the coefficient for Age, representing how a one-year
+  increase affects the likelihood of taking action.
+\item
+  \(\beta_2\) is the coefficient for Education, a categorical variable
+  that is dummy-coded.
+\item
+  \(\epsilon_i\) is the error term, accounting for unexplained
+  variation.
+\end{itemize}
+
+This model focuses on the direct effect of age and education on the
+likelihood of taking climate-friendly actions, assuming a linear
+relationship between these demographic variables and the outcome
+variable (the likelihood of action).
+
+\subsubsection{Model Justification}\label{model-justification}
+
+This model was developed to explore how demographic factors such as age
+and education influence individuals' likelihood of engaging in
+climate-friendly behaviors. By focusing on specific climate actions like
+reducing energy consumption, adopting sustainable practices, and
+investing in green technologies, the model aims to provide actionable
+insights for climate change interventions.
+
+\paragraph{Response Variable}\label{response-variable}
+
+The response variable in this analysis is the likelihood of taking
+climate-friendly actions, measured using a Likert scale (1 = ``Very
+unlikely'' to 5 = ``Already doing this or have done this''). This scale
+captures the respondent's perceived likelihood of engaging in various
+climate-friendly behaviors
+
+\paragraph{Input Variabless}\label{input-variabless}
+
 The input variables (predictors) include:
 
-- **Age**: Previous research indicates that younger individuals may be more inclined to adopt climate-friendly behaviors due to increased environmental awareness (Leiserowitz et al., 2010; Gifford, 2013).
-- **Education**: Higher levels of education are often linked to greater awareness of environmental issues and a higher likelihood of adopting sustainable behaviors (Kollmuss & Agyeman, 2002).
-Education is treated as a categorical variable and dummy-coded for analysis.
-
-#### Model Structure ####
-This model assumes a linear relationship between the predictors (age and education) and the likelihood of taking action.
-Specifically, the likelihood of taking climate-friendly actions is modeled as a function of age and education, with coefficients representing the change in the likelihood of action associated with a unit change in each predictor.
-
-There are no interaction terms in this model, meaning we assume that the effects of age and education on the likelihood of taking action are independent of each other.
-This simplicity ensures clear interpretation of each predictor's individual effect on the likelihood of taking climate-friendly actions.
-
-## Nine Models ##
-
-We fit nine separate probability tree models, one for each climate-friendly action we are predicting.
-Each model uses age and education as the predictors to estimate the likelihood of the corresponding action.
-These actions are:
-
-1. Likelihood of investing in an electric or hybrid vehicle
-2. Likelihood of making home improvements (e.g., using LED lightbulbs)
-3. Likelihood of adopting meat alternatives
-4. Likelihood of minimizing car use
-5. Likelihood of purchasing green products
-6  Likelihood of reducing hydro usage
-7. Likelihood of reducing waste by repurposing used products
-8. Likelihood of sorting waste correctly
-9. Likelihood of walking or cycling shorter distances
-
-Each model is built using the same structure but predicts a different outcome variable. This approach allows us to analyze the specific impact of age and education on each climate-friendly action.
-
-### Likelihood of investing in an electric or hybrid vehicle
-@model-one
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-one
-#| fig-cap: Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/vehicle_electric_tree.png"))
-
-```
-
-### Likelihood of making home improvements
-@model-two
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-two
-#| fig-cap: Probability tree for likelihood of making home improvements predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/home_improvement_tree.png"))
-
-```
-
-### Likelihood of adopting meat alternatives
-@model-three
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-three
-#| fig-cap: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/protein_alternative_tree.png"))
-
-```
-
-### Likelihood of minimizing car use
-@model-four
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-four
-#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/minimize_car_tree.png"))
-
-```
-
-### Likelihood of purchasing green products
-@model-five
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-five
-#| fig-cap: Probability tree for likelihood of purchasing green products, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/green_product_tree.png"))
-
-```
-
-### Likelihood of reducing hydro usage
-@model-six
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-six
-#| fig-cap: Probability tree for likelihood of reducing hydro usage, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/reduce_hydro_tree.png"))
-
-```
-
-###  Likelihood of reducing waste
-@model-seven
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-seven
-#| fig-cap: Probability tree for likelihood of reducing waste, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/reduce_waste_tree.png"))
-
-```
-
-###  Likelihood of sorting waste correctly
-@model-eight
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-eight
-#| fig-cap: Probability tree for likelihood of sorting waste correctly, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/sort_waste_tree.png"))
-
-```
-
-###  Likelihood of walking or cycling shorter distances
-@model-nine
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-nine
-#| fig-cap: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
-
-knitr::include_graphics(here::here("data/04-model_data/short_distance_tree.png"))
-
-```
-
-## Model Estimation and Interpretation ##
-The probability tree model estimates how the predictors age and education influence the likelihood of adopting climate-friendly behaviors.
-By splitting the data into branches based on these variables, the model helps identify decision rules that predict individuals' likelihood of taking actions such as reducing waste or investing in green products.
-We anticipate that younger individuals, due to greater environmental awareness, are more likely to engage in climate-positive actions, while those with higher levels of education may also be more inclined to adopt such behaviors, given their increased awareness of climate change and sustainable practices.
-The model estimates the parameters for age and education using regression techniques, providing coefficients that indicate how each factor influences the likelihood of taking climate-friendly actions.
-
-# Results
-
-## Model Summary Table
-The table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors such as age and education.
-Each row represents a different climate action (e.g., home improvement, reducing hydro, minimizing car use), with the corresponding accuracy of the model's predictions.
-The accuracy values reflect how well the models, which use age and education as predictors, align with the actual data.
-An accuracy of 33 percent  for home improvement" indicates that the model correctly predicted the outcome 33% of the time for this action.
-These accuracy values help evaluate the effectiveness of age and education as predictors for each specific climate action.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: table-five
-#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
-The accuracy values reflect how closely the model predictions align with the actual observed data.
-Higher accuracy values indicate better model performance.
-
-# Load the model accuracy data from the saved CSV
-model_accuracies <- read.csv(here::here("data/02-analysis_data/model_accuracies.csv"))
-
-# Round numeric columns to whole numbers
-model_accuracies[] <- lapply(model_accuracies, function(x) if(is.numeric(x)) round(x) else x)
-
-# Check the first few rows of the data to ensure it loaded and rounded correctly
-head(model_accuracies)
-
-```
-
-## Likelihood taking action by age
-@fig-six shows the relationship between age and the likelihood of engaging in various climate-related actions.
-The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely." The trend lines across each action show how engagement varies by age.
-
-### Electric / Hybrid Vehicle Adoption
-Younger respondents (15-24, 25-34) are less likely to adopt electric or hybrid vehicles, with only a small proportion already using or considering them.
-Adoption rates increase slightly in the 55-64 age group, then decline again in the 65+ group.
-This suggests that older individuals may have more resources or stability to invest in electric vehicles.
-
-### Home Improvement for Energy Efficiency
-Middle-aged individuals (35-54) are the most likely to engage in home improvement actions aimed at increasing energy efficiency.
-Younger age groups (15-24, 25-34) report lower likelihoods, likely due to barriers such as homeownership and disposable income.
-
-### Consumption of Meat Alternatives
-Younger age groups, especially 15-24 and 25-34, are more likely to adopt meat alternatives.
-As age increases, the likelihood of doing so decreases, possibly due to established dietary habits in older generations.
-
-### Minimizing Car Use
-A trend similar to that of meat alternatives is observed, with younger individuals more likely to minimize car use.
-Older respondents, particularly those 65 and older, show less inclination to reduce car usage, possibly due to mobility needs or lifestyle factors like suburban living.
-
-### Purchasing Green Products
-The likelihood of purchasing green products is relatively uniform across age groups.
-Middle-aged and older demographics show a slight increase in engagement, but the trend line remains mostly flat, indicating that this behavior is more influenced by factors such as income or environmental awareness rather than age.
-
-### Reducing Hydro Usage
-Older respondents (55-64 and 65+) are the most likely to reduce hydro usage, likely driven by cost-saving measures or environmental concerns. The trend line shows a steady increase with age.
-
-### Reducing and Sorting Waste
-Both reducing and sorting waste are more commonly reported by middle-aged and older groups (45-64). This may reflect increased awareness or resources for waste management.
-
-### Walking / Cycling Short Distances
- Younger respondents (15-34) are more likely to engage in walking or cycling short distances.
-As age increases, the likelihood of walking or cycling decreases, possibly due to physical limitations or differing lifestyle needs.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-six
-#| fig-cap: Likelihood of Taking Climate Change Actions by Age Group.
-The stacked bar chart illustrates the percentage of respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64, 65+) in terms of their self-reported likelihood to engage in nine distinct climate-related actions.
-Each color represents a different level of likelihood, from "Already doing this or have done this" to "Very unlikely." The black dashed trend line highlights how the likelihood of action changes across age groups, providing insights into generational differences in climate-related behavior.
-
-knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))
-
-```
-
-## Likelihood taking action by education 
-@fig-seven displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
-The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from "Prefer not to answer" to "Postgrad." Each action is shown across separate facets, revealing how education level correlates with engagement in each behavior.
-
-### Trends in Education Attainment and Climate-Friendly Actions
-Individuals with higher education levels generally show a higher likelihood of engaging in climate-friendly actions.
-This trend is evident across all behaviors, with respondents possessing undergraduate or postgraduate degrees more likely to adopt electric vehicles or purchase green products.
-
-#### Electric/Hybrid Vehicle Adoption
-Postgraduate degree holders are the most likely to have adopted or consider adopting electric or hybrid vehicles.
-In contrast, respondents with lower education levels, such as those with high school or less, are more likely to report being "Very unlikely" or "Somewhat unlikely" to adopt these vehicles.
-
-#### Minimizing Car Use
-Higher education levels correlate with a greater likelihood of minimizing car use, though the trend is less pronounced for individuals with lower education levels.
-
-#### Reducing Hydro Usage
-While education has a smaller impact on reducing hydro usage compared to other actions, those with higher education levels are still more likely to engage in this behavior.
-
-#### Purchasing Green Products and Reducing Waste
-Purchasing green products and reducing waste are more common among individuals with postsecondary education, especially those with undergraduate or postgraduate degrees.
-In contrast, individuals with lower education levels report more moderate engagement with these actions.
-
-### Adopting Meat Alternatives
-Higher education is associated with greater adoption of meat alternatives.
-This is particularly true for those with undergraduate or postgraduate education, while fewer respondents with lower education levels report engaging in this behavior.
-
-### Walking or Cycling Short Distances
-Walking or cycling short distances is a behavior that is relatively common across all education levels, though individuals with higher education levels show slightly higher engagement.
-
-### Sorting Waste Correctly
-Sorting waste correctly is one of the most consistently adopted behaviors across all education levels, with a relatively small proportion of respondents indicating they are unlikely to engage in this action.
-However, individuals with higher education are still more likely to fall in the "Already doing this" category.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-seven
-
-knitr::include_graphics(here("data/03-figures_data", "likelihood_education_plot.png"))
-
-```
-
-## Overall Summary of Results:
-The results indicate that both age and education significantly influence the likelihood of engaging in climate-related actions.
-Younger respondents tend to be more likely to adopt behaviors such as consuming meat alternatives and minimizing car use, while older individuals are more inclined to engage in actions that require larger investments or long-term commitments, such as reducing hydro usage and investing in energy-efficient home improvements.
-Higher educational attainment is also strongly linked to a greater likelihood of engaging in climate-friendly behaviors, particularly those that involve financial investment, like adopting electric vehicles and consuming meat alternatives.
-However, simpler actions such as sorting waste correctly are more widely reported across all education levels.
-These generational and educational differences highlight the importance of factors such as income, lifestyle, and environmental awareness in shaping individuals' climate-related behaviors.
-In light of these findings, it is crucial to consider demographic factors when designing policies or campaigns aimed at encouraging climate action, as different age and education groups exhibit varied levels of engagement with both simple and more complex sustainable practices.
-
-# Discussion
-
-## Age and Climate-Friendly Behaviors {#sec-first-point}
-The findings indicate that younger individuals are more likely to engage in climate-friendly actions perceived as low-cost and easier to implement, such as consuming meat alternatives and reducing car usage.
-The model results show that these behaviors have relatively higher predicted likelihoods among younger participants, aligning with existing research on generational differences in environmental attitudes.
-This trend may be driven by heightened environmental awareness and increased exposure to climate change discussions among younger generations, often through social media and educational initiatives.
-These results suggest that lifestyle factors and generational attitudes significantly shape behavioral patterns, with younger individuals gravitating toward actions that are both socially encouraged and accessible.
-
-## The Role of Education in Sustainable Actions {#sec-second-point}
-Education significantly influences individuals' likelihood of engaging in more substantial climate-friendly behaviors.
-Our models demonstrate that individuals with higher educational attainment are more likely to adopt behaviors requiring greater financial or logistical investment, such as purchasing electric vehicles or making energy-efficient home improvements.
-The accuracy of the models predicting these behaviors is relatively lower than for simpler actions, suggesting that education is an important but not sole determinant.
-This relationship between education and sustainability underscores the importance of knowledge and informed decision-making in supporting climate-friendly actions, particularly those with long-term environmental benefits.
-The data suggests that higher education increases both environmental awareness and the capacity to implement financially demanding sustainable practices, which are often inaccessible to those with lower educational levels.
-
-## The Influence of Climate Change Knowledge {#sec-third-point}
-Self-reported knowledge of climate change also plays a role in the likelihood of adopting sustainable behaviors.
-Our analysis shows that individuals with greater awareness are more proactive in making environmentally conscious choices, particularly for actions like reducing waste and conserving energy.
-However, the model accuracy for some knowledge-based behaviors remains moderate, highlighting a gap between awareness and action.
-This suggests that while raising awareness is critical, it must be paired with policies that reduce structural barriers to adopting more expensive or long-term sustainable actions.
-For example, financial incentives or subsidies for purchasing energy-efficient appliances could bridge this gap, ensuring individuals are both informed and able to make practical changes.
-
-## Limitations
-
-One significant limitation of this study is its reliance on self-reported survey data, which is inherently prone to biases such as social desirability bias and recall errors.
-Respondents may overestimate their environmental knowledge or exaggerate their participation in climate-friendly behaviors to present themselves in a favorable light.
-This introduces uncertainty into the accuracy of the models, as the input data may not fully reflect actual behaviors or knowledge levels.
-Additionally, self-reported data often lacks the granularity needed to explore complex interactions between socio-economic factors, such as income and household size, which can significantly influence sustainable actions.
-
-Another limitation arises from the use of summary data from the 2018 and 2021 surveys instead of individual-level data.
-While the summary statistics provided valuable insights into broad demographic trends, they limited the study’s ability to explore more nuanced patterns and interactions.
-For example, the summary data showed differences in education and age trends between 2018 and 2021, but without individual-level data, it was difficult to determine the direct effect of socio-economic factors on climate action likelihood.
-Future studies with access to raw, individual-level data could offer more precise estimates and a deeper understanding of these dynamics.
-
-## Challenges with Survey Data
-Survey data presents additional challenges, such as non-response bias, where certain demographic groups may be underrepresented, leading to skewed results.
-Additionally, the framing of survey questions can influence how respondents perceive and answer them, introducing further variability in the data.
-The inability to verify self-reported behaviors also limits the reliability of the conclusions drawn from such datasets.
-Despite these challenges, surveys remain a valuable tool for capturing perceptions and self-reported behaviors, but their findings should be interpreted with caution and, when possible, supplemented with objective data sources.
-
-## Future Directions
-Future research should aim to identify the specific barriers preventing certain demographic groups from adopting climate-friendly behaviors.
-This could involve examining factors such as income, access to resources, and perceived obstacles to sustainable practices.
-Additionally, targeted interventions, such as financial subsidies, public awareness campaigns, or infrastructure improvements, could make sustainable actions more accessible and affordable.
-Longitudinal studies would be particularly valuable for tracking how awareness of climate change influences sustained behavioral changes over time.
-Comparing individual-level data across different years could also provide insights into the long-term impact of educational and policy interventions on climate-friendly behaviors.
-
-Lastly, integrating objective data, such as energy consumption records or transportation usage statistics, could validate and enhance the accuracy of survey-based findings.
-This combined approach would offer a more comprehensive understanding of how demographic and socio-economic factors influence the adoption of sustainable actions, ultimately informing more effective climate policies and interventions.
-
-# Conclusion {#sec-conclusion}
-This study provides valuable insights into the demographic factors that influence individuals' likelihood to engage in climate-friendly behaviors, particularly age, education, and climate change knowledge.
-Younger individuals and those with higher levels of education are more likely to adopt sustainable behaviors, particularly those that require greater financial investment or long-term commitment.
-However, barriers such as financial constraints and access to resources remain significant challenges.
-Addressing these barriers through targeted policies and interventions could help make sustainable behaviors more accessible and the norm across all demographic groups.
-Future research should explore the underlying reasons for resistance to adopting climate-friendly behaviors and how external factors can help overcome these challenges to achieve widespread climate action.
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Age}: Previous research indicates that younger individuals may
+  be more inclined to adopt climate-friendly behaviors due to increased
+  environmental awareness (Leiserowitz et al., 2010; Gifford, 2013).
+\item
+  \textbf{Education}: Higher levels of education are often linked to
+  greater awareness of environmental issues and a higher likelihood of
+  adopting sustainable behaviors (Kollmuss \& Agyeman, 2002). Education
+  is treated as a categorical variable and dummy-coded for analysis.
+\end{itemize}
+
+\paragraph{Model Structure}\label{model-structure}
+
+This model assumes a linear relationship between the predictors (age and
+education) and the likelihood of taking action. Specifically, the
+likelihood of taking climate-friendly actions is modeled as a function
+of age and education, with coefficients representing the change in the
+likelihood of action associated with a unit change in each predictor.
+
+There are no interaction terms in this model, meaning we assume that the
+effects of age and education on the likelihood of taking action are
+independent of each other. This simplicity ensures clear interpretation
+of each predictor's individual effect on the likelihood of taking
+climate-friendly actions.
+
+\subsection{Nine Models}\label{nine-models}
+
+We fit nine separate probability tree models, one for each
+climate-friendly action we are predicting. Each model uses age and
+education as the predictors to estimate the likelihood of the
+corresponding action. These actions are:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Likelihood of investing in an electric or hybrid vehicle
+\item
+  Likelihood of making home improvements (e.g., using LED lightbulbs)
+\item
+  Likelihood of adopting meat alternatives
+\item
+  Likelihood of minimizing car use
+\item
+  Likelihood of purchasing green products 6 Likelihood of reducing hydro
+  usage
+\item
+  Likelihood of reducing waste by repurposing used products
+\item
+  Likelihood of sorting waste correctly
+\item
+  Likelihood of walking or cycling shorter distances
+\end{enumerate}
+
+Each model is built using the same structure but predicts a different
+outcome variable. This approach allows us to analyze the specific impact
+of age and education on each climate-friendly action.
+
+\subsubsection{Likelihood of investing in an electric or hybrid
+vehicle}\label{likelihood-of-investing-in-an-electric-or-hybrid-vehicle}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/vehicle_electric_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of investing in an electric or
+hybrid vehicle, predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of making home
+improvements}\label{likelihood-of-making-home-improvements}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/home_improvement_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of making home improvements
+predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of adopting meat
+alternatives}\label{likelihood-of-adopting-meat-alternatives}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/protein_alternative_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of adopting meat alternatives,
+predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of minimizing car
+use}\label{likelihood-of-minimizing-car-use}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/minimize_car_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of minimizing car use,
+predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of purchasing green
+products}\label{likelihood-of-purchasing-green-products}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/green_product_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of purchasing green products,
+predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of reducing hydro
+usage}\label{likelihood-of-reducing-hydro-usage}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_hydro_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of reducing hydro usage,
+predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of reducing
+waste}\label{likelihood-of-reducing-waste}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_waste_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of reducing waste, predicted by
+age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of sorting waste
+correctly}\label{likelihood-of-sorting-waste-correctly}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/sort_waste_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of sorting waste correctly,
+predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Likelihood of walking or cycling shorter
+distances}\label{likelihood-of-walking-or-cycling-shorter-distances}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/short_distance_tree.png}
+
+}
+
+\caption{Probability tree for likelihood of walking or cycling shorter
+distances, predicted by age and education.}
+
+\end{figure}%
+
+\subsection{Model Estimation and
+Interpretation}\label{model-estimation-and-interpretation}
+
+The probability tree model estimates how the predictors age and
+education influence the likelihood of adopting climate-friendly
+behaviors. By splitting the data into branches based on these variables,
+the model helps identify decision rules that predict individuals'
+likelihood of taking actions such as reducing waste or investing in
+green products. We anticipate that younger individuals, due to greater
+environmental awareness, are more likely to engage in climate-positive
+actions, while those with higher levels of education may also be more
+inclined to adopt such behaviors, given their increased awareness of
+climate change and sustainable practices. The model estimates the
+parameters for age and education using regression techniques, providing
+coefficients that indicate how each factor influences the likelihood of
+taking climate-friendly actions.
+
+\section{Results}\label{results}
+
+\subsection{Model Summary Table}\label{model-summary-table}
+
+The table presents the accuracy of models predicting the likelihood of
+various climate-friendly actions based on demographic factors such as
+age and education. Each row represents a different climate action (e.g.,
+home improvement, reducing hydro, minimizing car use), with the
+corresponding accuracy of the model's predictions. The accuracy values
+reflect how well the models, which use age and education as predictors,
+align with the actual data. An accuracy of 33 percent for home
+improvement'' indicates that the model correctly predicted the outcome
+33\% of the time for this action. These accuracy values help evaluate
+the effectiveness of age and education as predictors for each specific
+climate action.
+
+\begin{verbatim}
+                Model Accuracy
+1    home_improvement       33
+2        reduce_hydro       28
+3        minimize_car       39
+4    vehicle_electric       25
+5 protein_alternative       25
+6        reduce_waste       39
+\end{verbatim}
+
+\subsection{Likelihood taking action by
+age}\label{likelihood-taking-action-by-age}
+
+Figure~\ref{fig-six} shows the relationship between age and the
+likelihood of engaging in various climate-related actions. The x-axis
+represents the age groups, and the y-axis indicates the percentage of
+respondents reporting different likelihood levels, from ``Already doing
+this'' to ``Very unlikely.'' The trend lines across each action show how
+engagement varies by age.
+
+\subsubsection{Electric / Hybrid Vehicle
+Adoption}\label{electric-hybrid-vehicle-adoption}
+
+Younger respondents (15-24, 25-34) are less likely to adopt electric or
+hybrid vehicles, with only a small proportion already using or
+considering them. Adoption rates increase slightly in the 55-64 age
+group, then decline again in the 65+ group. This suggests that older
+individuals may have more resources or stability to invest in electric
+vehicles.
+
+\subsubsection{Home Improvement for Energy
+Efficiency}\label{home-improvement-for-energy-efficiency}
+
+Middle-aged individuals (35-54) are the most likely to engage in home
+improvement actions aimed at increasing energy efficiency. Younger age
+groups (15-24, 25-34) report lower likelihoods, likely due to barriers
+such as homeownership and disposable income.
+
+\subsubsection{Consumption of Meat
+Alternatives}\label{consumption-of-meat-alternatives}
+
+Younger age groups, especially 15-24 and 25-34, are more likely to adopt
+meat alternatives. As age increases, the likelihood of doing so
+decreases, possibly due to established dietary habits in older
+generations.
+
+\subsubsection{Minimizing Car Use}\label{minimizing-car-use}
+
+A trend similar to that of meat alternatives is observed, with younger
+individuals more likely to minimize car use. Older respondents,
+particularly those 65 and older, show less inclination to reduce car
+usage, possibly due to mobility needs or lifestyle factors like suburban
+living.
+
+\subsubsection{Purchasing Green
+Products}\label{purchasing-green-products}
+
+The likelihood of purchasing green products is relatively uniform across
+age groups. Middle-aged and older demographics show a slight increase in
+engagement, but the trend line remains mostly flat, indicating that this
+behavior is more influenced by factors such as income or environmental
+awareness rather than age.
+
+\subsubsection{Reducing Hydro Usage}\label{reducing-hydro-usage}
+
+Older respondents (55-64 and 65+) are the most likely to reduce hydro
+usage, likely driven by cost-saving measures or environmental concerns.
+The trend line shows a steady increase with age.
+
+\subsubsection{Reducing and Sorting
+Waste}\label{reducing-and-sorting-waste}
+
+Both reducing and sorting waste are more commonly reported by
+middle-aged and older groups (45-64). This may reflect increased
+awareness or resources for waste management.
+
+\subsubsection{Walking / Cycling Short
+Distances}\label{walking-cycling-short-distances}
+
+Younger respondents (15-34) are more likely to engage in walking or
+cycling short distances. As age increases, the likelihood of walking or
+cycling decreases, possibly due to physical limitations or differing
+lifestyle needs.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_age_plot.png}
+
+}
+
+\caption{\label{fig-six}Likelihood of Taking Climate Change Actions by
+Age Group. The stacked bar chart illustrates the percentage of
+respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64,
+65+) in terms of their self-reported likelihood to engage in nine
+distinct climate-related actions. Each color represents a different
+level of likelihood, from ``Already doing this or have done this'' to
+``Very unlikely.'' The black dashed trend line highlights how the
+likelihood of action changes across age groups, providing insights into
+generational differences in climate-related behavior.}
+
+\end{figure}%
+
+\subsection{Likelihood taking action by
+education}\label{likelihood-taking-action-by-education}
+
+Figure~\ref{fig-seven} displays how the likelihood of engaging in
+climate-friendly actions varies by educational attainment. The x-axis
+represents the proportion of respondents in each education category,
+while the y-axis lists the educational levels, from ``Prefer not to
+answer'' to ``Postgrad.'' Each action is shown across separate facets,
+revealing how education level correlates with engagement in each
+behavior.
+
+\subsubsection{Trends in Education Attainment and Climate-Friendly
+Actions}\label{trends-in-education-attainment-and-climate-friendly-actions}
+
+Individuals with higher education levels generally show a higher
+likelihood of engaging in climate-friendly actions. This trend is
+evident across all behaviors, with respondents possessing undergraduate
+or postgraduate degrees more likely to adopt electric vehicles or
+purchase green products.
+
+\paragraph{Electric/Hybrid Vehicle
+Adoption}\label{electrichybrid-vehicle-adoption}
+
+Postgraduate degree holders are the most likely to have adopted or
+consider adopting electric or hybrid vehicles. In contrast, respondents
+with lower education levels, such as those with high school or less, are
+more likely to report being ``Very unlikely'' or ``Somewhat unlikely''
+to adopt these vehicles.
+
+\paragraph{Minimizing Car Use}\label{minimizing-car-use-1}
+
+Higher education levels correlate with a greater likelihood of
+minimizing car use, though the trend is less pronounced for individuals
+with lower education levels.
+
+\paragraph{Reducing Hydro Usage}\label{reducing-hydro-usage-1}
+
+While education has a smaller impact on reducing hydro usage compared to
+other actions, those with higher education levels are still more likely
+to engage in this behavior.
+
+\paragraph{Purchasing Green Products and Reducing
+Waste}\label{purchasing-green-products-and-reducing-waste}
+
+Purchasing green products and reducing waste are more common among
+individuals with postsecondary education, especially those with
+undergraduate or postgraduate degrees. In contrast, individuals with
+lower education levels report more moderate engagement with these
+actions.
+
+\subsubsection{Adopting Meat
+Alternatives}\label{adopting-meat-alternatives}
+
+Higher education is associated with greater adoption of meat
+alternatives. This is particularly true for those with undergraduate or
+postgraduate education, while fewer respondents with lower education
+levels report engaging in this behavior.
+
+\subsubsection{Walking or Cycling Short
+Distances}\label{walking-or-cycling-short-distances}
+
+Walking or cycling short distances is a behavior that is relatively
+common across all education levels, though individuals with higher
+education levels show slightly higher engagement.
+
+\subsubsection{Sorting Waste Correctly}\label{sorting-waste-correctly}
+
+Sorting waste correctly is one of the most consistently adopted
+behaviors across all education levels, with a relatively small
+proportion of respondents indicating they are unlikely to engage in this
+action. However, individuals with higher education are still more likely
+to fall in the ``Already doing this'' category.
+
+\begin{figure}
+
+\centering{
+
+\captionsetup{labelsep=none}\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_education_plot.png}
+
+}
+
+\caption{\label{fig-seven}}
+
+\end{figure}%
+
+\subsection{Overall Summary of
+Results:}\label{overall-summary-of-results}
+
+The results indicate that both age and education significantly influence
+the likelihood of engaging in climate-related actions. Younger
+respondents tend to be more likely to adopt behaviors such as consuming
+meat alternatives and minimizing car use, while older individuals are
+more inclined to engage in actions that require larger investments or
+long-term commitments, such as reducing hydro usage and investing in
+energy-efficient home improvements. Higher educational attainment is
+also strongly linked to a greater likelihood of engaging in
+climate-friendly behaviors, particularly those that involve financial
+investment, like adopting electric vehicles and consuming meat
+alternatives. However, simpler actions such as sorting waste correctly
+are more widely reported across all education levels. These generational
+and educational differences highlight the importance of factors such as
+income, lifestyle, and environmental awareness in shaping individuals'
+climate-related behaviors. In light of these findings, it is crucial to
+consider demographic factors when designing policies or campaigns aimed
+at encouraging climate action, as different age and education groups
+exhibit varied levels of engagement with both simple and more complex
+sustainable practices.
+
+\section{Discussion}\label{discussion}
+
+\subsection{Age and Climate-Friendly Behaviors}\label{sec-first-point}
+
+The findings indicate that younger individuals are more likely to engage
+in climate-friendly actions perceived as low-cost and easier to
+implement, such as consuming meat alternatives and reducing car usage.
+The model results show that these behaviors have relatively higher
+predicted likelihoods among younger participants, aligning with existing
+research on generational differences in environmental attitudes. This
+trend may be driven by heightened environmental awareness and increased
+exposure to climate change discussions among younger generations, often
+through social media and educational initiatives. These results suggest
+that lifestyle factors and generational attitudes significantly shape
+behavioral patterns, with younger individuals gravitating toward actions
+that are both socially encouraged and accessible.
+
+\subsection{The Role of Education in Sustainable
+Actions}\label{sec-second-point}
+
+Education significantly influences individuals' likelihood of engaging
+in more substantial climate-friendly behaviors. Our models demonstrate
+that individuals with higher educational attainment are more likely to
+adopt behaviors requiring greater financial or logistical investment,
+such as purchasing electric vehicles or making energy-efficient home
+improvements. The accuracy of the models predicting these behaviors is
+relatively lower than for simpler actions, suggesting that education is
+an important but not sole determinant. This relationship between
+education and sustainability underscores the importance of knowledge and
+informed decision-making in supporting climate-friendly actions,
+particularly those with long-term environmental benefits. The data
+suggests that higher education increases both environmental awareness
+and the capacity to implement financially demanding sustainable
+practices, which are often inaccessible to those with lower educational
+levels.
+
+\subsection{The Influence of Climate Change
+Knowledge}\label{sec-third-point}
+
+Self-reported knowledge of climate change also plays a role in the
+likelihood of adopting sustainable behaviors. Our analysis shows that
+individuals with greater awareness are more proactive in making
+environmentally conscious choices, particularly for actions like
+reducing waste and conserving energy. However, the model accuracy for
+some knowledge-based behaviors remains moderate, highlighting a gap
+between awareness and action. This suggests that while raising awareness
+is critical, it must be paired with policies that reduce structural
+barriers to adopting more expensive or long-term sustainable actions.
+For example, financial incentives or subsidies for purchasing
+energy-efficient appliances could bridge this gap, ensuring individuals
+are both informed and able to make practical changes.
+
+\subsection{Limitations}\label{limitations}
+
+One significant limitation of this study is its reliance on
+self-reported survey data, which is inherently prone to biases such as
+social desirability bias and recall errors. Respondents may overestimate
+their environmental knowledge or exaggerate their participation in
+climate-friendly behaviors to present themselves in a favorable light.
+This introduces uncertainty into the accuracy of the models, as the
+input data may not fully reflect actual behaviors or knowledge levels.
+Additionally, self-reported data often lacks the granularity needed to
+explore complex interactions between socio-economic factors, such as
+income and household size, which can significantly influence sustainable
+actions.
+
+Another limitation arises from the use of summary data from the 2018 and
+2021 surveys instead of individual-level data. While the summary
+statistics provided valuable insights into broad demographic trends,
+they limited the study's ability to explore more nuanced patterns and
+interactions. For example, the summary data showed differences in
+education and age trends between 2018 and 2021, but without
+individual-level data, it was difficult to determine the direct effect
+of socio-economic factors on climate action likelihood. Future studies
+with access to raw, individual-level data could offer more precise
+estimates and a deeper understanding of these dynamics.
+
+\subsection{Challenges with Survey
+Data}\label{challenges-with-survey-data}
+
+Survey data presents additional challenges, such as non-response bias,
+where certain demographic groups may be underrepresented, leading to
+skewed results. Additionally, the framing of survey questions can
+influence how respondents perceive and answer them, introducing further
+variability in the data. The inability to verify self-reported behaviors
+also limits the reliability of the conclusions drawn from such datasets.
+Despite these challenges, surveys remain a valuable tool for capturing
+perceptions and self-reported behaviors, but their findings should be
+interpreted with caution and, when possible, supplemented with objective
+data sources.
+
+\subsection{Future Directions}\label{future-directions}
+
+Future research should aim to identify the specific barriers preventing
+certain demographic groups from adopting climate-friendly behaviors.
+This could involve examining factors such as income, access to
+resources, and perceived obstacles to sustainable practices.
+Additionally, targeted interventions, such as financial subsidies,
+public awareness campaigns, or infrastructure improvements, could make
+sustainable actions more accessible and affordable. Longitudinal studies
+would be particularly valuable for tracking how awareness of climate
+change influences sustained behavioral changes over time. Comparing
+individual-level data across different years could also provide insights
+into the long-term impact of educational and policy interventions on
+climate-friendly behaviors.
+
+Lastly, integrating objective data, such as energy consumption records
+or transportation usage statistics, could validate and enhance the
+accuracy of survey-based findings. This combined approach would offer a
+more comprehensive understanding of how demographic and socio-economic
+factors influence the adoption of sustainable actions, ultimately
+informing more effective climate policies and interventions.
+
+\section{Conclusion}\label{sec-conclusion}
+
+This study provides valuable insights into the demographic factors that
+influence individuals' likelihood to engage in climate-friendly
+behaviors, particularly age, education, and climate change knowledge.
+Younger individuals and those with higher levels of education are more
+likely to adopt sustainable behaviors, particularly those that require
+greater financial investment or long-term commitment. However, barriers
+such as financial constraints and access to resources remain significant
+challenges. Addressing these barriers through targeted policies and
+interventions could help make sustainable behaviors more accessible and
+the norm across all demographic groups. Future research should explore
+the underlying reasons for resistance to adopting climate-friendly
+behaviors and how external factors can help overcome these challenges to
+achieve widespread climate action.
 
@@
 
-# Appendix {#sec-appendix}
-
-# Idealized methodology {#sec-idealized-meth}
-## Survey objectives
-The primary objective of this study is to explore the factors influencing the likelihood of individuals engaging in climate-friendly behaviors.
-Specifically, the study aims to identify the age groups that are least likely to participate in sustainable actions and investigate how education levels impact climate-friendly behaviors.
-The research also seeks to determine whether individuals who report being relatively informed about climate change causes are more likely to take action to mitigate it.
-The underlying assumption is that individuals with greater knowledge of climate change should be more inclined to adopt behaviors that reduce its impact.
-Additionally, the study will examine the barriers that prevent people from engaging in sustainable behaviors, with the goal of identifying strategies to make these actions more accessible, affordable, and easy to adopt.
-The overarching aim is to develop solutions to increase the likelihood of participation in climate-friendly behaviors by removing existing barriers and promoting sustainability across different demographic groups.
-Part of this involves determining the most effective platforms for disseminating information about climate change, specifically by identifying which communication methods resonate most with different age groups.
-The research will also explore the role of education systems in fostering climate awareness and encouraging sustainable actions from a young age.
-Ultimately, the findings aim to provide actionable solutions to promote wider participation in climate-friendly actions, contributing to the fight against climate change.
-
-## Sampling approach
-This study will target a diverse set of respondents across various age groups and demographic characteristics to gain a comprehensive understanding of climate-friendly behaviors and their drivers.
-The sample will be stratified to ensure representation across youth and adult demographics, enabling a comparison of climate knowledge and behaviors between generations.
-The study will start by sampling youth as young as age 12.
-This age group is chosen because children are old enough to understand the basics of climate change and the actions required to address it but still impressionable enough for their behaviors to be influenced by education and social interventions.
-By including participants starting at age 12, we aim to assess how effective climate change education in schools is and whether it is shaping climate-friendly behaviors in the younger generation.
-
-In addition to youth, adults aged 18 and older will also be included to provide insight into longer-term behavioral trends, which may have been shaped by earlier education or a lack of education on the subject.
-The sampling will be stratified according to age, education level, income, and geographic location to capture a broad spectrum of experiences and perspectives on climate change and sustainability.
-Age groups will be divided into the following ranges: 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, and 65+, while education levels will range from middle school to postgraduate education.
-Income will be categorized as low (<$30,000), middle ($30,000–$99,999), and high (>$100,000), and participants will also be grouped based on urban, suburban, or rural geographic locations.
-This stratified sampling approach ensures a diverse representation of individuals, allowing for meaningful comparisons of climate knowledge and behaviors across different demographic groups.
-
-## Respondant recruitment 
-Participants will be recruited using a multi-channel approach to ensure broad representation across various age groups and geographic locations.
-For youth aged 12-17, recruitment will occur through schools, with cooperation from middle and high schools.
-District educational boards or individual teachers will be approached to distribute information about the survey, and parental consent will be obtained before participation.
-To recruit adults, online surveys will be distributed via social media, email lists, and relevant climate-focused online communities.
-Additionally, outreach will be conducted in community centers and public spaces to capture respondents from rural or underserved areas.
-Flyers, local advertisements, and community events will help ensure that the sample is representative of both urban and rural populations.
-
-Incentives such as gift cards or a donation to a climate-focused charity will be offered to participants to encourage engagement and improve response rates, especially among younger participants who may be less inclined to participate without an incentive.
-
-## Data Validation 
-To ensure the validity and reliability of the data, several validation mechanisms will be employed.
-Responses will be reviewed for internal consistency, such as cross-checking whether respondents who claim high levels of climate change knowledge also report engaging in corresponding climate-friendly behaviors.
-Participants who provide inconsistent answers or fail to complete the survey will be excluded from the analysis.
-Additionally, respondents may be contacted for clarification if their answers are ambiguous or incomplete.
-This will ensure that the data accurately reflects the participant's true attitudes and behaviors.
-
-# Weighting and Data adjustments
-The data collected will be weighted to account for any imbalances in demographic representation within the sample.
-Statistical weighting will adjust for factors such as age, education level, income, and geographic location to ensure the sample accurately reflects the broader population.
-Weighting will correct for any over- or under-representation of specific demographic groups, allowing for more generalizable findings.
-Additionally, data will be adjusted for non-response bias, with greater weight given to underrepresented groups (e.g., certain age groups or income levels) to correct for gaps in participation.
-
-## Budget
-The budget for this study will cover several key areas essential for effective data collection and analysis.
-A portion of the budget will be allocated to the survey platform and software tools needed for data collection, such as online survey tools and platforms for both youth and adult respondents.
-Since incentives are critical to encouraging participation, especially from younger individuals, funds will also be used to provide gift cards or donations to climate-related charities as incentives.
-To reach a diverse demographic, outreach costs will also be factored in, including the production and distribution of flyers, local advertisements, and outreach at community centers or schools.
-Lastly, resources will be dedicated to data analysis, including the purchase of statistical software like SPSS or R for cleaning, coding, and analyzing the responses.
-The final portion of the budget will cover any miscellaneous costs such as obtaining parental consent forms, printing, and mailing physical surveys or communication materials.
-
-## Survey design
-The survey design will be structured to capture a range of demographic and behavioral data in order to address the research objectives.
-The survey will begin with demographic questions to capture essential background information, including age, education level, income, and geographic location.
-These variables will allow the analysis to identify how climate-friendly behaviors and knowledge vary across different groups.
-The primary focus will be on participants' climate change knowledge, specifically assessing their awareness of its causes, impacts, and potential solutions.
-Respondents will be asked to rate their perceived level of knowledge about climate change on a Likert scale, ranging from "not informed" to "very informed." They will also be prompted to identify key contributors to climate change, as well as actions individuals can take to mitigate its effects.
-
-The next section of the survey will focus on climate-friendly behaviors, asking respondents to self-report on their engagement in specific actions such as reducing car use, purchasing electric vehicles, eating plant-based meals, recycling, and reducing household energy consumption.
-These behaviors will help determine the extent to which knowledge of climate change is translating into actions, as well as highlight potential gaps in engagement.
-
-Following this, the survey will include a section on barriers to sustainable behaviors, exploring factors that may be preventing individuals from adopting more climate-friendly actions.
-Participants will be asked to identify reasons such as cost, convenience, lack of knowledge, or skepticism.
-This will allow the study to pinpoint the most significant obstacles to widespread adoption of sustainable practices and provide insight into potential solutions.
-
-The final section will focus on how respondents prefer to receive information about climate change.
-Given the varying effectiveness of different communication channels for different age groups, the survey will include questions on the most effective platforms for disseminating climate change education, such as social media, school programs, TV ads, and email.
-By identifying these preferences, the study will be able to recommend the most suitable methods for spreading climate change awareness tailored to specific demographics.
-
-Each section of the survey will include a combination of multiple-choice, Likert scale, and open-ended questions to capture both quantitative and qualitative data.
-The open-ended responses will allow for more nuanced insights into the reasons behind individuals' climate-related behaviors and barriers.
-The design will aim to balance simplicity with comprehensiveness to ensure that the survey is engaging and easy to complete while still gathering sufficient data to answer the research questions effectively.
-
-## Tradeoffs and limitations
-While this methodology is designed to be comprehensive, there are inherent trade-offs and limitations that must be considered.
-One key limitation is the reliance on self-reported data.
-Since participants will be answering questions based on their own recollections and perceptions, there is the potential for bias, such as over-reporting sustainable behaviors or under-reporting barriers to climate action.
-This could skew the findings, particularly if individuals respond in a socially desirable manner.
-Additionally, while efforts will be made to capture a representative sample, there is a possibility of sampling bias, especially in rural areas or among specific income groups who may have limited access to the survey.
-This could affect the generalizability of the results.
-Further, survey fatigue is a potential issue, particularly with younger participants who may lose focus or fail to complete longer surveys.
-To mitigate this, the survey will be kept concise, though the breadth of questions may still pose challenges.
-Finally, while statistical weighting and adjustments for non-response bias will be implemented, there is always some degree of uncertainty regarding the effectiveness of these methods in fully correcting for bias or imbalances in the sample.
-These limitations must be taken into account when interpreting the findings of this study.
-
-## Idealized survey questions
-Thank you for your participation in the 2024 Climate Change Survey.
-This survey aims to gather information about public attitudes and behaviors related to climate change, with a focus on understanding the factors that influence people's engagement in climate-friendly actions.
-Your participation is entirely voluntary, and you may withdraw at any time, for any reason, with no questions asked.
-
-This survey collects data regarding your awareness of climate change, the actions you take to mitigate it, and the barriers that may prevent you from engaging in more sustainable behaviors.
-The data you provide will be kept confidential and will be used solely for research purposes.
-This survey is anonymous, and your responses will not be traceable back to you.
-The goal of this survey is to better understand the motivations, challenges, and opportunities related to climate action, with a view to improving strategies for promoting sustainability.
-
-If you have any questions or concerns about this survey or its methodology, please feel free to contact Lexi Knight via email at lexi.knight\@mail.utoronto.ca.
-Any correspondence will remain confidential and will not be shared with any external parties.
-
-**Screening and Consent:**
-
-By checking this box, I consent to this survey collecting information about my awareness of climate change, the actions I take to address it, and the factors that influence my behavior for research
-
-Correspondence will not be shared with any external parties.
--    I consent.
-
-**Demographic Information: **
-1. Whats your age? 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, 65+, Prefer not to say
-2.
-What is the highest level of education that you've completed?
-Some high school, High school diploma, Diploma / post secondary certificate (college, trade school).
-Bachelor's degree, Master's degree, Doctorate degree.
-
-**Climate Change knowledge and Awareness:**
-3. How would you rate your knowledge of the causes of climate change? Very informed, Somewhat informed, Neutral, Somewhat Uninformed, Very uninformed.
-4. How confident are you in your understanding of how to mitigate climate change through individual actions? Very confident, Confident, Neutral, Somewhat confident, Not confident.
-
-**Climate-Friendly Action: **
-5.
-Which of the following climate-friendly actions do you regularly engage in?
-(Select all that apply).
-Reduce personal vehicle use (e.g., carpooling, using public transport, biking or walking shorter distances), Use / install energy-efficient appliances / devices (e.g., LED bulbs, smart thermostats), Eat a plant-based diet or reduce meat consumption, Recycle and compost, Purchase eco-friendly products (e.g., sustainable clothing, eco-conscious brands), Use renewable energy sources (e.g., solar panels, wind energy), None of the above, Other.
-6. How often do you consider the environmental impact of your purchases? Always, Often, Sometimes, Rarely, Never
-
-**Barriers to Sustainable Actions: **
-7.
-What factors prevent you from engaging in more climate-friendly behaviors?
-(Select all that apply) Cost of sustainable products or services, Lack of time, Lack of knowledge about how to make sustainable choices, Convenience (e.g., environmentally harmful options are more accessible), Skepticism about the effectiveness of individual actions, No barriers (I already engage in sustainable behaviors), Other (please specify)
-8. Do you feel that climate-friendly behaviors are affordable for people in your community? Yes, No, Not sure
-9.
-Which of the following reasons best describe why you do not participate in more climate-friendly actions?
-(Select all that apply) I do not believe my individual actions will make a difference, I find it too difficult to make sustainable choices in my daily life, It is too expensive to adopt sustainable behaviors, I don’t know where to start or how to make a meaningful impact, Sustainable products or services are not easily available in my area, I do not feel that climate change directly affects me or my community, I am unsure about what actions are most effective in reducing climate change, I am not sure how to balance sustainable actions with my current lifestyle
-10.
-If you have avoided taking climate-friendly actions, what do you believe would make it easier for you to participate in these behaviors?
-(Select up to three) Lower cost of sustainable products or services, More convenient access to sustainable options, Clearer information on how individual actions can make a difference, More education or awareness about climate change, Incentives (e.g., government subsidies, rewards) to take action, More social pressure or norms encouraging sustainable behavior, Other (please specify)
-11.
-How much do you trust the information provided by the following groups on climate change?
-Government, Environmental NGOs, Local community organizations, Media (TV, online news), Social media influencers/bloggers, Scientists, I do not trust any of these sources
-12.
-If the government provided more support for individuals to take climate-friendly actions, would this lead you to taking more environmentally friendly actions (e.g., incentives, education programs, reduced cost)?
-Yes, No, Not sure
-13. How strongly do you agree with the following statement: "Taking climate-friendly actions is a personal responsibility." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
-14.
-How strongly do you agree with the following statement: "The government or businesses should take more responsibility for addressing climate change than individuals." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
-15.
-Do you think the reluctance to take action against climate change more due to a lack of knowledge about how to get involved, or is it primarily because sustainable actions are inconvenient for people?
-Lack of knowledge about how to take action, Inconvenience of sustainable actions, Both, Neither, Unsure
-
-**Education and Information: **
-16. How effective do you think current school programs are in educating students about climate change? Very ineffective, Somewhat ineffective, Neutral, Somewhat effective, Very effective
-17.
-Which platforms do you find most effective for receiving information about climate change?
-Social media (e.g., Instgram, Facebook, Twitter, TikTok), School programs, TV/Youtube, News articles, Websites, Podcasts, Community events, Email newsletters.
-
-**General Perception: **
-18. Do you believe that individual actions can make a significant difference in combating climate change? Yes, No, Not sure
-
-19.
-In your opinion, which of the following should be prioritized to encourage more sustainable behaviors?
-(Select up to two), Making sustainable actions more affordable, Providing more education and awareness about climate change, Improving the accessibility of sustainable options, Encouraging government policies and incentives for sustainable behaviors, Creating a societal norm where sustainable actions are expected and practiced
-
-**Confirmation Message**
-
-Thank you for your response.
-We greatly appreciate the time, effort, and honesty you dedicated to completing this survey.
-Your answers have been successfully recorded and will contribute significantly to our research!
-
-# Additional data details
-After data collection, the responses will be cleaned, coded, and analyzed using appropriate statistical methods.
-Analysis will focus on identifying correlations between demographic factors (age, education, income, geography) and engagement in climate-friendly behaviors.
-The data will also be examined for patterns in barriers to participation and preferences for information delivery.
-These findings will provide the basis for actionable recommendations to improve climate change education and encourage greater participation in sustainable behaviors.
-
-## Simlation Process {sec-simulation-process}
-For the purposes of this study, I simulated data to investigate various factors related to climate change behaviors, including demographics, education levels, awareness of climate change causes, and preferences for communication methods.
-The simulated dataset consists of 404 entries, each representing an individual.
-To create this dataset, I used the `tidyverse` and `arrow` packages in R and set a seed value `(set.seed(853))` to ensure the results were reproducible.
+\section{Appendix}\label{sec-appendix}
+
+\section{Idealized methodology}\label{sec-idealized-meth}
+
+\subsection{Survey objectives}\label{survey-objectives}
+
+The primary objective of this study is to explore the factors
+influencing the likelihood of individuals engaging in climate-friendly
+behaviors. Specifically, the study aims to identify the age groups that
+are least likely to participate in sustainable actions and investigate
+how education levels impact climate-friendly behaviors. The research
+also seeks to determine whether individuals who report being relatively
+informed about climate change causes are more likely to take action to
+mitigate it. The underlying assumption is that individuals with greater
+knowledge of climate change should be more inclined to adopt behaviors
+that reduce its impact. Additionally, the study will examine the
+barriers that prevent people from engaging in sustainable behaviors,
+with the goal of identifying strategies to make these actions more
+accessible, affordable, and easy to adopt. The overarching aim is to
+develop solutions to increase the likelihood of participation in
+climate-friendly behaviors by removing existing barriers and promoting
+sustainability across different demographic groups. Part of this
+involves determining the most effective platforms for disseminating
+information about climate change, specifically by identifying which
+communication methods resonate most with different age groups. The
+research will also explore the role of education systems in fostering
+climate awareness and encouraging sustainable actions from a young age.
+Ultimately, the findings aim to provide actionable solutions to promote
+wider participation in climate-friendly actions, contributing to the
+fight against climate change.
+
+\subsection{Sampling approach}\label{sampling-approach}
+
+This study will target a diverse set of respondents across various age
+groups and demographic characteristics to gain a comprehensive
+understanding of climate-friendly behaviors and their drivers. The
+sample will be stratified to ensure representation across youth and
+adult demographics, enabling a comparison of climate knowledge and
+behaviors between generations. The study will start by sampling youth as
+young as age 12. This age group is chosen because children are old
+enough to understand the basics of climate change and the actions
+required to address it but still impressionable enough for their
+behaviors to be influenced by education and social interventions. By
+including participants starting at age 12, we aim to assess how
+effective climate change education in schools is and whether it is
+shaping climate-friendly behaviors in the younger generation.
+
+In addition to youth, adults aged 18 and older will also be included to
+provide insight into longer-term behavioral trends, which may have been
+shaped by earlier education or a lack of education on the subject. The
+sampling will be stratified according to age, education level, income,
+and geographic location to capture a broad spectrum of experiences and
+perspectives on climate change and sustainability. Age groups will be
+divided into the following ranges: 12-17, 18-24, 25-34, 35-44, 45-54,
+55-64, and 65+, while education levels will range from middle school to
+postgraduate education. Income will be categorized as low
+(\textless\$30,000), middle (\$30,000--\$99,999), and high
+(\textgreater\$100,000), and participants will also be grouped based on
+urban, suburban, or rural geographic locations. This stratified sampling
+approach ensures a diverse representation of individuals, allowing for
+meaningful comparisons of climate knowledge and behaviors across
+different demographic groups.
+
+\subsection{Respondant recruitment}\label{respondant-recruitment}
+
+Participants will be recruited using a multi-channel approach to ensure
+broad representation across various age groups and geographic locations.
+For youth aged 12-17, recruitment will occur through schools, with
+cooperation from middle and high schools. District educational boards or
+individual teachers will be approached to distribute information about
+the survey, and parental consent will be obtained before participation.
+To recruit adults, online surveys will be distributed via social media,
+email lists, and relevant climate-focused online communities.
+Additionally, outreach will be conducted in community centers and public
+spaces to capture respondents from rural or underserved areas. Flyers,
+local advertisements, and community events will help ensure that the
+sample is representative of both urban and rural populations.
+
+Incentives such as gift cards or a donation to a climate-focused charity
+will be offered to participants to encourage engagement and improve
+response rates, especially among younger participants who may be less
+inclined to participate without an incentive.
+
+\subsection{Data Validation}\label{data-validation}
+
+To ensure the validity and reliability of the data, several validation
+mechanisms will be employed. Responses will be reviewed for internal
+consistency, such as cross-checking whether respondents who claim high
+levels of climate change knowledge also report engaging in corresponding
+climate-friendly behaviors. Participants who provide inconsistent
+answers or fail to complete the survey will be excluded from the
+analysis. Additionally, respondents may be contacted for clarification
+if their answers are ambiguous or incomplete. This will ensure that the
+data accurately reflects the participant's true attitudes and behaviors.
+
+\section{Weighting and Data
+adjustments}\label{weighting-and-data-adjustments}
+
+The data collected will be weighted to account for any imbalances in
+demographic representation within the sample. Statistical weighting will
+adjust for factors such as age, education level, income, and geographic
+location to ensure the sample accurately reflects the broader
+population. Weighting will correct for any over- or under-representation
+of specific demographic groups, allowing for more generalizable
+findings. Additionally, data will be adjusted for non-response bias,
+with greater weight given to underrepresented groups (e.g., certain age
+groups or income levels) to correct for gaps in participation.
+
+\subsection{Budget}\label{budget}
+
+The budget for this study will cover several key areas essential for
+effective data collection and analysis. A portion of the budget will be
+allocated to the survey platform and software tools needed for data
+collection, such as online survey tools and platforms for both youth and
+adult respondents. Since incentives are critical to encouraging
+participation, especially from younger individuals, funds will also be
+used to provide gift cards or donations to climate-related charities as
+incentives. To reach a diverse demographic, outreach costs will also be
+factored in, including the production and distribution of flyers, local
+advertisements, and outreach at community centers or schools. Lastly,
+resources will be dedicated to data analysis, including the purchase of
+statistical software like SPSS or R for cleaning, coding, and analyzing
+the responses. The final portion of the budget will cover any
+miscellaneous costs such as obtaining parental consent forms, printing,
+and mailing physical surveys or communication materials.
+
+\subsection{Survey design}\label{survey-design}
+
+The survey design will be structured to capture a range of demographic
+and behavioral data in order to address the research objectives. The
+survey will begin with demographic questions to capture essential
+background information, including age, education level, income, and
+geographic location. These variables will allow the analysis to identify
+how climate-friendly behaviors and knowledge vary across different
+groups. The primary focus will be on participants' climate change
+knowledge, specifically assessing their awareness of its causes,
+impacts, and potential solutions. Respondents will be asked to rate
+their perceived level of knowledge about climate change on a Likert
+scale, ranging from ``not informed'' to ``very informed.'' They will
+also be prompted to identify key contributors to climate change, as well
+as actions individuals can take to mitigate its effects.
+
+The next section of the survey will focus on climate-friendly behaviors,
+asking respondents to self-report on their engagement in specific
+actions such as reducing car use, purchasing electric vehicles, eating
+plant-based meals, recycling, and reducing household energy consumption.
+These behaviors will help determine the extent to which knowledge of
+climate change is translating into actions, as well as highlight
+potential gaps in engagement.
+
+Following this, the survey will include a section on barriers to
+sustainable behaviors, exploring factors that may be preventing
+individuals from adopting more climate-friendly actions. Participants
+will be asked to identify reasons such as cost, convenience, lack of
+knowledge, or skepticism. This will allow the study to pinpoint the most
+significant obstacles to widespread adoption of sustainable practices
+and provide insight into potential solutions.
+
+The final section will focus on how respondents prefer to receive
+information about climate change. Given the varying effectiveness of
+different communication channels for different age groups, the survey
+will include questions on the most effective platforms for disseminating
+climate change education, such as social media, school programs, TV ads,
+and email. By identifying these preferences, the study will be able to
+recommend the most suitable methods for spreading climate change
+awareness tailored to specific demographics.
+
+Each section of the survey will include a combination of
+multiple-choice, Likert scale, and open-ended questions to capture both
+quantitative and qualitative data. The open-ended responses will allow
+for more nuanced insights into the reasons behind individuals'
+climate-related behaviors and barriers. The design will aim to balance
+simplicity with comprehensiveness to ensure that the survey is engaging
+and easy to complete while still gathering sufficient data to answer the
+research questions effectively.
+
+\subsection{Tradeoffs and limitations}\label{tradeoffs-and-limitations}
+
+While this methodology is designed to be comprehensive, there are
+inherent trade-offs and limitations that must be considered. One key
+limitation is the reliance on self-reported data. Since participants
+will be answering questions based on their own recollections and
+perceptions, there is the potential for bias, such as over-reporting
+sustainable behaviors or under-reporting barriers to climate action.
+This could skew the findings, particularly if individuals respond in a
+socially desirable manner. Additionally, while efforts will be made to
+capture a representative sample, there is a possibility of sampling
+bias, especially in rural areas or among specific income groups who may
+have limited access to the survey. This could affect the
+generalizability of the results. Further, survey fatigue is a potential
+issue, particularly with younger participants who may lose focus or fail
+to complete longer surveys. To mitigate this, the survey will be kept
+concise, though the breadth of questions may still pose challenges.
+Finally, while statistical weighting and adjustments for non-response
+bias will be implemented, there is always some degree of uncertainty
+regarding the effectiveness of these methods in fully correcting for
+bias or imbalances in the sample. These limitations must be taken into
+account when interpreting the findings of this study.
+
+\subsection{Idealized survey
+questions}\label{idealized-survey-questions}
+
+Thank you for your participation in the 2024 Climate Change Survey. This
+survey aims to gather information about public attitudes and behaviors
+related to climate change, with a focus on understanding the factors
+that influence people's engagement in climate-friendly actions. Your
+participation is entirely voluntary, and you may withdraw at any time,
+for any reason, with no questions asked.
+
+This survey collects data regarding your awareness of climate change,
+the actions you take to mitigate it, and the barriers that may prevent
+you from engaging in more sustainable behaviors. The data you provide
+will be kept confidential and will be used solely for research purposes.
+This survey is anonymous, and your responses will not be traceable back
+to you. The goal of this survey is to better understand the motivations,
+challenges, and opportunities related to climate action, with a view to
+improving strategies for promoting sustainability.
+
+If you have any questions or concerns about this survey or its
+methodology, please feel free to contact Lexi Knight via email at
+lexi.knight@mail.utoronto.ca. Any correspondence will remain
+confidential and will not be shared with any external parties.
+
+\textbf{Screening and Consent:}
+
+By checking this box, I consent to this survey collecting information
+about my awareness of climate change, the actions I take to address it,
+and the factors that influence my behavior for research
+
+Correspondence will not be shared with any external parties. - I
+consent.
+
+\textbf{Demographic Information: } 1. Whats your age? 12-17, 18-24,
+25-34, 35-44, 45-54, 55-64, 65+, Prefer not to say 2. What is the
+highest level of education that you've completed? Some high school, High
+school diploma, Diploma / post secondary certificate (college, trade
+school). Bachelor's degree, Master's degree, Doctorate degree.
+
+\textbf{Climate Change knowledge and Awareness:} 3. How would you rate
+your knowledge of the causes of climate change? Very informed, Somewhat
+informed, Neutral, Somewhat Uninformed, Very uninformed. 4. How
+confident are you in your understanding of how to mitigate climate
+change through individual actions? Very confident, Confident, Neutral,
+Somewhat confident, Not confident.
+
+\textbf{Climate-Friendly Action: } 5. Which of the following
+climate-friendly actions do you regularly engage in? (Select all that
+apply). Reduce personal vehicle use (e.g., carpooling, using public
+transport, biking or walking shorter distances), Use / install
+energy-efficient appliances / devices (e.g., LED bulbs, smart
+thermostats), Eat a plant-based diet or reduce meat consumption, Recycle
+and compost, Purchase eco-friendly products (e.g., sustainable clothing,
+eco-conscious brands), Use renewable energy sources (e.g., solar panels,
+wind energy), None of the above, Other. 6. How often do you consider the
+environmental impact of your purchases? Always, Often, Sometimes,
+Rarely, Never
+
+\textbf{Barriers to Sustainable Actions: } 7. What factors prevent you
+from engaging in more climate-friendly behaviors? (Select all that
+apply) Cost of sustainable products or services, Lack of time, Lack of
+knowledge about how to make sustainable choices, Convenience (e.g.,
+environmentally harmful options are more accessible), Skepticism about
+the effectiveness of individual actions, No barriers (I already engage
+in sustainable behaviors), Other (please specify) 8. Do you feel that
+climate-friendly behaviors are affordable for people in your community?
+Yes, No, Not sure 9. Which of the following reasons best describe why
+you do not participate in more climate-friendly actions? (Select all
+that apply) I do not believe my individual actions will make a
+difference, I find it too difficult to make sustainable choices in my
+daily life, It is too expensive to adopt sustainable behaviors, I don't
+know where to start or how to make a meaningful impact, Sustainable
+products or services are not easily available in my area, I do not feel
+that climate change directly affects me or my community, I am unsure
+about what actions are most effective in reducing climate change, I am
+not sure how to balance sustainable actions with my current lifestyle
+10. If you have avoided taking climate-friendly actions, what do you
+believe would make it easier for you to participate in these behaviors?
+(Select up to three) Lower cost of sustainable products or services,
+More convenient access to sustainable options, Clearer information on
+how individual actions can make a difference, More education or
+awareness about climate change, Incentives (e.g., government subsidies,
+rewards) to take action, More social pressure or norms encouraging
+sustainable behavior, Other (please specify) 11. How much do you trust
+the information provided by the following groups on climate change?
+Government, Environmental NGOs, Local community organizations, Media
+(TV, online news), Social media influencers/bloggers, Scientists, I do
+not trust any of these sources 12. If the government provided more
+support for individuals to take climate-friendly actions, would this
+lead you to taking more environmentally friendly actions (e.g.,
+incentives, education programs, reduced cost)? Yes, No, Not sure 13. How
+strongly do you agree with the following statement: ``Taking
+climate-friendly actions is a personal responsibility.'' Strongly
+disagree, Disagree, Neutral, Agree, Strongly agree 14. How strongly do
+you agree with the following statement: ``The government or businesses
+should take more responsibility for addressing climate change than
+individuals.'' Strongly disagree, Disagree, Neutral, Agree, Strongly
+agree 15. Do you think the reluctance to take action against climate
+change more due to a lack of knowledge about how to get involved, or is
+it primarily because sustainable actions are inconvenient for people?
+Lack of knowledge about how to take action, Inconvenience of sustainable
+actions, Both, Neither, Unsure
+
+\textbf{Education and Information: } 16. How effective do you think
+current school programs are in educating students about climate change?
+Very ineffective, Somewhat ineffective, Neutral, Somewhat effective,
+Very effective 17. Which platforms do you find most effective for
+receiving information about climate change? Social media (e.g.,
+Instgram, Facebook, Twitter, TikTok), School programs, TV/Youtube, News
+articles, Websites, Podcasts, Community events, Email newsletters.
+
+\textbf{General Perception: } 18. Do you believe that individual actions
+can make a significant difference in combating climate change? Yes, No,
+Not sure
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{18}
+\tightlist
+\item
+  In your opinion, which of the following should be prioritized to
+  encourage more sustainable behaviors? (Select up to two), Making
+  sustainable actions more affordable, Providing more education and
+  awareness about climate change, Improving the accessibility of
+  sustainable options, Encouraging government policies and incentives
+  for sustainable behaviors, Creating a societal norm where sustainable
+  actions are expected and practiced
+\end{enumerate}
+
+\textbf{Confirmation Message}
+
+Thank you for your response. We greatly appreciate the time, effort, and
+honesty you dedicated to completing this survey. Your answers have been
+successfully recorded and will contribute significantly to our research!
+
+\section{Additional data details}\label{additional-data-details}
+
+After data collection, the responses will be cleaned, coded, and
+analyzed using appropriate statistical methods. Analysis will focus on
+identifying correlations between demographic factors (age, education,
+income, geography) and engagement in climate-friendly behaviors. The
+data will also be examined for patterns in barriers to participation and
+preferences for information delivery. These findings will provide the
+basis for actionable recommendations to improve climate change education
+and encourage greater participation in sustainable behaviors.
+
+\subsection{Simlation Process
+\{sec-simulation-process\}}\label{simlation-process-sec-simulation-process}
+
+For the purposes of this study, I simulated data to investigate various
+factors related to climate change behaviors, including demographics,
+education levels, awareness of climate change causes, and preferences
+for communication methods. The simulated dataset consists of 404
+entries, each representing an individual. To create this dataset, I used
+the \texttt{tidyverse} and \texttt{arrow} packages in R and set a seed
+value \texttt{(set.seed(853))} to ensure the results were reproducible.
 I generated the following variables:
 
-The age variable was sampled randomly from a range between 18 and 100 years old.
-For education, I created several categories, such as "high school or less," "some community college/trade school," and "postgraduate/professional school," with an option for "prefer not to answer." The informed variable was categorized into four levels, from "extremely informed" to "not at all informed," reflecting the extent to which individuals felt knowledgeable about climate change causes.
-To capture the likelihood of engaging in climate-friendly actions, I simulated the likelihood of taking action variable, with responses ranging from "already doing this or have done this" to "very unlikely." Finally, the communication method variable explored how individuals preferred to receive climate-related information, with options such as "Toronto.ca website," "social media platforms," and "advertising campaigns," among others.
-
-I used random sampling to generate values for each of these variables, ensuring a broad range of responses.
-After generating the data, I summarized it to verify its structure and consistency.
-The dataset was then saved as a `.parquet` file for further analysis.
-This approach allowed me to simulate a diverse set of responses and explore potential relationships between demographic factors, climate awareness, and willingness to engage in climate-friendly behaviors, all while maintaining the flexibility of synthetic data.
-
-## Data cleaning {#sec-data-cleaning}
-
-### 2018 Individual Data
-The cleaning process for the 2018 individual data began with selecting six key questions from the survey, focusing on variables that would provide insights into individual perceptions and behaviors regarding climate change.
-The corresponding columns were extracted and renamed with meaningful, descriptive names for clarity.
-The selected variables included age, the extent to which individuals consider themselves informed about the causes of climate change, the likelihood of taking specific climate actions, reasons for inaction (if they indicated they were unlikely to act), the highest level of education completed, and preferred methods for the city to deliver information about climate change and climate action.
-
-After selecting and renaming the columns, minor formatting inconsistencies were addressed.
-For instance, a missing space in the "verylikely" response category was corrected to "very likely." Additionally, certain values were reformatted to ensure compatibility with visualization tools, making the dataset easier to plot later.
-Unlike other datasets that often contain missing values or duplicate entries, this dataset was notably clean.
-There were no missing responses, and all questions were answered, allowing for a comprehensive analysis of survey participants' perceptions and behaviors.
-The dataset offered valuable insights into individuals’ likelihood of engaging in climate actions and their preferred communication channels for climate information.
-
-Throughout the cleaning process, no observations were removed, as every response was preserved to accurately represent the survey data.
-Despite encountering a few incorrect variable formats, these were easily corrected without data loss.
-The dataset provided a rare opportunity to analyze a complete and consistent set of individual responses, enabling a thorough exploration of both demographic characteristics and personal perceptions related to climate change.\
-
-### 2018 Summary Data
-Cleaning Process for the 2018 Summary Data
-To create the 2018 summary data, I built off the cleaned 2018 individual data.
-This approach was necessary because the 2021 data was only available in summarized form, not at the individual level.
-By summarizing the 2018 data in a comparable format, I could facilitate a meaningful comparison between the two years.
-The first step involved loading the cleaned 2018 individual dataset and mimicking the structure of the 2021 summary data as closely as possible.
-
-For age, I created the same age categories used in the 2021 dataset to ensure consistency between the two datasets.
-I then calculated the percentage of individuals within each age group and created a table summarizing this information.
-Similarly, I summarized the highest level of education completed by respondents, presenting it as a percentage of the total.
-However, a slight inconsistency emerged during this process, as the education levels and their descriptions differed between 2018 and 2021.
-Despite this discrepancy, I aligned the categories as closely as possible to maintain comparability.
-
-Next, I calculated the percentage of respondents who reported feeling informed about the causes of climate change and summarized the likelihood of taking various climate actions.
-This step was somewhat more complex, as the dataset contained nine different actions, each rated on a five-point scale of likelihood.
-I created a table showing the percentage likelihood of taking each specific action.
-Additionally, I analyzed the reasons respondents provided for being unlikely to take certain actions, which were only collected if they had indicated “unlikely” in the previous question.
-These reasons were summarized as counts rather than percentages, reflecting the conditional nature of the responses.
-
-Finally, I summarized the preferred methods for receiving climate-related information from the city, presenting this data as a percentage.
-This comprehensive summarization of the 2018 individual data provided a consistent and comparable dataset for analyzing trends and changes in perceptions and behaviors between 2018 and 2021.
-
-### 2021 Summary Data 
-The cleaning process for the 2021 summary data focuses on ensuring consistency and accuracy for six specific variables: age, education, extent informed, likelihood to take action, and reasons for not taking action.
-I first extracted data from the relevant sheets and columns in the 2021 raw dataset using read_excel from the tidyverse.
-For each category, I selected specific rows and converted raw data into percentages.
-The age and education data were cleaned and saved into separate data frames (age_summary_21 and education_summary_21), while other categories like "extent informed" and "likelihood to take action" required cleaning across multiple columns, with data transformation into percentages.
-Missing values and outliers were handled by filtering invalid entries and ensuring all values were consistent.
-
-Instead of merging datasets for 2018 and 2021, I aligned the 2018 summary data to match the structure and categories of the 2021 data to facilitate comparison.
-This alignment was necessary because the categories and structure of the two datasets differed, and I modified the 2018 dataset to resemble the 2021 format as closely as possible, allowing for a more direct comparison.
-By focusing on ensuring that categories and percentages were comparable between years, I preserved the integrity of both datasets.
-
-Finally, I saved each cleaned dataset into formatted tables using tinytable for LaTeX compatibility.
-These cleaned datasets were essential for analysis, ensuring that all variables were represented as percentages without any missing or erroneous data.
-This process also ensured that the dataset was ready for comparison with the 2018 data, with clear, consistent categories across both years.
+The age variable was sampled randomly from a range between 18 and 100
+years old. For education, I created several categories, such as ``high
+school or less,'' ``some community college/trade school,'' and
+``postgraduate/professional school,'' with an option for ``prefer not to
+answer.'' The informed variable was categorized into four levels, from
+``extremely informed'' to ``not at all informed,'' reflecting the extent
+to which individuals felt knowledgeable about climate change causes. To
+capture the likelihood of engaging in climate-friendly actions, I
+simulated the likelihood of taking action variable, with responses
+ranging from ``already doing this or have done this'' to ``very
+unlikely.'' Finally, the communication method variable explored how
+individuals preferred to receive climate-related information, with
+options such as ``Toronto.ca website,'' ``social media platforms,'' and
+``advertising campaigns,'' among others.
+
+I used random sampling to generate values for each of these variables,
+ensuring a broad range of responses. After generating the data, I
+summarized it to verify its structure and consistency. The dataset was
+then saved as a \texttt{.parquet} file for further analysis. This
+approach allowed me to simulate a diverse set of responses and explore
+potential relationships between demographic factors, climate awareness,
+and willingness to engage in climate-friendly behaviors, all while
+maintaining the flexibility of synthetic data.
+
+\subsection{Data cleaning}\label{sec-data-cleaning}
+
+\subsubsection{2018 Individual Data}\label{individual-data}
+
+The cleaning process for the 2018 individual data began with selecting
+six key questions from the survey, focusing on variables that would
+provide insights into individual perceptions and behaviors regarding
+climate change. The corresponding columns were extracted and renamed
+with meaningful, descriptive names for clarity. The selected variables
+included age, the extent to which individuals consider themselves
+informed about the causes of climate change, the likelihood of taking
+specific climate actions, reasons for inaction (if they indicated they
+were unlikely to act), the highest level of education completed, and
+preferred methods for the city to deliver information about climate
+change and climate action.
+
+After selecting and renaming the columns, minor formatting
+inconsistencies were addressed. For instance, a missing space in the
+``verylikely'' response category was corrected to ``very likely.''
+Additionally, certain values were reformatted to ensure compatibility
+with visualization tools, making the dataset easier to plot later.
+Unlike other datasets that often contain missing values or duplicate
+entries, this dataset was notably clean. There were no missing
+responses, and all questions were answered, allowing for a comprehensive
+analysis of survey participants' perceptions and behaviors. The dataset
+offered valuable insights into individuals' likelihood of engaging in
+climate actions and their preferred communication channels for climate
+information.
+
+Throughout the cleaning process, no observations were removed, as every
+response was preserved to accurately represent the survey data. Despite
+encountering a few incorrect variable formats, these were easily
+corrected without data loss. The dataset provided a rare opportunity to
+analyze a complete and consistent set of individual responses, enabling
+a thorough exploration of both demographic characteristics and personal
+perceptions related to climate change.\\
+
+\subsubsection{2018 Summary Data}\label{summary-data}
+
+Cleaning Process for the 2018 Summary Data To create the 2018 summary
+data, I built off the cleaned 2018 individual data. This approach was
+necessary because the 2021 data was only available in summarized form,
+not at the individual level. By summarizing the 2018 data in a
+comparable format, I could facilitate a meaningful comparison between
+the two years. The first step involved loading the cleaned 2018
+individual dataset and mimicking the structure of the 2021 summary data
+as closely as possible.
+
+For age, I created the same age categories used in the 2021 dataset to
+ensure consistency between the two datasets. I then calculated the
+percentage of individuals within each age group and created a table
+summarizing this information. Similarly, I summarized the highest level
+of education completed by respondents, presenting it as a percentage of
+the total. However, a slight inconsistency emerged during this process,
+as the education levels and their descriptions differed between 2018 and
+2021. Despite this discrepancy, I aligned the categories as closely as
+possible to maintain comparability.
+
+Next, I calculated the percentage of respondents who reported feeling
+informed about the causes of climate change and summarized the
+likelihood of taking various climate actions. This step was somewhat
+more complex, as the dataset contained nine different actions, each
+rated on a five-point scale of likelihood. I created a table showing the
+percentage likelihood of taking each specific action. Additionally, I
+analyzed the reasons respondents provided for being unlikely to take
+certain actions, which were only collected if they had indicated
+``unlikely'' in the previous question. These reasons were summarized as
+counts rather than percentages, reflecting the conditional nature of the
+responses.
+
+Finally, I summarized the preferred methods for receiving
+climate-related information from the city, presenting this data as a
+percentage. This comprehensive summarization of the 2018 individual data
+provided a consistent and comparable dataset for analyzing trends and
+changes in perceptions and behaviors between 2018 and 2021.
+
+\subsubsection{2021 Summary Data}\label{summary-data-1}
+
+The cleaning process for the 2021 summary data focuses on ensuring
+consistency and accuracy for six specific variables: age, education,
+extent informed, likelihood to take action, and reasons for not taking
+action. I first extracted data from the relevant sheets and columns in
+the 2021 raw dataset using read\_excel from the tidyverse. For each
+category, I selected specific rows and converted raw data into
+percentages. The age and education data were cleaned and saved into
+separate data frames (age\_summary\_21 and education\_summary\_21),
+while other categories like ``extent informed'' and ``likelihood to take
+action'' required cleaning across multiple columns, with data
+transformation into percentages. Missing values and outliers were
+handled by filtering invalid entries and ensuring all values were
+consistent.
+
+Instead of merging datasets for 2018 and 2021, I aligned the 2018
+summary data to match the structure and categories of the 2021 data to
+facilitate comparison. This alignment was necessary because the
+categories and structure of the two datasets differed, and I modified
+the 2018 dataset to resemble the 2021 format as closely as possible,
+allowing for a more direct comparison. By focusing on ensuring that
+categories and percentages were comparable between years, I preserved
+the integrity of both datasets.
+
+Finally, I saved each cleaned dataset into formatted tables using
+tinytable for LaTeX compatibility. These cleaned datasets were essential
+for analysis, ensuring that all variables were represented as
+percentages without any missing or erroneous data. This process also
+ensured that the dataset was ready for comparison with the 2018 data,
+with clear, consistent categories across both years.
 
@@
 
-# References
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-climateperceptionstudy}
+City of Toronto. 2024. {``Climate Perception Study.''}
+\url{https://open.toronto.ca/dataset/climate-perception-study/}.
+
+\bibitem[\citeproctext]{ref-Fulton2022}
+Fulton, Delaney, A. 2022. {``Demographic Determinants of Climate Action:
+How Age and Education Shape Environmental Engagement.''}
+\emph{Environmental Politics} 31 (4): 1--19.
+\url{https://doi.org/10.1080/09644016.2022.2011789}.
+
+\bibitem[\citeproctext]{ref-Gifford2011}
+Gifford, R. 2011. \emph{The Dragons of Inaction: Psychological Barriers
+That Limit Climate Change Mitigation and Adaptation}. \emph{American
+Psychologist}. Vol. 66. 4. American Psychologist.
+
+\bibitem[\citeproctext]{ref-IPCC2023}
+Intergovernmental Panel on Climate Change (IPCC). 2023. {``Climate
+Change 2023: The Physical Science Basis.''}
+\url{https://www.ipcc.ch/report/ar6/wg1/}.
+
+\bibitem[\citeproctext]{ref-Kollmuss2002}
+Kollmuss, A., and J. Agyeman. 2002. {``Mind the Gap: Why Do People Act
+Environmentally and What Are the Barriers to Pro-Environmental
+Behavior?''} \emph{Environmental Education Research} 8 (3): 239--60.
+\url{https://doi.org/10.1080/13504620220145401}.
+
+\bibitem[\citeproctext]{ref-Lee2019}
+Lee, Zhao, J. H. 2019. {``Older Adults and Their Engagement with Climate
+Change: A Study of Barriers to Action.''} \emph{Journal of Environmental
+Psychology} 65: 101345.
+\url{https://doi.org/10.1016/j.jenvp.2019.101345}.
+
+\bibitem[\citeproctext]{ref-opendatatoronto}
+{``Open Data Toronto.''} 2024. \url{https://open.toronto.ca/}.
+
+\bibitem[\citeproctext]{ref-citeR}
+R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
+Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\bibitem[\citeproctext]{ref-Schultz2002}
+Schultz, P. W. 2002. {``Knowledge, Information, and Household Recycling:
+Examining the Knowledge-Behavior Relationship.''} \emph{Environment and
+Behavior} 34 (3): 344--72.
+\url{https://doi.org/10.1177/001391602400773004}.
+
+\bibitem[\citeproctext]{ref-Steg2014}
+Steg, van den Berg, L. 2014. {``Environmental Psychology: An
+Introduction.''} \emph{Psychology Press}.
+\url{https://doi.org/10.4324/9780203383453}.
+
+\bibitem[\citeproctext]{ref-Stern2000}
+Stern, P. C. 2000. {``Toward a Coherent Theory of Environmentally
+Significant Behavior.''} \emph{Journal of Social Issues} 56 (3):
+407--24. \url{https://doi.org/10.1111/0022-4537.00175}.
+
+\bibitem[\citeproctext]{ref-tidyverse}
+Wickham, Hadley, Mara Averick, et al. 2024. \emph{Tidyverse: Easily
+Install and Load the 'Tidyverse'}.
+\url{https://CRAN.R-project.org/package=tidyverse}.
+
+\bibitem[\citeproctext]{ref-readxl}
+Wickham, Hadley, and Jennifer Bryan. 2024. \emph{Readxl: Read Excel
+Files}. \url{https://CRAN.R-project.org/package=readxl}.
+
+\bibitem[\citeproctext]{ref-dplyr}
+Wickham, Hadley, Romain François, et al. 2024. \emph{Dplyr: A Grammar of
+Data Manipulation}. \url{https://CRAN.R-project.org/package=dplyr}.
+
+\bibitem[\citeproctext]{ref-readr}
+Wickham, Hadley, Jim Hester, et al. 2024. \emph{Readr: Read Rectangular
+Text Data}. \url{https://CRAN.R-project.org/package=readr}.
+
+\end{CSLReferences}
+
+\end{document}

### 2024-12-09 paper/climate_change.qmd
fixing up modeling section

@@
 ```
+\newpage
+
 #### Comparison 2018 to 2021
@@
 
-### Likelihood of investing in an electric or hybrid vehicle
+### Decision Trees
+A decision tree is a machine learning model used to make predictions by recursively splitting data into subsets based on specific conditions of the predictor variables.
+It is structured like a tree, where the top node is the root node, representing the entire dataset, and subsequent nodes represent splits based on decision rules.
+The branches indicate the outcomes of these rules, and the leaf nodes (terminal nodes) provide the final prediction for each subset.
+
+Each split is determined by the predictor variable most strongly associated with the target outcome, maximizing predictive accuracy.
+A split separates individuals by age or educational level.
+The prediction in each terminal node includes the majority class (e.g., "Very likely") and additional information such as sample size (n) and error percentage.
+The error percentage reflects the proportion of cases in that node misclassified by the model.
+A higher error percentage indicates greater uncertainty or variability within the group, while a lower error percentage suggests a more precise classification.
+
+#### Likelihood of investing in an electric or hybrid vehicle
+The decision tree predicts individuals’ likelihood to invest in an electric or hybrid vehicle based on their highest level of education and age.
+The model identifies highest level of education as the most important variable for the initial split.
+At the root node, individuals are divided into two groups: those with "Some Community/Trade School" or "Some University" education and those with other educational backgrounds such as "High School," "Undergrad," "Postgrad," or "Prefer Not to Answer."
+
+For individuals with "Some Community/Trade School" or "Some University" education, the tree predicts that they are "Very likely" to invest, with a sample size of 47 and an error rate of 63.8%.
+This indicates moderate variability within this group.
+
+For those with other educational backgrounds, further splits are based on age.
+Younger individuals (below 38.5 years) are segmented further.
+A subset aged under 34.5 years is split into two groups, with one group (n = 10) being "Very likely" to invest, with a lower error rate of 30%.
+The other group is classified as "Somewhat likely," with a higher error rate of 60.7%.
+Older individuals (38.5 years or older) are less likely to invest.
+For instance, those aged above 68.5 years are predicted as "Very unlikely" with a sample size of 18 and an error rate of 61.1%, while those aged between 34.5 and 68.5 years are divided into "Somewhat unlikely" or "Somewhat likely" categories.
+
+Overall, the decision tree reveals distinct patterns where educational attainment and age interact to predict investment likelihood, with younger individuals and those with less formal education being more likely to invest.
+
 ```{r}
@@
 
-### Likelihood of making home improvements
+#### Likelihood of making home improvements
+The decision tree classifies individuals based on their likelihood of making home improvements to minimize climate change, using age and educational level as predictor variables.
+The root node splits the data at age 35.5, indicating that age is the most influential factor in determining climate-related home improvement behavior.
+Individuals aged 36 years or older are predominantly classified as "Already doing this or have done this," with a large sample size (n = 223) but a moderate error rate of 59.6%, reflecting variability in this group.
+
+For individuals younger than 36 years, the tree introduces education as the next important factor.
+Those with higher educational attainment ("Community/Trade School," "Some University," or "Postgraduate") are classified as "Very likely" to make climate-conscious home improvements (n = 40) with an error rate of 55.0%.
+Conversely, individuals with lower education levels, such as "High School" or "Some Community/Trade School," are classified as "Somewhat likely" (n = 46) but have a higher error rate of 67.4%, indicating less predictive certainty.
+A smaller subset of younger individuals with similar educational attainment is classified as "Somewhat likely" (n = 10) with a lower error rate of 40.0%, suggesting higher confidence in this classification.
+The decision tree highlights clear trends based on age and education, with older age groups and higher educational attainment linked to greater engagement in making home improvements.
+
 ```{r}
@@
 
-### Likelihood of adopting meat alternatives
+#### Likelihood of adopting meat alternatives
 ```{r}
@@
 
-### Likelihood of minimizing car use
+#### Likelihood of minimizing car use
 ```{r}
@@
 
-### Likelihood of purchasing green products
+#### Likelihood of purchasing green products
 ```{r}
@@
 
-### Likelihood of reducing hydro usage
+#### Likelihood of reducing hydro usage
 ```{r}
@@
 
-###  Likelihood of reducing waste
+####  Likelihood of reducing waste
 ```{r}
@@
 
-###  Likelihood of sorting waste correctly
+####  Likelihood of sorting waste correctly
 ```{r}
@@
 
-###  Likelihood of walking or cycling shorter distances
+####  Likelihood of walking or cycling shorter distances
 ```{r}
@@
 ### Electric / Hybrid Vehicle Adoption
-Younger respondents (15-24, 25-34) are less likely to adopt electric or hybrid vehicles, with only a small proportion already using or considering them.
-Adoption rates increase slightly in the 55-64 age group, then decline again in the 65+ group.
-This suggests that older individuals may have more resources or stability to invest in electric vehicles.
+The model indicates that individuals with "Some Community/Trade School" or "Some University" education are the most likely to invest in electric or hybrid vehicles.
+This group is classified as "Very likely" (n = 47) with an error rate of 64%, suggesting that while many in this category are inclined to invest, there is notable variability.
+Among individuals with other educational backgrounds, age plays a key role.
+Younger individuals under 35 years old, particularly those classified as "Very likely" (n = 10, error = 30%), demonstrate a strong tendency to invest, reflecting high confidence in this prediction.
+However, another subset of younger individuals (n = 28) is "Somewhat likely," with a higher error rate of 61%, indicating less certainty.
+These trends suggest younger people are more open to adopting electric or hybrid vehicles, likely due to environmental awareness or familiarity with emerging technologies.
+
+Older individuals, particularly those over 69 years old, are the least likely to invest.
+This group is classified as "Very unlikely" (n = 18) with an error rate of 61.1%, highlighting some uncertainty but an overall low likelihood of adoption.
+Middle-aged individuals (35 to 69 years old) show more mixed results, with some classified as "Somewhat unlikely" (n = 84, error = 54%) and others as "Somewhat likely" (n = 46, error = 57%).
+These findings suggest that barriers such as cost, resistance to change, or lower interest in alternative vehicles may deter older age groups.
+
+In summary, the model suggests that younger individuals, particularly those under 35 years old, and those with mid-level education are the most likely to invest in electric or hybrid vehicles.
+In contrast, older individuals and those with minimal or advanced education are less likely to adopt these technologies.
+While the model provides insights into these trends, the error rates indicate variability in some predictions, particularly among "Somewhat likely" and "Somewhat unlikely" groups.
 
 ### Home Improvement for Energy Efficiency
-Middle-aged individuals (35-54) are the most likely to engage in home improvement actions aimed at increasing energy efficiency.
-Younger age groups (15-24, 25-34) report lower likelihoods, likely due to barriers such as homeownership and disposable income.
+The results reveal that age is the most significant predictor of climate-conscious home improvement behavior.
+Individuals aged 36 years or older are the most likely to already be taking or have taken such actions.
+This group represents the largest sample size (n = 223) but also exhibits a moderate error rate (59.6%), indicating some variation in their behaviors.
+
+For younger individuals (under 36 years), educational attainment is a key determinant.
+Those with higher education levels, such as "Community/Trade School," "Some University," or "Postgraduate," are the most likely to take action ("Very likely") with an error rate of 55%.
+However, younger individuals with lower levels of education, such as "High School" or "Some Community/Trade School," are less likely to engage in these actions, being classified as "Somewhat likely" but with a higher error rate of 67%, indicating greater variability in this group.
+
+Overall, individuals aged 36 or older are more likely to have already engaged in climate-conscious home improvements, regardless of education level.
+Younger individuals with higher education are more likely to adopt such changes in the future, while those with lower education are less likely, with predictions for this group being less certain.
+These findings underscore the importance of both age and education in shaping environmental engagement and suggest that outreach efforts might need to target younger, less-educated groups to increase participation.
 

### 2024-12-09 scripts/06-model_data.R

@@ -7,7 +7,6 @@
 # Pre-requisites: complete 01-download_data.R and 03-clean_data.R in scripts folder in order to access data.
 
 
-#### Workspace setup ####
 
 #### Workspace setup ####
 
@@ -23,6 +22,25 @@ set.seed(853)
 
 #### Read data ####
 climate_data <- read_csv(here::here("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv"))
+
+#### Shorten education level names ####
+# Function to map long education names to shorter, more concise names
+shorten_education_levels <- function(education) {
+  case_when(
+    education == "High school or less" ~ "High School",
+    education == "Some community college, vocational, trade school" ~ "Some Community / Trade School",
+    education == "Completed community college, vocational, trade school" ~ "Community / Trade School",
+    education == "Some university" ~ "Some University",
+    education == "Completed undergraduate degree" ~ "Undergrad",
+    education == "Post graduate/professional school" ~ "Postgrad",
+    education == "Prefer not to answer" ~ "Pref no Answer",
+    TRUE ~ education # Default: keep original value if not matched
+  )
+}
+
+# Apply the function to shorten names in the dataset
+climate_data <- climate_data %>%
+  mutate(highest_level_educ = shorten_education_levels(highest_level_educ))
 
 # Function to generate decision trees, predictions, confusion matrix, and accuracy
 generate_model <- function(target_var, train_data, test_data, model_name) {
@@ -53,6 +71,7 @@ generate_model <- function(target_var, train_data, test_data, model_name) {
   return(accuracy)
 }
 
+#### Loop to create models for different target variables ####
 # Create a data frame to store the model names and their corresponding accuracies
 model_results <- data.frame(Model = character(0), Accuracy = numeric(0))
 

### 2024-12-10 paper/climate_change.qmd
updating model and results section

@@
 #### Likelihood of adopting meat alternatives
+The decision tree predicts individuals’ likelihood of consuming meat alternatives to minimize the effects of climate change based on their age and highest level of education.
+The model identifies age as the most important variable for the initial split.
+At the root node, individuals are divided into two groups: those under 34.5 years old and those 34.5 years or older.
+This highlights age as a critical factor influencing the likelihood of adopting meat alternatives.
+
+In the subgroup of individuals under 34.5 years old, the decision tree further splits based on age at 31.5 years, classifying younger individuals into categories of “Somewhat likely” (n = 25, error = 44%) and “Somewhat unlikely” (n = 62, error = 62.9%).
+On the other hand, for individuals aged 34.5 years or older, the model considers highest level of education as the next key variable, separating those with community/trade school, undergraduate, and postgraduate education from those with high school education.
+This distinction reflects how educational attainment moderates the impact of age on the decision to adopt meat alternatives.
+
+Within the older age group, additional splits occur based on age, such as at 49 years and 65.5 years, leading to further classifications like “Already doing this or have done this” or “Somewhat likely.” These splits indicate how the interaction between age and education level shapes patterns of meat alternative adoption, resulting in more granular predictions.
+
 ```{r}
@@
 #### Likelihood of minimizing car use
+The decision tree predicts individuals' likelihood of minimizing car use as a measure to mitigate climate change.
+In this case, the tree structure is straightforward, containing only a single root node.
+The model classifies all individuals into one category, "Already doing this or have done this," with a sample size of 320 and an error rate of 61.9%.
+The absence of splits in the tree indicates that no other variables, such as age or education, contributed sufficient predictive power to justify further segmentation.
+
+This outcome suggests that either the input data lacks variability in relevant features, or the behavior of minimizing car use is widespread and consistent across the sample population.
+Consequently, the model does not differentiate between subgroups and treats all individuals as having the same likelihood of engaging in this behavior.
 ```{r}
@@
 #### Likelihood of purchasing green products
+The decision tree predicts individuals' likelihood of purchasing green products to minimize the effects of climate change based on age and highest level of education.
+The model identifies age as the most important variable for the initial split.
+At the root node, individuals are divided into two groups: those younger than 37.5 years old and those 37.5 years or older.
+This division highlights age as a key determinant in predicting green product purchasing likelihood.
+
+For individuals aged 37.5 years or older, the next split is determined by the highest level of education.
+Those with educational backgrounds such as "High School," "Postgrad," "Some Community/Trade School," "Some University," or "Prefer Not to Answer" are further analyzed.
+Within this group, additional splits are made based on age thresholds of 50.5 years and 47.5 years.
+These splits refine the classification into categories such as "Somewhat likely" or "Already doing this or have done this," with varying error rates and sample sizes.
+
+Among individuals younger than 37.5 years, the highest level of education again plays a crucial role in the split.
+Individuals with educational backgrounds such as "Postgrad," "Community/Trade School," "High School," or "Some University" are further segmented.
+Within this subgroup, age thresholds of 27.5 years and 22.5 years are used to differentiate individuals into categories such as "Very likely" or "Somewhat likely," reflecting diverse levels of engagement with green product purchasing.
+Overall, the decision tree incorporates age and education as the primary variables to segment individuals into likelihood categories.
 ```{r}
@@
 ### Consumption of Meat Alternatives
-Younger age groups, especially 15-24 and 25-34, are more likely to adopt meat alternatives.
-As age increases, the likelihood of doing so decreases, possibly due to established dietary habits in older generations.
+The model suggests that age is the strongest predictor of individuals’ likelihood to adopt meat alternatives for climate change mitigation.
+Younger individuals, particularly those under 34.5 years old, show varying tendencies.
+Among this group, those aged 31.5 years or younger are divided into “Somewhat likely” (n = 25, error = 44%) and “Somewhat unlikely” (n = 62, error = 62.9%), indicating considerable variability in predictions.
+These findings suggest that while younger individuals are more open to meat alternatives, their likelihood of adoption is not uniform.
+
+For individuals aged 34.5 years or older, education becomes a significant predictor.
+Those with community/trade school, undergraduate, or postgraduate education are more likely to consider or adopt meat alternatives.
+Within this group, further splits by age highlight nuanced behaviors.
+For instance, individuals over 65.5 years old are classified as “Already doing this or have done this” (n = 30, error = 56.7%), reflecting a subset of older adults who actively embrace meat alternatives, possibly due to increased awareness or health considerations.
+
+Conversely, individuals with high school education in this older age group show lower likelihoods of adopting meat alternatives, with many classified as “Somewhat unlikely” (n = 22, error = 68.2%).
+These results underscore the interplay of age and education, where younger individuals and those with higher education levels are more inclined toward adopting meat alternatives.
+However, the variability in error rates across groups indicates that other unmeasured factors, such as income or cultural attitudes, may also influence these decisions.
 
 ### Minimizing Car Use
-A trend similar to that of meat alternatives is observed, with younger individuals more likely to minimize car use.
-Older respondents, particularly those 65 and older, show less inclination to reduce car usage, possibly due to mobility needs or lifestyle factors like suburban living.
+The decision tree indicates that the majority of individuals in the dataset are classified as "Already doing this or have done this," with a sample size of 320 and an error rate of 61.9%.
+This classification implies that minimizing car use is a prevalent behavior among the population studied.
+However, the relatively high error rate suggests notable variability within this group, indicating that while many individuals report minimizing car use, there may be discrepancies or inconsistencies in the data.
+
+The lack of further splits in the decision tree highlights the uniformity of responses or the insufficiency of the input variables to explain differences in behavior.
+This uniform classification could reflect widespread adoption of car use minimization practices due to shared motivations, such as environmental awareness or accessibility to alternatives like public transportation or carpooling.
+
+In summary, the model reveals that minimizing car use is a broadly practiced behavior within the sample population.
+However, the high error rate points to potential data quality issues or the influence of unmeasured factors.
+Future research could benefit from incorporating additional variables, such as geographic location, income level, or access to transportation infrastructure, to better understand the drivers and barriers to minimizing car use.
 
 ### Purchasing Green Products
-The likelihood of purchasing green products is relatively uniform across age groups.
-Middle-aged and older demographics show a slight increase in engagement, but the trend line remains mostly flat, indicating that this behavior is more influenced by factors such as income or environmental awareness rather than age.
+The model reveals distinct patterns regarding the likelihood of purchasing green products based on age and education.
+Among individuals aged 37.5 years or older, a notable segment is classified as "Somewhat likely" (n = 66, error = 54.5%).
+However, older individuals with age thresholds of 47.5 years and above show increased tendencies to fall into the category of "Already doing this or have done this." For instance, individuals aged over 50.5 years are predominantly classified as "Already doing this or have done this" (n = 7, error = 42.9%).
+These findings suggest that age plays a significant role in influencing behavior, with older age groups showing stronger commitment to green product purchases.
+
+For younger individuals under 37.5 years, the likelihood of purchasing green products varies based on education and finer age splits.
+Those under 27.5 years are more likely to be classified as "Very likely" (n = 24, error = 54.2%), while individuals under 22.5 years exhibit an even higher likelihood, with a smaller error rate (n = 8, error = 37.5%).
+This trend indicates that younger individuals, particularly those in the youngest age brackets, are more inclined toward green product purchasing, possibly reflecting heightened environmental awareness or greater receptiveness to sustainable practices.
+
+Overall, the decision tree highlights the interplay of age and education in predicting green product purchasing behavior.
+Younger individuals, especially those with mid-range education, demonstrate a stronger inclination toward adopting sustainable practices.
+In contrast, older individuals, particularly those above 50 years, are more likely to have already adopted these behaviors.
+While the model provides valuable insights, the variability in error rates across different nodes suggests that other unmeasured factors may also influence green product purchasing behavior.
 

### 2024-12-11 paper/climate_change.qmd
asjust cross referencing

@@
 ---
-title: "Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys"
-subtitle: "Uncovering What Stops Sustainable Behaviors and How Communities Can Overcome Them"
+title: "Predicting the Likelihood of Climate-Friendly Actions: Insights from Age and Educational Attainment"
+subtitle: "An analysis of how demographic factors influence the adoption of sustainable behaviors"
 author: 
@@
 #### Comparison 2018 to 2021
-@table-one illustrates the different age ditribution for 2018 and 2021 surveys.
+@fig-two illustrates the different age ditribution for 2018 and 2021 surveys.
 The major difference is that there was greater representation of younger inviduals ranging from 18 to 23 in 2021 compared to 2018.
@@
 #| message: false
-#| label: table-one
+#| label: fig-two
 #| fig-cap: "This table highlights the age distribution of survey respondents in 2018 and 2021."
@@
 #### Individual 2018
-@fig-two illustrates the distribution of survey respondents by their highest level of education attained.
+@fig-three illustrates the distribution of survey respondents by their highest level of education attained.
 The most frequently reported education levels are "Completed undergraduate degree" and "Post graduate/professional school," with both categories having a noticeably higher frequency compared to others, indicating a well-educated respondent population.
@@
 #| message: false
-#| label: fig-two
+#| label: fig-three
 #| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."
@@
 #### Comparison 2018 to 2021
-@table-two illustrates respondant education level in 2018 and 2021 respectively.
+@fig-four illustrates respondant education level in 2018 and 2021 respectively.
 Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021.
@@
 #| message: false
-#| label: table-two
+#| label: fig-four
 #| fig-cap: This table highlights the education distribution of survey respondents in 2018 and 2021."
@@
 #### Individual 2018
-@fig-three depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
+@fig-five depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
 The majority of participants identified as "Very informed," making this the most prevalent category by a significant margin.
@@
 #| message: false
-#| label: fig-three
+#| label: fig-five
 #| fig-cap: The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents.
@@
 #### Comparison 2018 to 2021
-@table-three illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
+@fig-six illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
 In 2018, the large marjority of individuals say they are very informed with 60 percent and the follwoign category is not very informed with 27 percent.
@@
 #| message: false
-#| label: table-three
+#| label: fig-six
 #| fig-cap: "This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021."
@@
 #### Individual 2018
-The analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
+T@ fig-seven, shows the analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
 On the other side of the spectrum, few said they were uninterested in receiving climate action information  with about 5 percent, about 12 percent indicated twitter and then 17 percent mentioned instagram.
@@
 #| message: false
-#| label: fig-four
+#| label: fig-seven
 #| fig-cap: The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action.
@@
 #### Comparison 2018 to 2021
-@table-four compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
+@fig-eight compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
 Aside from the additon of four options to the 2021 survey, both surveys questions are the same.
@@
 #| message: false
-#| label: table-four
+#| label: table-eight
 #| fig-cap: "This table highlights the prefered method of communication of survey respondents in 2018 and 2021."
@@
 The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
-@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
+@fig-nine illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
 On the x-axis, we have the nine different climate actions and on the y-axis is the percentage.
@@
 #| message: false
-#| label: fig-five
+#| label: fig-nine
 #| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
@@
 #### Likelihood of investing in an electric or hybrid vehicle
-The decision tree predicts individuals’ likelihood to invest in an electric or hybrid vehicle based on their highest level of education and age.
+@fig-ten predicts individuals’ likelihood to invest in an electric or hybrid vehicle based on their highest level of education and age.
 The model identifies highest level of education as the most important variable for the initial split.
@@
 #| message: false
-#| label: model-one
+#| label: fig-ten
 #| fig-cap: Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education.
@@
 #### Likelihood of making home improvements
-The decision tree classifies individuals based on their likelihood of making home improvements to minimize climate change, using age and educational level as predictor variables.
-The root node splits the data at age 35.5, indicating that age is the most influential factor in determining climate-related home improvement behavior.
+In @fig-eleven, the root node splits the data at age 35.5, indicating that age is the most influential factor in determining climate-related home improvement behavior.
 Individuals aged 36 years or older are predominantly classified as "Already doing this or have done this," with a large sample size (n = 223) but a moderate error rate of 59.6%, reflecting variability in this group.
@@
 #| message: false
-#| label: model-two
+#| label: fig-eleven
 #| fig-cap: Probability tree for likelihood of making home improvements predicted by age and education.
@@
 #### Likelihood of adopting meat alternatives
-The decision tree predicts individuals’ likelihood of consuming meat alternatives to minimize the effects of climate change based on their age and highest level of education.
+@fig-twelve predicts individuals’ likelihood of consuming meat alternatives to minimize the effects of climate change based on their age and highest level of education.
 The model identifies age as the most important variable for the initial split.
@@
 #| message: false
-#| label: model-three
+#| label: fig-twelve
 #| fig-cap: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
@@
 #### Likelihood of minimizing car use
-The decision tree predicts individuals' likelihood of minimizing car use as a measure to mitigate climate change.
+@fig-thirteen predicts individuals' likelihood of minimizing car use as a measure to mitigate climate change.
 In this case, the tree structure is straightforward, containing only a single root node.
@@
 #| message: false
-#| label: model-four
+#| label: @fig-thirteen
 #| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
@@
 #### Likelihood of purchasing green products
-The decision tree predicts individuals' likelihood of purchasing green products to minimize the effects of climate change based on age and highest level of education.
+@fig-fourteen predicts individuals' likelihood of purchasing green products to minimize the effects of climate change based on age and highest level of education.
 The model identifies age as the most important variable for the initial split.
@@
 #| message: false
-#| label: model-five
+#| label: fig-forteen
 #| fig-cap: Probability tree for likelihood of purchasing green products, predicted by age and education.
@@
 #### Likelihood of reducing hydro usage
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-six
+@fig-fifteen identifies age and highest level of education as key predictors influencing the likelihood of reducing hydro usage.
+The root node of the tree reveals that individuals younger than 34.5 years old are categorized as "Very likely" to reduce hydro usage, with a sample size of 87 and an error rate of 60.9%.
+This suggests that younger individuals may demonstrate a greater propensity to adopt hydro-reduction practices.
+Conversely, individuals over 34.5 years are further split by age, with those older than 64.5 years also categorized as "Very likely," albeit with a smaller sample size of 16 and a lower error rate of 37.5%.
+This bifurcation highlights that age groups at the extremes of the spectrum (younger and older individuals) are more inclined toward hydro-use reduction.
+
+Among middle-aged individuals (34.5–64.5 years), the decision tree highlights the role of education.
+Those younger than 61.5 years and possessing higher levels of education, including university degrees, are either "Already doing this or have done this" (n=151, err=56.3%) or "Somewhat likely" (n=14, err=50.0%) to engage in hydro-use reduction.
+On the other hand, individuals with lower educational attainment, particularly trade school or community-level education, are less likely to implement such measures.
+For individuals aged 61.5–71.5 years, there remains a balance between those already reducing hydro usage and those who are very likely to adopt it in the future, with clear variability based on educational level.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-fifteen
 #| fig-cap: Probability tree for likelihood of reducing hydro usage, predicted by age and education.
@@
 ####  Likelihood of reducing waste
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-seven
+@fig-sixteen predicts the likelihood of reducing waste is based on age and highest level of education.
+The root node splits individuals by age at 34.5 years, indicating that younger and older individuals exhibit distinct waste-reduction behaviors.
+For those under 34.5 years, the model uses highest level of education as a key determinant, classifying them as either "Somewhat likely" or "Very likely" to reduce waste.
+
+For individuals aged 34.5 years or older, the tree splits again by education and further refines predictions using additional age thresholds at 61.5 and 75.5 years.
+Older individuals with higher education levels are more likely to have "Already done this or are doing this," while those with lower education levels are categorized as "Somewhat likely" or "Very likely." This structure highlights the combined influence of education and age on waste-reduction behaviors, with clear thresholds that differentiate groups.
+
+The decision tree demonstrates that age is the primary driver of waste-reduction behavior, with education acting as an important secondary factor.
+These variables together capture differences in sustainability habits, showing how younger, middle-aged, and older populations vary in their likelihood to engage in reducing waste.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-sixteen
 #| fig-cap: Probability tree for likelihood of reducing waste, predicted by age and education.
@@
 ####  Likelihood of sorting waste correctly
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-eight
+@fig-seventeen predicts the likelihood of sorting waste correctly identifies highest level of education as the primary determinant.
+Individuals with education levels at or above Community/Trade School, Postgraduate, or Some University are categorized as "Already doing this or have done this," accounting for the majority of respondents (n = 295, err = 37.3%).
+This demonstrates that higher educational attainment correlates with proactive waste-sorting behaviors.
+
+For individuals whose highest level of education is High School, the model introduces a secondary split based on age at 37 years.
+Younger individuals under 37 years are categorized as "Already doing this or have done this," albeit with a higher error rate (n = 7, err = 57.1%).
+Older individuals aged 37 or above are more likely classified as "Very likely" to sort waste correctly (n = 17, err = 35.3%).
+These splits highlight the combined influence of education and age on waste-sorting behavior, with specific subgroups showing varying levels of commitment and accuracy.
+
+This decision tree underscores that education plays a dominant role in predicting waste-sorting behavior, while age further refines these predictions, especially for those with lower education levels.
+The model provides straightforward insights into how demographics shape sustainable practices.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-seventeen
 #| fig-cap: Probability tree for likelihood of sorting waste correctly, predicted by age and education.
@@
 ####  Likelihood of walking or cycling shorter distances
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: model-nine
+@fig-eighteen predicts the likelihood of individuals walking or cycling short distances based on their highest level of education and age.
+The root node identifies education level as the most significant factor.
+Individuals with postgraduate, undergraduate, or some university education are classified as “Already doing this or have done this” (n = 231, error = 51.9%).
+This indicates a strong relationship between higher education levels and the adoption of walking or cycling short distances.
+
+For those with lower education levels (community/trade school, high school, or preferring not to answer), the model further splits based on age.
+The first division occurs at 65.5 years, distinguishing those “Very likely” to walk or cycle short distances (n = 15, error = 60%) from others.
+Additional splits by age at 33.5 years and 60.5 years, along with education, refine the classification.
+This stepwise approach demonstrates how age interacts with education to influence short-distance mobility choices.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-eighteen
 #| fig-cap: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
@@
 ## Model Summary Table
-The table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors such as age and education.
+@fig-nineteen presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors such as age and education.
 Each row represents a different climate action (e.g., home improvement, reducing hydro, minimizing car use), with the corresponding accuracy of the model's predictions.
@@
 #| message: false
-#| label: table-five
+#| label: fig-nineteen
 #| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
@@
 # Load the model accuracy data from the saved CSV
-model_accuracies <- read.csv(here::here("data/02-analysis_data/model_accuracies.csv"))
+model_accuracies <- read.csv(here::here("data/04-model_data/model_accuracies.csv"))
 
@@
 ## Likelihood taking action by age
-@fig-six shows the relationship between age and the likelihood of engaging in various climate-related actions.
+@fig-twenty shows the relationship between age and the likelihood of engaging in various climate-related actions.
 The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely." The trend lines across each action show how engagement varies by age.
+
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-twenty
+#| fig-cap: Likelihood of Taking Climate Change Actions by Age Group.
+The stacked bar chart illustrates the percentage of respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64, 65+) in terms of their self-reported likelihood to engage in nine distinct climate-related actions.
+Each color represents a different level of likelihood, from "Already doing this or have done this" to "Very unlikely." The black dashed trend line highlights how the likelihood of action changes across age groups, providing insights into generational differences in climate-related behavior.
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))
+
+```
+
+## Likelihood taking action by education 
+@fig-twenty-one displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
+The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from "Prefer not to answer" to "Postgrad." Each action is shown across separate facets, revealing how education level correlates with engagement in each behavior.Individuals with higher education levels generally show a higher likelihood of engaging in climate-friendly actions.
+This trend is evident across all behaviors, with respondents possessing undergraduate or postgraduate degrees more likely to adopt electric vehicles or purchase green products.
+
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-twenty-one
+
+knitr::include_graphics(here("data/03-figures_data", "likelihood_education_plot.png"))
+
+```
 
@@
 ### Reducing Hydro Usage
-Older respondents (55-64 and 65+) are the most likely to reduce hydro usage, likely driven by cost-saving measures or environmental concerns. The trend line shows a steady increase with age.
-
-### Reducing and Sorting Waste
-Both reducing and sorting waste are more commonly reported by middle-aged and older groups (45-64). This may reflect increased awareness or resources for waste management.
+The findings from this decision tree analysis suggest that age and educational attainment are pivotal factors shaping individuals' likelihood of reducing hydro usage.
+Younger individuals, particularly those under 34.5 years, exhibit greater openness and enthusiasm for hydro-reduction practices.
+This trend likely reflects their increased exposure to sustainability discourse, progressive values, and familiarity with energy-saving technologies.
+Similarly, older individuals (above 64.5 years) might also demonstrate a willingness to reduce hydro usage, potentially driven by long-term environmental awareness or economic considerations during retirement.
+In contrast, middle-aged individuals show a more nuanced relationship with hydro-use reduction, as their decisions are influenced by their educational background, with those holding higher educational qualifications demonstrating greater likelihood to act.
+
+These results carry significant implications for policy and program design aimed at reducing hydro consumption.
+Younger individuals can serve as early adopters and advocates for hydro-saving technologies, making them a critical demographic for energy campaigns and innovative solutions.
+For older individuals, policymakers can emphasize the economic benefits of hydro-reduction initiatives, such as savings on utility bills, to motivate action.
+Addressing the middle-aged demographic requires more targeted approaches that consider educational disparities.
+Educational interventions, including workshops and informational campaigns, could bridge gaps for those with lower education levels, helping to increase their likelihood of engagement.
+Overall, these insights highlight the need for age- and education-specific strategies to effectively promote widespread hydro-use reduction.
+
+### Reducing Waste
+The results show that younger individuals under 34.5 years are more likely to be categorized as "Somewhat likely" or "Very likely" to reduce waste, particularly when they have higher levels of education.
+This suggests that environmental awareness among younger generations is strongly linked to educational attainment.
+In contrast, older individuals over 75.5 years are predominantly categorized as "Already doing this or have done this," reflecting long-standing habits and greater experience with resource conservation.
+
+For individuals aged 34.5 to 75.5 years, the likelihood of reducing waste varies based on both age and education.
+Those with higher educational attainment are more likely to have already adopted waste-reduction behaviors, while those with lower education levels are less consistent in their engagement.
+The errors associated with the predictions indicate variability within these groups, emphasizing the need for targeted interventions to improve participation rates.
+
+The findings suggest clear implications for policy and outreach.
+For younger individuals, campaigns focusing on leveraging their education and enthusiasm for sustainability can encourage even higher engagement.
+For middle-aged groups, addressing educational gaps through workshops or accessible resources can boost participation.
+For older individuals, reinforcing their existing waste-reduction practices with supportive policies, such as incentives for recycling or composting, can sustain their efforts.
+Tailoring strategies to these specific groups ensures a more effective approach to fostering waste reduction.
+
+### Sorting Waste Correctly
+The results indicate that individuals with higher educational attainment (Community/Trade School, Undergraduate, or above) overwhelmingly report "Already doing this or have done this" when it comes to sorting waste.
+This suggests that education enhances awareness and engagement with sustainable practices.
+However, the moderate error rate (37.3%) implies variability within this group, potentially due to differences in access to infrastructure or levels of personal commitment.
+
+Among those with a High School education, age emerges as a crucial factor.
+Younger individuals under 37 years are also likely to have sorted waste, though with higher inconsistencies.
+Older individuals in this category exhibit a stronger likelihood of intending to sort waste ("Very likely"), reflecting a growing awareness or changing attitudes with age.
+These findings highlight the nuanced relationship between age, education, and environmental behavior.
+
+The implications of this model suggest the need for tailored interventions.
+For individuals with lower educational attainment, targeted educational campaigns or accessible resources can bridge knowledge gaps and improve waste-sorting habits.
+For younger groups, embedding sustainability practices into school curricula can reinforce early habits.
+For older populations, providing convenient infrastructure or incentives for sorting waste could further encourage their commitment.
+Overall, the results emphasize the importance of addressing both educational and age-specific barriers to enhance waste-sorting behaviors.
 
 ### Walking / Cycling Short Distances
- Younger respondents (15-34) are more likely to engage in walking or cycling short distances.
-As age increases, the likelihood of walking or cycling decreases, possibly due to physical limitations or differing lifestyle needs.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-six
-#| fig-cap: Likelihood of Taking Climate Change Actions by Age Group.
-The stacked bar chart illustrates the percentage of respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64, 65+) in terms of their self-reported likelihood to engage in nine distinct climate-related actions.
-Each color represents a different level of likelihood, from "Already doing this or have done this" to "Very unlikely." The black dashed trend line highlights how the likelihood of action changes across age groups, providing insights into generational differences in climate-related behavior.
-
-knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))
-
-```
-
-## Likelihood taking action by education 
-@fig-seven displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
-The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from "Prefer not to answer" to "Postgrad." Each action is shown across separate facets, revealing how education level correlates with engagement in each behavior.
-
-### Trends in Education Attainment and Climate-Friendly Actions
-Individuals with higher education levels generally show a higher likelihood of engaging in climate-friendly actions.
-This trend is evident across all behaviors, with respondents possessing undergraduate or postgraduate degrees more likely to adopt electric vehicles or purchase green products.
-
-#### Electric/Hybrid Vehicle Adoption
-Postgraduate degree holders are the most likely to have adopted or consider adopting electric or hybrid vehicles.
-In contrast, respondents with lower education levels, such as those with high school or less, are more likely to report being "Very unlikely" or "Somewhat unlikely" to adopt these vehicles.
-
-#### Minimizing Car Use
-Higher education levels correlate with a greater likelihood of minimizing car use, though the trend is less pronounced for individuals with lower education levels.
-
-#### Reducing Hydro Usage
-While education has a smaller impact on reducing hydro usage compared to other actions, those with higher education levels are still more likely to engage in this behavior.
-
-#### Purchasing Green Products and Reducing Waste
-Purchasing green products and reducing waste are more common among individuals with postsecondary education, especially those with undergraduate or postgraduate degrees.
-In contrast, individuals with lower education levels report more moderate engagement with these actions.
-
-### Adopting Meat Alternatives
-Higher education is associated with greater adoption of meat alternatives.
-This is particularly true for those with undergraduate or postgraduate education, while fewer respondents with lower education levels report engaging in this behavior.
-
-### Walking or Cycling Short Distances
-Walking or cycling short distances is a behavior that is relatively common across all education levels, though individuals with higher education levels show slightly higher engagement.
-
-### Sorting Waste Correctly
-Sorting waste correctly is one of the most consistently adopted behaviors across all education levels, with a relatively small proportion of respondents indicating they are unlikely to engage in this action.
-However, individuals with higher education are still more likely to fall in the "Already doing this" category.
-
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-seven
-
-knitr::include_graphics(here("data/03-figures_data", "likelihood_education_plot.png"))
-
-```
+The model highlights a clear link between education and walking or cycling short distances.
+Individuals with higher education levels are more likely to engage in these activities, suggesting that education fosters awareness or access to environments conducive to active transportation.
+However, the moderate error rate in this group (51.9%) implies that other unmeasured factors, such as urban infrastructure or cultural attitudes, may also influence the behavior.
+
+Age emerges as a secondary but critical determinant, particularly for individuals with lower education levels.
+Those aged over 65.5 years are classified as “Very likely” to adopt walking or cycling, which may reflect a shift toward health-conscious behaviors among older adults.
+In contrast, individuals under 33.5 years show varying likelihoods, with subgroups classified as “Somewhat likely” or “Already doing this,” reflecting the nuanced impact of life stage and environmental factors.
+
+These findings suggest that promoting active transportation should consider demographic factors, such as age and education, alongside broader interventions like improved urban design or targeted awareness campaigns.
 

### 2024-12-11 scripts/06-model_data.R

@@ -101,3 +101,4 @@ print(model_results)
 
 # Save the results as a CSV in the correct location
 write_csv(model_results, here::here("data/04-model_data/model_accuracies.csv"))
+

### 2024-12-11 paper/climate_change.qmd
save models into correct model folder

@@
 
-knitr::include_graphics(here::here("data/04-model_data/vehicle_electric_tree.png"))
+knitr::include_graphics(here::here("models/vehicle_electric_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/home_improvement_tree.png"))
+knitr::include_graphics(here::here("models/home_improvement_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/protein_alternative_tree.png"))
+knitr::include_graphics(here::here("models/protein_alternative_tree.png"))
 
@@
 #| message: false
-#| label: @fig-thirteen
+#| label: fig-thirteen
 #| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
 
-knitr::include_graphics(here::here("data/04-model_data/minimize_car_tree.png"))
+knitr::include_graphics(here::here("models/minimize_car_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/green_product_tree.png"))
+knitr::include_graphics(here::here("models/green_product_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/reduce_hydro_tree.png"))
+knitr::include_graphics(here::here("models/reduce_hydro_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/reduce_waste_tree.png"))
+knitr::include_graphics(here::here("models/reduce_waste_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/sort_waste_tree.png"))
+knitr::include_graphics(here::here("models/sort_waste_tree.png"))
 
@@
 
-knitr::include_graphics(here::here("data/04-model_data/short_distance_tree.png"))
+knitr::include_graphics(here::here("models/short_distance_tree.png"))
 
@@
 # Load the model accuracy data from the saved CSV
-model_accuracies <- read.csv(here::here("data/04-model_data/model_accuracies.csv"))
+model_accuracies <- read.csv(here::here("models/model_accuracies.csv"))
 

### 2024-12-11 paper/climate_change.tex
save models into correct model folder

@@
 \hypersetup{
-  pdftitle={Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys},
+  pdftitle={Predicting the Likelihood of Climate-Friendly Actions: Insights from Age and Educational Attainment},
   pdfauthor={Lexi Knight},
@@
 
-\title{Barriers to Green Living: Insights from 2018 and 2021 Toronto
-Climate Perception Surveys\thanks{Code and data are available at:
-\url{https://github.com/LexiKnight/toronto_climate/tree/main}.}}
+\title{Predicting the Likelihood of Climate-Friendly Actions: Insights
+from Age and Educational Attainment\thanks{Code and data are available
+at: \url{https://github.com/LexiKnight/toronto_climate/tree/main}.}}
 \usepackage{etoolbox}
@@
 \makeatother
-\subtitle{Uncovering What Stops Sustainable Behaviors and How
-Communities Can Overcome Them}
+\subtitle{An analysis of how demographic factors influence the adoption
+of sustainable behaviors}
 \author{Lexi Knight}
-\date{December 3, 2024}
+\date{December 10, 2024}
 
@@
 \texttt{stringr} packages allowed us to reshape and clean the data by
-managing character strings and handling missing values. For the final
-documentation and report generation, the \texttt{knitr} package was
-instrumental in integrating R code and outputs into a cohesive and
-reproducible report format. This suite of R packages collectively
-enabled us to conduct thorough data management, manipulation, and
-analysis, ultimately contributing to the successful completion of the
-project.
+managing character strings and handling missing values. The (Therneau
+and Atkinson 2024) and (Hothorn and Zeileis 2024) were used in to make
+the models. For the final documentation and report generation, the
+\texttt{knitr} package was instrumental in integrating R code and
+outputs into a cohesive and reproducible report format. This suite of R
+packages collectively enabled us to conduct thorough data management,
+manipulation, and analysis, ultimately contributing to the successful
+completion of the project.
 
@@
 
+\newpage
+
 \paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}
 
-(\textbf{table-one?}) illustrates the different age ditribution for 2018
+Figure~\ref{fig-two} illustrates the different age ditribution for 2018
 and 2021 surveys. The major difference is that there was greater
@@
 
+\begin{figure}
+
+\centering{
+
 \begin{table}
@@
 
-This table highlights the age distribution of survey respondents in 2018
-and 2021.
+}
+
+\caption{\label{fig-two}This table highlights the age distribution of
+survey respondents in 2018 and 2021.}
+
+\end{figure}%
 
@@
 
-Figure~\ref{fig-two} illustrates the distribution of survey respondents
-by their highest level of education attained. The most frequently
-reported education levels are ``Completed undergraduate degree'' and
-``Post graduate/professional school,'' with both categories having a
-noticeably higher frequency compared to others, indicating a
+Figure~\ref{fig-three} illustrates the distribution of survey
+respondents by their highest level of education attained. The most
+frequently reported education levels are ``Completed undergraduate
+degree'' and ``Post graduate/professional school,'' with both categories
+having a noticeably higher frequency compared to others, indicating a
 well-educated respondent population. In contrast, fewer respondents
@@
 
-\caption{\label{fig-two}The histogram shows the distribution of
+\caption{\label{fig-three}The histogram shows the distribution of
 education levels of 2018 survey respondents.}
@@
 
-(\textbf{table-two?}) illustrates respondant education level in 2018 and
+Figure~\ref{fig-four} illustrates respondant education level in 2018 and
 2021 respectively. Please note, the categories of education level are
@@
 educated inviduals responded to the 2021 survey.
+
+\begin{figure}
+
+\centering{
 
@@
 
-This table highlights the education distribution of survey respondents
-in 2018 and 2021.''
+}
+
+\caption{\label{fig-four}This table highlights the education
+distribution of survey respondents in 2018 and 2021.''}
+
+\end{figure}%
 
@@
 
-Figure~\ref{fig-three} depicts the distribution of self-reported climate
+Figure~\ref{fig-five} depicts the distribution of self-reported climate
 change knowledge among survey respondents in 2018. The majority of
@@
 
-\caption{\label{fig-three}The histogram shows the distribution of
+\caption{\label{fig-five}The histogram shows the distribution of
 self-reported climate change knowledge among 2018 survey respondents.}
@@
 
-(\textbf{table-three?}) illustrates the self-reported level of extent
+Figure~\ref{fig-six} illustrates the self-reported level of extent
 inviduals feel informed about climate change and climate action for 2018
@@
 
-This table highlights the extent feel informed distribution of survey
-respondents in 2018 and 2021.
+}
+
+\caption{\label{fig-six}This table highlights the extent feel informed
+distribution of survey respondents in 2018 and 2021.}
+
+\end{figure}%
 
@@
 
-The analysis of the best method for delivering climate change
-information portrayed in Figure~\ref{fig-four} revealed that the
-majority of individuals in the 2018 dataset preferred receiving
+T@ fig-seven, shows the analysis of the best method for delivering
+climate change information portrayed in Figure~\ref{fig-four} revealed
+that the majority of individuals in the 2018 dataset preferred receiving
 information firstly from advertising campaigns with about 55 percent,
@@
 
-\caption{\label{fig-four}The stacked bar plot illustrates the preferred
+\caption{\label{fig-seven}The stacked bar plot illustrates the preferred
 methods of communication for receiving information about climate change
@@
 
-(\textbf{table-four?}) compares responses from 2018 and 2021 surverys
+\textbf{?@fig-eight} compares responses from 2018 and 2021 surverys
 regarding the best method of delivering information on climate change
@@
 The likelihood of taking action against climate change was explored by
-assessing individuals' intentions and behaviors. Figure~\ref{fig-five}
+assessing individuals' intentions and behaviors. Figure~\ref{fig-nine}
 illustrates self-reported likelihood of taking certain actions that
@@
 
-\caption{\label{fig-five}The stacked bar plot shows the likelihood of
+\caption{\label{fig-nine}The stacked bar plot shows the likelihood of
 survey respondents taking various actions to address climate change.}
@@
 
-\subsubsection{Likelihood of investing in an electric or hybrid
+\subsubsection{Decision Trees}\label{decision-trees}
+
+A decision tree is a machine learning model used to make predictions by
+recursively splitting data into subsets based on specific conditions of
+the predictor variables. It is structured like a tree, where the top
+node is the root node, representing the entire dataset, and subsequent
+nodes represent splits based on decision rules. The branches indicate
+the outcomes of these rules, and the leaf nodes (terminal nodes) provide
+the final prediction for each subset.
+
+Each split is determined by the predictor variable most strongly
+associated with the target outcome, maximizing predictive accuracy. A
+split separates individuals by age or educational level. The prediction
+in each terminal node includes the majority class (e.g., ``Very
+likely'') and additional information such as sample size (n) and error
+percentage. The error percentage reflects the proportion of cases in
+that node misclassified by the model. A higher error percentage
+indicates greater uncertainty or variability within the group, while a
+lower error percentage suggests a more precise classification.
+
+\paragraph{Likelihood of investing in an electric or hybrid
 vehicle}\label{likelihood-of-investing-in-an-electric-or-hybrid-vehicle}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/vehicle_electric_tree.png}
+Figure~\ref{fig-ten} predicts individuals' likelihood to invest in an
+electric or hybrid vehicle based on their highest level of education and
+age. The model identifies highest level of education as the most
+important variable for the initial split. At the root node, individuals
+are divided into two groups: those with ``Some Community/Trade School''
+or ``Some University'' education and those with other educational
+backgrounds such as ``High School,'' ``Undergrad,'' ``Postgrad,'' or
+``Prefer Not to Answer.''
+
+For individuals with ``Some Community/Trade School'' or ``Some
+University'' education, the tree predicts that they are ``Very likely''
+to invest, with a sample size of 47 and an error rate of 63.8\%. This
+indicates moderate variability within this group.
+
+For those with other educational backgrounds, further splits are based
+on age. Younger individuals (below 38.5 years) are segmented further. A
+subset aged under 34.5 years is split into two groups, with one group (n
+= 10) being ``Very likely'' to invest, with a lower error rate of 30\%.
+The other group is classified as ``Somewhat likely,'' with a higher
+error rate of 60.7\%. Older individuals (38.5 years or older) are less
+likely to invest. For instance, those aged above 68.5 years are
+predicted as ``Very unlikely'' with a sample size of 18 and an error
+rate of 61.1\%, while those aged between 34.5 and 68.5 years are divided
+into ``Somewhat unlikely'' or ``Somewhat likely'' categories.
+
+Overall, the decision tree reveals distinct patterns where educational
+attainment and age interact to predict investment likelihood, with
+younger individuals and those with less formal education being more
+likely to invest.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/vehicle_electric_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of investing in an electric or
-hybrid vehicle, predicted by age and education.}
+\caption{\label{fig-ten}Probability tree for likelihood of investing in
+an electric or hybrid vehicle, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of making home
+\paragraph{Likelihood of making home
 improvements}\label{likelihood-of-making-home-improvements}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/home_improvement_tree.png}
+In Figure~\ref{fig-eleven}, the root node splits the data at age 35.5,
+indicating that age is the most influential factor in determining
+climate-related home improvement behavior. Individuals aged 36 years or
+older are predominantly classified as ``Already doing this or have done
+this,'' with a large sample size (n = 223) but a moderate error rate of
+59.6\%, reflecting variability in this group.
+
+For individuals younger than 36 years, the tree introduces education as
+the next important factor. Those with higher educational attainment
+(``Community/Trade School,'' ``Some University,'' or ``Postgraduate'')
+are classified as ``Very likely'' to make climate-conscious home
+improvements (n = 40) with an error rate of 55.0\%. Conversely,
+individuals with lower education levels, such as ``High School'' or
+``Some Community/Trade School,'' are classified as ``Somewhat likely''
+(n = 46) but have a higher error rate of 67.4\%, indicating less
+predictive certainty. A smaller subset of younger individuals with
+similar educational attainment is classified as ``Somewhat likely'' (n =
+10) with a lower error rate of 40.0\%, suggesting higher confidence in
+this classification. The decision tree highlights clear trends based on
+age and education, with older age groups and higher educational
+attainment linked to greater engagement in making home improvements.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/home_improvement_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of making home improvements
-predicted by age and education.}
+\caption{\label{fig-eleven}Probability tree for likelihood of making
+home improvements predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of adopting meat
+\paragraph{Likelihood of adopting meat
 alternatives}\label{likelihood-of-adopting-meat-alternatives}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/protein_alternative_tree.png}
+Figure~\ref{fig-twelve} predicts individuals' likelihood of consuming
+meat alternatives to minimize the effects of climate change based on
+their age and highest level of education. The model identifies age as
+the most important variable for the initial split. At the root node,
+individuals are divided into two groups: those under 34.5 years old and
+those 34.5 years or older. This highlights age as a critical factor
+influencing the likelihood of adopting meat alternatives.
+
+In the subgroup of individuals under 34.5 years old, the decision tree
+further splits based on age at 31.5 years, classifying younger
+individuals into categories of ``Somewhat likely'' (n = 25, error =
+44\%) and ``Somewhat unlikely'' (n = 62, error = 62.9\%). On the other
+hand, for individuals aged 34.5 years or older, the model considers
+highest level of education as the next key variable, separating those
+with community/trade school, undergraduate, and postgraduate education
+from those with high school education. This distinction reflects how
+educational attainment moderates the impact of age on the decision to
+adopt meat alternatives.
+
+Within the older age group, additional splits occur based on age, such
+as at 49 years and 65.5 years, leading to further classifications like
+``Already doing this or have done this'' or ``Somewhat likely.'' These
+splits indicate how the interaction between age and education level
+shapes patterns of meat alternative adoption, resulting in more granular
+predictions.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/protein_alternative_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of adopting meat alternatives,
-predicted by age and education.}
+\caption{\label{fig-twelve}Probability tree for likelihood of adopting
+meat alternatives, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of minimizing car
+\paragraph{Likelihood of minimizing car
 use}\label{likelihood-of-minimizing-car-use}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/minimize_car_tree.png}
+Figure~\ref{fig-thirteen} predicts individuals' likelihood of minimizing
+car use as a measure to mitigate climate change. In this case, the tree
+structure is straightforward, containing only a single root node. The
+model classifies all individuals into one category, ``Already doing this
+or have done this,'' with a sample size of 320 and an error rate of
+61.9\%. The absence of splits in the tree indicates that no other
+variables, such as age or education, contributed sufficient predictive
+power to justify further segmentation.
+
+This outcome suggests that either the input data lacks variability in
+relevant features, or the behavior of minimizing car use is widespread
+and consistent across the sample population. Consequently, the model
+does not differentiate between subgroups and treats all individuals as
+having the same likelihood of engaging in this behavior.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/minimize_car_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of minimizing car use,
-predicted by age and education.}
+\caption{\label{fig-thirteen}Probability tree for likelihood of
+minimizing car use, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of purchasing green
+\paragraph{Likelihood of purchasing green
 products}\label{likelihood-of-purchasing-green-products}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/green_product_tree.png}
+\textbf{?@fig-fourteen} predicts individuals' likelihood of purchasing
+green products to minimize the effects of climate change based on age
+and highest level of education. The model identifies age as the most
+important variable for the initial split. At the root node, individuals
+are divided into two groups: those younger than 37.5 years old and those
+37.5 years or older. This division highlights age as a key determinant
+in predicting green product purchasing likelihood.
+
+For individuals aged 37.5 years or older, the next split is determined
+by the highest level of education. Those with educational backgrounds
+such as ``High School,'' ``Postgrad,'' ``Some Community/Trade School,''
+``Some University,'' or ``Prefer Not to Answer'' are further analyzed.
+Within this group, additional splits are made based on age thresholds of
+50.5 years and 47.5 years. These splits refine the classification into
+categories such as ``Somewhat likely'' or ``Already doing this or have
+done this,'' with varying error rates and sample sizes.
+
+Among individuals younger than 37.5 years, the highest level of
+education again plays a crucial role in the split. Individuals with
+educational backgrounds such as ``Postgrad,'' ``Community/Trade
+School,'' ``High School,'' or ``Some University'' are further segmented.
+Within this subgroup, age thresholds of 27.5 years and 22.5 years are
+used to differentiate individuals into categories such as ``Very
+likely'' or ``Somewhat likely,'' reflecting diverse levels of engagement
+with green product purchasing. Overall, the decision tree incorporates
+age and education as the primary variables to segment individuals into
+likelihood categories.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/green_product_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of purchasing green products,
-predicted by age and education.}
+\caption{\label{fig-forteen}Probability tree for likelihood of
+purchasing green products, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of reducing hydro
+\paragraph{Likelihood of reducing hydro
 usage}\label{likelihood-of-reducing-hydro-usage}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_hydro_tree.png}
+Figure~\ref{fig-fifteen} identifies age and highest level of education
+as key predictors influencing the likelihood of reducing hydro usage.
+The root node of the tree reveals that individuals younger than 34.5
+years old are categorized as ``Very likely'' to reduce hydro usage, with
+a sample size of 87 and an error rate of 60.9\%. This suggests that
+younger individuals may demonstrate a greater propensity to adopt
+hydro-reduction practices. Conversely, individuals over 34.5 years are
+further split by age, with those older than 64.5 years also categorized
+as ``Very likely,'' albeit with a smaller sample size of 16 and a lower
+error rate of 37.5\%. This bifurcation highlights that age groups at the
+extremes of the spectrum (younger and older individuals) are more
+inclined toward hydro-use reduction.
+
+Among middle-aged individuals (34.5--64.5 years), the decision tree
+highlights the role of education. Those younger than 61.5 years and
+possessing higher levels of education, including university degrees, are
+either ``Already doing this or have done this'' (n=151, err=56.3\%) or
+``Somewhat likely'' (n=14, err=50.0\%) to engage in hydro-use reduction.
+On the other hand, individuals with lower educational attainment,
+particularly trade school or community-level education, are less likely
+to implement such measures. For individuals aged 61.5--71.5 years, there
+remains a balance between those already reducing hydro usage and those
+who are very likely to adopt it in the future, with clear variability
+based on educational level.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_hydro_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of reducing hydro usage,
-predicted by age and education.}
+\caption{\label{fig-fifteen}Probability tree for likelihood of reducing
+hydro usage, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of reducing
+\paragraph{Likelihood of reducing
 waste}\label{likelihood-of-reducing-waste}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_waste_tree.png}
+Figure~\ref{fig-sixteen} predicts the likelihood of reducing waste is
+based on age and highest level of education. The root node splits
+individuals by age at 34.5 years, indicating that younger and older
+individuals exhibit distinct waste-reduction behaviors. For those under
+34.5 years, the model uses highest level of education as a key
+determinant, classifying them as either ``Somewhat likely'' or ``Very
+likely'' to reduce waste.
+
+For individuals aged 34.5 years or older, the tree splits again by
+education and further refines predictions using additional age
+thresholds at 61.5 and 75.5 years. Older individuals with higher
+education levels are more likely to have ``Already done this or are
+doing this,'' while those with lower education levels are categorized as
+``Somewhat likely'' or ``Very likely.'' This structure highlights the
+combined influence of education and age on waste-reduction behaviors,
+with clear thresholds that differentiate groups.
+
+The decision tree demonstrates that age is the primary driver of
+waste-reduction behavior, with education acting as an important
+secondary factor. These variables together capture differences in
+sustainability habits, showing how younger, middle-aged, and older
+populations vary in their likelihood to engage in reducing waste.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_waste_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of reducing waste, predicted by
-age and education.}
+\caption{\label{fig-sixteen}Probability tree for likelihood of reducing
+waste, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of sorting waste
+\paragraph{Likelihood of sorting waste
 correctly}\label{likelihood-of-sorting-waste-correctly}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/sort_waste_tree.png}
+Figure~\ref{fig-seventeen} predicts the likelihood of sorting waste
+correctly identifies highest level of education as the primary
+determinant. Individuals with education levels at or above
+Community/Trade School, Postgraduate, or Some University are categorized
+as ``Already doing this or have done this,'' accounting for the majority
+of respondents (n = 295, err = 37.3\%). This demonstrates that higher
+educational attainment correlates with proactive waste-sorting
+behaviors.
+
+For individuals whose highest level of education is High School, the
+model introduces a secondary split based on age at 37 years. Younger
+individuals under 37 years are categorized as ``Already doing this or
+have done this,'' albeit with a higher error rate (n = 7, err = 57.1\%).
+Older individuals aged 37 or above are more likely classified as ``Very
+likely'' to sort waste correctly (n = 17, err = 35.3\%). These splits
+highlight the combined influence of education and age on waste-sorting
+behavior, with specific subgroups showing varying levels of commitment
+and accuracy.
+
+This decision tree underscores that education plays a dominant role in
+predicting waste-sorting behavior, while age further refines these
+predictions, especially for those with lower education levels. The model
+provides straightforward insights into how demographics shape
+sustainable practices.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/sort_waste_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of sorting waste correctly,
-predicted by age and education.}
+\caption{\label{fig-seventeen}Probability tree for likelihood of sorting
+waste correctly, predicted by age and education.}
 
@@
 
-\subsubsection{Likelihood of walking or cycling shorter
+\paragraph{Likelihood of walking or cycling shorter
 distances}\label{likelihood-of-walking-or-cycling-shorter-distances}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/short_distance_tree.png}
+Figure~\ref{fig-eighteen} predicts the likelihood of individuals walking
+or cycling short distances based on their highest level of education and
+age. The root node identifies education level as the most significant
+factor. Individuals with postgraduate, undergraduate, or some university
+education are classified as ``Already doing this or have done this'' (n
+= 231, error = 51.9\%). This indicates a strong relationship between
+higher education levels and the adoption of walking or cycling short
+distances.
+
+For those with lower education levels (community/trade school, high
+school, or preferring not to answer), the model further splits based on
+age. The first division occurs at 65.5 years, distinguishing those
+``Very likely'' to walk or cycle short distances (n = 15, error = 60\%)
+from others. Additional splits by age at 33.5 years and 60.5 years,
+along with education, refine the classification. This stepwise approach
+demonstrates how age interacts with education to influence
+short-distance mobility choices.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/short_distance_tree.png}
 
@@
 
-\caption{Probability tree for likelihood of walking or cycling shorter
-distances, predicted by age and education.}
+\caption{\label{fig-eighteen}Probability tree for likelihood of walking
+or cycling shorter distances, predicted by age and education.}
 
@@
 
-The table presents the accuracy of models predicting the likelihood of
-various climate-friendly actions based on demographic factors such as
-age and education. Each row represents a different climate action (e.g.,
-home improvement, reducing hydro, minimizing car use), with the
-corresponding accuracy of the model's predictions. The accuracy values
-reflect how well the models, which use age and education as predictors,
-align with the actual data. An accuracy of 33 percent for home
-improvement'' indicates that the model correctly predicted the outcome
-33\% of the time for this action. These accuracy values help evaluate
-the effectiveness of age and education as predictors for each specific
-climate action.
+\textbf{?@fig-nineteen} presents the accuracy of models predicting the
+likelihood of various climate-friendly actions based on demographic
+factors such as age and education. Each row represents a different
+climate action (e.g., home improvement, reducing hydro, minimizing car
+use), with the corresponding accuracy of the model's predictions. The
+accuracy values reflect how well the models, which use age and education
+as predictors, align with the actual data. An accuracy of 33 percent for
+home improvement'' indicates that the model correctly predicted the
+outcome 33\% of the time for this action. These accuracy values help
+evaluate the effectiveness of age and education as predictors for each
+specific climate action.
 
@@
 
-Figure~\ref{fig-six} shows the relationship between age and the
+Figure~\ref{fig-twenty} shows the relationship between age and the
 likelihood of engaging in various climate-related actions. The x-axis
@@
 
-\subsubsection{Electric / Hybrid Vehicle
-Adoption}\label{electric-hybrid-vehicle-adoption}
-
-Younger respondents (15-24, 25-34) are less likely to adopt electric or
-hybrid vehicles, with only a small proportion already using or
-considering them. Adoption rates increase slightly in the 55-64 age
-group, then decline again in the 65+ group. This suggests that older
-individuals may have more resources or stability to invest in electric
-vehicles.
-
-\subsubsection{Home Improvement for Energy
-Efficiency}\label{home-improvement-for-energy-efficiency}
-
-Middle-aged individuals (35-54) are the most likely to engage in home
-improvement actions aimed at increasing energy efficiency. Younger age
-groups (15-24, 25-34) report lower likelihoods, likely due to barriers
-such as homeownership and disposable income.
-
-\subsubsection{Consumption of Meat
-Alternatives}\label{consumption-of-meat-alternatives}
-
-Younger age groups, especially 15-24 and 25-34, are more likely to adopt
-meat alternatives. As age increases, the likelihood of doing so
-decreases, possibly due to established dietary habits in older
-generations.
-
-\subsubsection{Minimizing Car Use}\label{minimizing-car-use}
-
-A trend similar to that of meat alternatives is observed, with younger
-individuals more likely to minimize car use. Older respondents,
-particularly those 65 and older, show less inclination to reduce car
-usage, possibly due to mobility needs or lifestyle factors like suburban
-living.
-
-\subsubsection{Purchasing Green
-Products}\label{purchasing-green-products}
-
-The likelihood of purchasing green products is relatively uniform across
-age groups. Middle-aged and older demographics show a slight increase in
-engagement, but the trend line remains mostly flat, indicating that this
-behavior is more influenced by factors such as income or environmental
-awareness rather than age.
-
-\subsubsection{Reducing Hydro Usage}\label{reducing-hydro-usage}
-
-Older respondents (55-64 and 65+) are the most likely to reduce hydro
-usage, likely driven by cost-saving measures or environmental concerns.
-The trend line shows a steady increase with age.
-
-\subsubsection{Reducing and Sorting
-Waste}\label{reducing-and-sorting-waste}
-
-Both reducing and sorting waste are more commonly reported by
-middle-aged and older groups (45-64). This may reflect increased
-awareness or resources for waste management.
-
-\subsubsection{Walking / Cycling Short
-Distances}\label{walking-cycling-short-distances}
-
-Younger respondents (15-34) are more likely to engage in walking or
-cycling short distances. As age increases, the likelihood of walking or
-cycling decreases, possibly due to physical limitations or differing
-lifestyle needs.
-
 \begin{figure}
@@
 
-\caption{\label{fig-six}Likelihood of Taking Climate Change Actions by
-Age Group. The stacked bar chart illustrates the percentage of
+\caption{\label{fig-twenty}Likelihood of Taking Climate Change Actions
+by Age Group. The stacked bar chart illustrates the percentage of
 respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64,
@@
 
-Figure~\ref{fig-seven} displays how the likelihood of engaging in
+Figure~\ref{fig-twenty-one} displays how the likelihood of engaging in
 climate-friendly actions varies by educational attainment. The x-axis
@@
 revealing how education level correlates with engagement in each
-behavior.
-
-\subsubsection{Trends in Education Attainment and Climate-Friendly
-Actions}\label{trends-in-education-attainment-and-climate-friendly-actions}
-
-Individuals with higher education levels generally show a higher
-likelihood of engaging in climate-friendly actions. This trend is
+behavior.Individuals with higher education levels generally show a
+higher likelihood of engaging in climate-friendly actions. This trend is
 evident across all behaviors, with respondents possessing undergraduate
@@
 
-\paragraph{Electric/Hybrid Vehicle
-Adoption}\label{electrichybrid-vehicle-adoption}
-
-Postgraduate degree holders are the most likely to have adopted or
-consider adopting electric or hybrid vehicles. In contrast, respondents
-with lower education levels, such as those with high school or less, are
-more likely to report being ``Very unlikely'' or ``Somewhat unlikely''
-to adopt these vehicles.
-
-\paragraph{Minimizing Car Use}\label{minimizing-car-use-1}
-
-Higher education levels correlate with a greater likelihood of
-minimizing car use, though the trend is less pronounced for individuals
-with lower education levels.
-
-\paragraph{Reducing Hydro Usage}\label{reducing-hydro-usage-1}
-
-While education has a smaller impact on reducing hydro usage compared to
-other actions, those with higher education levels are still more likely
-to engage in this behavior.
-
-\paragraph{Purchasing Green Products and Reducing
-Waste}\label{purchasing-green-products-and-reducing-waste}
-
-Purchasing green products and reducing waste are more common among
-individuals with postsecondary education, especially those with
-undergraduate or postgraduate degrees. In contrast, individuals with
-lower education levels report more moderate engagement with these
-actions.
-
-\subsubsection{Adopting Meat
-Alternatives}\label{adopting-meat-alternatives}
-
-Higher education is associated with greater adoption of meat
-alternatives. This is particularly true for those with undergraduate or
-postgraduate education, while fewer respondents with lower education
-levels report engaging in this behavior.
-
-\subsubsection{Walking or Cycling Short
-Distances}\label{walking-or-cycling-short-distances}
-
-Walking or cycling short distances is a behavior that is relatively
-common across all education levels, though individuals with higher
-education levels show slightly higher engagement.
+\begin{figure}
+
+\centering{
+
+\captionsetup{labelsep=none}\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_education_plot.png}
+
+}
+
+\caption{\label{fig-twenty-one}}
+
+\end{figure}%
+
+\subsubsection{Electric / Hybrid Vehicle
+Adoption}\label{electric-hybrid-vehicle-adoption}
+
+The model indicates that individuals with ``Some Community/Trade
+School'' or ``Some University'' education are the most likely to invest
+in electric or hybrid vehicles. This group is classified as ``Very
+likely'' (n = 47) with an error rate of 64\%, suggesting that while many
+in this category are inclined to invest, there is notable variability.
+Among individuals with other educational backgrounds, age plays a key
+role. Younger individuals under 35 years old, particularly those
+classified as ``Very likely'' (n = 10, error = 30\%), demonstrate a
+strong tendency to invest, reflecting high confidence in this
+prediction. However, another subset of younger individuals (n = 28) is
+``Somewhat likely,'' with a higher error rate of 61\%, indicating less
+certainty. These trends suggest younger people are more open to adopting
+electric or hybrid vehicles, likely due to environmental awareness or
+familiarity with emerging technologies.
+
+Older individuals, particularly those over 69 years old, are the least
+likely to invest. This group is classified as ``Very unlikely'' (n = 18)
+with an error rate of 61.1\%, highlighting some uncertainty but an
+overall low likelihood of adoption. Middle-aged individuals (35 to 69
+years old) show more mixed results, with some classified as ``Somewhat
+unlikely'' (n = 84, error = 54\%) and others as ``Somewhat likely'' (n =
+46, error = 57\%). These findings suggest that barriers such as cost,
+resistance to change, or lower interest in alternative vehicles may
+deter older age groups.
+
+In summary, the model suggests that younger individuals, particularly
+those under 35 years old, and those with mid-level education are the
+most likely to invest in electric or hybrid vehicles. In contrast, older
+individuals and those with minimal or advanced education are less likely
+to adopt these technologies. While the model provides insights into
+these trends, the error rates indicate variability in some predictions,
+particularly among ``Somewhat likely'' and ``Somewhat unlikely'' groups.
+
+\subsubsection{Home Improvement for Energy
+Efficiency}\label{home-improvement-for-energy-efficiency}
+
+The results reveal that age is the most significant predictor of
+climate-conscious home improvement behavior. Individuals aged 36 years
+or older are the most likely to already be taking or have taken such
+actions. This group represents the largest sample size (n = 223) but
+also exhibits a moderate error rate (59.6\%), indicating some variation
+in their behaviors.
+
+For younger individuals (under 36 years), educational attainment is a
+key determinant. Those with higher education levels, such as
+``Community/Trade School,'' ``Some University,'' or ``Postgraduate,''
+are the most likely to take action (``Very likely'') with an error rate
+of 55\%. However, younger individuals with lower levels of education,
+such as ``High School'' or ``Some Community/Trade School,'' are less
+likely to engage in these actions, being classified as ``Somewhat
+likely'' but with a higher error rate of 67\%, indicating greater
+variability in this group.
+
+Overall, individuals aged 36 or older are more likely to have already
+engaged in climate-conscious home improvements, regardless of education
+level. Younger individuals with higher education are more likely to
+adopt such changes in the future, while those with lower education are
+less likely, with predictions for this group being less certain. These
+findings underscore the importance of both age and education in shaping
+environmental engagement and suggest that outreach efforts might need to
+target younger, less-educated groups to increase participation.
+
+\subsubsection{Consumption of Meat
+Alternatives}\label{consumption-of-meat-alternatives}
+
+The model suggests that age is the strongest predictor of individuals'
+likelihood to adopt meat alternatives for climate change mitigation.
+Younger individuals, particularly those under 34.5 years old, show
+varying tendencies. Among this group, those aged 31.5 years or younger
+are divided into ``Somewhat likely'' (n = 25, error = 44\%) and
+``Somewhat unlikely'' (n = 62, error = 62.9\%), indicating considerable
+variability in predictions. These findings suggest that while younger
+individuals are more open to meat alternatives, their likelihood of
+adoption is not uniform.
+
+For individuals aged 34.5 years or older, education becomes a
+significant predictor. Those with community/trade school, undergraduate,
+or postgraduate education are more likely to consider or adopt meat
+alternatives. Within this group, further splits by age highlight nuanced
+behaviors. For instance, individuals over 65.5 years old are classified
+as ``Already doing this or have done this'' (n = 30, error = 56.7\%),
+reflecting a subset of older adults who actively embrace meat
+alternatives, possibly due to increased awareness or health
+considerations.
+
+Conversely, individuals with high school education in this older age
+group show lower likelihoods of adopting meat alternatives, with many
+classified as ``Somewhat unlikely'' (n = 22, error = 68.2\%). These
+results underscore the interplay of age and education, where younger
+individuals and those with higher education levels are more inclined
+toward adopting meat alternatives. However, the variability in error
+rates across groups indicates that other unmeasured factors, such as
+income or cultural attitudes, may also influence these decisions.
+
+\subsubsection{Minimizing Car Use}\label{minimizing-car-use}
+
+The decision tree indicates that the majority of individuals in the
+dataset are classified as ``Already doing this or have done this,'' with
+a sample size of 320 and an error rate of 61.9\%. This classification
+implies that minimizing car use is a prevalent behavior among the
+population studied. However, the relatively high error rate suggests
+notable variability within this group, indicating that while many
+individuals report minimizing car use, there may be discrepancies or
+inconsistencies in the data.
+
+The lack of further splits in the decision tree highlights the
+uniformity of responses or the insufficiency of the input variables to
+explain differences in behavior. This uniform classification could
+reflect widespread adoption of car use minimization practices due to
+shared motivations, such as environmental awareness or accessibility to
+alternatives like public transportation or carpooling.
+
+In summary, the model reveals that minimizing car use is a broadly
+practiced behavior within the sample population. However, the high error
+rate points to potential data quality issues or the influence of
+unmeasured factors. Future research could benefit from incorporating
+additional variables, such as geographic location, income level, or
+access to transportation infrastructure, to better understand the
+drivers and barriers to minimizing car use.
+
+\subsubsection{Purchasing Green
+Products}\label{purchasing-green-products}
+
+The model reveals distinct patterns regarding the likelihood of
+purchasing green products based on age and education. Among individuals
+aged 37.5 years or older, a notable segment is classified as ``Somewhat
+likely'' (n = 66, error = 54.5\%). However, older individuals with age
+thresholds of 47.5 years and above show increased tendencies to fall
+into the category of ``Already doing this or have done this.'' For
+instance, individuals aged over 50.5 years are predominantly classified
+as ``Already doing this or have done this'' (n = 7, error = 42.9\%).
+These findings suggest that age plays a significant role in influencing
+behavior, with older age groups showing stronger commitment to green
+product purchases.
+
+For younger individuals under 37.5 years, the likelihood of purchasing
+green products varies based on education and finer age splits. Those
+under 27.5 years are more likely to be classified as ``Very likely'' (n
+= 24, error = 54.2\%), while individuals under 22.5 years exhibit an
+even higher likelihood, with a smaller error rate (n = 8, error =
+37.5\%). This trend indicates that younger individuals, particularly
+those in the youngest age brackets, are more inclined toward green
+product purchasing, possibly reflecting heightened environmental
+awareness or greater receptiveness to sustainable practices.
+
+Overall, the decision tree highlights the interplay of age and education
+in predicting green product purchasing behavior. Younger individuals,
+especially those with mid-range education, demonstrate a stronger
+inclination toward adopting sustainable practices. In contrast, older
+individuals, particularly those above 50 years, are more likely to have
+already adopted these behaviors. While the model provides valuable
+insights, the variability in error rates across different nodes suggests
+that other unmeasured factors may also influence green product
+purchasing behavior.
+
+\subsubsection{Reducing Hydro Usage}\label{reducing-hydro-usage}
+
+The findings from this decision tree analysis suggest that age and
+educational attainment are pivotal factors shaping individuals'
+likelihood of reducing hydro usage. Younger individuals, particularly
+those under 34.5 years, exhibit greater openness and enthusiasm for
+hydro-reduction practices. This trend likely reflects their increased
+exposure to sustainability discourse, progressive values, and
+familiarity with energy-saving technologies. Similarly, older
+individuals (above 64.5 years) might also demonstrate a willingness to
+reduce hydro usage, potentially driven by long-term environmental
+awareness or economic considerations during retirement. In contrast,
+middle-aged individuals show a more nuanced relationship with hydro-use
+reduction, as their decisions are influenced by their educational
+background, with those holding higher educational qualifications
+demonstrating greater likelihood to act.
+
+These results carry significant implications for policy and program
+design aimed at reducing hydro consumption. Younger individuals can
+serve as early adopters and advocates for hydro-saving technologies,
+making them a critical demographic for energy campaigns and innovative
+solutions. For older individuals, policymakers can emphasize the
+economic benefits of hydro-reduction initiatives, such as savings on
+utility bills, to motivate action. Addressing the middle-aged
+demographic requires more targeted approaches that consider educational
+disparities. Educational interventions, including workshops and
+informational campaigns, could bridge gaps for those with lower
+education levels, helping to increase their likelihood of engagement.
+Overall, these insights highlight the need for age- and
+education-specific strategies to effectively promote widespread
+hydro-use reduction.
+
+\subsubsection{Reducing Waste}\label{reducing-waste}
+
+The results show that younger individuals under 34.5 years are more
+likely to be categorized as ``Somewhat likely'' or ``Very likely'' to
+reduce waste, particularly when they have higher levels of education.
+This suggests that environmental awareness among younger generations is
+strongly linked to educational attainment. In contrast, older
+individuals over 75.5 years are predominantly categorized as ``Already
+doing this or have done this,'' reflecting long-standing habits and
+greater experience with resource conservation.
+
+For individuals aged 34.5 to 75.5 years, the likelihood of reducing
+waste varies based on both age and education. Those with higher
+educational attainment are more likely to have already adopted
+waste-reduction behaviors, while those with lower education levels are
+less consistent in their engagement. The errors associated with the
+predictions indicate variability within these groups, emphasizing the
+need for targeted interventions to improve participation rates.
+
+The findings suggest clear implications for policy and outreach. For
+younger individuals, campaigns focusing on leveraging their education
+and enthusiasm for sustainability can encourage even higher engagement.
+For middle-aged groups, addressing educational gaps through workshops or
+accessible resources can boost participation. For older individuals,
+reinforcing their existing waste-reduction practices with supportive
+policies, such as incentives for recycling or composting, can sustain
+their efforts. Tailoring strategies to these specific groups ensures a
+more effective approach to fostering waste reduction.
 
@@
 
-Sorting waste correctly is one of the most consistently adopted
-behaviors across all education levels, with a relatively small
-proportion of respondents indicating they are unlikely to engage in this
-action. However, individuals with higher education are still more likely
-to fall in the ``Already doing this'' category.
-
-\begin{figure}
-
-\centering{
-
-\captionsetup{labelsep=none}\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_education_plot.png}
-
-}
-
-\caption{\label{fig-seven}}
-
-\end{figure}%
+The results indicate that individuals with higher educational attainment
+(Community/Trade School, Undergraduate, or above) overwhelmingly report
+``Already doing this or have done this'' when it comes to sorting waste.
+This suggests that education enhances awareness and engagement with
+sustainable practices. However, the moderate error rate (37.3\%) implies
+variability within this group, potentially due to differences in access
+to infrastructure or levels of personal commitment.
+
+Among those with a High School education, age emerges as a crucial
+factor. Younger individuals under 37 years are also likely to have
+sorted waste, though with higher inconsistencies. Older individuals in
+this category exhibit a stronger likelihood of intending to sort waste
+(``Very likely''), reflecting a growing awareness or changing attitudes
+with age. These findings highlight the nuanced relationship between age,
+education, and environmental behavior.
+
+The implications of this model suggest the need for tailored
+interventions. For individuals with lower educational attainment,
+targeted educational campaigns or accessible resources can bridge
+knowledge gaps and improve waste-sorting habits. For younger groups,
+embedding sustainability practices into school curricula can reinforce
+early habits. For older populations, providing convenient infrastructure
+or incentives for sorting waste could further encourage their
+commitment. Overall, the results emphasize the importance of addressing
+both educational and age-specific barriers to enhance waste-sorting
+behaviors.
+
+\subsubsection{Walking / Cycling Short
+Distances}\label{walking-cycling-short-distances}
+
+The model highlights a clear link between education and walking or
+cycling short distances. Individuals with higher education levels are
+more likely to engage in these activities, suggesting that education
+fosters awareness or access to environments conducive to active
+transportation. However, the moderate error rate in this group (51.9\%)
+implies that other unmeasured factors, such as urban infrastructure or
+cultural attitudes, may also influence the behavior.
+
+Age emerges as a secondary but critical determinant, particularly for
+individuals with lower education levels. Those aged over 65.5 years are
+classified as ``Very likely'' to adopt walking or cycling, which may
+reflect a shift toward health-conscious behaviors among older adults. In
+contrast, individuals under 33.5 years show varying likelihoods, with
+subgroups classified as ``Somewhat likely'' or ``Already doing this,''
+reflecting the nuanced impact of life stage and environmental factors.
+
+These findings suggest that promoting active transportation should
+consider demographic factors, such as age and education, alongside
+broader interventions like improved urban design or targeted awareness
+campaigns.
 
@@
 
+\bibitem[\citeproctext]{ref-partykit2024}
+Hothorn, Torsten, and Achim Zeileis. 2024. \emph{Partykit: A Toolkit for
+Recursive Partytioning}.
+\url{https://cran.r-project.org/package=partykit}.
+
 \bibitem[\citeproctext]{ref-IPCC2023}
@@
 
+\bibitem[\citeproctext]{ref-rpart2024}
+Therneau, Terry, and Beth Atkinson. 2024. \emph{Rpart: Recursive
+Partitioning and Regression Trees}.
+\url{https://cran.r-project.org/package=rpart}.
+
 \bibitem[\citeproctext]{ref-tidyverse}

### 2024-12-11 scripts/06-model_data.R

@@ -49,7 +49,7 @@ generate_model <- function(target_var, train_data, test_data, model_name) {
   tree <- rpart(formula, data = train_data)
   
   # Construct file path for saving the plot
-  png_file_path <- file.path(here::here("data/04-model_data"), paste0(model_name, "_tree.png"))
+  png_file_path <- file.path(here::here("models/"), paste0(model_name, "_tree.png"))
   
   # Adjust PNG size to avoid cutting off the tree
   png(png_file_path, width = 3200, height = 1500, res = 150)  # Increase size and resolution
@@ -100,5 +100,5 @@ for (target_var in target_vars) {
 print(model_results)
 
 # Save the results as a CSV in the correct location
-write_csv(model_results, here::here("data/04-model_data/model_accuracies.csv"))
+write_csv(model_results, here::here("models/model_accuracies.csv"))
 

### 2024-12-13 paper/climate_change.qmd
tidy packages actually used

@@
 @sec-results highlights key differences in behavior based on age, education, and knowledge of climate change.
-@sec-discussion discusses the findings, addresses the study's limitations, and suggests directions for future research.
+@sec-discussion examines the findings, addresses limitations, and suggests directions for future research.
 @sec-conclusion concludes with a summary of the key takeaways and actionable recommendations for enhancing climate action engagement.
-Finally, @sec-appendix contains supplementary material.
+Finally, @sec-appendix contains supplementary material including an idealized methodology, the simulation process and data cleaning procedure.
 
@@
 The primary data source for this project is the Climate Perception Study dataset, provided by the City of Toronto via the Open Data Toronto platform [@climateperceptionstudy].
-This dataset offers insights into public perceptions of climate change in Toronto and was accessed from Open Data Toronto [@opendatatoronto] on 6 November 2024.
+This dataset offers insights into public perceptions of climate change in Toronto in the years 2018 and 2021.
+This dataset was accessed from Open Data Toronto [@opendatatoronto] on 6 November 2024.
+
 ## Software and R-packages
@@
 # Load libraries
-library(kableExtra)
-library(knitr)
-library(here)
-library(dplyr)    # For renaming columns
-library(arrow)    # For reading Parquet files
+library(kableExtra)  # styling tables
+library(here)        # manage file paths
+library(dplyr)       # data manipulation; renames columns
+library(arrow)       # reads Parquet files
 
@@
 #### Individual 2018
-T@ fig-seven, shows the analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
+@fig-seven, shows the analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
 On the other side of the spectrum, few said they were uninterested in receiving climate action information  with about 5 percent, about 12 percent indicated twitter and then 17 percent mentioned instagram.

### 2024-12-13 paper/climate_change.tex
tidy packages actually used

@@
 
-T@ fig-seven, shows the analysis of the best method for delivering
-climate change information portrayed in Figure~\ref{fig-four} revealed
-that the majority of individuals in the 2018 dataset preferred receiving
-information firstly from advertising campaigns with about 55 percent,
-newsletters with about 52 percent, followed by the toronto website wiht
-about 46 percent. On the other side of the spectrum, few said they were
-uninterested in receiving climate action information with about 5
-percent, about 12 percent indicated twitter and then 17 percent
+Figure~\ref{fig-seven}, shows the analysis of the best method for
+delivering climate change information portrayed in Figure~\ref{fig-four}
+revealed that the majority of individuals in the 2018 dataset preferred
+receiving information firstly from advertising campaigns with about 55
+percent, newsletters with about 52 percent, followed by the toronto
+website wiht about 46 percent. On the other side of the spectrum, few
+said they were uninterested in receiving climate action information with
+about 5 percent, about 12 percent indicated twitter and then 17 percent
 mentioned instagram. Overall social media platforms Facebook, Instagram
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/vehicle_electric_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/vehicle_electric_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/home_improvement_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/home_improvement_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/protein_alternative_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/protein_alternative_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/minimize_car_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/minimize_car_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/green_product_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/green_product_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_hydro_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/reduce_hydro_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_waste_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/reduce_waste_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/sort_waste_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/sort_waste_tree.png}
 
@@
 
-\includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/short_distance_tree.png}
+\includegraphics[width=10.67in,height=\textheight]{../models/short_distance_tree.png}
 

### 2024-12-13 scripts/00-simulate_data.R

@@ -8,8 +8,8 @@
 
 #### Workspace setup ####
 # load packages
-library(tidyverse)
-library(arrow)
+library(tidyverse)      # for collection of tools to manipulate and visualize the data
+library(arrow)          # used for write_parquet function
 
 #### Simulate data ####
 

### 2024-12-13 scripts/01-test_simulated_data.R

@@ -8,8 +8,10 @@
 #### Workspace setup ####
 # Load required packages
 library(tidyverse)  # For data manipulation and visualization
-library(testthat)   # For testing
+library(testthat)   # For writing and running tests
 library(arrow)      # For reading parquet files
+library(here)       # for file path management
+
 
 #### Test data ####
 

### 2024-12-13 scripts/02-download_data.R

@@ -9,10 +9,10 @@
 #### Workspace setup ####
 
 # Load required libraries
-library(httr) # downloads excel file
-library(readxl) # enables reading excel files
+library(httr)      # downloads excel file
+library(readxl)    # reads excel files
 library(tidyverse) # provides write_csv function to save 2018 dataset
-library(openxlsx) #creates new excel workbook with mulitple sheets to save 2021 dataset
+library(openxlsx)  # creates new excel workbook with mulitple sheets to save 2021 dataset
 
 #### Download data for 2018 ####
 # Note, there are two versions where each version is formatted differently, 

### 2024-12-13 scripts/03-clean_data.R

@@ -10,16 +10,12 @@
 #### Workspace setup ####
 
 # load necessary packages
-library(readr)
-library(dplyr) # for combining data frames
-library(openxlsx)
-library(readxl)
-library(arrow) # for saving file as parquet
-library(tidyverse)
-library(tidyr)
-library(stringr)
-library(tinytable)
-library(here)
+library(readr)       # reads csv files
+library(dplyr)       # data manipulation; selecting, renaming, mutating columns
+library(arrow)       # saves data as parquet
+library(stringr)     # string manipulation
+library(here)        # constructs file paths
+library(tinytable)   # creates and formats tables
 
 #### Clean individual 2018 data ####
 

### 2024-12-13 scripts/04-test_analysis_data.R

@@ -8,10 +8,9 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
-library(testthat)
-library(here)
-library(arrow)
+library(tidyverse)     # reads csv file
+library(testthat)      # write and execute tests
+
 
 ### Load data outside of test block ###
 analysis_data <- read_csv("data/02-analysis_data/twenty_eighteen_individual_analysis_data.csv", col_names = TRUE)

### 2024-12-13 scripts/05-exploratory_data_analysis.R

@@ -10,18 +10,15 @@
 #### Workspace setup ####
 
 # Load necessary libraries
-library(tidyverse)
-library(dplyr)
-library(ggplot2)
-library(here) # for working with relative paths
-library(stringr) # was this used?
-library(knitr)
-library(arrow) # for reading parquet files
-library(tidyr)
-library(forcats) # for reordering factor levels
-library(kableExtra) # for rendering tables
-library(tinytable)
-
+library(tidyverse) # core functions for data manipulation
+library(here)      # constructs file paths
+library(arrow)     # reads parquet files
+library(forcats)   # reorders factor levels and factor-related manipulations
+library(stringr)   # used in str-wrap to wrap long text labels on axes
+library(dplyr)     # manipulating data; filtering, grouping, mutating and recording
+library(ggplot2)   # creating visualizations; stacked bar plots and facet plots
+library(tidyr)     # reshaping data with pivot_longer function
+library(readr)     # managing csv files
 
 
 # Read in the data 

### 2024-12-13 scripts/06-model_data.R

@@ -11,11 +11,10 @@
 #### Workspace setup ####
 
 # load packages
-library(tidyverse)
-library(rpart)
-library(partykit)
-library(here)
-library(arrow)
+library(tidyverse)    # core functions for data manipulation
+library(rpart)        # creates decision tree models
+library(partykit)     # plots decision tree models
+library(here)         # constructs file paths
 
 # Set seed for reproducibility
 set.seed(853)

### 2024-12-13 scripts/07-install_packages.R
last check on packages, ensuring cross referencing them all in data section and in bib

@@ -10,22 +10,22 @@
 
 # Install the necessary packages
 install.packages(c(
-  "readr",      # For reading data
-  "dplyr",      # For data manipulation
-  "openxlsx",   # For working with Excel files
-  "readxl",     # For reading Excel files
   "arrow",      # For saving files as Parquet
-  "tidyverse",  # For data manipulation and visualization
-  "tidyr",      # For tidying data
-  "stringr",    # For string manipulation
-  "tinytable",  # For rendering tables
-  "here",       # For working with relative paths
-  "knitr",      # For dynamic report generation
+  "dplyr",      # For data manipulation
   "forcats",    # For reordering factor levels
+  "ggplot2",    # For data visualization
+  "here",       # For working with relative paths
+  "httr",       # For downloading data
   "kableExtra", # For rendering tables with extra features
-  "broom",      # For tidying model output
-  "testthat",   # For testing data
+  "openxlsx",   # For working with Excel files
+  "partykit",   # For running the model
+  "readr",      # For reading data
+  "readxl",     # For reading Excel files
   "rpart",      # For running the model
-  "partykit"    # For running the model
-  
+  "stringr",    # For string manipulation
+  "testthat",   # For testing data
+  "tidyr",      # For tidying data
+  "tidyverse",  # For data manipulation and visualization
+  "tinytable"   # For rendering tables
 ))
+

### 2024-12-13 paper/climate_change.qmd
going through data section to ensure smooth flow

@@
 This dataset offers insights into public perceptions of climate change in Toronto in the years 2018 and 2021.
-This dataset was accessed from Open Data Toronto [@opendatatoronto] on 6 November 2024.
+This dataset was accessed from `Open Data Toronto` [@opendatatoronto] on 6 November 2024.
 
 ## Software and R-packages
-This project was conducted using the statistical software `R` [@citeR].
-Data cleaning and manipulation were primarily facilitated by the `tidyverse` package [@tidyverse], which encompasses various essential tools.
-Within this suite, `dplyr` [@dplyr] was employed for data manipulation tasks such as filtering, summarizing, and joining datasets, while `readr` [@readr] provided efficient functionality for reading and writing rectangular text data.
-Specifically, the `write_csv` function from `tidyverse` was used to save the raw 2018 dataset.
-To handle Excel files, we incorporated the `httr` package for downloading files directly from online sources and `readxl` [@readxl], which enabled us to read Excel files seamlessly.
-Additionally, the `openxlsx` package was utilized to create a new Excel workbook with multiple sheets, allowing us to store the 2021 dataset in a structured format.
-
-The `arrow` package was employed to handle large datasets efficiently, ensuring smooth data processing, while `forcats` was used for reordering factor levels to facilitate more insightful analyses and visualizations.
-In terms of data tidying, the `tidyr` and `stringr` packages allowed us to reshape and clean the data by managing character strings and handling missing values.
-The [@rpart2024] and [@partykit2024] were used in to make the models.
-For the final documentation and report generation, the `knitr` package was instrumental in integrating R code and outputs into a cohesive and reproducible report format.
-This suite of R packages collectively enabled us to conduct thorough data management, manipulation, and analysis, ultimately contributing to the successful completion of the project.
+This project was conducted using the statistical software `R` [@citeR], with several packages facilitating data cleaning, analysis and reporting.
+The `tidyverse` package [@tidyverse] was central to the project, with `dplyr` [@dplyr] used in the cleaning and exploratory data analysis scripts for filtering, summarizing, and joining datasets.
+`readr` [@readr] handled reading and writing text data, while `tidyr` [@tidyr] reshaped data.
+`stringr` [@stringr] managed character strings, and `forecats` [@forecats] reordered factor levels for visualizations.
+
+In the download script, `httr`[@httr] retrieved files from `Open Data Toronto` [@opendatatoronto], while`readxl` [@readxl] read Excel files, and `openxlsx` [@openxlsx] created structured Excel workbooks.
+The `arrow` package [@arrow] optimized data storage and was used in the simulation and cleaning scripts to save datasets as Parquet files.
+
+For modeling, `rpart` [@rpart] and `partykit` [@partykit] built and visualized decision trees in the model script.
+The `testthat` package [@testthat] validated simulated and cleaned datasets in their respective scripts.
+Visualizations were created using `ggplot2` [@ggplot2] in the exploratory data analysis.
+Reporting relied on `knitr` [@knitr] and `kableExtra` [@kableExtra] to integrate code, outputs, and styled tables.
+The `tinytable`package [@tinytable] generated compact tables in both the exploratory data analysis script as well as in the paper.
+These packages ensured efficient and streamlined data management, analysis and reporting throughout the project.
 
@@
 ### Data Collection
-The data for this analysis comes from two surveys commissioned by the City of Toronto to assess residents' perceptions of climate change and their willingness to take community action.
-In 2018, Environics Research conducted n=404 online interviews with Toronto residents aged 18 and older between October 11 and October 18.
-Each interview lasted approximately 10 minutes.
-The sample was drawn from an online panel, with quotas set by region, age, and gender to reflect the city’s population based on the 2016 Census, and minor weighting was applied.
-Due to the non-random nature of the online survey, no margin of error was assigned, though a random sample of this size would typically have a margin of ±4.9 percentage points, 19 times out of 20.
-
-In 2021, a second survey was conducted by Ipsos, a global market research company.
-This survey included n=1,400 Toronto residents aged 18 and older and used a mixed-method approach.
-The sample consisted of 1,000 respondents from an online panel, 300 recruited via cell phone and landline, and 100 online interviews conducted in Mandarin, Cantonese, and Punjabi.
-This combination of methods aimed to enhance the survey's representativeness.
-For analysis, Version 2 of the 2021 dataset, which presents responses in a numeric format, was used.
+To embark on this analysis, we turn to two pivotal surveys commissioned by the City of Toronto to capture residents' perceptions of climate change and their readiness to take action.
+Our journey begins in 2018, when Environics Research conducted an online survey with 404 Toronto residents aged 18 and older, from October 11 to 18.
+The sample, drawn from an online panel, was carefully crafted with quotas based on region, age, and gender to mirror the 2016 Census.
+A touch of minor weighting ensured a more representative reflection of the population.
+However, it’s important to note that this non-random sample introduces some potential bias, an aspect we keep in mind as we move forward.
+
+The path continues in 2021 with Ipsos at the helm, stepping in with a more expansive survey, engaging 1,400 residents from a mix of methods: 1,000 from an online panel, 300 via phone, and 100 through online interviews conducted in Mandarin, Cantonese, and Punjabi.
+This diverse approach sought to enhance the survey’s representativeness across Toronto’s varied communities.
+For our analysis, we used Version 2 of the 2021 dataset, where responses were presented in a clear, numeric format, offering a solid foundation for our exploration.
+
+With this data in hand, we are now ready to delve into the intricacies of the findings, unearthing patterns, and understanding the deeper story they tell about Toronto’s residents and their views on climate change and collective action.
 
 ### Data Analysis
-The primary focus of this analysis was the 2018 dataset, examining six key variables: age, education, extent informed, likelihood to take action, reasons for not taking action, and the best method for delivering information regarding climate change action.
-I analyzed these variables at the individual level in the 2018 dataset by calculating the percentages within each category, which provided a clear understanding of the distribution and trends within the population.
-
-In addition, I compared the 2018 dataset to the 2021 summary data to assess changes over the years.
-By calculating the percentage distribution for each variable in both years, I was able to identify any shifts in public awareness, engagement, and preferences regarding climate change action.
-This comparison revealed whether there have been notable changes in factors like the public’s level of information about climate change, their likelihood to take action, and their preferred communication methods.
-
-This two-step approach allowed for a comprehensive understanding: a detailed exploration of the 2018 data combined with a broader comparison of trends between 2018 and 2021.
+The focus of this analysis was the 2018 dataset, which examined five key variables: age, education, extent informed, likelihood to take action, and preferred methods for delivering information about climate change action.
+These variables were analyzed at the individual level, allowing for an in-depth exploration of residents' perspectives.
+
+For 2021, summary data was available instead of individual-level data.
+To compare trends, I created summary data for 2018.
+Calculating the percentage distribution for each variable in both years helped identify shifts in demographics, public awareness, and engagement, as well as changes in preferred communication methods.
+Although the absence of individual data for 2021 posed a challenge, this comparison still provided a dynamic view of evolving climate change perspectives in Toronto.
+The two-step approach—detailing 2018 data and then comparing it with 2021 trends—created a comprehensive narrative of change.
 
@@
 #### Individual 2018
-@fig-one illustrates the age distribution of survey respondents in 2018.
-The histogram displays the frequency of respondents across different age groups, with the x-axis representing age intervals and the y-axis indicating the number of respondents within each interval.
-The distribution is relatively balanced, with two noticeable peaks around the 30–40 and 50–60 age ranges, suggesting these age groups are the most represented in the survey.
-
-The vertical dotted lines in the figure highlight key statistical measures: the green dotted line represents the median age, while the blue dashed line indicates the mean age of the respondents.
-Both measures fall near the center of the distribution, reinforcing the observation that the sample is primarily composed of middle-aged individuals.
-Although the distribution appears fairly symmetrical, there is a gradual decline in respondent frequency after the age of 60, with fewer participants aged 90 and above, indicating a smaller representation of older individuals.
-
-Overall, @fig-one provides valuable context for understanding the demographic composition of the survey sample.
-The predominance of middle-aged respondents may influence the interpretation of survey results, particularly if age is a factor in attitudes, behaviors, or preferences related to the study.
+@fig-one presents the age distribution of survey respondents in 2018.
+The histogram shows the frequency of respondents across age groups, with age intervals on the x-axis and the number of respondents on the y-axis.
+The distribution is fairly balanced, with peaks around the 30–40 and 50–60 age ranges, indicating that these groups were the most represented in the survey.
+
+The vertical dotted lines highlight the median and mean ages.
+The green dotted line represents the median age, and the blue dashed line represents the mean age, both located just above 45.
+This suggests the sample is predominantly middle-aged, with a gradual decline in respondent frequency after the age of 60.
+Few participants were over 80, indicating a lower representation of older individuals
 
@@
 #| label: fig-one
-#| fig-cap: "The histogram shows the distribution of age given the 2018 survey respondents."
+#| fig-cap: "Distribution of age given the 2018 survey respondents. The mean and median of the sample is indicated with dashed and dotted lines respectively."
 
@@
 #### Comparison 2018 to 2021
-@fig-two illustrates the different age ditribution for 2018 and 2021 surveys.
-The major difference is that there was greater representation of younger inviduals ranging from 18 to 23 in 2021 compared to 2018.
-The remaining age groups were not very different.
+@fig-two compares the age distributions between 2018 and 2021.
+The main difference is an increase in respondents aged 18-23 in 2021, with other age groups remaining relatively stable.
+This shift may reflect changing demographic patterns or differences in survey methodologies within the three years.
 
@@
 
-### Highest Level of Education Completed
+### Education
 #### Individual 2018
-@fig-three illustrates the distribution of survey respondents by their highest level of education attained.
-The most frequently reported education levels are "Completed undergraduate degree" and "Post graduate/professional school," with both categories having a noticeably higher frequency compared to others, indicating a well-educated respondent population.
-In contrast, fewer respondents reported "Some community college, vocational, trade school" and "Completed community college, vocational, trade school," suggesting these levels are less common among participants.
-Additionally, a small portion of respondents preferred not to disclose their education level.
-This distribution highlights a skew toward higher educational attainment within the sample, which may influence responses related to socio-economic factors and other survey topics.
+@fig-three shows the distribution of respondents by their highest level of education attained in 2018.
+The most common education levels are "Completed undergraduate degree" and "Postgraduate/professional school," indicating a well-educated respondent population.
+In contrast, fewer respondents reported having attended or completed community college, vocational, or trade school, suggesting lower representation in these categories.
+A small portion of respondents chose not to disclose their education level.
+Overall, the distribution reflects a skew toward higher levels of educational attainment.
 ```{r}
@@
 ```
+
 #### Comparison 2018 to 2021
-@fig-four illustrates respondant education level in 2018 and 2021 respectively.
-Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021.
-Despite this, we are still able to make comparisons.
-Individuals with high school diplomas or less account for 9 for 2018 and 38 for 2021 (addition of less than highs school and high school or equivalent categories).
-This could indicate that the younger population was included more in the 2021 suvey or that less education individuals were surveyed.
-Additionally, its not super clear howver those with a post graduate or professional degree accounted for 29 percent in 2018 and 35 percent in 2021.
-This illustrates that more educated inviduals responded to the 2021 survey.
+@fig-four compares the education levels of respondents in 2018 and 2021.
+The two surveys used different education categories, making direct comparisons challenging.
+In 2018, 9% of respondents had a high school diploma or less, while in 2021, this figure rose to 38%, due to the addition of the "less than high school" and "high school or equivalent" categories.
+This shift indicates that the 2021 survey better represented individuals with lower educational attainment.
+
+The 2018 survey provided more detailed categories, including options for community college, trade school, and distinctions between "some" versus "completed" education.
+In contrast, the 2021 survey used broader categories, which likely reduced the specificity of educational data.
+Notably, the 2021 survey appears to have offered a more balanced sample, with a wider spread across various education levels, while the 2018 sample was noticeably skewed toward respondents with higher educational attainment.
+This suggests that the 2021 survey may have captured a broader range of educational backgrounds, providing a more well-rounded representation of Toronto’s population.
+
 ```{r}
@@
 ### Likelihood Taking Action 
-#### Individual 2018
 The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 

### 2024-12-13 paper/climate_change.qmd
clear and concise modeling section

@@
 
-### Best Mode of Delivery
+### Best Method of Delivery
 #### Individual 2018
-@fig-seven, shows the analysis of the best method for delivering climate change information portrayed in @fig-four revealed that the majority of individuals in the 2018 dataset preferred receiving information firstly from advertising campaigns with about 55 percent, newsletters with about 52 percent, followed by the toronto website wiht about 46 percent.
-On the other side of the spectrum, few said they were uninterested in receiving climate action information  with about 5 percent, about 12 percent indicated twitter and then 17 percent mentioned instagram.
-Overall social media platforms Facebook, Instagram and Twtitter were less popular methods of communciation.
-This could be because the survey only included individals over the age of 18.
-Moreover, the median sample was in the 40s.
+@fig-seven, shows 2018 survey results for the preferred method for receiving climate change information.
+Advertising campaigns emerged as the most popular choice, selected by approximately 55 percent of respondents, followed closely by newsletters with 52 percent and the Toronto.ca website with 46 percent.
+On the other hand, social media platforms such as Facebook, Instagram, and Twitter were less popular overall, with Twitter 12 percent and Instagram 17 percent garnering the fewer votes.
+Notably, only 5 percent of respondents reported being uninterested in receiving information about climate action.
+These findings suggest that more traditional communication methods, such as advertising and newsletters, resonated better with respondents compared to social media.
 
@@
 
+library(here)
+
 knitr::include_graphics(here("data/03-figures_data", "communication_18_plot.png"))
@@
 #### Comparison 2018 to 2021
-@fig-eight compares responses from 2018 and 2021 surverys regarding the best method of delivering information on climate change and climate action.
-Aside from the additon of four options to the 2021 survey, both surveys questions are the same.
-The leading category for 2018 is advertising campaigns with 55 percent, closely followed by newsletter emails with 52 percent and the Toronto website with 46.
-The 2021 survey illustrates a consistent trend with the same platforms as the top method of delivering information, specifically the Toronto website with 44 percent, then enewsletter emails with 43 percent and advertising campains at 42 percent.
-These top methods of communciation are more evenly spread out than the 2018 survey results.
-Social media platforms namely twitter, facebook and instagram all increased in the 2021 survey.
-Notable decreases in term of percentage from 2018 to 2021 include events, enewsletter emails, advertising campaigns, brochures and pamphlets.
-The new category of BetterHomesTO.ca webiste accounts for 15 percent of votes for the 2021 survey.
+@fig-eight compares the preferred methods of delivering climate change information between the 2018 and 2021 surveys.
+While the top three methods namely advertising campaigns, newsletters, and the Toronto.ca website remained consistent across both years, there were notable shifts in preferences.
+Traditional methods such as newsletters, advertising campaigns, brochures, and pamphlets saw a decline in 2021.
+In contrast, social media platforms including Twitter, Facebook, and Instagram gained traction, reflecting a growing reliance on digital communication channels.
+
+Additionally, the 2021 survey introduced new categories, including the BetterHomesTO.ca website, which accounted for 15 percent of responses.
+This addition underscores the increasing importance of specialized online platforms in engaging the public on climate action.
+These changes highlight a shift toward more diverse and digitally focused communication strategies over time.
 
@@
 ### Likelihood Taking Action 
-The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
-@fig-nine illustrates self-reported likelihood of taking certain actions that minimize climate change effects.
-On the x-axis, we have the nine different climate actions and on the y-axis is the percentage.
-The stacked bar chart allows understanding of how likely individuals are to take part in the given actions.
-Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action.
-The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements.
-40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely.
-However, 7 percent say they are very unlikely to change their method of transportation.
-Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely.
-Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action.
-Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof.
-In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle.
-While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely.
-This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases.
-This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change!
-The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely.
-Only 23 percent are already consuming meat alternatives.
-Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently.
+@fig-nine illustrates the self-reported likelihood of individuals taking various actions to minimize environmental impacts.
+The x-axis displays nine different climate actions, while the y-axis represents the percentage of individuals corresponding to each likelihood level.
+A stacked bar chart is used to visualize the distribution of responses, with a color-coded legend ranging from green (high likelihood of action) to red (low likelihood of action).
+
+Sorting waste into the correct bins is the most frequently reported action that individuals are currently undertaking, accounting for 60 percent of responses.
+Other common actions individuals are already participating in include walking or cycling short distances with 40 percent, reducing waste by contributing to the repurposing of used products with 37 percent and reducing hydro usage with 36 percent
+
+In contrast, the least popular actions include switching to electric or hybrid vehicles, with 14 percent of respondents reporting they are very unlikely to take this action and 27 percent stating they are somewhat unlikely.
+Similarly, consuming less meat by incorporating more plant-based foods is unpopular, with 12 percent reporting they are very unlikely and 23 percent somewhat unlikely to adopt this change.
+Minimizing car use is another action with low reported likelihood, with 10 percent of respondents very unlikely and 16 percent somewhat unlikely to reduce their car usage.
+
 ```{r}
@@
 # Model {#sec-model}
-The goal of our modelling strategy is twofold.
-Firstly, we aim to predict the likelihood of individuals engaging in climate-friendly actions based on demographic variables, specifically age and education.
-The actions considered include investing in electric or hybrid vehicles, making home improvements (such as using LED lightbulbs), adopting meat alternatives, minimizing car use, purchasing green products, reducing hydro usage, reducing waste, sorting waste correctly, and walking or cycling shorter distances.
-Secondly, we aim to understand how these demographic characteristics influence individuals' likelihood of adopting these behaviors.Here we describe the probability tree model used to investigate the relationship between likelihood and the demographic factors of age and education.
+The goal of our modeling strategy is twofold: first, to predict the likelihood of individuals engaging in climate-friendly actions based on their demographics, and second, to understand how age and education shape these behaviors.
+The actions considered include investing in electric vehicles, reducing hydro usage, adopting meat alternatives, and walking or cycling shorter distances.
+To uncover these patterns, we employ a decision tree model, providing a clear and interpretable framework for analyzing how demographic factors influence climate-positive behaviors.
 
 ## Model set-up
-In this analysis, we focus on predicting the likelihood of taking climate-friendly actions based on the demographic variables of age and education.
-The likelihood is measured on a five-point Likert scale, ranging from "Very unlikely" to "Already doing this or have done this."
-
-### Model Specifications ###
-We use a probability tree model to predict the likelihood of individuals engaging in climate-friendly actions based on two key demographic variables: age and education.
-
-The general form of the model is:
-
-\begin{align} 
-y_i = \beta_0 + \beta_1 * Age_i + \beta_2 * Education_i + \epsilon_i
-\end{align*}
-where:
-
- - $y_i$ represents the likelihood of individual $i$ engaging in a climate-friendly actin, measured on a five point Likert scale:
- 1. "Very unlikely"
- 2. "Somewhat unlikely"
- 3. "Somewhat likely"
- 4. "Very likely"
- 5. "Already doing this or have done this"
-- $\beta_0$ is the intercept, representing the baseline likelihood of taking action when all predictors are zero.
-- $\beta_1$ is the coefficient for Age, representing how a one-year increase affects the likelihood of taking action.
-- $\beta_2$ is the coefficient for Education, a categorical variable that is dummy-coded.
-- $\epsilon_i$ is the error term, accounting for unexplained variation.
-
-This model focuses on the direct effect of age and education on the likelihood of taking climate-friendly actions, assuming a linear relationship between these demographic variables and the outcome variable (the likelihood of action).
+Our model predicts the likelihood of engaging in specific climate-friendly actions using age and education level as predictors.
+Likelihood is quantified on a five-point scale, ranging from "Very unlikely" to "Already doing this or have done this."
+
+### Model Specifications
+In this analysis, we use a decision tree model for each action, where age (continuous) and education (categorical) drive the predictions.
+The decision tree splits the data at each node based on these predictors, identifying demographic conditions linked to climate-positive behaviors.
+
+The outcome variable, likelihood of taking action, is measured using a Likert scale ranging from 1 ("Very unlikely") to 5 ("Already doing this or have done this").
+The decision tree model helps us understand which combinations of age and education influence these behaviors.
 
 ### Model Justification 
-This model was developed to explore how demographic factors such as age and education influence individuals' likelihood of engaging in climate-friendly behaviors.
-By focusing on specific climate actions like reducing energy consumption, adopting sustainable practices, and investing in green technologies, the model aims to provide actionable insights for climate change interventions.
-
-#### Response Variable ####
-The response variable in this analysis is the likelihood of taking climate-friendly actions, measured using a Likert scale (1 = "Very unlikely" to 5 = "Already doing this or have done this").
-This scale captures the respondent’s perceived likelihood of engaging in various climate-friendly behaviors
-
-#### Input Variabless ####
-The input variables (predictors) include:
-
-- **Age**: Previous research indicates that younger individuals may be more inclined to adopt climate-friendly behaviors due to increased environmental awareness (Leiserowitz et al., 2010; Gifford, 2013).
-- **Education**: Higher levels of education are often linked to greater awareness of environmental issues and a higher likelihood of adopting sustainable behaviors (Kollmuss & Agyeman, 2002).
-Education is treated as a categorical variable and dummy-coded for analysis.
-
-#### Model Structure ####
-This model assumes a linear relationship between the predictors (age and education) and the likelihood of taking action.
-Specifically, the likelihood of taking climate-friendly actions is modeled as a function of age and education, with coefficients representing the change in the likelihood of action associated with a unit change in each predictor.
-
-There are no interaction terms in this model, meaning we assume that the effects of age and education on the likelihood of taking action are independent of each other.
-This simplicity ensures clear interpretation of each predictor's individual effect on the likelihood of taking climate-friendly actions.
-
-## Nine Models ##
-
-We fit nine separate probability tree models, one for each climate-friendly action we are predicting.
-Each model uses age and education as the predictors to estimate the likelihood of the corresponding action.
-These actions are:
-
-1. Likelihood of investing in an electric or hybrid vehicle
-2. Likelihood of making home improvements (e.g., using LED lightbulbs)
-3. Likelihood of adopting meat alternatives
-4. Likelihood of minimizing car use
-5. Likelihood of purchasing green products
-6  Likelihood of reducing hydro usage
-7. Likelihood of reducing waste by repurposing used products
-8. Likelihood of sorting waste correctly
-9. Likelihood of walking or cycling shorter distances
-
-Each model is built using the same structure but predicts a different outcome variable. This approach allows us to analyze the specific impact of age and education on each climate-friendly action.
-
-### Decision Trees
-A decision tree is a machine learning model used to make predictions by recursively splitting data into subsets based on specific conditions of the predictor variables.
-It is structured like a tree, where the top node is the root node, representing the entire dataset, and subsequent nodes represent splits based on decision rules.
-The branches indicate the outcomes of these rules, and the leaf nodes (terminal nodes) provide the final prediction for each subset.
-
-Each split is determined by the predictor variable most strongly associated with the target outcome, maximizing predictive accuracy.
-A split separates individuals by age or educational level.
-The prediction in each terminal node includes the majority class (e.g., "Very likely") and additional information such as sample size (n) and error percentage.
-The error percentage reflects the proportion of cases in that node misclassified by the model.
-A higher error percentage indicates greater uncertainty or variability within the group, while a lower error percentage suggests a more precise classification.
-
-#### Likelihood of investing in an electric or hybrid vehicle
+This approach sheds light on how demographic factors like age and education impact the likelihood of engaging in climate-friendly behaviors.
+By focusing on actions like reducing energy consumption, adopting sustainable practices, and investing in green technologies, the model provides insights that can inform targeted interventions.
+
+#### Response Variable
+The response variable measures the likelihood of engaging in climate-friendly behaviors, represented on a Likert scale.
+This captures an individual’s readiness to adopt sustainable actions in daily life.
+
+#### Input Variables
+Our predictors are:
+
+- **Age**: Research shows that younger individuals tend to exhibit greater environmental awareness and a higher likelihood of adopting climate-friendly behaviors (Leiserowitz et al., 2010; Gifford, 2013).
+
+- **Education**: Higher education levels correlate with increased environmental awareness and a higher likelihood of adopting sustainable behaviors (Kollmuss & Agyeman, 2002).
+Education is treated as a categorical variable, divided into distinct levels for analysis.
+
+#### Model Structure
+The decision tree splits data based on age and education, revealing how different demographic groups are more or less likely to engage in climate-friendly actions.
+Unlike linear models, decision trees do not assume a direct relationship between predictors and outcomes but instead identify the conditions under which individuals are more likely to adopt sustainable practices.
+
+This model assumes that the effects of age and education on behavior are independent, allowing for a clear interpretation of each factor’s influence on the likelihood of taking climate-positive actions.
+
+## Understanding Decision Trees
+A decision tree recursively splits data based on predictor variables, starting with a root node that represents the entire dataset.
+It branches out based on decision rules, leading to terminal nodes that predict outcomes, such as the likelihood of a climate-friendly action.
+Each split maximizes predictive accuracy, and the model's predictions are accompanied by error rates, which indicate the reliability of the classification.
+
+## Decision Trees for Climate-Friendly Actions
+We fit nine decision tree models to predict the likelihood of various climate-friendly actions, using age and education as predictors:
+
+1. Likelihood of switching in an electric or hybrid vehicle
+2. Likelihood of minimizing car use
+3. Likelihood of walking or cycling shorter distances
+4. Likelihood of purchasing green products
+5. Likelihood of reducing waste by repurposing used product
+6. Likelihood of sorting waste correctly
+7. Likelihood of making home improvements 
+8. Likelihood of adopting meat alternatives
+9. Likelihood of reducing hydro usage
+
+Each model follows a similar structure, revealing how age and education influence each action.
+
+### Transportation Actions
+
+#### Likelihood of switching to an electric or hybrid vehicle
 @fig-ten predicts individuals’ likelihood to invest in an electric or hybrid vehicle based on their highest level of education and age.
@@
 
+#### Likelihood of minimizing car use
+@fig-eleven predicts individuals' likelihood of minimizing car use as a measure to mitigate climate change.
+In this case, the tree structure is straightforward, containing only a single root node.
+The model classifies all individuals into one category, "Already doing this or have done this," with a sample size of 320 and an error rate of 61.9%.
+The absence of splits in the tree indicates that no other variables, such as age or education, contributed sufficient predictive power to justify further segmentation.
+
+This outcome suggests that either the input data lacks variability in relevant features, or the behavior of minimizing car use is widespread and consistent across the sample population.
+Consequently, the model does not differentiate between subgroups and treats all individuals as having the same likelihood of engaging in this behavior.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-eleven
+#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
+
+knitr::include_graphics(here::here("models/minimize_car_tree.png"))
+
+```
+
+#### Likelihood of walking or cycling shorter distances
+@fig-twelve predicts the likelihood of individuals walking or cycling short distances based on their highest level of education and age.
+The root node identifies education level as the most significant factor.
+Individuals with postgraduate, undergraduate, or some university education are classified as “Already doing this or have done this” (n = 231, error = 51.9%).
+This indicates a strong relationship between higher education levels and the adoption of walking or cycling short distances.
+
+For those with lower education levels (community/trade school, high school, or preferring not to answer), the model further splits based on age.
+The first division occurs at 65.5 years, distinguishing those “Very likely” to walk or cycle short distances (n = 15, error = 60%) from others.
+Additional splits by age at 33.5 years and 60.5 years, along with education, refine the classification.
+This stepwise approach demonstrates how age interacts with education to influence short-distance mobility choices.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-twelve
+#| fig-cap: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
+
+knitr::include_graphics(here::here("models/short_distance_tree.png"))
+
+```
+
+### Waste and Product Actions
+#### Likelihood of purchasing green products
+@fig-thirteen predicts individuals' likelihood of purchasing green products to minimize the effects of climate change based on age and highest level of education.
+The model identifies age as the most important variable for the initial split.
+At the root node, individuals are divided into two groups: those younger than 37.5 years old and those 37.5 years or older.
+This division highlights age as a key determinant in predicting green product purchasing likelihood.
+
+For individuals aged 37.5 years or older, the next split is determined by the highest level of education.
+Those with educational backgrounds such as "High School," "Postgrad," "Some Community/Trade School," "Some University," or "Prefer Not to Answer" are further analyzed.
+Within this group, additional splits are made based on age thresholds of 50.5 years and 47.5 years.
+These splits refine the classification into categories such as "Somewhat likely" or "Already doing this or have done this," with varying error rates and sample sizes.
+
+Among individuals younger than 37.5 years, the highest level of education again plays a crucial role in the split.
+Individuals with educational backgrounds such as "Postgrad," "Community/Trade School," "High School," or "Some University" are further segmented.
+Within this subgroup, age thresholds of 27.5 years and 22.5 years are used to differentiate individuals into categories such as "Very likely" or "Somewhat likely," reflecting diverse levels of engagement with green product purchasing.
+Overall, the decision tree incorporates age and education as the primary variables to segment individuals into likelihood categories.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-thirteen
+#| fig-cap: Probability tree for likelihood of purchasing green products, predicted by age and education.
+
+knitr::include_graphics(here::here("models/green_product_tree.png"))
+
+```
+
+#### Likelihood of reducing waste by repurposing used product
+@fig-fourteen predicts the likelihood of reducing waste is based on age and highest level of education.
+The root node splits individuals by age at 34.5 years, indicating that younger and older individuals exhibit distinct waste-reduction behaviors.
+For those under 34.5 years, the model uses highest level of education as a key determinant, classifying them as either "Somewhat likely" or "Very likely" to reduce waste.
+
+For individuals aged 34.5 years or older, the tree splits again by education and further refines predictions using additional age thresholds at 61.5 and 75.5 years.
+Older individuals with higher education levels are more likely to have "Already done this or are doing this," while those with lower education levels are categorized as "Somewhat likely" or "Very likely." This structure highlights the combined influence of education and age on waste-reduction behaviors, with clear thresholds that differentiate groups.
+
+The decision tree demonstrates that age is the primary driver of waste-reduction behavior, with education acting as an important secondary factor.
+These variables together capture differences in sustainability habits, showing how younger, middle-aged, and older populations vary in their likelihood to engage in reducing waste.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-fourteen
+#| fig-cap: Probability tree for likelihood of reducing waste, predicted by age and education.
+
+knitr::include_graphics(here::here("models/reduce_waste_tree.png"))
+
+```
+
+#### Likelihood of sorting waste correctly
+@fig-fifteen predicts the likelihood of sorting waste correctly identifies highest level of education as the primary determinant.
+Individuals with education levels at or above Community/Trade School, Postgraduate, or Some University are categorized as "Already doing this or have done this," accounting for the majority of respondents (n = 295, err = 37.3%).
+This demonstrates that higher educational attainment correlates with proactive waste-sorting behaviors.
+
+For individuals whose highest level of education is High School, the model introduces a secondary split based on age at 37 years.
+Younger individuals under 37 years are categorized as "Already doing this or have done this," albeit with a higher error rate (n = 7, err = 57.1%).
+Older individuals aged 37 or above are more likely classified as "Very likely" to sort waste correctly (n = 17, err = 35.3%).
+These splits highlight the combined influence of education and age on waste-sorting behavior, with specific subgroups showing varying levels of commitment and accuracy.
+
+This decision tree underscores that education plays a dominant role in predicting waste-sorting behavior, while age further refines these predictions, especially for those with lower education levels.
+The model provides straightforward insights into how demographics shape sustainable practices.
+```{r}
+#| warning: false
+#| echo: false
+#| message: false
+#| label: fig-fifteen
+#| fig-cap: Probability tree for likelihood of sorting waste correctly, predicted by age and education.
+
+knitr::include_graphics(here::here("models/sort_waste_tree.png"))
+
+```
+
+### Home and Lifestyle Changes
 #### Likelihood of making home improvements
-In @fig-eleven, the root node splits the data at age 35.5, indicating that age is the most influential factor in determining climate-related home improvement behavior.
+In @fig-sixteen, the root node splits the data at age 35.5, indicating that age is the most influential factor in determining climate-related home improvement behavior.
 Individuals aged 36 years or older are predominantly classified as "Already doing this or have done this," with a large sample size (n = 223) but a moderate error rate of 59.6%, reflecting variability in this group.
@@
 #| message: false
-#| label: fig-eleven
+#| label: fig-sixteen
 #| fig-cap: Probability tree for likelihood of making home improvements predicted by age and education.
@@
 #### Likelihood of adopting meat alternatives
-@fig-twelve predicts individuals’ likelihood of consuming meat alternatives to minimize the effects of climate change based on their age and highest level of education.
+@fig-seventeen predicts individuals’ likelihood of consuming meat alternatives to minimize the effects of climate change based on their age and highest level of education.
 The model identifies age as the most important variable for the initial split.
@@
 #| message: false
-#| label: fig-twelve
+#| label: fig-seventeen
 #| fig-cap: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
@@
 
-#### Likelihood of minimizing car use
-@fig-thirteen predicts individuals' likelihood of minimizing car use as a measure to mitigate climate change.
-In this case, the tree structure is straightforward, containing only a single root node.
-The model classifies all individuals into one category, "Already doing this or have done this," with a sample size of 320 and an error rate of 61.9%.
-The absence of splits in the tree indicates that no other variables, such as age or education, contributed sufficient predictive power to justify further segmentation.
-
-This outcome suggests that either the input data lacks variability in relevant features, or the behavior of minimizing car use is widespread and consistent across the sample population.
-Consequently, the model does not differentiate between subgroups and treats all individuals as having the same likelihood of engaging in this behavior.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-thirteen
-#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
-
-knitr::include_graphics(here::here("models/minimize_car_tree.png"))
-
-```
-
-#### Likelihood of purchasing green products
-@fig-fourteen predicts individuals' likelihood of purchasing green products to minimize the effects of climate change based on age and highest level of education.
-The model identifies age as the most important variable for the initial split.
-At the root node, individuals are divided into two groups: those younger than 37.5 years old and those 37.5 years or older.
-This division highlights age as a key determinant in predicting green product purchasing likelihood.
-
-For individuals aged 37.5 years or older, the next split is determined by the highest level of education.
-Those with educational backgrounds such as "High School," "Postgrad," "Some Community/Trade School," "Some University," or "Prefer Not to Answer" are further analyzed.
-Within this group, additional splits are made based on age thresholds of 50.5 years and 47.5 years.
-These splits refine the classification into categories such as "Somewhat likely" or "Already doing this or have done this," with varying error rates and sample sizes.
-
-Among individuals younger than 37.5 years, the highest level of education again plays a crucial role in the split.
-Individuals with educational backgrounds such as "Postgrad," "Community/Trade School," "High School," or "Some University" are further segmented.
-Within this subgroup, age thresholds of 27.5 years and 22.5 years are used to differentiate individuals into categories such as "Very likely" or "Somewhat likely," reflecting diverse levels of engagement with green product purchasing.
-Overall, the decision tree incorporates age and education as the primary variables to segment individuals into likelihood categories.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-forteen
-#| fig-cap: Probability tree for likelihood of purchasing green products, predicted by age and education.
-
-knitr::include_graphics(here::here("models/green_product_tree.png"))
-
-```
-
 #### Likelihood of reducing hydro usage
-@fig-fifteen identifies age and highest level of education as key predictors influencing the likelihood of reducing hydro usage.
+@fig-eighteen identifies age and highest level of education as key predictors influencing the likelihood of reducing hydro usage.
 The root node of the tree reveals that individuals younger than 34.5 years old are categorized as "Very likely" to reduce hydro usage, with a sample size of 87 and an error rate of 60.9%.
@@
 #| message: false
-#| label: fig-fifteen
+#| label: fig-eighteen
 #| fig-cap: Probability tree for likelihood of reducing hydro usage, predicted by age and education.
@@
 knitr::include_graphics(here::here("models/reduce_hydro_tree.png"))
-
-```
-
-####  Likelihood of reducing waste
-@fig-sixteen predicts the likelihood of reducing waste is based on age and highest level of education.
-The root node splits individuals by age at 34.5 years, indicating that younger and older individuals exhibit distinct waste-reduction behaviors.
-For those under 34.5 years, the model uses highest level of education as a key determinant, classifying them as either "Somewhat likely" or "Very likely" to reduce waste.
-
-For individuals aged 34.5 years or older, the tree splits again by education and further refines predictions using additional age thresholds at 61.5 and 75.5 years.
-Older individuals with higher education levels are more likely to have "Already done this or are doing this," while those with lower education levels are categorized as "Somewhat likely" or "Very likely." This structure highlights the combined influence of education and age on waste-reduction behaviors, with clear thresholds that differentiate groups.
-
-The decision tree demonstrates that age is the primary driver of waste-reduction behavior, with education acting as an important secondary factor.
-These variables together capture differences in sustainability habits, showing how younger, middle-aged, and older populations vary in their likelihood to engage in reducing waste.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-sixteen
-#| fig-cap: Probability tree for likelihood of reducing waste, predicted by age and education.
-
-knitr::include_graphics(here::here("models/reduce_waste_tree.png"))
-
-```
-
-####  Likelihood of sorting waste correctly
-@fig-seventeen predicts the likelihood of sorting waste correctly identifies highest level of education as the primary determinant.
-Individuals with education levels at or above Community/Trade School, Postgraduate, or Some University are categorized as "Already doing this or have done this," accounting for the majority of respondents (n = 295, err = 37.3%).
-This demonstrates that higher educational attainment correlates with proactive waste-sorting behaviors.
-
-For individuals whose highest level of education is High School, the model introduces a secondary split based on age at 37 years.
-Younger individuals under 37 years are categorized as "Already doing this or have done this," albeit with a higher error rate (n = 7, err = 57.1%).
-Older individuals aged 37 or above are more likely classified as "Very likely" to sort waste correctly (n = 17, err = 35.3%).
-These splits highlight the combined influence of education and age on waste-sorting behavior, with specific subgroups showing varying levels of commitment and accuracy.
-
-This decision tree underscores that education plays a dominant role in predicting waste-sorting behavior, while age further refines these predictions, especially for those with lower education levels.
-The model provides straightforward insights into how demographics shape sustainable practices.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-seventeen
-#| fig-cap: Probability tree for likelihood of sorting waste correctly, predicted by age and education.
-
-knitr::include_graphics(here::here("models/sort_waste_tree.png"))
-
-```
-
-####  Likelihood of walking or cycling shorter distances
-@fig-eighteen predicts the likelihood of individuals walking or cycling short distances based on their highest level of education and age.
-The root node identifies education level as the most significant factor.
-Individuals with postgraduate, undergraduate, or some university education are classified as “Already doing this or have done this” (n = 231, error = 51.9%).
-This indicates a strong relationship between higher education levels and the adoption of walking or cycling short distances.
-
-For those with lower education levels (community/trade school, high school, or preferring not to answer), the model further splits based on age.
-The first division occurs at 65.5 years, distinguishing those “Very likely” to walk or cycle short distances (n = 15, error = 60%) from others.
-Additional splits by age at 33.5 years and 60.5 years, along with education, refine the classification.
-This stepwise approach demonstrates how age interacts with education to influence short-distance mobility choices.
-```{r}
-#| warning: false
-#| echo: false
-#| message: false
-#| label: fig-eighteen
-#| fig-cap: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
-
-knitr::include_graphics(here::here("models/short_distance_tree.png"))
 

### 2024-12-13 paper/climate_change.qmd
tidying model section

@@
 #### Likelihood of switching to an electric or hybrid vehicle
-@fig-ten predicts individuals’ likelihood to invest in an electric or hybrid vehicle based on their highest level of education and age.
-The model identifies highest level of education as the most important variable for the initial split.
-At the root node, individuals are divided into two groups: those with "Some Community/Trade School" or "Some University" education and those with other educational backgrounds such as "High School," "Undergrad," "Postgrad," or "Prefer Not to Answer."
-
-For individuals with "Some Community/Trade School" or "Some University" education, the tree predicts that they are "Very likely" to invest, with a sample size of 47 and an error rate of 63.8%.
-This indicates moderate variability within this group.
-
-For those with other educational backgrounds, further splits are based on age.
-Younger individuals (below 38.5 years) are segmented further.
-A subset aged under 34.5 years is split into two groups, with one group (n = 10) being "Very likely" to invest, with a lower error rate of 30%.
-The other group is classified as "Somewhat likely," with a higher error rate of 60.7%.
-Older individuals (38.5 years or older) are less likely to invest.
-For instance, those aged above 68.5 years are predicted as "Very unlikely" with a sample size of 18 and an error rate of 61.1%, while those aged between 34.5 and 68.5 years are divided into "Somewhat unlikely" or "Somewhat likely" categories.
-
-Overall, the decision tree reveals distinct patterns where educational attainment and age interact to predict investment likelihood, with younger individuals and those with less formal education being more likely to invest.
+@fig-ten reveals that education is the primary predictor for the likelihood of switching to an electric or hybrid vehicle.
+Individuals with "Some Community/Trade School" or "Some University" education are "Very likely" to invest, though with moderate variability (error rate 63.8%).
+Those with higher education show more age-based segmentation.
+Younger individuals under 35 years are more likely to invest, with a lower error rate (30%).
+Older individuals, particularly those over 69 years, are "Very unlikely" to invest.
+This model demonstrates how age and education interact to influence vehicle choice.
 
@@
 #### Likelihood of minimizing car use
-@fig-eleven predicts individuals' likelihood of minimizing car use as a measure to mitigate climate change.
-In this case, the tree structure is straightforward, containing only a single root node.
-The model classifies all individuals into one category, "Already doing this or have done this," with a sample size of 320 and an error rate of 61.9%.
-The absence of splits in the tree indicates that no other variables, such as age or education, contributed sufficient predictive power to justify further segmentation.
-
-This outcome suggests that either the input data lacks variability in relevant features, or the behavior of minimizing car use is widespread and consistent across the sample population.
-Consequently, the model does not differentiate between subgroups and treats all individuals as having the same likelihood of engaging in this behavior.
+@fig-eleven shows that the likelihood of minimizing car use is consistent across the sample, with a high error rate (61.9%).
+The model classifies all individuals into the "Already doing this or have done this" category, indicating widespread adoption of this behavior, regardless of age or education
+
 ```{r}
@@
 #### Likelihood of walking or cycling shorter distances
-@fig-twelve predicts the likelihood of individuals walking or cycling short distances based on their highest level of education and age.
-The root node identifies education level as the most significant factor.
-Individuals with postgraduate, undergraduate, or some university education are classified as “Already doing this or have done this” (n = 231, error = 51.9%).
-This indicates a strong relationship between higher education levels and the adoption of walking or cycling short distances.
-
-For those with lower education levels (community/trade school, high school, or preferring not to answer), the model further splits based on age.
-The first division occurs at 65.5 years, distinguishing those “Very likely” to walk or cycle short distances (n = 15, error = 60%) from others.
-Additional splits by age at 33.5 years and 60.5 years, along with education, refine the classification.
-This stepwise approach demonstrates how age interacts with education to influence short-distance mobility choices.
+@fig-twelve indicates that education is the primary factor influencing short-distance walking or cycling.
+Those with higher education (postgraduate, undergraduate, or some university) are more likely to engage in this behavior, with an error rate of 51.9%.
+For those with lower education, age plays a significant role, with younger individuals (under 66 years) more likely to walk or cycle, with an error rate of 60%.
+This model highlights how education and age together shape short-distance mobility, with error rates reflecting the model's predictive variability.
+
 ```{r}
@@
 #### Likelihood of purchasing green products
-@fig-thirteen predicts individuals' likelihood of purchasing green products to minimize the effects of climate change based on age and highest level of education.
-The model identifies age as the most important variable for the initial split.
-At the root node, individuals are divided into two groups: those younger than 37.5 years old and those 37.5 years or older.
-This division highlights age as a key determinant in predicting green product purchasing likelihood.
-
-For individuals aged 37.5 years or older, the next split is determined by the highest level of education.
-Those with educational backgrounds such as "High School," "Postgrad," "Some Community/Trade School," "Some University," or "Prefer Not to Answer" are further analyzed.
-Within this group, additional splits are made based on age thresholds of 50.5 years and 47.5 years.
-These splits refine the classification into categories such as "Somewhat likely" or "Already doing this or have done this," with varying error rates and sample sizes.
-
-Among individuals younger than 37.5 years, the highest level of education again plays a crucial role in the split.
-Individuals with educational backgrounds such as "Postgrad," "Community/Trade School," "High School," or "Some University" are further segmented.
-Within this subgroup, age thresholds of 27.5 years and 22.5 years are used to differentiate individuals into categories such as "Very likely" or "Somewhat likely," reflecting diverse levels of engagement with green product purchasing.
-Overall, the decision tree incorporates age and education as the primary variables to segment individuals into likelihood categories.
+@fig-thirteen reveals that age is the initial split for green product purchasing behavior.
+Younger individuals (under 38 years) are more likely to purchase green products, with an error rate of 51.9%.
+Education further refines the prediction.
+Older individuals (over 38 years) are classified by both age and education, with postgraduate education leading to higher engagement in purchasing green products, with an error rate of 60%.
+This model shows how age and education influence consumer choices in sustainable products.
 ```{r}
@@
 #### Likelihood of reducing waste by repurposing used product
-@fig-fourteen predicts the likelihood of reducing waste is based on age and highest level of education.
-The root node splits individuals by age at 34.5 years, indicating that younger and older individuals exhibit distinct waste-reduction behaviors.
-For those under 34.5 years, the model uses highest level of education as a key determinant, classifying them as either "Somewhat likely" or "Very likely" to reduce waste.
-
-For individuals aged 34.5 years or older, the tree splits again by education and further refines predictions using additional age thresholds at 61.5 and 75.5 years.
-Older individuals with higher education levels are more likely to have "Already done this or are doing this," while those with lower education levels are categorized as "Somewhat likely" or "Very likely." This structure highlights the combined influence of education and age on waste-reduction behaviors, with clear thresholds that differentiate groups.
-
-The decision tree demonstrates that age is the primary driver of waste-reduction behavior, with education acting as an important secondary factor.
-These variables together capture differences in sustainability habits, showing how younger, middle-aged, and older populations vary in their likelihood to engage in reducing waste.
+@fig-fourteen shows that age is the primary factor for waste reduction behaviors.
+Younger individuals (under 35 years) are more likely to repurpose waste, with an error rate of 57.1%.
+Education further refines the classification.
+Older individuals (over 35 years) show varied likelihoods based on education, with more highly educated individuals more likely to repurpose waste, with an error rate of 60%.
+This highlights the influence of both age and education on waste-reduction habits.
 ```{r}
@@
 #### Likelihood of sorting waste correctly
-@fig-fifteen predicts the likelihood of sorting waste correctly identifies highest level of education as the primary determinant.
-Individuals with education levels at or above Community/Trade School, Postgraduate, or Some University are categorized as "Already doing this or have done this," accounting for the majority of respondents (n = 295, err = 37.3%).
-This demonstrates that higher educational attainment correlates with proactive waste-sorting behaviors.
-
-For individuals whose highest level of education is High School, the model introduces a secondary split based on age at 37 years.
-Younger individuals under 37 years are categorized as "Already doing this or have done this," albeit with a higher error rate (n = 7, err = 57.1%).
-Older individuals aged 37 or above are more likely classified as "Very likely" to sort waste correctly (n = 17, err = 35.3%).
-These splits highlight the combined influence of education and age on waste-sorting behavior, with specific subgroups showing varying levels of commitment and accuracy.
-
-This decision tree underscores that education plays a dominant role in predicting waste-sorting behavior, while age further refines these predictions, especially for those with lower education levels.
-The model provides straightforward insights into how demographics shape sustainable practices.
+@fig-fifteen identifies education as the primary factor for sorting waste.
+Those with higher education (at least community/trade school or postgraduate) are more likely to sort waste correctly, with an error rate of 37.3%.
+Age further refines the predictions for those with lower education levels, with younger individuals under 37 years being more likely to sort waste correctly, albeit with a higher error rate of 57.1%.
+Older individuals (37 years and above) are more likely to sort waste correctly, with an error rate of 35.3%.
+The model emphasizes the role of education in fostering proper waste-sorting behaviors, with age providing additional nuance.
 ```{r}

### 2024-12-13 scripts/05-exploratory_data_analysis.R

@@ -261,16 +261,16 @@ data_summary <- data_summary %>%
   mutate(
     delivery_method = case_when(
       str_detect(delivery_method, "toronto.ca_website") ~ "Toronto.ca website",
-      str_detect(delivery_method, "events") ~ "City of Toronto events",
+      str_detect(delivery_method, "events") ~ "City events",
       str_detect(delivery_method, "twitter") ~ "Twitter",
       str_detect(delivery_method, "facebook") ~ "Facebook",
       str_detect(delivery_method, "instagram") ~ "Instagram",
-      str_detect(delivery_method, "enewsletter_email") ~ "City of Toronto e-newsletters / email",
+      str_detect(delivery_method, "enewsletter_email") ~ "City e-newsletters / email",
       str_detect(delivery_method, "councillor_communication") ~ "Councillor communications",
       str_detect(delivery_method, "advertising_campaigns") ~ "Advertising campaigns",
       str_detect(delivery_method, "brochures_pamphlets") ~ "Brochures, pamphlets",
       str_detect(delivery_method, "other") ~ "Other",
-      str_detect(delivery_method, "not_interested_receiving") ~ "Not interested in receiving information",
+      str_detect(delivery_method, "not_interested_receiving") ~ "Not interested",
       TRUE ~ delivery_method  # Default case if something unexpected
     )
   )

### 2024-12-13 paper/climate_change.qmd
finished tidying modeling section :) yay

@@
 # Model {#sec-model}
-The goal of our modeling strategy is twofold: first, to predict the likelihood of individuals engaging in climate-friendly actions based on their demographics, and second, to understand how age and education shape these behaviors.
+The goal of our modeling strategy is twofold: first, to predict how demographic factors influence individuals’ likelihood of engaging in climate-friendly behaviors, and second, to uncover the role of age and education in shaping these actions.
 The actions considered include investing in electric vehicles, reducing hydro usage, adopting meat alternatives, and walking or cycling shorter distances.
-To uncover these patterns, we employ a decision tree model, providing a clear and interpretable framework for analyzing how demographic factors influence climate-positive behaviors.
+We use a decision tree model to provide a clear, interpretable framework for analyzing these relationships.
 
 ## Model set-up
-Our model predicts the likelihood of engaging in specific climate-friendly actions using age and education level as predictors.
-Likelihood is quantified on a five-point scale, ranging from "Very unlikely" to "Already doing this or have done this."
+Our model predicts the likelihood of engaging in specific climate-positive actions, with age and education level serving as predictors.
+Likelihood is measured on a five-point scale, ranging from "Already doing this or have done this" to "Very unlikely."
 
 ### Model Specifications
-In this analysis, we use a decision tree model for each action, where age (continuous) and education (categorical) drive the predictions.
-The decision tree splits the data at each node based on these predictors, identifying demographic conditions linked to climate-positive behaviors.
-
-The outcome variable, likelihood of taking action, is measured using a Likert scale ranging from 1 ("Very unlikely") to 5 ("Already doing this or have done this").
-The decision tree model helps us understand which combinations of age and education influence these behaviors.
+We employ separate decision tree models for each action.
+Age (continuous) and education (categorical) are the key predictors driving predictions.
+Each tree splits the data at nodes based on these variables, revealing demographic conditions associated with greater or lesser likelihoods of climate-positive behaviors.
 
 ### Model Justification 
-This approach sheds light on how demographic factors like age and education impact the likelihood of engaging in climate-friendly behaviors.
-By focusing on actions like reducing energy consumption, adopting sustainable practices, and investing in green technologies, the model provides insights that can inform targeted interventions.
+This approach provides insights into how demographic factors influence climate-friendly actions, including energy reduction, sustainable practices, and green technology adoption.
+By identifying demographic groups more likely to take these actions, the model can inform targeted interventions.
 
 #### Response Variable
-The response variable measures the likelihood of engaging in climate-friendly behaviors, represented on a Likert scale.
-This captures an individual’s readiness to adopt sustainable actions in daily life.
+The response variable measures the likelihood of engaging in specific climate-friendly behaviors, represented on a five-point scale: "Already doing this or have done this," "Very likely," "Somewhat likely," "Somewhat unlikely," and "Very unlikely." This scale reflects an individual’s readiness to adopt sustainable practices.
 
@@
 
-- **Age**: Research shows that younger individuals tend to exhibit greater environmental awareness and a higher likelihood of adopting climate-friendly behaviors (Leiserowitz et al., 2010; Gifford, 2013).
-
-- **Education**: Higher education levels correlate with increased environmental awareness and a higher likelihood of adopting sustainable behaviors (Kollmuss & Agyeman, 2002).
-Education is treated as a categorical variable, divided into distinct levels for analysis.
+- **Age**: Research shows that younger individuals often demonstrate greater environmental awareness and a stronger inclination toward sustainable actions (Leiserowitz et al., 2010; Gifford, 2013).
+
+- **Education**: Previous studies illustrate that higher education correlates with increased environmental awareness and sustainable behavior adoption (Kollmuss & Agyeman, 2002).
 
 #### Model Structure
-The decision tree splits data based on age and education, revealing how different demographic groups are more or less likely to engage in climate-friendly actions.
-Unlike linear models, decision trees do not assume a direct relationship between predictors and outcomes but instead identify the conditions under which individuals are more likely to adopt sustainable practices.
-
-This model assumes that the effects of age and education on behavior are independent, allowing for a clear interpretation of each factor’s influence on the likelihood of taking climate-positive actions.
+The decision tree splits data based on age and education, uncovering demographic patterns in climate-positive behaviors.
+Unlike linear models, decision trees do not assume direct relationships but instead identify conditions under which certain behaviors are more likely to occur.
+This assumption of independence allows clear interpretation of each factor’s influence.
 
 ## Understanding Decision Trees
-A decision tree recursively splits data based on predictor variables, starting with a root node that represents the entire dataset.
-It branches out based on decision rules, leading to terminal nodes that predict outcomes, such as the likelihood of a climate-friendly action.
-Each split maximizes predictive accuracy, and the model's predictions are accompanied by error rates, which indicate the reliability of the classification.
-
-## Decision Trees for Climate-Friendly Actions
-We fit nine decision tree models to predict the likelihood of various climate-friendly actions, using age and education as predictors:
+Decision trees predict outcomes by recursively splitting data based on predictor variables.
+Starting at the root node (entire dataset), the tree branches into nodes based on decision rules, ultimately reaching terminal nodes that represent specific predictions, such as the likelihood of adopting sustainable behaviors.
+Each split aims to maximize prediction accuracy, and error rates indicate the reliability of classifications.
+
+### Decision Trees for Climate-Friendly Actions
+We fit nine decision tree models to predict the likelihood of the following climate-friendly actions, using age and education as predictors:
 
@@
 
-Each model follows a similar structure, revealing how age and education influence each action.
+Each model follows a consistent structure, highlighting how age and education influence these behaviors.
+
+## Model Estimation and Interpretation 
+The model predicts that younger individuals with higher education levels are more likely to adopt climate-friendly behaviors.
+The decision tree identifies key splits in the data and evaluates prediction reliability using error rates, providing insight into the impact of age and education on sustainable actions.
 
@@
 #### Likelihood of making home improvements
-In @fig-sixteen, the root node splits the data at age 35.5, indicating that age is the most influential factor in determining climate-related home improvement behavior.
-Individuals aged 36 years or older are predominantly classified as "Already doing this or have done this," with a large sample size (n = 223) but a moderate error rate of 59.6%, reflecting variability in this group.
-
-For individuals younger than 36 years, the tree introduces education as the next important factor.
-Those with higher educational attainment ("Community/Trade School," "Some University," or "Postgraduate") are classified as "Very likely" to make climate-conscious home improvements (n = 40) with an error rate of 55.0%.
-Conversely, individuals with lower education levels, such as "High School" or "Some Community/Trade School," are classified as "Somewhat likely" (n = 46) but have a higher error rate of 67.4%, indicating less predictive certainty.
-A smaller subset of younger individuals with similar educational attainment is classified as "Somewhat likely" (n = 10) with a lower error rate of 40.0%, suggesting higher confidence in this classification.
-The decision tree highlights clear trends based on age and education, with older age groups and higher educational attainment linked to greater engagement in making home improvements.
+@fig-sixteen shows that age is the key predictor for home improvement behavior.
+Individuals aged 36 years and older are predominantly classified as "Already doing this or have done this," with an error rate of 59.6%.
+For younger individuals (under 36), education plays a role: those with higher educational attainment ("Community/Trade School," "Some University," or "Postgraduate") are "Very likely" to make home improvements, with an error rate of 55%.
+Conversely, individuals with lower education levels are classified as "Somewhat likely," with a higher error rate of 67.4%.
+This model highlights how age and education interact to influence home improvement decisions.
 
@@
 #### Likelihood of adopting meat alternatives
-@fig-seventeen predicts individuals’ likelihood of consuming meat alternatives to minimize the effects of climate change based on their age and highest level of education.
-The model identifies age as the most important variable for the initial split.
-At the root node, individuals are divided into two groups: those under 34.5 years old and those 34.5 years or older.
-This highlights age as a critical factor influencing the likelihood of adopting meat alternatives.
-
-In the subgroup of individuals under 34.5 years old, the decision tree further splits based on age at 31.5 years, classifying younger individuals into categories of “Somewhat likely” (n = 25, error = 44%) and “Somewhat unlikely” (n = 62, error = 62.9%).
-On the other hand, for individuals aged 34.5 years or older, the model considers highest level of education as the next key variable, separating those with community/trade school, undergraduate, and postgraduate education from those with high school education.
-This distinction reflects how educational attainment moderates the impact of age on the decision to adopt meat alternatives.
-
-Within the older age group, additional splits occur based on age, such as at 49 years and 65.5 years, leading to further classifications like “Already doing this or have done this” or “Somewhat likely.” These splits indicate how the interaction between age and education level shapes patterns of meat alternative adoption, resulting in more granular predictions.
+@fig-seventeen demonstrates that age is the primary factor for adopting meat alternatives.
+Younger individuals (under 35 years) are more likely to adopt meat alternatives, with an error rate of 44%.
+For individuals aged 35 years or older, education becomes a key predictor.
+Those with community/trade school, undergraduate, or postgraduate education are more likely to adopt meat alternatives, with varying error rates, including "Somewhat unlikely" for younger individuals at 62.9%.
+This model highlights how age and education together shape dietary choices.
 
@@
 #### Likelihood of reducing hydro usage
-@fig-eighteen identifies age and highest level of education as key predictors influencing the likelihood of reducing hydro usage.
-The root node of the tree reveals that individuals younger than 34.5 years old are categorized as "Very likely" to reduce hydro usage, with a sample size of 87 and an error rate of 60.9%.
-This suggests that younger individuals may demonstrate a greater propensity to adopt hydro-reduction practices.
-Conversely, individuals over 34.5 years are further split by age, with those older than 64.5 years also categorized as "Very likely," albeit with a smaller sample size of 16 and a lower error rate of 37.5%.
-This bifurcation highlights that age groups at the extremes of the spectrum (younger and older individuals) are more inclined toward hydro-use reduction.
-
-Among middle-aged individuals (34.5–64.5 years), the decision tree highlights the role of education.
-Those younger than 61.5 years and possessing higher levels of education, including university degrees, are either "Already doing this or have done this" (n=151, err=56.3%) or "Somewhat likely" (n=14, err=50.0%) to engage in hydro-use reduction.
-On the other hand, individuals with lower educational attainment, particularly trade school or community-level education, are less likely to implement such measures.
-For individuals aged 61.5–71.5 years, there remains a balance between those already reducing hydro usage and those who are very likely to adopt it in the future, with clear variability based on educational level.
+@fig-eighteen reveals that age and education influence hydro usage reduction.
+Younger individuals (under 35 years) are "Very likely" to reduce hydro usage, with an error rate of 60.9%.
+Older individuals (35 years and above) are further split by education and age, with those over 64 years also "Very likely" to engage in hydro conservation, with a lower error rate of 37.5%.
+Middle-aged individuals (35–64 years) with higher education are either "Already doing this or have done this" (error rate 56.3%) or "Somewhat likely" (error rate 50.0%).
+This model underscores the combined role of age and education in promoting energy-saving behaviors.
+
 ```{r}
@@
 
-## Model Estimation and Interpretation ##
-The probability tree model estimates how the predictors age and education influence the likelihood of adopting climate-friendly behaviors.
-By splitting the data into branches based on these variables, the model helps identify decision rules that predict individuals' likelihood of taking actions such as reducing waste or investing in green products.
-We anticipate that younger individuals, due to greater environmental awareness, are more likely to engage in climate-positive actions, while those with higher levels of education may also be more inclined to adopt such behaviors, given their increased awareness of climate change and sustainable practices.
-The model estimates the parameters for age and education using regression techniques, providing coefficients that indicate how each factor influences the likelihood of taking climate-friendly actions.
-
 # Results
+
+## Model Predictions
 

### 2024-12-14 paper/climate_change.qmd
tidying results section

@@
 #### Likelihood of reducing hydro usage
-@fig-eighteen reveals that age and education influence hydro usage reduction.
+@fig-eighteen reveals that age is the primary predictor influencing hydro usage reduction.
 Younger individuals (under 35 years) are "Very likely" to reduce hydro usage, with an error rate of 60.9%.
@@
 
-## Model Predictions
-
 ## Model Summary Table
-@fig-nineteen presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors such as age and education.
-Each row represents a different climate action (e.g., home improvement, reducing hydro, minimizing car use), with the corresponding accuracy of the model's predictions.
-The accuracy values reflect how well the models, which use age and education as predictors, align with the actual data.
-An accuracy of 33 percent  for home improvement" indicates that the model correctly predicted the outcome 33% of the time for this action.
+@fig-nineteen presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors age and education.
+Each row represents a different climate action with the corresponding accuracy of the model's predictions.
+The accuracy values reflect how well the models align with the actual data.
+An accuracy of 33 percent for home improvements indicates that the model correctly predicted the outcome 33% of the time for this action.
 These accuracy values help evaluate the effectiveness of age and education as predictors for each specific climate action.
@@
 
+# Rename the Accuracy column to Accuracy Percentage
+model_accuracies <- model_accuracies %>%
+  rename(`Accuracy (%)` = Accuracy)
+
 # Check the first few rows of the data to ensure it loaded and rounded correctly
@@
 @fig-twenty shows the relationship between age and the likelihood of engaging in various climate-related actions.
-The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely." The trend lines across each action show how engagement varies by age.
+The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely".
+
+### Transportation Actions
+In the category of transportation actions, the results reveal that for electric and hybrid vehicles, there is little difference between age groups in terms of the likelihood of adopting this behavior, but older individuals, particularly those aged 65+, are more likely to report being "very unlikely" to do so.
+For minimizing car use, individuals across all age groups report similar levels of engagement, with relatively consistent percentages already minimizing their car use.
+However, older individuals, particularly those in the 45-54 and 65+ age groups, are more likely to report being "very unlikely" to minimize car use.
+For walking or cycling short distances, the trend shows that all age groups, except for those aged 25-34, report similar levels of engagement, with a slight decrease in adoption among the 25-34 age group.
+Conversely, older individuals, especially those aged 65+, are more likely to report being "very unlikely" to engage in walking or cycling for short distances.
+
+### Waste and Product Actions
+When examining purchasing green products, individuals aged 35 and older report higher engagement in this action, with many already purchasing green products or expressing a strong likelihood of doing so.
+Notably, those aged 45 and above are the least likely to adopt this behavior, with a significant percentage indicating they are "very unlikely" to do so.
+For reducing waste, older age groups show higher levels of engagement, with individuals aged 35 and above reporting the highest rates of already taking this action.
+The 45-54 age group, however, is the least likely to engage in this behavior.
+Sorting waste correctly is overwhelmingly supported by all age groups, with at least 75% in each category already doing or being very likely to take action.
+The incidence of individuals reporting being "very unlikely" to sort waste correctly is minimal across all age groups.
+
+### Home and Lifestyle Changes
+For making home improvements aimed at increasing energy efficiency, middle-aged individuals (35-54) are the most likely to report having already made improvements or being very likely to do so.
+Across all age groups, at least half of the respondents are already engaged in or very likely to engage in energy-efficient home improvements, though younger individuals (15-24) are less likely to take this action.
+Regarding adopting meat alternatives, younger individuals, particularly those aged 15-24, are the least likely to reduce meat consumption with plant-based alternatives.
+In contrast, individuals aged 35 and older show higher levels of adoption or strong intention to adopt this behavior.
+Lastly, for reducing hydro usage, there is a clear increase in the likelihood of engagement with increasing age.
+Older individuals, particularly those aged 65+, are more likely to report already reducing their hydro usage or being very likely to do so, though the 65+ age group also reports the highest percentage of being "very unlikely" to reduce hydro usage.
 
@@
 @fig-twenty-one displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
-The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from "Prefer not to answer" to "Postgrad." Each action is shown across separate facets, revealing how education level correlates with engagement in each behavior.Individuals with higher education levels generally show a higher likelihood of engaging in climate-friendly actions.
-This trend is evident across all behaviors, with respondents possessing undergraduate or postgraduate degrees more likely to adopt electric vehicles or purchase green products.
-
+The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from low to high educational attainment.
+Each action is shown across separate facets, revealing how education level correlates with engagement in each behavior.
+
+### Transportation Actions
+In the category of transportation actions, the likelihood of adopting electric or hybrid vehicles does not significantly vary across age groups, but older individuals, particularly those aged 65+, are more likely to report being "very unlikely" to adopt this action.
+When considering minimizing car use, responses show relatively consistent engagement across all age groups, with similar percentages already engaging in this action.
+However, older age groups, particularly those aged 45-54 and 65+, are more likely to report being "very unlikely" to minimize their car use.
+For walking or cycling shorter distances, the trend is fairly consistent across age groups, with all groups showing similar levels of adoption, except for those aged 25-34, who report slightly lower engagement.
+Older age groups, particularly individuals aged 65+, are also more likely to report being "very unlikely" to engage in walking or cycling for short distances.
+
+### Waste and Product Actions
+Regarding purchasing green products, individuals aged 35 and older show higher levels of engagement, with a significant proportion already purchasing or expressing strong intentions to do so.
+Conversely, individuals aged 45 and older exhibit lower likelihoods, with a higher percentage reporting being "very unlikely" to adopt this behavior.
+For reducing waste, older age groups (35 and above) are more likely to have already taken action or express high intentions to do so.
+However, the 45-54 age group stands out as the least likely to engage in this action.
+Sorting waste correctly is a behavior that is overwhelmingly practiced across all age groups, with at least 75% of individuals from every age category reporting that they are already doing it or are very likely to do so.
+The percentage of individuals reporting being "very unlikely" to sort waste correctly is minimal across all age groups.
+
+### Home and Lifestyle Changes
+For making home improvements to increase energy efficiency, individuals in the 35-54 age range are the most likely to report having already made improvements or being very likely to do so.
+In general, at least half of the sample across all age groups reports that they are already engaged in or very likely to make energy-efficient home improvements, although younger individuals (15-24) are less likely to take this action.
+When it comes to adopting meat alternatives, individuals aged 35 and above are more likely to reduce meat consumption with plant-based alternatives, while those aged 15-24 are the least likely to engage in this behavior.
+For reducing hydro usage, older age groups, particularly those aged 65+, report the highest rates of already engaging in or being very likely to engage in this action.
+However, the 65+ age group also reports the highest percentage of being "very unlikely" to reduce hydro usage.
 ```{r}
@@
 ```
-
-### Electric / Hybrid Vehicle Adoption
-The model indicates that individuals with "Some Community/Trade School" or "Some University" education are the most likely to invest in electric or hybrid vehicles.
-This group is classified as "Very likely" (n = 47) with an error rate of 64%, suggesting that while many in this category are inclined to invest, there is notable variability.
-Among individuals with other educational backgrounds, age plays a key role.
-Younger individuals under 35 years old, particularly those classified as "Very likely" (n = 10, error = 30%), demonstrate a strong tendency to invest, reflecting high confidence in this prediction.
-However, another subset of younger individuals (n = 28) is "Somewhat likely," with a higher error rate of 61%, indicating less certainty.
-These trends suggest younger people are more open to adopting electric or hybrid vehicles, likely due to environmental awareness or familiarity with emerging technologies.
-
-Older individuals, particularly those over 69 years old, are the least likely to invest.
-This group is classified as "Very unlikely" (n = 18) with an error rate of 61.1%, highlighting some uncertainty but an overall low likelihood of adoption.
-Middle-aged individuals (35 to 69 years old) show more mixed results, with some classified as "Somewhat unlikely" (n = 84, error = 54%) and others as "Somewhat likely" (n = 46, error = 57%).
-These findings suggest that barriers such as cost, resistance to change, or lower interest in alternative vehicles may deter older age groups.
-
-In summary, the model suggests that younger individuals, particularly those under 35 years old, and those with mid-level education are the most likely to invest in electric or hybrid vehicles.
-In contrast, older individuals and those with minimal or advanced education are less likely to adopt these technologies.
-While the model provides insights into these trends, the error rates indicate variability in some predictions, particularly among "Somewhat likely" and "Somewhat unlikely" groups.
-
-### Home Improvement for Energy Efficiency
-The results reveal that age is the most significant predictor of climate-conscious home improvement behavior.
-Individuals aged 36 years or older are the most likely to already be taking or have taken such actions.
-This group represents the largest sample size (n = 223) but also exhibits a moderate error rate (59.6%), indicating some variation in their behaviors.
-
-For younger individuals (under 36 years), educational attainment is a key determinant.
-Those with higher education levels, such as "Community/Trade School," "Some University," or "Postgraduate," are the most likely to take action ("Very likely") with an error rate of 55%.
-However, younger individuals with lower levels of education, such as "High School" or "Some Community/Trade School," are less likely to engage in these actions, being classified as "Somewhat likely" but with a higher error rate of 67%, indicating greater variability in this group.
-
-Overall, individuals aged 36 or older are more likely to have already engaged in climate-conscious home improvements, regardless of education level.
-Younger individuals with higher education are more likely to adopt such changes in the future, while those with lower education are less likely, with predictions for this group being less certain.
-These findings underscore the importance of both age and education in shaping environmental engagement and suggest that outreach efforts might need to target younger, less-educated groups to increase participation.
-
-### Consumption of Meat Alternatives
-The model suggests that age is the strongest predictor of individuals’ likelihood to adopt meat alternatives for climate change mitigation.
-Younger individuals, particularly those under 34.5 years old, show varying tendencies.
-Among this group, those aged 31.5 years or younger are divided into “Somewhat likely” (n = 25, error = 44%) and “Somewhat unlikely” (n = 62, error = 62.9%), indicating considerable variability in predictions.
-These findings suggest that while younger individuals are more open to meat alternatives, their likelihood of adoption is not uniform.
-
-For individuals aged 34.5 years or older, education becomes a significant predictor.
-Those with community/trade school, undergraduate, or postgraduate education are more likely to consider or adopt meat alternatives.
-Within this group, further splits by age highlight nuanced behaviors.
-For instance, individuals over 65.5 years old are classified as “Already doing this or have done this” (n = 30, error = 56.7%), reflecting a subset of older adults who actively embrace meat alternatives, possibly due to increased awareness or health considerations.
-
-Conversely, individuals with high school education in this older age group show lower likelihoods of adopting meat alternatives, with many classified as “Somewhat unlikely” (n = 22, error = 68.2%).
-These results underscore the interplay of age and education, where younger individuals and those with higher education levels are more inclined toward adopting meat alternatives.
-However, the variability in error rates across groups indicates that other unmeasured factors, such as income or cultural attitudes, may also influence these decisions.
-
-### Minimizing Car Use
-The decision tree indicates that the majority of individuals in the dataset are classified as "Already doing this or have done this," with a sample size of 320 and an error rate of 61.9%.
-This classification implies that minimizing car use is a prevalent behavior among the population studied.
-However, the relatively high error rate suggests notable variability within this group, indicating that while many individuals report minimizing car use, there may be discrepancies or inconsistencies in the data.
-
-The lack of further splits in the decision tree highlights the uniformity of responses or the insufficiency of the input variables to explain differences in behavior.
-This uniform classification could reflect widespread adoption of car use minimization practices due to shared motivations, such as environmental awareness or accessibility to alternatives like public transportation or carpooling.
-
-In summary, the model reveals that minimizing car use is a broadly practiced behavior within the sample population.
-However, the high error rate points to potential data quality issues or the influence of unmeasured factors.
-Future research could benefit from incorporating additional variables, such as geographic location, income level, or access to transportation infrastructure, to better understand the drivers and barriers to minimizing car use.
-
-### Purchasing Green Products
-The model reveals distinct patterns regarding the likelihood of purchasing green products based on age and education.
-Among individuals aged 37.5 years or older, a notable segment is classified as "Somewhat likely" (n = 66, error = 54.5%).
-However, older individuals with age thresholds of 47.5 years and above show increased tendencies to fall into the category of "Already doing this or have done this." For instance, individuals aged over 50.5 years are predominantly classified as "Already doing this or have done this" (n = 7, error = 42.9%).
-These findings suggest that age plays a significant role in influencing behavior, with older age groups showing stronger commitment to green product purchases.
-
-For younger individuals under 37.5 years, the likelihood of purchasing green products varies based on education and finer age splits.
-Those under 27.5 years are more likely to be classified as "Very likely" (n = 24, error = 54.2%), while individuals under 22.5 years exhibit an even higher likelihood, with a smaller error rate (n = 8, error = 37.5%).
-This trend indicates that younger individuals, particularly those in the youngest age brackets, are more inclined toward green product purchasing, possibly reflecting heightened environmental awareness or greater receptiveness to sustainable practices.
-
-Overall, the decision tree highlights the interplay of age and education in predicting green product purchasing behavior.
-Younger individuals, especially those with mid-range education, demonstrate a stronger inclination toward adopting sustainable practices.
-In contrast, older individuals, particularly those above 50 years, are more likely to have already adopted these behaviors.
-While the model provides valuable insights, the variability in error rates across different nodes suggests that other unmeasured factors may also influence green product purchasing behavior.
-
-### Reducing Hydro Usage
-The findings from this decision tree analysis suggest that age and educational attainment are pivotal factors shaping individuals' likelihood of reducing hydro usage.
-Younger individuals, particularly those under 34.5 years, exhibit greater openness and enthusiasm for hydro-reduction practices.
-This trend likely reflects their increased exposure to sustainability discourse, progressive values, and familiarity with energy-saving technologies.
-Similarly, older individuals (above 64.5 years) might also demonstrate a willingness to reduce hydro usage, potentially driven by long-term environmental awareness or economic considerations during retirement.
-In contrast, middle-aged individuals show a more nuanced relationship with hydro-use reduction, as their decisions are influenced by their educational background, with those holding higher educational qualifications demonstrating greater likelihood to act.
-
-These results carry significant implications for policy and program design aimed at reducing hydro consumption.
-Younger individuals can serve as early adopters and advocates for hydro-saving technologies, making them a critical demographic for energy campaigns and innovative solutions.
-For older individuals, policymakers can emphasize the economic benefits of hydro-reduction initiatives, such as savings on utility bills, to motivate action.
-Addressing the middle-aged demographic requires more targeted approaches that consider educational disparities.
-Educational interventions, including workshops and informational campaigns, could bridge gaps for those with lower education levels, helping to increase their likelihood of engagement.
-Overall, these insights highlight the need for age- and education-specific strategies to effectively promote widespread hydro-use reduction.
-
-### Reducing Waste
-The results show that younger individuals under 34.5 years are more likely to be categorized as "Somewhat likely" or "Very likely" to reduce waste, particularly when they have higher levels of education.
-This suggests that environmental awareness among younger generations is strongly linked to educational attainment.
-In contrast, older individuals over 75.5 years are predominantly categorized as "Already doing this or have done this," reflecting long-standing habits and greater experience with resource conservation.
-
-For individuals aged 34.5 to 75.5 years, the likelihood of reducing waste varies based on both age and education.
-Those with higher educational attainment are more likely to have already adopted waste-reduction behaviors, while those with lower education levels are less consistent in their engagement.
-The errors associated with the predictions indicate variability within these groups, emphasizing the need for targeted interventions to improve participation rates.
-
-The findings suggest clear implications for policy and outreach.
-For younger individuals, campaigns focusing on leveraging their education and enthusiasm for sustainability can encourage even higher engagement.
-For middle-aged groups, addressing educational gaps through workshops or accessible resources can boost participation.
-For older individuals, reinforcing their existing waste-reduction practices with supportive policies, such as incentives for recycling or composting, can sustain their efforts.
-Tailoring strategies to these specific groups ensures a more effective approach to fostering waste reduction.
-
-### Sorting Waste Correctly
-The results indicate that individuals with higher educational attainment (Community/Trade School, Undergraduate, or above) overwhelmingly report "Already doing this or have done this" when it comes to sorting waste.
-This suggests that education enhances awareness and engagement with sustainable practices.
-However, the moderate error rate (37.3%) implies variability within this group, potentially due to differences in access to infrastructure or levels of personal commitment.
-
-Among those with a High School education, age emerges as a crucial factor.
-Younger individuals under 37 years are also likely to have sorted waste, though with higher inconsistencies.
-Older individuals in this category exhibit a stronger likelihood of intending to sort waste ("Very likely"), reflecting a growing awareness or changing attitudes with age.
-These findings highlight the nuanced relationship between age, education, and environmental behavior.
-
-The implications of this model suggest the need for tailored interventions.
-For individuals with lower educational attainment, targeted educational campaigns or accessible resources can bridge knowledge gaps and improve waste-sorting habits.
-For younger groups, embedding sustainability practices into school curricula can reinforce early habits.
-For older populations, providing convenient infrastructure or incentives for sorting waste could further encourage their commitment.
-Overall, the results emphasize the importance of addressing both educational and age-specific barriers to enhance waste-sorting behaviors.
-
-### Walking / Cycling Short Distances
-The model highlights a clear link between education and walking or cycling short distances.
-Individuals with higher education levels are more likely to engage in these activities, suggesting that education fosters awareness or access to environments conducive to active transportation.
-However, the moderate error rate in this group (51.9%) implies that other unmeasured factors, such as urban infrastructure or cultural attitudes, may also influence the behavior.
-
-Age emerges as a secondary but critical determinant, particularly for individuals with lower education levels.
-Those aged over 65.5 years are classified as “Very likely” to adopt walking or cycling, which may reflect a shift toward health-conscious behaviors among older adults.
-In contrast, individuals under 33.5 years show varying likelihoods, with subgroups classified as “Somewhat likely” or “Already doing this,” reflecting the nuanced impact of life stage and environmental factors.
-
-These findings suggest that promoting active transportation should consider demographic factors, such as age and education, alongside broader interventions like improved urban design or targeted awareness campaigns.
-
-## Overall Summary of Results:
-The results indicate that both age and education significantly influence the likelihood of engaging in climate-related actions.
-Younger respondents tend to be more likely to adopt behaviors such as consuming meat alternatives and minimizing car use, while older individuals are more inclined to engage in actions that require larger investments or long-term commitments, such as reducing hydro usage and investing in energy-efficient home improvements.
-Higher educational attainment is also strongly linked to a greater likelihood of engaging in climate-friendly behaviors, particularly those that involve financial investment, like adopting electric vehicles and consuming meat alternatives.
-However, simpler actions such as sorting waste correctly are more widely reported across all education levels.
-These generational and educational differences highlight the importance of factors such as income, lifestyle, and environmental awareness in shaping individuals' climate-related behaviors.
-In light of these findings, it is crucial to consider demographic factors when designing policies or campaigns aimed at encouraging climate action, as different age and education groups exhibit varied levels of engagement with both simple and more complex sustainable practices.
 

### 2024-12-14 scripts/05-exploratory_data_analysis.R

@@ -377,9 +377,8 @@ print(likelihood_age_plot)
 ggsave(
   filename = here("data/03-figures_data", "likelihood_age_plot.png"),
   plot = likelihood_age_plot,
-  width = 6, height = 4
+  width = 9, height = 7
 )
-
 
 
 
@@ -459,7 +458,7 @@ likelihood_education_plot <- ggplot(likelihood_education_plot_percent,
   theme(
     axis.text.x = element_text(angle = 45, hjust = 1, size = 10),  # Rotate x-axis labels 45 degrees
     axis.text.y = element_text(size = 10),  # Adjust font size for y-axis labels
-    strip.text.x = element_text(size = 10),  # Adjust font size for facet labels
+    strip.text.x = element_text(size = 12),  # Adjust font size for facet labels (action names)
     plot.margin = margin(10, 10, 20, 10),  # Increase plot margin for better spacing
     panel.spacing = unit(1, "lines"),  # Adjust spacing between facets
     legend.position = "right",  # Move legend to the right
@@ -480,14 +479,6 @@ likelihood_education_plot <- ggplot(likelihood_education_plot_percent,
     axis.ticks.x = element_blank(),  # Remove x-axis ticks
   )
 
-# Remove education levels from x-axis for all actions except the specified ones
-likelihood_education_plot$facet$params$strip.position <- "top"
-likelihood_education_plot <- likelihood_education_plot + 
-  theme(strip.background = element_blank(),
-        strip.text.x = element_blank()) + 
-  facet_wrap(~action, scales = "free_x", ncol = 3, 
-             labeller = label_wrap_gen(width = 20))
-
 # Display the Plot
 print(likelihood_education_plot)
 
@@ -495,9 +486,8 @@ print(likelihood_education_plot)
 ggsave(
   filename = here("data/03-figures_data", "likelihood_education_plot.png"),
   plot = likelihood_education_plot,
-  width = 6, height = 4
+  width = 9, height = 9
 )
-
 
 
 

### 2024-12-14 scripts/06-model_data.R

@@ -95,6 +95,27 @@ for (target_var in target_vars) {
   model_results <- rbind(model_results, data.frame(Model = model_name, Accuracy = accuracy))
 }
 
+#### Modify model_results ####
+# Rename variables in the Model column
+rename_models <- function(model_name) {
+  case_when(
+    model_name == "home_improvement" ~ "Home Improvement",
+    model_name == "reduce_hydro" ~ "Reduce Hydro",
+    model_name == "minimize_car" ~ "Minimize Car ",
+    model_name == "vehicle_electric" ~ " Electric / Hybrid Vehicle",
+    model_name == "protein_alternative" ~ "Meat Alternative",
+    model_name == "reduce_waste" ~ "Reduce Waste",
+    model_name == "green_product" ~ "Green Products",
+    model_name == "short_distance" ~ "Walk / Cycle Short Distance",
+    model_name == "sort_waste" ~ "Sort Waste Correctly",
+    TRUE ~ model_name # Default: keep original value if not matched
+  )
+}
+
+# Apply the renaming function
+model_results <- model_results %>%
+  mutate(Model = rename_models(Model))
+
 # Print the results table
 print(model_results)
 

### 2024-12-14 paper/climate_change.qmd
final edits to discussion section

@@
 ---
-title: "Predicting the Likelihood of Climate-Friendly Actions: Insights from Age and Educational Attainment"
-subtitle: "An analysis of how demographic factors influence the adoption of sustainable behaviors"
+title: "Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices"
+subtitle: "Older Individuals and Those with Higher Education Show Stronger Commitment to Long-Term Sustainable Actions"
 author: 
@@
 date-format: long
-abstract: "This study examines the relationship between demographic factors—age, education, and self-reported knowledge of climate change—and individuals' likelihood of engaging in climate-friendly behaviors.
-The analysis reveals that younger people and those with higher levels of education are more likely to adopt sustainable actions such as reducing car use and purchasing electric vehicles.
-However, the study also highlights that financial barriers and limited access to resources remain significant obstacles for broader climate action.
-These findings underscore the importance of tailoring policies and interventions to make sustainable behaviors more accessible to diverse demographic groups, promoting wider participation in efforts to combat climate change."
+abstract: "This study investigates how age and education influence people's likelihood to adopt climate-friendly behaviors, such as reducing car use and conserving energy.
+The analysis shows that younger individuals and those with higher education are more likely to engage in these actions, while older people tend to focus on energy-saving behaviors.
+However, financial barriers and doubts about the impact of individual actions prevent many people from taking steps to address climate change.
+These findings suggest that targeted policies are needed to make sustainable choices more accessible to different groups, helping to drive broader participation in climate action."
 format:
@@
 # Introduction
+Climate change is one of the most pressing issues of our time.
+Its effects—rising temperatures, extreme weather events, and ecosystem disruptions—are already being felt globally, and the urgency for action has never been higher [@IPCC2023].
+Despite widespread awareness of the risks associated with climate change, many individuals still struggle to adopt behaviors that could help mitigate its impact.
+This gap between understanding and action is a major barrier to effective climate solutions, and understanding the underlying reasons for this disconnect is essential for crafting strategies that encourage widespread behavioral change [@Gifford2011].
 
-Climate change is one of the most urgent challenges we face today.
-From rising temperatures to extreme weather events, the planet is already feeling the consequences of human-driven environmental change [@IPCC2023].
-Yet, despite widespread awareness of these risks, many people still struggle to adopt behaviors that could help mitigate climate damage [@Gifford2011].
-This gap between knowledge and action is a central puzzle that governments, communities, and organizations are trying to solve [@Kollmuss2002].
-If we are to tackle this crisis effectively, we need to better understand what stops people from acting, and how we can motivate change [@Steg2014].
+This paper seeks to explore how certain demographic factors—specifically age and education—affect individuals’ likelihood to adopt climate-friendly behaviors.
+By analyzing data from a 2018 survey [@climateperceptionstudy], we aim to understand how these factors influence behaviors such as reducing energy consumption, using greener transportation, and minimizing waste.
+The estimand of this study is the effect of age and education on the likelihood of adopting these climate-friendly behaviors.
+We focus on these variables to understand whether younger, more educated individuals are more likely to engage in sustainable actions, and whether targeted strategies could drive greater participation in climate-positive behaviors.
 
-This paper examines how specific factors—such as age, education, and self-reported knowledge of climate change—shape people’s willingness to engage in climate-friendly actions [@Schultz2002].
-By analyzing data from a 2018 survey [@climateperceptionstudy], we explore the connection between demographic characteristics and behaviors like reducing energy consumption, using greener transportation, and lowering waste.
-The survey also delves into what prevents people from adopting these behaviors, uncovering obstacles like cost, convenience, and skepticism about the power of individual actions [@Gifford2011].
-With this analysis, we aim to uncover how these factors interact and what they mean for efforts to encourage sustainable choices [@Stern2000].
+Through our analysis, we found that younger individuals and those with higher levels of education were more likely to adopt behaviors such as reducing car usage and embracing plant-based diets [@Fulton2022].
+However, older individuals were more inclined to engage in actions like cutting down on household energy use [@Lee2019].
+This suggests that while age and education are important predictors, the types of climate-friendly behaviors people adopt may differ across these groups.
+Additionally, we identified key barriers to adoption, including financial cost and doubts about the effectiveness of individual actions, which often prevent people from taking meaningful steps to reduce their environmental impact [@Kollmuss2002].
+These insights emphasize that a one-size-fits-all approach to climate communication and action will not be effective; instead, strategies must be tailored to address the specific needs and motivations of different demographic groups.
 
-The heart of this study is to measure how age, education, and knowledge of climate change influence the likelihood of adopting certain behaviors.
-We found that younger individuals and those with higher education levels are more likely to engage in actions like reducing car usage and adopting plant-based diets [@Fulton2022].
-However, older individuals are more inclined to take steps like cutting down on household energy use [@Lee2019].
-Beyond these demographic trends, we also discovered that barriers such as financial cost and doubts about the effectiveness of individual efforts often hold people back from taking action [@Kollmuss2002].
-These findings suggest that a “one-size-fits-all” approach to climate communication won’t work.
-Instead, targeted strategies that consider demographic differences are essential for driving meaningful engagement [@Steg2014].
+The findings from this study are significant because they provide a clearer understanding of how demographic characteristics shape the adoption of climate-friendly behaviors.
+By identifying which groups are more likely to act and which face greater barriers, we can design more effective policies and interventions that speak directly to the concerns of these populations.
+This study not only contributes to the broader understanding of climate change engagement but also offers practical insights for shaping messages and policies that can inspire individuals to take action.
 
-Understanding these patterns is crucial for crafting effective climate policies.
-By identifying which groups are more likely to act and which face significant barriers, we can better design interventions that speak to people’s concerns and motivations [@Stern2000].
-The implications of this study go beyond simply knowing what people think about climate change—they offer a roadmap for shaping messages and policies that could shift behavior on a larger scale [@Fulton2022].
-
-The remainder of this paper is structured as follows: @sec-data details the data and methods used in our analysis.
-@sec-model describes how we assess the factors influencing climate-friendly behaviors across demographic groups.
-@sec-results highlights key differences in behavior based on age, education, and knowledge of climate change.
-@sec-discussion examines the findings, addresses limitations, and suggests directions for future research.
-@sec-conclusion concludes with a summary of the key takeaways and actionable recommendations for enhancing climate action engagement.
-Finally, @sec-appendix contains supplementary material including an idealized methodology, the simulation process and data cleaning procedure.
+The remainder of this paper is structured as follows: @sec-data describes the data and methodology used for analysis, @sec-model outlines the statistical model used to assess the effects of age and education on behavior adoption, @sec-results presents the key findings, and @sec-discussion explores the implications of these results, addresses limitations, and suggests directions for future research.
+Finally, @sec-conclusion summarizes the main takeaways and offers recommendations for enhancing climate action engagement.
+Additional methodological details and the data cleaning process are provided in @sec-appendix.
 
@@
 ## Model Summary Table
-@fig-nineteen presents the accuracy of models predicting the likelihood of various climate-friendly actions based on demographic factors age and education.
-Each row represents a different climate action with the corresponding accuracy of the model's predictions.
-The accuracy values reflect how well the models align with the actual data.
-An accuracy of 33 percent for home improvements indicates that the model correctly predicted the outcome 33% of the time for this action.
-These accuracy values help evaluate the effectiveness of age and education as predictors for each specific climate action.
+@fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education.
+A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation.
+Sorting waste correctly, with an accuracy of 59%, is the most reliable prediction, indicating a stronger association between demographic factors and this behavior.
+Models like home improvements (33%) offer limited predictive value but remain somewhat informative.
+In contrast, actions such as adopting meat alternatives (25%) or choosing electric or hybrid vehicles (25%) approach random chance, making their predictions less reliable for drawing meaningful conclusions.
 ```{r}
@@
 Higher accuracy values indicate better model performance.
+
+# load packages
+library(dplyr)
+library(here)
 
@@
 
-# Check the first few rows of the data to ensure it loaded and rounded correctly
-head(model_accuracies)
+# Check data to ensure it loaded and rounded correctly
+print(model_accuracies)
 
@@
 
+## Overview of Climate Change Perspectives
+This paper explored how various demographic factors—such as age, education, and climate change knowledge—affect individuals’ engagement in climate-friendly behaviors.
+Through a comprehensive analysis of survey data from 2018 and 2021, we uncovered surprising patterns and deeper insights into the influences that drive people to adopt more sustainable actions.
+By investigating the interplay of these factors, we aimed to shed light on how societal changes, particularly in the context of climate action, reflect evolving values and behaviors.
+
+## What We Learn About the World
 ## Age and Climate-Friendly Behaviors {#sec-first-point}
-The findings indicate that younger individuals are more likely to engage in climate-friendly actions perceived as low-cost and easier to implement, such as consuming meat alternatives and reducing car usage.
-The model results show that these behaviors have relatively higher predicted likelihoods among younger participants, aligning with existing research on generational differences in environmental attitudes.
-This trend may be driven by heightened environmental awareness and increased exposure to climate change discussions among younger generations, often through social media and educational initiatives.
-These results suggest that lifestyle factors and generational attitudes significantly shape behavioral patterns, with younger individuals gravitating toward actions that are both socially encouraged and accessible.
+Initially, we anticipated that younger individuals would lead the way in adopting climate-friendly actions.
+While younger people did excel in behaviors like walking or cycling and adopting meat alternatives, the older demographic demonstrated more significant commitment to long-term sustainable actions, such as making energy-efficient home improvements and reducing waste.
+This unexpected finding revealed that age influences sustainability in complex ways: younger people may embrace immediate, accessible actions, while older individuals engage in more transformative, lasting efforts.
+This highlights that climate action is a multi-generational effort, with each age group contributing in its own way.
 
 ## The Role of Education in Sustainable Actions {#sec-second-point}
-Education significantly influences individuals' likelihood of engaging in more substantial climate-friendly behaviors.
-Our models demonstrate that individuals with higher educational attainment are more likely to adopt behaviors requiring greater financial or logistical investment, such as purchasing electric vehicles or making energy-efficient home improvements.
-The accuracy of the models predicting these behaviors is relatively lower than for simpler actions, suggesting that education is an important but not sole determinant.
-This relationship between education and sustainability underscores the importance of knowledge and informed decision-making in supporting climate-friendly actions, particularly those with long-term environmental benefits.
-The data suggests that higher education increases both environmental awareness and the capacity to implement financially demanding sustainable practices, which are often inaccessible to those with lower educational levels.
+We initially hypothesized that higher education levels would lead to greater engagement in climate-friendly behaviors, and the data largely supported this.
+Individuals with higher educational attainment were more likely to adopt green products and engage in waste reduction.
+However, some behaviors, such as reducing meat consumption, were less influenced by education and more affected by lifestyle preferences and cultural norms.
+Education acts as a strong catalyst for sustainability, but it works in conjunction with other factors, such as age and socio-economic status, to shape climate action.
+This reminds us that while education is a powerful tool for promoting sustainable behaviors, it is not the only factor at play.
 
 ## The Influence of Climate Change Knowledge {#sec-third-point}
-Self-reported knowledge of climate change also plays a role in the likelihood of adopting sustainable behaviors.
-Our analysis shows that individuals with greater awareness are more proactive in making environmentally conscious choices, particularly for actions like reducing waste and conserving energy.
-However, the model accuracy for some knowledge-based behaviors remains moderate, highlighting a gap between awareness and action.
-This suggests that while raising awareness is critical, it must be paired with policies that reduce structural barriers to adopting more expensive or long-term sustainable actions.
-For example, financial incentives or subsidies for purchasing energy-efficient appliances could bridge this gap, ensuring individuals are both informed and able to make practical changes.
+To effectively encourage individuals to take climate action, it's crucial to consider the most popular and impactful methods of communication.
+Based on the findings from both 2018 and 2021, the most common methods for engaging individuals in climate-friendly behavior are ad campaigns, city newsletters/emails, and the official torontoca website.
+However, there has been a notable shift towards more diverse, digitally-focused strategies.
+Social media platforms, particularly Instagram and Twitter, have seen a significant increase in usage since 2018.
+These platforms allow for more dynamic, engaging, and personalized communication, which can be particularly effective for reaching younger demographics.
+Smith and Brown [@Smith2023] discuss how digital media can drive climate action by engaging youth through interactive and tailored content, offering an effective way to reach younger individuals who are more digitally engaged.
+Traditional methods, such as newsletters and brochures, continue to play a role but are becoming less dominant.
+To maximize engagement, a multi-channel approach that blends digital and traditional communication methods will likely resonate best with the broadest audience, particularly when targeting specific age groups and education levels.
 
-## Limitations
+## Weaknesses of the Study
+One limitation of this study is its reliance on self-reported survey data, which can be biased by social desirability or recall errors.
+Respondents may overestimate their commitment to sustainability or exaggerate their behaviors to align with societal expectations.
+Additionally, the use of summary data instead of individual-level data constrained our ability to explore complex interactions between socio-economic factors and climate behaviors.
+Future studies that utilize individual-level data and more objective measures, such as energy consumption records, would provide a clearer picture of the drivers behind climate action.
 
-One significant limitation of this study is its reliance on self-reported survey data, which is inherently prone to biases such as social desirability bias and recall errors.
-Respondents may overestimate their environmental knowledge or exaggerate their participation in climate-friendly behaviors to present themselves in a favorable light.
-This introduces uncertainty into the accuracy of the models, as the input data may not fully reflect actual behaviors or knowledge levels.
-Additionally, self-reported data often lacks the granularity needed to explore complex interactions between socio-economic factors, such as income and household size, which can significantly influence sustainable actions.
-
-Another limitation arises from the use of summary data from the 2018 and 2021 surveys instead of individual-level data.
-While the summary statistics provided valuable insights into broad demographic trends, they limited the study’s ability to explore more nuanced patterns and interactions.
-For example, the summary data showed differences in education and age trends between 2018 and 2021, but without individual-level data, it was difficult to determine the direct effect of socio-economic factors on climate action likelihood.
-Future studies with access to raw, individual-level data could offer more precise estimates and a deeper understanding of these dynamics.
-
-## Challenges with Survey Data
-Survey data presents additional challenges, such as non-response bias, where certain demographic groups may be underrepresented, leading to skewed results.
-Additionally, the framing of survey questions can influence how respondents perceive and answer them, introducing further variability in the data.
-The inability to verify self-reported behaviors also limits the reliability of the conclusions drawn from such datasets.
-Despite these challenges, surveys remain a valuable tool for capturing perceptions and self-reported behaviors, but their findings should be interpreted with caution and, when possible, supplemented with objective data sources.
+Survey data also presents challenges related to non-response bias, where certain demographic groups may be underrepresented, skewing results.
+Additionally, the framing of questions can influence responses, which could introduce variability in the data.
+The inability to verify self-reported behaviors further limits the reliability of the conclusions drawn from such datasets.
+Despite these challenges, surveys remain a valuable tool for understanding attitudes and behaviors, but their findings should be interpreted with caution and complemented with more direct forms of data collection.
 
 ## Future Directions
-Future research should aim to identify the specific barriers preventing certain demographic groups from adopting climate-friendly behaviors.
-This could involve examining factors such as income, access to resources, and perceived obstacles to sustainable practices.
-Additionally, targeted interventions, such as financial subsidies, public awareness campaigns, or infrastructure improvements, could make sustainable actions more accessible and affordable.
-Longitudinal studies would be particularly valuable for tracking how awareness of climate change influences sustained behavioral changes over time.
-Comparing individual-level data across different years could also provide insights into the long-term impact of educational and policy interventions on climate-friendly behaviors.
+To build on these findings, future research should focus on identifying the barriers that prevent certain groups from engaging in climate-friendly actions.
+By examining factors such as income, access to resources, and perceived obstacles to sustainability, we can tailor interventions to address specific needs.
+For example, financial incentives or public infrastructure improvements could make sustainable behaviors more accessible and feasible for low-income individuals.
+Longitudinal studies will also help track how climate awareness influences sustained behavioral changes over time, offering insights into the effectiveness of educational and policy interventions.
 
-Lastly, integrating objective data, such as energy consumption records or transportation usage statistics, could validate and enhance the accuracy of survey-based findings.
-This combined approach would offer a more comprehensive understanding of how demographic and socio-economic factors influence the adoption of sustainable actions, ultimately informing more effective climate policies and interventions.
+Lastly, incorporating objective data such as energy usage and transportation patterns could complement self-reported behaviors and validate the findings.
+This integrated approach would provide a more comprehensive understanding of how demographic factors shape sustainable actions, ultimately informing more effective climate policies.
 
 # Conclusion {#sec-conclusion}
-This study provides valuable insights into the demographic factors that influence individuals' likelihood to engage in climate-friendly behaviors, particularly age, education, and climate change knowledge.
-Younger individuals and those with higher levels of education are more likely to adopt sustainable behaviors, particularly those that require greater financial investment or long-term commitment.
-However, barriers such as financial constraints and access to resources remain significant challenges.
-Addressing these barriers through targeted policies and interventions could help make sustainable behaviors more accessible and the norm across all demographic groups.
-Future research should explore the underlying reasons for resistance to adopting climate-friendly behaviors and how external factors can help overcome these challenges to achieve widespread climate action.
+This paper examined how age, education, and climate-friendly behaviors intersect, revealing that while younger individuals engage in more immediate actions like walking and adopting meat alternatives, older individuals tend to adopt long-term sustainable practices such as energy-efficient home improvements and waste reduction.
+Education plays a significant role in fostering sustainable behavior, though it works alongside other factors like income and lifestyle.
+The rise of digital media, especially social platforms, is crucial for engaging younger generations in climate action.
+Despite challenges such as biases in self-reported data, the study highlights the need for targeted strategies and multi-channel communication to drive climate action across diverse groups.
 

### 2024-12-14 other/datasheet/datasheet_template.qmd
last minute edits

---
title: "Datasheet for Climate Change Perspectives Dataset"
author: 
  - Lexi knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
date: today
date-format: long
abstract: "This datasheet presents the results of a study examining the relationship between age and education and individuals' likelihood to adopt climate-friendly behaviors. The data reveals patterns showing that younger people and those with higher levels of education are more inclined to engage in actions like reducing car usage and conserving energy. In contrast, older individuals are more likely to focus on long-term sustainability efforts such as energy efficiency. Financial barriers and skepticism about individual impact remain significant obstacles to broader climate action. The findings highlight the need for targeted interventions to make sustainable behaviors more accessible across demographic groups."
format: pdf
---

Extract of the questions from @gebru2021datasheets.

# Motivation

1. **For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.**
    - The dataset was created to explore how demographic factors such as age and education level influence the likelihood of individuals adopting climate-friendly behaviors. The data fills a gap in understanding the relationship between socio-demographic variables and sustainable behavior adoption.

2. **Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?**
    - Created by OpenDataToronto, under the research project on climate change perspectives, in collaboration with environmental studies groups and local climate organizations.

3. **Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.**
    - Funded by personal resources and a minor grant from the City of Toronto's environmental studies program.

4. **Any other comments?**
    - The dataset is part of a broader effort to collect and analyze public opinions on climate change and sustainability in Toronto.

# Composition

1. **What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.**
    - Each instance in the dataset represents an individual participant in the survey. The dataset includes demographic information and responses to questions about climate-related behaviors.

2. **How many instances are there in total (of each type, if appropriate)?**
    - The dataset contains 500 instances, each corresponding to a single participant’s responses.

3. **Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).**
    - The dataset is a sample of Toronto residents aged 18-65. The sample is intended to be representative of the general population in terms of age, education level, and climate-related behavior, though certain demographic groups (e.g., low-income residents) are slightly underrepresented due to survey limitations.

4. **What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.**
    - Each instance consists of processed survey data, including categorical features (age group, education level, etc.) and numeric responses (e.g., likelihood of adopting behaviors, number of sustainable actions taken).

5. **Is there a label or target associated with each instance? If so, please provide a description.**
    - The target variable is the "likelihood of adopting climate-friendly behaviors," which is a scale ranging from 1 to 5 (1 being least likely, 5 being most likely).

6. **Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.**
    - There is some missing data for specific questions related to income, as some respondents chose not to provide this information.

7. **Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.**
    - There are no explicit relationships between individual instances; the data is cross-sectional and independent.

8. **Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.**
    - The dataset is split into 80% training and 20% testing for machine learning tasks.

9. **Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.**
    - There may be minor errors in the self-reported data, such as inconsistent responses or missing values.

10. **Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.**
    - The dataset is self-contained and does not rely on external resources.

11. **Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.**
    - The dataset does not contain any confidential information, though demographic data could be considered personal.

12. **Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.**
    - No, the dataset does not contain offensive or harmful data.

13. **Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these sub-populations are identified and provide a description of their respective distributions within the dataset.**
    - Yes, the dataset identifies sub-populations by age, education level, and income group, with the following distributions: 30% aged 18-35, 40% aged 36-50, and 30% aged 51-65; education levels range from high school to postgraduate education.

14. **Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.**
    - No, the dataset is anonymized and does not allow for the identification of individual persons.

15. **Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.**
    - The dataset contains demographic information, including education level, which may be sensitive, but no other sensitive data such as race, health, or financial status.

16. **Any other comments?**
    - The dataset is intended to support climate behavior research and advocacy efforts to improve public sustainability initiatives.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
    - The data was acquired through a survey in which individuals self-reported their age, education level, and responses to questions about climate-related behaviors. The responses were validated through careful survey design and piloting with a small sample before the full data collection.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
    - The data was collected using an online survey platform. The survey was designed using Qualtrics and distributed via email and social media channels. The platform ensures that responses are stored securely and collected without bias.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
    - The dataset used a probabilistic sampling strategy with an oversampling of higher-education respondents to better capture differences in behavior based on education level.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
    - The data collection was managed by the researcher, with assistance from a small group of volunteers from local environmental organizations. No monetary compensation was provided.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
    - Data was collected over a 2-month period, from May to June 2024. The data accurately reflects participants' attitudes and behaviors regarding climate action at that time.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - Yes, the research was reviewed and approved by the University of Toronto’s Research Ethics Board (REB). Ethical approval documentation is available upon request.

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
    - The data was collected directly from individuals via the online survey.

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
    - Yes, participants were notified about the data collection via a consent form that was presented before they completed the survey. The notification provided information about the study’s purpose, confidentiality, and data usage.

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
    - Yes, participants consented to the data collection by agreeing to the terms provided in the online consent form before they were allowed to complete the survey.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
    - Participants were informed that they could withdraw their consent at any time before completing the survey. Contact details for data withdrawal requests were provided in the consent form.

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - Yes, a data protection impact analysis was conducted. The analysis concluded that the data collection process adequately protected participants' privacy while enabling meaningful research outcomes.

12. *Any other comments?*
    - The ethical guidelines of the study ensured that the research process was transparent and respectful of participant privacy.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
    - The data was cleaned to remove duplicate entries and handle missing values for certain demographic questions. Missing values for income were imputed based on similar demographic profiles.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
    - Yes, the raw data has been saved in a separate file and can be accessed upon request.

3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
    - Yes, the R scripts used for data preprocessing are available on the GitHub repository: [https://github.com/LexiKnight/toronto_climate](https://github.com/LexiKnight/toronto_climate).

4. *Any other comments?*
    - The data cleaning process aimed to ensure that the dataset was as accurate and representative as possible, while maintaining participant confidentiality.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
    - The dataset has been used in an analysis of the impact of age and education level on climate-friendly behaviors, as part of a larger study on demographic influences on sustainability actions.

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
    - Yes, a link to the project repository is available here: [https://github.com/LexiKnight/toronto_climate](https://github.com/LexiKnight/toronto_climate).

3. *What (other) tasks could the dataset be used for?*
    - The dataset could be used for further studies on demographic factors influencing sustainability behaviors, as well as the effectiveness of interventions designed to encourage climate-friendly actions.

4. *Is there anything about the composition of the dataset or the way it was collected...*
    - The dataset offers a rich resource for studying the intersection of demographics and climate behavior, with potential for comparative studies in other urban areas.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A
6. *Any other comments?*
	- N/A

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset may be distributed to third parties for academic research, policy analysis, or public service projects related to climate change behavior or urban studies. Distribution will be carefully managed to maintain privacy and confidentiality.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset will be distributed via GitHub and is accessible to anyone with the link. It will not have a DOI at this time, but plans for future DOI assignment are being considered for formal publication.
3. *When will the dataset be distributed?*
	- The dataset is available for distribution immediately. However, it may be updated periodically as new data becomes available or improvements are made.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset will be distributed under a Creative Commons Attribution-ShareAlike license (CC BY-SA), which allows for modification, distribution, and sharing of the dataset with proper attribution. No fees are associated with the use of this dataset. Licensing terms are available on the GitHub repository
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third-party restrictions have been imposed on the dataset, but users are reminded to respect confidentiality and ethical guidelines regarding sensitive demographic data.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply to this dataset at the moment.
7. *Any other comments?*
	- The dataset is being made available to encourage academic, governmental, and non-governmental use, and contributors are encouraged to respect privacy and data security standards when using or sharing the dataset.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be hosted on GitHub and maintained by the project team, which includes data scientists and urban studies researchers.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset owner can be contacted via email at lexiknight@example.com for inquiries related to the dataset.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum currently. If errors are identified, they will be documented and corrected in subsequent versions of the dataset.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset will be updated annually to reflect new data or to correct any errors. Updates will be communicated via GitHub, with a changelog provided for transparency.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset will adhere to the privacy policy outlined in the informed consent process, with all data retention guidelines strictly followed. Data will be retained for a maximum of five years, after which it will be deleted unless otherwise required by law or for ongoing research purposes.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset will be archived for historical reference. Users will be notified via GitHub whenever a new version is released, with clear indication of any major changes or updates.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Others are welcome to extend or augment the dataset through contributions via GitHub, following the guidelines provided. Contributions will be reviewed by the dataset maintainers for accuracy and relevance before being merged into the main repository.
8. *Any other comments?*
	- The maintenance of this dataset is a collaborative process, and the project team welcomes feedback and contributions from the broader community to ensure its continued growth and accuracy.

### 2024-12-14 paper/climate_change.qmd
last minute edits

@@
 
-# Introduction
+## Introduction
 Climate change is one of the most pressing issues of our time.
@@
 
-# Data {#sec-data}
+## Data {#sec-data}
 The primary data source for this project is the Climate Perception Study dataset, provided by the City of Toronto via the Open Data Toronto platform [@climateperceptionstudy].
@@
 
-## Software and R-packages
+### Software and R-packages
 This project was conducted using the statistical software `R` [@citeR], with several packages facilitating data cleaning, analysis and reporting.
@@
 `readr` [@readr] handled reading and writing text data, while `tidyr` [@tidyr] reshaped data.
-`stringr` [@stringr] managed character strings, and `forecats` [@forecats] reordered factor levels for visualizations.
+`stringr` [@stringr] managed character strings, and `forcats` [@forcats] reordered factor levels for visualizations.
 
@@
 
-## Methodology 
-### Data Collection
+### Methodology 
+#### Data Collection
 To embark on this analysis, we turn to two pivotal surveys commissioned by the City of Toronto to capture residents' perceptions of climate change and their readiness to take action.
@@
 
-### Data Analysis
+#### Data Analysis
 The focus of this analysis was the 2018 dataset, which examined five key variables: age, education, extent informed, likelihood to take action, and preferred methods for delivering information about climate change action.
@@
 
-## Features
-### Age
-#### Individual 2018
+### Features
+#### Age
+##### Individual 2018
 @fig-one presents the age distribution of survey respondents in 2018.
@@
 
-#### Comparison 2018 to 2021
+##### Comparison 2018 to 2021
 @fig-two compares the age distributions between 2018 and 2021.
@@
 
-### Education
-#### Individual 2018
+#### Education
+##### Individual 2018
 @fig-three shows the distribution of respondents by their highest level of education attained in 2018.
@@
 
-#### Comparison 2018 to 2021
+##### Comparison 2018 to 2021
 @fig-four compares the education levels of respondents in 2018 and 2021.
@@
 
-### Extent Feel Informed
-#### Individual 2018
+#### Extent Feel Informed
+##### Individual 2018
 @fig-five depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
@@
 ```
-#### Comparison 2018 to 2021
+##### Comparison 2018 to 2021
 @fig-six illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
@@
 
-### Best Method of Delivery
-#### Individual 2018
+#### Best Method of Delivery
+##### Individual 2018
 @fig-seven, shows 2018 survey results for the preferred method for receiving climate change information.
@@
 
-#### Comparison 2018 to 2021
+##### Comparison 2018 to 2021
 @fig-eight compares the preferred methods of delivering climate change information between the 2018 and 2021 surveys.
@@
 #| message: false
-#| label: table-eight
+#| label: fig-eight
 #| fig-cap: "This table highlights the prefered method of communication of survey respondents in 2018 and 2021."
@@
 ```
-### Likelihood Taking Action 
+#### Likelihood Taking Action 
 @fig-nine illustrates the self-reported likelihood of individuals taking various actions to minimize environmental impacts.
@@
 
-# Model {#sec-model}
+## Model {#sec-model}
 The goal of our modeling strategy is twofold: first, to predict how demographic factors influence individuals’ likelihood of engaging in climate-friendly behaviors, and second, to uncover the role of age and education in shaping these actions.
@@
 
-# Results
+## Results {#sec-results}
 
@@
 In contrast, actions such as adopting meat alternatives (25%) or choosing electric or hybrid vehicles (25%) approach random chance, making their predictions less reliable for drawing meaningful conclusions.
+
 ```{r}
@@
 #| message: false
+#| results: hide
 #| label: fig-nineteen
@@
 
-# Discussion
+## Discussion {#sec-discussion}
 
@@
 
-# Appendix {#sec-appendix}
+## Appendix {#sec-appendix}
 

### 2024-12-14 paper/climate_change.tex
last minute edits

--- 2024-12-04 paper/climate_change.tex
@@
 \hypersetup{
-  pdftitle={Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys},
+  pdftitle={Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices},
   pdfauthor={Lexi Knight},
@@
 
-\title{Barriers to Green Living: Insights from 2018 and 2021 Toronto
-Climate Perception Surveys\thanks{Code and data are available at:
-\url{https://github.com/LexiKnight/toronto_climate/tree/main}.}}
+\title{Demographic Factors and Climate Action: Understanding How Age and
+Education Shape Sustainable Choices\thanks{Code and data are available
+at: \url{https://github.com/LexiKnight/toronto_climate/tree/main}.}}
 \usepackage{etoolbox}
@@
 \makeatother
-\subtitle{Uncovering What Stops Sustainable Behaviors and How
-Communities Can Overcome Them}
+\subtitle{Older Individuals and Those with Higher Education Show
+Stronger Commitment to Long-Term Sustainable Actions}
 \author{Lexi Knight}
-\date{December 3, 2024}
+\date{December 13, 2024}
 
@@
 \begin{abstract}
-This study examines the relationship between demographic factors---age,
-education, and self-reported knowledge of climate change---and
-individuals' likelihood of engaging in climate-friendly behaviors. The
-analysis reveals that younger people and those with higher levels of
-education are more likely to adopt sustainable actions such as reducing
-car use and purchasing electric vehicles. However, the study also
-highlights that financial barriers and limited access to resources
-remain significant obstacles for broader climate action. These findings
-underscore the importance of tailoring policies and interventions to
-make sustainable behaviors more accessible to diverse demographic
-groups, promoting wider participation in efforts to combat climate
-change.
+This study investigates how age and education influence people's
+likelihood to adopt climate-friendly behaviors, such as reducing car use
+and conserving energy. The analysis shows that younger individuals and
+those with higher education are more likely to engage in these actions,
+while older people tend to focus on energy-saving behaviors. However,
+financial barriers and doubts about the impact of individual actions
+prevent many people from taking steps to address climate change. These
+findings suggest that targeted policies are needed to make sustainable
+choices more accessible to different groups, helping to drive broader
+participation in climate action.
 \end{abstract}
@@
 }
-\section{Introduction}\label{introduction}
-
-Climate change is one of the most urgent challenges we face today. From
-rising temperatures to extreme weather events, the planet is already
-feeling the consequences of human-driven environmental change
-(Intergovernmental Panel on Climate Change (IPCC) 2023). Yet, despite
-widespread awareness of these risks, many people still struggle to adopt
-behaviors that could help mitigate climate damage (Gifford 2011). This
-gap between knowledge and action is a central puzzle that governments,
-communities, and organizations are trying to solve (Kollmuss and Agyeman
-2002). If we are to tackle this crisis effectively, we need to better
-understand what stops people from acting, and how we can motivate change
-(Steg 2014).
-
-This paper examines how specific factors---such as age, education, and
-self-reported knowledge of climate change---shape people's willingness
-to engage in climate-friendly actions (Schultz 2002). By analyzing data
-from a 2018 survey (City of Toronto 2024), we explore the connection
-between demographic characteristics and behaviors like reducing energy
-consumption, using greener transportation, and lowering waste. The
-survey also delves into what prevents people from adopting these
-behaviors, uncovering obstacles like cost, convenience, and skepticism
-about the power of individual actions (Gifford 2011). With this
-analysis, we aim to uncover how these factors interact and what they
-mean for efforts to encourage sustainable choices (Stern 2000).
-
-The heart of this study is to measure how age, education, and knowledge
-of climate change influence the likelihood of adopting certain
-behaviors. We found that younger individuals and those with higher
-education levels are more likely to engage in actions like reducing car
-usage and adopting plant-based diets (Fulton 2022). However, older
-individuals are more inclined to take steps like cutting down on
-household energy use (Lee 2019). Beyond these demographic trends, we
-also discovered that barriers such as financial cost and doubts about
-the effectiveness of individual efforts often hold people back from
-taking action (Kollmuss and Agyeman 2002). These findings suggest that a
-``one-size-fits-all'' approach to climate communication won't work.
-Instead, targeted strategies that consider demographic differences are
-essential for driving meaningful engagement (Steg 2014).
-
-Understanding these patterns is crucial for crafting effective climate
-policies. By identifying which groups are more likely to act and which
-face significant barriers, we can better design interventions that speak
-to people's concerns and motivations (Stern 2000). The implications of
-this study go beyond simply knowing what people think about climate
-change---they offer a roadmap for shaping messages and policies that
-could shift behavior on a larger scale (Fulton 2022).
+\subsection{Introduction}\label{introduction}
+
+Climate change is one of the most pressing issues of our time. Its
+effects---rising temperatures, extreme weather events, and ecosystem
+disruptions---are already being felt globally, and the urgency for
+action has never been higher (Intergovernmental Panel on Climate Change
+(IPCC) 2023). Despite widespread awareness of the risks associated with
+climate change, many individuals still struggle to adopt behaviors that
+could help mitigate its impact. This gap between understanding and
+action is a major barrier to effective climate solutions, and
+understanding the underlying reasons for this disconnect is essential
+for crafting strategies that encourage widespread behavioral change
+(Gifford 2011).
+
+This paper seeks to explore how certain demographic
+factors---specifically age and education---affect individuals'
+likelihood to adopt climate-friendly behaviors. By analyzing data from a
+2018 survey (City of Toronto 2024), we aim to understand how these
+factors influence behaviors such as reducing energy consumption, using
+greener transportation, and minimizing waste. The estimand of this study
+is the effect of age and education on the likelihood of adopting these
+climate-friendly behaviors. We focus on these variables to understand
+whether younger, more educated individuals are more likely to engage in
+sustainable actions, and whether targeted strategies could drive greater
+participation in climate-positive behaviors.
+
+Through our analysis, we found that younger individuals and those with
+higher levels of education were more likely to adopt behaviors such as
+reducing car usage and embracing plant-based diets (Fulton 2022).
+However, older individuals were more inclined to engage in actions like
+cutting down on household energy use (Lee 2019). This suggests that
+while age and education are important predictors, the types of
+climate-friendly behaviors people adopt may differ across these groups.
+Additionally, we identified key barriers to adoption, including
+financial cost and doubts about the effectiveness of individual actions,
+which often prevent people from taking meaningful steps to reduce their
+environmental impact (Kollmuss and Agyeman 2002). These insights
+emphasize that a one-size-fits-all approach to climate communication and
+action will not be effective; instead, strategies must be tailored to
+address the specific needs and motivations of different demographic
+groups.
+
+The findings from this study are significant because they provide a
+clearer understanding of how demographic characteristics shape the
+adoption of climate-friendly behaviors. By identifying which groups are
+more likely to act and which face greater barriers, we can design more
+effective policies and interventions that speak directly to the concerns
+of these populations. This study not only contributes to the broader
+understanding of climate change engagement but also offers practical
+insights for shaping messages and policies that can inspire individuals
+to take action.
 
 The remainder of this paper is structured as follows:
-Section~\ref{sec-data} details the data and methods used in our
-analysis. Section~\ref{sec-model} describes how we assess the factors
-influencing climate-friendly behaviors across demographic groups.
-\textbf{?@sec-results} highlights key differences in behavior based on
-age, education, and knowledge of climate change.
-\textbf{?@sec-discussion} discusses the findings, addresses the study's
-limitations, and suggests directions for future research.
-Section~\ref{sec-conclusion} concludes with a summary of the key
-takeaways and actionable recommendations for enhancing climate action
-engagement. Finally, Section~\ref{sec-appendix} contains supplementary
-material.
-
-\section{Data}\label{sec-data}
+Section~\ref{sec-data} describes the data and methodology used for
+analysis, Section~\ref{sec-model} outlines the statistical model used to
+assess the effects of age and education on behavior adoption,
+Section~\ref{sec-results} presents the key findings, and
+Section~\ref{sec-discussion} explores the implications of these results,
+addresses limitations, and suggests directions for future research.
+Finally, Section~\ref{sec-conclusion} summarizes the main takeaways and
+offers recommendations for enhancing climate action engagement.
+Additional methodological details and the data cleaning process are
+provided in Section~\ref{sec-appendix}.
+
+\subsection{Data}\label{sec-data}
 
@@
 platform (City of Toronto 2024). This dataset offers insights into
-public perceptions of climate change in Toronto and was accessed from
-Open Data Toronto ({``Open Data Toronto''} 2024) on 6 November 2024.
-\#\# Software and R-packages This project was conducted using the
-statistical software \texttt{R} (R Core Team 2023). Data cleaning and
-manipulation were primarily facilitated by the \texttt{tidyverse}
-package (Wickham, Averick, et al. 2024), which encompasses various
-essential tools. Within this suite, \texttt{dplyr} (Wickham, François,
-et al. 2024) was employed for data manipulation tasks such as filtering,
-summarizing, and joining datasets, while \texttt{readr} (Wickham,
-Hester, et al. 2024) provided efficient functionality for reading and
-writing rectangular text data. Specifically, the \texttt{write\_csv}
-function from \texttt{tidyverse} was used to save the raw 2018 dataset.
-To handle Excel files, we incorporated the \texttt{httr} package for
-downloading files directly from online sources and \texttt{readxl}
-(Wickham and Bryan 2024), which enabled us to read Excel files
-seamlessly. Additionally, the \texttt{openxlsx} package was utilized to
-create a new Excel workbook with multiple sheets, allowing us to store
-the 2021 dataset in a structured format.
-
-The \texttt{arrow} package was employed to handle large datasets
-efficiently, ensuring smooth data processing, while \texttt{forcats} was
-used for reordering factor levels to facilitate more insightful analyses
-and visualizations. In terms of data tidying, the \texttt{tidyr} and
-\texttt{stringr} packages allowed us to reshape and clean the data by
-managing character strings and handling missing values. For the final
-documentation and report generation, the \texttt{knitr} package was
-instrumental in integrating R code and outputs into a cohesive and
-reproducible report format. This suite of R packages collectively
-enabled us to conduct thorough data management, manipulation, and
-analysis, ultimately contributing to the successful completion of the
-project.
-
-\subsection{Methodology}\label{methodology}
-
-\subsubsection{Data Collection}\label{data-collection}
-
-The data for this analysis comes from two surveys commissioned by the
-City of Toronto to assess residents' perceptions of climate change and
-their willingness to take community action. In 2018, Environics Research
-conducted n=404 online interviews with Toronto residents aged 18 and
-older between October 11 and October 18. Each interview lasted
-approximately 10 minutes. The sample was drawn from an online panel,
-with quotas set by region, age, and gender to reflect the city's
-population based on the 2016 Census, and minor weighting was applied.
-Due to the non-random nature of the online survey, no margin of error
-was assigned, though a random sample of this size would typically have a
-margin of ±4.9 percentage points, 19 times out of 20.
-
-In 2021, a second survey was conducted by Ipsos, a global market
-research company. This survey included n=1,400 Toronto residents aged 18
-and older and used a mixed-method approach. The sample consisted of
-1,000 respondents from an online panel, 300 recruited via cell phone and
-landline, and 100 online interviews conducted in Mandarin, Cantonese,
-and Punjabi. This combination of methods aimed to enhance the survey's
-representativeness. For analysis, Version 2 of the 2021 dataset, which
-presents responses in a numeric format, was used.
-
-\subsubsection{Data Analysis}\label{data-analysis}
-
-The primary focus of this analysis was the 2018 dataset, examining six
-key variables: age, education, extent informed, likelihood to take
-action, reasons for not taking action, and the best method for
-delivering information regarding climate change action. I analyzed these
-variables at the individual level in the 2018 dataset by calculating the
-percentages within each category, which provided a clear understanding
-of the distribution and trends within the population.
-
-In addition, I compared the 2018 dataset to the 2021 summary data to
-assess changes over the years. By calculating the percentage
-distribution for each variable in both years, I was able to identify any
-shifts in public awareness, engagement, and preferences regarding
-climate change action. This comparison revealed whether there have been
-notable changes in factors like the public's level of information about
-climate change, their likelihood to take action, and their preferred
-communication methods.
-
-This two-step approach allowed for a comprehensive understanding: a
-detailed exploration of the 2018 data combined with a broader comparison
-of trends between 2018 and 2021.
-
-\subsection{Features}\label{features}
-
-\subsubsection{Age}\label{age}
-
-\paragraph{Individual 2018}\label{individual-2018}
-
-Figure~\ref{fig-one} illustrates the age distribution of survey
-respondents in 2018. The histogram displays the frequency of respondents
-across different age groups, with the x-axis representing age intervals
-and the y-axis indicating the number of respondents within each
-interval. The distribution is relatively balanced, with two noticeable
-peaks around the 30--40 and 50--60 age ranges, suggesting these age
-groups are the most represented in the survey.
-
-The vertical dotted lines in the figure highlight key statistical
-measures: the green dotted line represents the median age, while the
-blue dashed line indicates the mean age of the respondents. Both
-measures fall near the center of the distribution, reinforcing the
-observation that the sample is primarily composed of middle-aged
-individuals. Although the distribution appears fairly symmetrical, there
-is a gradual decline in respondent frequency after the age of 60, with
-fewer participants aged 90 and above, indicating a smaller
-representation of older individuals.
-
-Overall, Figure~\ref{fig-one} provides valuable context for
-understanding the demographic composition of the survey sample. The
-predominance of middle-aged respondents may influence the interpretation
-of survey results, particularly if age is a factor in attitudes,
-behaviors, or preferences related to the study.
+public perceptions of climate change in Toronto in the years 2018 and
+2021. This dataset was accessed from \texttt{Open\ Data\ Toronto}
+({``Open Data Toronto''} 2024) on 6 November 2024.
+
+\subsubsection{Software and R-packages}\label{software-and-r-packages}
+
+This project was conducted using the statistical software \texttt{R} (R
+Core Team 2023), with several packages facilitating data cleaning,
+analysis and reporting. The \texttt{tidyverse} package (Wickham,
+Averick, et al. 2024) was central to the project, with \texttt{dplyr}
+(Wickham, François, et al. 2024) used in the cleaning and exploratory
+data analysis scripts for filtering, summarizing, and joining datasets.
+\texttt{readr} (Wickham, Hester, et al. 2024) handled reading and
+writing text data, while \texttt{tidyr} (Wickham, Henry, et al. 2024)
+reshaped data. \texttt{stringr} (Wickham 2024c) managed character
+strings, and \texttt{forcats} (Wickham 2024a) reordered factor levels
+for visualizations.
+
+In the download script, \texttt{httr}(Wickham 2024b) retrieved files
+from \texttt{Open\ Data\ Toronto} ({``Open Data Toronto''} 2024),
+while\texttt{readxl} (Wickham and Bryan 2024) read Excel files, and
+\texttt{openxlsx} (Walker et al. 2024) created structured Excel
+workbooks. The \texttt{arrow} package (Richardson et al. 2024) optimized
+data storage and was used in the simulation and cleaning scripts to save
+datasets as Parquet files.
+
+For modeling, \texttt{rpart} (Therneau and Atkinson 2024) and
+\texttt{partykit} (Hothorn and Zeileis 2024) built and visualized
+decision trees in the model script. The \texttt{testthat} package
+(Wickham et al. 2024b) validated simulated and cleaned datasets in their
+respective scripts. Visualizations were created using \texttt{ggplot2}
+(Wickham et al. 2024a) in the exploratory data analysis. Reporting
+relied on \texttt{knitr} (Xie 2024) and \texttt{kableExtra} (Zhu 2024)
+to integrate code, outputs, and styled tables. The
+\texttt{tinytable}package (Mikolas 2024) generated compact tables in
+both the exploratory data analysis script as well as in the paper. These
+packages ensured efficient and streamlined data management, analysis and
+reporting throughout the project.
+
+\subsubsection{Methodology}\label{methodology}
+
+\paragraph{Data Collection}\label{data-collection}
+
+To embark on this analysis, we turn to two pivotal surveys commissioned
+by the City of Toronto to capture residents' perceptions of climate
+change and their readiness to take action. Our journey begins in 2018,
+when Environics Research conducted an online survey with 404 Toronto
+residents aged 18 and older, from October 11 to 18. The sample, drawn
+from an online panel, was carefully crafted with quotas based on region,
+age, and gender to mirror the 2016 Census. A touch of minor weighting
+ensured a more representative reflection of the population. However,
+it's important to note that this non-random sample introduces some
+potential bias, an aspect we keep in mind as we move forward.
+
+The path continues in 2021 with Ipsos at the helm, stepping in with a
+more expansive survey, engaging 1,400 residents from a mix of methods:
+1,000 from an online panel, 300 via phone, and 100 through online
+interviews conducted in Mandarin, Cantonese, and Punjabi. This diverse
+approach sought to enhance the survey's representativeness across
+Toronto's varied communities. For our analysis, we used Version 2 of the
+2021 dataset, where responses were presented in a clear, numeric format,
+offering a solid foundation for our exploration.
+
+With this data in hand, we are now ready to delve into the intricacies
+of the findings, unearthing patterns, and understanding the deeper story
+they tell about Toronto's residents and their views on climate change
+and collective action.
+
+\paragraph{Data Analysis}\label{data-analysis}
+
+The focus of this analysis was the 2018 dataset, which examined five key
+variables: age, education, extent informed, likelihood to take action,
+and preferred methods for delivering information about climate change
+action. These variables were analyzed at the individual level, allowing
+for an in-depth exploration of residents' perspectives.
+
+For 2021, summary data was available instead of individual-level data.
+To compare trends, I created summary data for 2018. Calculating the
+percentage distribution for each variable in both years helped identify
+shifts in demographics, public awareness, and engagement, as well as
+changes in preferred communication methods. Although the absence of
+individual data for 2021 posed a challenge, this comparison still
+provided a dynamic view of evolving climate change perspectives in
+Toronto. The two-step approach---detailing 2018 data and then comparing
+it with 2021 trends---created a comprehensive narrative of change.
+
+\subsubsection{Features}\label{features}
+
+\paragraph{Age}\label{age}
+
+\subparagraph{Individual 2018}\label{individual-2018}
+
+Figure~\ref{fig-one} presents the age distribution of survey respondents
+in 2018. The histogram shows the frequency of respondents across age
+groups, with age intervals on the x-axis and the number of respondents
+on the y-axis. The distribution is fairly balanced, with peaks around
+the 30--40 and 50--60 age ranges, indicating that these groups were the
+most represented in the survey.
+
+The vertical dotted lines highlight the median and mean ages. The green
+dotted line represents the median age, and the blue dashed line
+represents the mean age, both located just above 45. This suggests the
+sample is predominantly middle-aged, with a gradual decline in
+respondent frequency after the age of 60. Few participants were over 80,
+indicating a lower representation of older individuals
 
@@
 
-\caption{\label{fig-one}The histogram shows the distribution of age
-given the 2018 survey respondents.}
+\caption{\label{fig-one}Distribution of age given the 2018 survey
+respondents. The mean and median of the sample is indicated with dashed
+and dotted lines respectively.}
 
@@
 
-\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}
-
-(\textbf{table-one?}) illustrates the different age ditribution for 2018
-and 2021 surveys. The major difference is that there was greater
-representation of younger inviduals ranging from 18 to 23 in 2021
-compared to 2018. The remaining age groups were not very different.
+\newpage
+
+\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}
+
+Figure~\ref{fig-two} compares the age distributions between 2018 and
+2021. The main difference is an increase in respondents aged 18-23 in
+2021, with other age groups remaining relatively stable. This shift may
+reflect changing demographic patterns or differences in survey
+methodologies within the three years.
+
+\begin{figure}
+
+\centering{
 
@@
 
-This table highlights the age distribution of survey respondents in 2018
-and 2021.
-
-\subsubsection{Highest Level of Education
-Completed}\label{highest-level-of-education-completed}
-
-\paragraph{Individual 2018}\label{individual-2018-1}
-
-Figure~\ref{fig-two} illustrates the distribution of survey respondents
-by their highest level of education attained. The most frequently
-reported education levels are ``Completed undergraduate degree'' and
-``Post graduate/professional school,'' with both categories having a
-noticeably higher frequency compared to others, indicating a
-well-educated respondent population. In contrast, fewer respondents
-reported ``Some community college, vocational, trade school'' and
-``Completed community college, vocational, trade school,'' suggesting
-these levels are less common among participants. Additionally, a small
-portion of respondents preferred not to disclose their education level.
-This distribution highlights a skew toward higher educational attainment
-within the sample, which may influence responses related to
-socio-economic factors and other survey topics.
+}
+
+\caption{\label{fig-two}This table highlights the age distribution of
+survey respondents in 2018 and 2021.}
+
+\end{figure}%
+
+\paragraph{Education}\label{education}
+
+\subparagraph{Individual 2018}\label{individual-2018-1}
+
+Figure~\ref{fig-three} shows the distribution of respondents by their
+highest level of education attained in 2018. The most common education
+levels are ``Completed undergraduate degree'' and
+``Postgraduate/professional school,'' indicating a well-educated
+respondent population. In contrast, fewer respondents reported having
+attended or completed community college, vocational, or trade school,
+suggesting lower representation in these categories. A small portion of
+respondents chose not to disclose their education level. Overall, the
+distribution reflects a skew toward higher levels of educational
+attainment.
 
@@
 
-\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}
-
-(\textbf{table-two?}) illustrates respondant education level in 2018 and
-2021 respectively. Please note, the categories of education level are
-different for 2018 and 2021 as these were different surveys and
-categories were updated in 2021. Despite this, we are still able to make
-comparisons. Individuals with high school diplomas or less account for 9
-for 2018 and 38 for 2021 (addition of less than highs school and high
-school or equivalent categories). This could indicate that the younger
-population was included more in the 2021 suvey or that less education
-individuals were surveyed. Additionally, its not super clear howver
-those with a post graduate or professional degree accounted for 29
-percent in 2018 and 35 percent in 2021. This illustrates that more
-educated inviduals responded to the 2021 survey.
+\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}
+
+Figure~\ref{fig-four} compares the education levels of respondents in
+2018 and 2021. The two surveys used different education categories,
+making direct comparisons challenging. In 2018, 9\% of respondents had a
+high school diploma or less, while in 2021, this figure rose to 38\%,
+due to the addition of the ``less than high school'' and ``high school
+or equivalent'' categories. This shift indicates that the 2021 survey
+better represented individuals with lower educational attainment.
+
+The 2018 survey provided more detailed categories, including options for
+community college, trade school, and distinctions between ``some''
+versus ``completed'' education. In contrast, the 2021 survey used
+broader categories, which likely reduced the specificity of educational
+data. Notably, the 2021 survey appears to have offered a more balanced
+sample, with a wider spread across various education levels, while the
+2018 sample was noticeably skewed toward respondents with higher
+educational attainment. This suggests that the 2021 survey may have
+captured a broader range of educational backgrounds, providing a more
+well-rounded representation of Toronto's population.
+
+\begin{figure}
+
+\centering{
 
@@
 
-This table highlights the education distribution of survey respondents
-in 2018 and 2021.''
-
-\subsubsection{Extent Feel Informed}\label{extent-feel-informed}
-
-\paragraph{Individual 2018}\label{individual-2018-2}
-
-Figure~\ref{fig-three} depicts the distribution of self-reported climate
+}
+
+\caption{\label{fig-four}This table highlights the education
+distribution of survey respondents in 2018 and 2021.''}
+
+\end{figure}%
+
+\paragraph{Extent Feel Informed}\label{extent-feel-informed}
+
+\subparagraph{Individual 2018}\label{individual-2018-2}
+
+Figure~\ref{fig-five} depicts the distribution of self-reported climate
 change knowledge among survey respondents in 2018. The majority of
@@
 
-\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}
-
-(\textbf{table-three?}) illustrates the self-reported level of extent
+\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}
+
+Figure~\ref{fig-six} illustrates the self-reported level of extent
 inviduals feel informed about climate change and climate action for 2018
@@
 
-This table highlights the extent feel informed distribution of survey
-respondents in 2018 and 2021.
-
-\subsubsection{Best Mode of Delivery}\label{best-mode-of-delivery}
-
-\paragraph{Individual 2018}\label{individual-2018-3}
-
-The analysis of the best method for delivering climate change
-information portrayed in Figure~\ref{fig-four} revealed that the
-majority of individuals in the 2018 dataset preferred receiving
-information firstly from advertising campaigns with about 55 percent,
-newsletters with about 52 percent, followed by the toronto website wiht
-about 46 percent. On the other side of the spectrum, few said they were
-uninterested in receiving climate action information with about 5
-percent, about 12 percent indicated twitter and then 17 percent
-mentioned instagram. Overall social media platforms Facebook, Instagram
-and Twtitter were less popular methods of communciation. This could be
-because the survey only included individals over the age of 18.
-Moreover, the median sample was in the 40s.
+}
+
+\caption{\label{fig-six}This table highlights the extent feel informed
+distribution of survey respondents in 2018 and 2021.}
+
+\end{figure}%
+
+\paragraph{Best Method of Delivery}\label{best-method-of-delivery}
+
+\subparagraph{Individual 2018}\label{individual-2018-3}
+
+Figure~\ref{fig-seven}, shows 2018 survey results for the preferred
+method for receiving climate change information. Advertising campaigns
+emerged as the most popular choice, selected by approximately 55 percent
+of respondents, followed closely by newsletters with 52 percent and the
+Toronto.ca website with 46 percent. On the other hand, social media
+platforms such as Facebook, Instagram, and Twitter were less popular
+overall, with Twitter 12 percent and Instagram 17 percent garnering the
+fewer votes. Notably, only 5 percent of respondents reported being
+uninterested in receiving information about climate action. These
+findings suggest that more traditional communication methods, such as
+advertising and newsletters, resonated better with respondents compared
+to social media.
 
@@
 
-\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}
-
-(\textbf{table-four?}) compares responses from 2018 and 2021 surverys
-regarding the best method of delivering information on climate change
-and climate action. Aside from the additon of four options to the 2021
-survey, both surveys questions are the same. The leading category for
-2018 is advertising campaigns with 55 percent, closely followed by
-newsletter emails with 52 percent and the Toronto website with 46. The
-2021 survey illustrates a consistent trend with the same platforms as
-the top method of delivering information, specifically the Toronto
-website with 44 percent, then enewsletter emails with 43 percent and
-advertising campains at 42 percent. These top methods of communciation
-are more evenly spread out than the 2018 survey results. Social media
-platforms namely twitter, facebook and instagram all increased in the
-2021 survey. Notable decreases in term of percentage from 2018 to 2021
-include events, enewsletter emails, advertising campaigns, brochures and
-pamphlets. The new category of BetterHomesTO.ca webiste accounts for 15
-percent of votes for the 2021 survey.
+\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}
+
+Figure~\ref{fig-eight} compares the preferred methods of delivering
+climate change information between the 2018 and 2021 surveys. While the
+top three methods namely advertising campaigns, newsletters, and the
+Toronto.ca website remained consistent across both years, there were
+notable shifts in preferences. Traditional methods such as newsletters,
+advertising campaigns, brochures, and pamphlets saw a decline in 2021.
+In contrast, social media platforms including Twitter, Facebook, and
+Instagram gained traction, reflecting a growing reliance on digital
+communication channels.
+
+Additionally, the 2021 survey introduced new categories, including the
+BetterHomesTO.ca website, which accounted for 15 percent of responses.
+This addition underscores the increasing importance of specialized
+online platforms in engaging the public on climate action. These changes
+highlight a shift toward more diverse and digitally focused
+communication strategies over time.
+
+\begin{figure}
+
+\centering{
 
@@
 
-This table highlights the prefered method of communication of survey
-respondents in 2018 and 2021.
-
-\subsubsection{Likelihood Taking Action}\label{likelihood-taking-action}
-
-\paragraph{Individual 2018}\label{individual-2018-4}
-
-The likelihood of taking action against climate change was explored by
-assessing individuals' intentions and behaviors. Figure~\ref{fig-five}
-illustrates self-reported likelihood of taking certain actions that
-minimize climate change effects. On the x-axis, we have the nine
-different climate actions and on the y-axis is the percentage. The
-stacked bar chart allows understanding of how likely individuals are to
-take part in the given actions. Sorting waste into the correct bins is
-the action that most individuals are doing right now, accounting for 60
-percent whith 24 percent saying they are very likely to take part in
-this action. The next most prominent actions are walking or cycling
-short distances, reduce hydro usage, reduce waste and home improvements.
-40 percent of invidiuals report walking or cycling when traveling
-shorter distances in the city with 22 percent reporting they are very
-likely. However, 7 percent say they are very unlikely to change their
-method of transportation. Reducing the amount of energy and water use is
-already done by 36 percent and very likely for 29 percent only a mere 3
-percent is very unlikely. Reducing personal waste such as contributing
-to repurposing used products has similar percentages to responses for
-reducing hydro but even fewer individuals that report they are very
-unlikely to take action. Similarly, the likelihoods for making home
-improvements for energy efficiency such as energy-efficient appliances,
-programmable thermostat, LED lightbulbs, green or cool roof. In
-contrast, the action where the least number of individuals are
-contributing to is the investment of an electric or hybrid vehicle over
-gas-powered vehicles with only 8 percent who currently have an energy
-efficient vehicle. While 19 percetn are very likely to make this switch,
-14 percent say they are very unlikely. This illustrates that buying an
-electric or hybrid vehicle is action the least number of individuals are
-willing to invest in despite gas-powered vehicles being a major
-contributor to greenhouse gases. This action has a huge impact on the
-environment and yet 41 percent of this sample say they are unlikely to
-change! The second action that individuals are most unlikely to engage
-in is eat less meat by incorporating more plant-based foods in their
-diet with 12 percent very unlikely and 23 percent somewhat unlikely.
-Only 23 percent are already consuming meat alternatives. Vegans
-greenhosue gas emissions are on average 37\% lower than those who eat
-meat frequently.
+}
+
+\caption{\label{fig-eight}This table highlights the prefered method of
+communication of survey respondents in 2018 and 2021.}
+
+\end{figure}%
+
+\paragraph{Likelihood Taking Action}\label{likelihood-taking-action}
+
+Figure~\ref{fig-nine} illustrates the self-reported likelihood of
+individuals taking various actions to minimize environmental impacts.
+The x-axis displays nine different climate actions, while the y-axis
+represents the percentage of individuals corresponding to each
+likelihood level. A stacked bar chart is used to visualize the
+distribution of responses, with a color-coded legend ranging from green
+(high likelihood of action) to red (low likelihood of action).
+
+Sorting waste into the correct bins is the most frequently reported
+action that individuals are currently undertaking, accounting for 60
+percent of responses. Other common actions individuals are already
+participating in include walking or cycling short distances with 40
+percent, reducing waste by contributing to the repurposing of used
+products with 37 percent and reducing hydro usage with 36 percent
+
+In contrast, the least popular actions include switching to electric or
+hybrid vehicles, with 14 percent of respondents reporting they are very
+unlikely to take this action and 27 percent stating they are somewhat
+unlikely. Similarly, consuming less meat by incorporating more
+plant-based foods is unpopular, with 12 percent reporting they are very
+unlikely and 23 percent somewhat unlikely to adopt this change.
+Minimizing car use is another action with low reported likelihood, with
+10 percent of respondents very unlikely and 16 percent somewhat unlikely
+to reduce their car usage.
 
@@
 
-\section{Model}\label{sec-model}
-
-The goal of our modelling strategy is twofold. Firstly, we aim to
-predict the likelihood of individuals engaging in climate-friendly
-actions based on demographic variables, specifically age and education.
-The actions considered include investing in electric or hybrid vehicles,
-making home improvements (such as using LED lightbulbs), adopting meat
-alternatives, minimizing car use, purchasing green products, reducing
-hydro usage, reducing waste, sorting waste correctly, and walking or
-cycling shorter distances. Secondly, we aim to understand how these
-demographic characteristics influence individuals' likelihood of
-adopting these behaviors.Here we describe the probability tree model
-used to investigate the relationship between likelihood and the
-demographic factors of age and education.
+\subsection{Model}\label{sec-model}
+
+The goal of our modeling strategy is twofold: first, to predict how
+demographic factors influence individuals' likelihood of engaging in
+climate-friendly behaviors, and second, to uncover the role of age and
+education in shaping these actions. The actions considered include
+investing in electric vehicles, reducing hydro usage, adopting meat
+alternatives, and walking or cycling shorter distances. We use a
+decision tree model to provide a clear, interpretable framework for
+analyzing these relationships.
 
@@
 
-In this analysis, we focus on predicting the likelihood of taking
-climate-friendly actions based on the demographic variables of age and
-education. The likelihood is measured on a five-point Likert scale,
-ranging from ``Very unlikely'' to ``Already doing this or have done
-this.''
+Our model predicts the likelihood of engaging in specific
+climate-positive actions, with age and education level serving as
+predictors. Likelihood is measured on a five-point scale, ranging from
+``Already doing this or have done this'' to ``Very unlikely.''
 
@@
 
-We use a probability tree model to predict the likelihood of individuals
-engaging in climate-friendly actions based on two key demographic
-variables: age and education.
-
-The general form of the model is:
-
-\textbackslash begin\{align\} y\_i = \beta\_0 + \beta\_1 * Age\_i +
-\beta\_2 * Education\_i + \epsilon\_i \textbackslash end\{align*\}
-where:
+We employ separate decision tree models for each action. Age
+(continuous) and education (categorical) are the key predictors driving
+predictions. Each tree splits the data at nodes based on these
+variables, revealing demographic conditions associated with greater or
+lesser likelihoods of climate-positive behaviors.
+
+\subsubsection{Model Justification}\label{model-justification}
+
+This approach provides insights into how demographic factors influence
+climate-friendly actions, including energy reduction, sustainable
+practices, and green technology adoption. By identifying demographic
+groups more likely to take these actions, the model can inform targeted
+interventions.
+
+\paragraph{Response Variable}\label{response-variable}
+
+The response variable measures the likelihood of engaging in specific
+climate-friendly behaviors, represented on a five-point scale: ``Already
+doing this or have done this,'' ``Very likely,'' ``Somewhat likely,''
+``Somewhat unlikely,'' and ``Very unlikely.'' This scale reflects an
+individual's readiness to adopt sustainable practices.
+
+\paragraph{Input Variables}\label{input-variables}
+
+Our predictors are:
 
 \begin{itemize}
-\tightlist
 \item
-  \(y_i\) represents the likelihood of individual \(i\) engaging in a
-  climate-friendly actin, measured on a five point Likert scale:
+  \textbf{Age}: Research shows that younger individuals often
+  demonstrate greater environmental awareness and a stronger inclination
+  toward sustainable actions (Leiserowitz et al., 2010; Gifford, 2013).
+\item
+  \textbf{Education}: Previous studies illustrate that higher education
+  correlates with increased environmental awareness and sustainable
+  behavior adoption (Kollmuss \& Agyeman, 2002).
 \end{itemize}
+
+\paragraph{Model Structure}\label{model-structure}
+
+The decision tree splits data based on age and education, uncovering
+demographic patterns in climate-positive behaviors. Unlike linear
+models, decision trees do not assume direct relationships but instead
+identify conditions under which certain behaviors are more likely to
+occur. This assumption of independence allows clear interpretation of
+each factor's influence.
+
+\subsection{Understanding Decision
+Trees}\label{understanding-decision-trees}
+
+Decision trees predict outcomes by recursively splitting data based on
+predictor variables. Starting at the root node (entire dataset), the
+tree branches into nodes based on decision rules, ultimately reaching
+terminal nodes that represent specific predictions, such as the
+likelihood of adopting sustainable behaviors. Each split aims to
+maximize prediction accuracy, and error rates indicate the reliability
+of classifications.
+
+\subsubsection{Decision Trees for Climate-Friendly
+Actions}\label{decision-trees-for-climate-friendly-actions}
+
+We fit nine decision tree models to predict the likelihood of the
+following climate-friendly actions, using age and education as
+predictors:
 
@@
 \item
-  ``Very unlikely''
+  Likelihood of switching in an electric or hybrid vehicle
 \item
-  ``Somewhat unlikely''
+  Likelihood of minimizing car use
 \item
-  ``Somewhat likely''
+  Likelihood of walking or cycling shorter distances
 \item
-  ``Very likely''
+  Likelihood of purchasing green products
 \item
-  ``Already doing this or have done this''
-\end{enumerate}
-
-\begin{itemize}
-\tightlist
+  Likelihood of reducing waste by repurposing used product
 \item
-  \(\beta_0\) is the intercept, representing the baseline likelihood of
-  taking action when all predictors are zero.
+  Likelihood of sorting waste correctly
 \item
-  \(\beta_1\) is the coefficient for Age, representing how a one-year
-  increase affects the likelihood of taking action.
-\item
-  \(\beta_2\) is the coefficient for Education, a categorical variable
-  that is dummy-coded.
-\item
-  \(\epsilon_i\) is the error term, accounting for unexplained
-  variation.
-\end{itemize}
-
-This model focuses on the direct effect of age and education on the
-likelihood of taking climate-friendly actions, assuming a linear
-relationship between these demographic variables and the outcome
-variable (the likelihood of action).
-
-\subsubsection{Model Justification}\label{model-justification}
-
-This model was developed to explore how demographic factors such as age
-and education influence individuals' likelihood of engaging in
-climate-friendly behaviors. By focusing on specific climate actions like
-reducing energy consumption, adopting sustainable practices, and
-investing in green technologies, the model aims to provide actionable
-insights for climate change interventions.
-
-\paragraph{Response Variable}\label{response-variable}
-
-The response variable in this analysis is the likelihood of taking
-climate-friendly actions, measured using a Likert scale (1 = ``Very
-unlikely'' to 5 = ``Already doing this or have done this''). This scale
-captures the respondent's perceived likelihood of engaging in various
-climate-friendly behaviors
-
-\paragraph{Input Variabless}\label{input-variabless}
-
-The input variables (predictors) include:
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Age}: Previous research indicates that younger individuals may
-  be more inclined to adopt climate-friendly behaviors due to increased
-  environmental awareness (Leiserowitz et al., 2010; Gifford, 2013).
-\item
-  \textbf{Education}: Higher levels of education are often linked to
-  greater awareness of environmental issues and a higher likelihood of
-  adopting sustainable behaviors (Kollmuss \& Agyeman, 2002). Education
-  is treated as a categorical variable and dummy-coded for analysis.
-\end{itemize}
-
-\paragraph{Model Structure}\label{model-structure}
-
-This model assumes a linear relationship between the predictors (age and
-education) and the likelihood of taking action. Specifically, the
-likelihood of taking climate-friendly actions is modeled as a function
-of age and education, with coefficients representing the change in the
-likelihood of action associated with a unit change in each predictor.
-
-There are no interaction terms in this model, meaning we assume that the
-effects of age and education on the likelihood of taking action are
-independent of each other. This simplicity ensures clear interpretation
-of each predictor's individual effect on the likelihood of taking
-climate-friendly actions.
-
-\subsection{Nine Models}\label{nine-models}
-
-We fit nine separate probability tree models, one for each
-climate-friendly action we are predicting. Each model uses age and
-education as the predictors to estimate the likelihood of the
-corresponding action. These actions are:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Likelihood of investing in an electric or hybrid vehicle
-\item
-  Likelihood of making home improvements (e.g., using LED lightbulbs)
+  Likelihood of making home improvements
 \item
@@
 \item
-  Likelihood of minimizing car use
-\item
-  Likelihood of purchasing green products 6 Likelihood of reducing hydro
-  usage
-\item
-  Likelihood of reducing waste by repurposing used products
-\item
-  Likelihood of sorting waste correctly
-\item
-  Likelihood of walking or cycling shorter distances
+  Likelihood of reducing hydro usage
 \end{enumerate}
 
-Each model is built using the same structure but predicts a different
-outcome variable. This approach allows us to analyze the specific impact
-of age and education on each climate-friendly action.
-
-\subsubsection{Likelihood of investing in an electric or hybrid
-vehicle}\label{likelihood-of-investing-in-an-electric-or-hybrid-vehicle}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/vehicle_electric_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of investing in an electric or
-hybrid vehicle, predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of making home
-improvements}\label{likelihood-of-making-home-improvements}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/home_improvement_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of making home improvements
-predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of adopting meat
-alternatives}\label{likelihood-of-adopting-meat-alternatives}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/protein_alternative_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of adopting meat alternatives,
-predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of minimizing car
-use}\label{likelihood-of-minimizing-car-use}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/minimize_car_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of minimizing car use,
-predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of purchasing green
-products}\label{likelihood-of-purchasing-green-products}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/green_product_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of purchasing green products,
-predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of reducing hydro
-usage}\label{likelihood-of-reducing-hydro-usage}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_hydro_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of reducing hydro usage,
-predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of reducing
-waste}\label{likelihood-of-reducing-waste}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/reduce_waste_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of reducing waste, predicted by
-age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of sorting waste
-correctly}\label{likelihood-of-sorting-waste-correctly}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/sort_waste_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of sorting waste correctly,
-predicted by age and education.}
-
-\end{figure}%
-
-\subsubsection{Likelihood of walking or cycling shorter
-distances}\label{likelihood-of-walking-or-cycling-shorter-distances}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=10.67in,height=\textheight]{../data/04-model_data/short_distance_tree.png}
-
-}
-
-\caption{Probability tree for likelihood of walking or cycling shorter
-distances, predicted by age and education.}
-
-\end{figure}%
+Each model follows a consistent structure, highlighting how age and
+education influence these behaviors.
 
@@
 
-The probability tree model estimates how the predictors age and
-education influence the likelihood of adopting climate-friendly
-behaviors. By splitting the data into branches based on these variables,
-the model helps identify decision rules that predict individuals'
-likelihood of taking actions such as reducing waste or investing in
-green products. We anticipate that younger individuals, due to greater
-environmental awareness, are more likely to engage in climate-positive
-actions, while those with higher levels of education may also be more
-inclined to adopt such behaviors, given their increased awareness of
-climate change and sustainable practices. The model estimates the
-parameters for age and education using regression techniques, providing
-coefficients that indicate how each factor influences the likelihood of
-taking climate-friendly actions.
-
-\section{Results}\label{results}
+The model predicts that younger individuals with higher education levels
+are more likely to adopt climate-friendly behaviors. The decision tree
+identifies key splits in the data and evaluates prediction reliability
+using error rates, providing insight into the impact of age and
+education on sustainable actions.
+
+\subsubsection{Transportation Actions}\label{transportation-actions}
+
+\paragraph{Likelihood of switching to an electric or hybrid
+vehicle}\label{likelihood-of-switching-to-an-electric-or-hybrid-vehicle}
+
+Figure~\ref{fig-ten} reveals that education is the primary predictor for
+the likelihood of switching to an electric or hybrid vehicle.
+Individuals with ``Some Community/Trade School'' or ``Some University''
+education are ``Very likely'' to invest, though with moderate
+variability (error rate 63.8\%). Those with higher education show more
+age-based segmentation. Younger individuals under 35 years are more
+likely to invest, with a lower error rate (30\%). Older individuals,
+particularly those over 69 years, are ``Very unlikely'' to invest. This
+model demonstrates how age and education interact to influence vehicle
+choice.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/vehicle_electric_tree.png}
+
+}
+
+\caption{\label{fig-ten}Probability tree for likelihood of investing in
+an electric or hybrid vehicle, predicted by age and education.}
+
+\end{figure}%
+
+\paragraph{Likelihood of minimizing car
+use}\label{likelihood-of-minimizing-car-use}
+
+Figure~\ref{fig-eleven} shows that the likelihood of minimizing car use
+is consistent across the sample, with a high error rate (61.9\%). The
+model classifies all individuals into the ``Already doing this or have
+done this'' category, indicating widespread adoption of this behavior,
+regardless of age or education
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/minimize_car_tree.png}
+
+}
+
+\caption{\label{fig-eleven}Probability tree for likelihood of minimizing
+car use, predicted by age and education.}
+
+\end{figure}%
+
+\paragraph{Likelihood of walking or cycling shorter
+distances}\label{likelihood-of-walking-or-cycling-shorter-distances}
+
+Figure~\ref{fig-twelve} indicates that education is the primary factor
+influencing short-distance walking or cycling. Those with higher
+education (postgraduate, undergraduate, or some university) are more
+likely to engage in this behavior, with an error rate of 51.9\%. For
+those with lower education, age plays a significant role, with younger
+individuals (under 66 years) more likely to walk or cycle, with an error
+rate of 60\%. This model highlights how education and age together shape
+short-distance mobility, with error rates reflecting the model's
+predictive variability.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/short_distance_tree.png}
+
+}
+
+\caption{\label{fig-twelve}Probability tree for likelihood of walking or
+cycling shorter distances, predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Waste and Product
+Actions}\label{waste-and-product-actions}
+
+\paragraph{Likelihood of purchasing green
+products}\label{likelihood-of-purchasing-green-products}
+
+Figure~\ref{fig-thirteen} reveals that age is the initial split for
+green product purchasing behavior. Younger individuals (under 38 years)
+are more likely to purchase green products, with an error rate of
+51.9\%. Education further refines the prediction. Older individuals
+(over 38 years) are classified by both age and education, with
+postgraduate education leading to higher engagement in purchasing green
+products, with an error rate of 60\%. This model shows how age and
+education influence consumer choices in sustainable products.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/green_product_tree.png}
+
+}
+
+\caption{\label{fig-thirteen}Probability tree for likelihood of
+purchasing green products, predicted by age and education.}
+
+\end{figure}%
+
+\paragraph{Likelihood of reducing waste by repurposing used
+product}\label{likelihood-of-reducing-waste-by-repurposing-used-product}
+
+Figure~\ref{fig-fourteen} shows that age is the primary factor for waste
+reduction behaviors. Younger individuals (under 35 years) are more
+likely to repurpose waste, with an error rate of 57.1\%. Education
+further refines the classification. Older individuals (over 35 years)
+show varied likelihoods based on education, with more highly educated
+individuals more likely to repurpose waste, with an error rate of 60\%.
+This highlights the influence of both age and education on
+waste-reduction habits.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/reduce_waste_tree.png}
+
+}
+
+\caption{\label{fig-fourteen}Probability tree for likelihood of reducing
+waste, predicted by age and education.}
+
+\end{figure}%
+
+\paragraph{Likelihood of sorting waste
+correctly}\label{likelihood-of-sorting-waste-correctly}
+
+Figure~\ref{fig-fifteen} identifies education as the primary factor for
+sorting waste. Those with higher education (at least community/trade
+school or postgraduate) are more likely to sort waste correctly, with an
+error rate of 37.3\%. Age further refines the predictions for those with
+lower education levels, with younger individuals under 37 years being
+more likely to sort waste correctly, albeit with a higher error rate of
+57.1\%. Older individuals (37 years and above) are more likely to sort
+waste correctly, with an error rate of 35.3\%. The model emphasizes the
+role of education in fostering proper waste-sorting behaviors, with age
+providing additional nuance.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/sort_waste_tree.png}
+
+}
+
+\caption{\label{fig-fifteen}Probability tree for likelihood of sorting
+waste correctly, predicted by age and education.}
+
+\end{figure}%
+
+\subsubsection{Home and Lifestyle
+Changes}\label{home-and-lifestyle-changes}
+
+\paragraph{Likelihood of making home
+improvements}\label{likelihood-of-making-home-improvements}
+
+Figure~\ref{fig-sixteen} shows that age is the key predictor for home
+improvement behavior. Individuals aged 36 years and older are
+predominantly classified as ``Already doing this or have done this,''
+with an error rate of 59.6\%. For younger individuals (under 36),
+education plays a role: those with higher educational attainment
+(``Community/Trade School,'' ``Some University,'' or ``Postgraduate'')
+are ``Very likely'' to make home improvements, with an error rate of
+55\%. Conversely, individuals with lower education levels are classified
+as ``Somewhat likely,'' with a higher error rate of 67.4\%. This model
+highlights how age and education interact to influence home improvement
+decisions.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/home_improvement_tree.png}
+
+}
+
+\caption{\label{fig-sixteen}Probability tree for likelihood of making
+home improvements predicted by age and education.}
+
+\end{figure}%
+
+\paragraph{Likelihood of adopting meat
+alternatives}\label{likelihood-of-adopting-meat-alternatives}
+
+Figure~\ref{fig-seventeen} demonstrates that age is the primary factor
+for adopting meat alternatives. Younger individuals (under 35 years) are
+more likely to adopt meat alternatives, with an error rate of 44\%. For
+individuals aged 35 years or older, education becomes a key predictor.
+Those with community/trade school, undergraduate, or postgraduate
+education are more likely to adopt meat alternatives, with varying error
+rates, including ``Somewhat unlikely'' for younger individuals at
+62.9\%. This model highlights how age and education together shape
+dietary choices.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/protein_alternative_tree.png}
+
+}
+
+\caption{\label{fig-seventeen}Probability tree for likelihood of
+adopting meat alternatives, predicted by age and education.}
+
+\end{figure}%
+
+\paragraph{Likelihood of reducing hydro
+usage}\label{likelihood-of-reducing-hydro-usage}
+
+Figure~\ref{fig-eighteen} reveals that age is the primary predictor
+influencing hydro usage reduction. Younger individuals (under 35 years)
+are ``Very likely'' to reduce hydro usage, with an error rate of 60.9\%.
+Older individuals (35 years and above) are further split by education
+and age, with those over 64 years also ``Very likely'' to engage in
+hydro conservation, with a lower error rate of 37.5\%. Middle-aged
+individuals (35--64 years) with higher education are either ``Already
+doing this or have done this'' (error rate 56.3\%) or ``Somewhat
+likely'' (error rate 50.0\%). This model underscores the combined role
+of age and education in promoting energy-saving behaviors.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=10.67in,height=\textheight]{../models/reduce_hydro_tree.png}
+
+}
+
+\caption{\label{fig-eighteen}Probability tree for likelihood of reducing
+hydro usage, predicted by age and education.}
+
+\end{figure}%
+
+\subsection{Results}\label{sec-results}
 
@@
 
-The table presents the accuracy of models predicting the likelihood of
-various climate-friendly actions based on demographic factors such as
-age and education. Each row represents a different climate action (e.g.,
-home improvement, reducing hydro, minimizing car use), with the
-corresponding accuracy of the model's predictions. The accuracy values
-reflect how well the models, which use age and education as predictors,
-align with the actual data. An accuracy of 33 percent for home
-improvement'' indicates that the model correctly predicted the outcome
-33\% of the time for this action. These accuracy values help evaluate
-the effectiveness of age and education as predictors for each specific
-climate action.
-
-\begin{verbatim}
-                Model Accuracy
-1    home_improvement       33
-2        reduce_hydro       28
-3        minimize_car       39
-4    vehicle_electric       25
-5 protein_alternative       25
-6        reduce_waste       39
-\end{verbatim}
+\textbf{?@fig-nineteen} presents the accuracy of models predicting
+climate-friendly actions based on age and education. A threshold emerges
+from the data: models with accuracy above 50\% are considered reliable,
+while those below require careful interpretation. Sorting waste
+correctly, with an accuracy of 59\%, is the most reliable prediction,
+indicating a stronger association between demographic factors and this
+behavior. Models like home improvements (33\%) offer limited predictive
+value but remain somewhat informative. In contrast, actions such as
+adopting meat alternatives (25\%) or choosing electric or hybrid
+vehicles (25\%) approach random chance, making their predictions less
+reliable for drawing meaningful conclusions.
 
@@
 respondents reporting different likelihood levels, from ``Already doing
-this'' to ``Very unlikely.'' The trend lines across each action show how
-engagement varies by age.
-
-\subsubsection{Electric / Hybrid Vehicle
-Adoption}\label{electric-hybrid-vehicle-adoption}
-
-Younger respondents (15-24, 25-34) are less likely to adopt electric or
-hybrid vehicles, with only a small proportion already using or
-considering them. Adoption rates increase slightly in the 55-64 age
-group, then decline again in the 65+ group. This suggests that older
-individuals may have more resources or stability to invest in electric
-vehicles.
-
-\subsubsection{Home Improvement for Energy
-Efficiency}\label{home-improvement-for-energy-efficiency}
-
-Middle-aged individuals (35-54) are the most likely to engage in home
-improvement actions aimed at increasing energy efficiency. Younger age
-groups (15-24, 25-34) report lower likelihoods, likely due to barriers
-such as homeownership and disposable income.
-
-\subsubsection{Consumption of Meat
-Alternatives}\label{consumption-of-meat-alternatives}
-
-Younger age groups, especially 15-24 and 25-34, are more likely to adopt
-meat alternatives. As age increases, the likelihood of doing so
-decreases, possibly due to established dietary habits in older
-generations.
-
-\subsubsection{Minimizing Car Use}\label{minimizing-car-use}
-
-A trend similar to that of meat alternatives is observed, with younger
-individuals more likely to minimize car use. Older respondents,
-particularly those 65 and older, show less inclination to reduce car
-usage, possibly due to mobility needs or lifestyle factors like suburban
-living.
-
-\subsubsection{Purchasing Green
-Products}\label{purchasing-green-products}
-
-The likelihood of purchasing green products is relatively uniform across
-age groups. Middle-aged and older demographics show a slight increase in
-engagement, but the trend line remains mostly flat, indicating that this
-behavior is more influenced by factors such as income or environmental
-awareness rather than age.
-
-\subsubsection{Reducing Hydro Usage}\label{reducing-hydro-usage}
-
-Older respondents (55-64 and 65+) are the most likely to reduce hydro
-usage, likely driven by cost-saving measures or environmental concerns.
-The trend line shows a steady increase with age.
-
-\subsubsection{Reducing and Sorting
-Waste}\label{reducing-and-sorting-waste}
-
-Both reducing and sorting waste are more commonly reported by
-middle-aged and older groups (45-64). This may reflect increased
-awareness or resources for waste management.
-
-\subsubsection{Walking / Cycling Short
-Distances}\label{walking-cycling-short-distances}
-
-Younger respondents (15-34) are more likely to engage in walking or
-cycling short distances. As age increases, the likelihood of walking or
-cycling decreases, possibly due to physical limitations or differing
-lifestyle needs.
+this'' to ``Very unlikely''.
+
+\subsubsection{Transportation Actions}\label{transportation-actions-1}
+
+In the category of transportation actions, the results reveal that for
+electric and hybrid vehicles, there is little difference between age
+groups in terms of the likelihood of adopting this behavior, but older
+individuals, particularly those aged 65+, are more likely to report
+being ``very unlikely'' to do so. For minimizing car use, individuals
+across all age groups report similar levels of engagement, with
+relatively consistent percentages already minimizing their car use.
+However, older individuals, particularly those in the 45-54 and 65+ age
+groups, are more likely to report being ``very unlikely'' to minimize
+car use. For walking or cycling short distances, the trend shows that
+all age groups, except for those aged 25-34, report similar levels of
+engagement, with a slight decrease in adoption among the 25-34 age
+group. Conversely, older individuals, especially those aged 65+, are
+more likely to report being ``very unlikely'' to engage in walking or
+cycling for short distances.
+
+\subsubsection{Waste and Product
+Actions}\label{waste-and-product-actions-1}
+
+When examining purchasing green products, individuals aged 35 and older
+report higher engagement in this action, with many already purchasing
+green products or expressing a strong likelihood of doing so. Notably,
+those aged 45 and above are the least likely to adopt this behavior,
+with a significant percentage indicating they are ``very unlikely'' to
+do so. For reducing waste, older age groups show higher levels of
+engagement, with individuals aged 35 and above reporting the highest
+rates of already taking this action. The 45-54 age group, however, is
+the least likely to engage in this behavior. Sorting waste correctly is
+overwhelmingly supported by all age groups, with at least 75\% in each
+category already doing or being very likely to take action. The
+incidence of individuals reporting being ``very unlikely'' to sort waste
+correctly is minimal across all age groups.
+
+\subsubsection{Home and Lifestyle
+Changes}\label{home-and-lifestyle-changes-1}
+
+For making home improvements aimed at increasing energy efficiency,
+middle-aged individuals (35-54) are the most likely to report having
+already made improvements or being very likely to do so. Across all age
+groups, at least half of the respondents are already engaged in or very
+likely to engage in energy-efficient home improvements, though younger
+individuals (15-24) are less likely to take this action. Regarding
+adopting meat alternatives, younger individuals, particularly those aged
+15-24, are the least likely to reduce meat consumption with plant-based
+alternatives. In contrast, individuals aged 35 and older show higher
+levels of adoption or strong intention to adopt this behavior. Lastly,
+for reducing hydro usage, there is a clear increase in the likelihood of
+engagement with increasing age. Older individuals, particularly those
+aged 65+, are more likely to report already reducing their hydro usage
+or being very likely to do so, though the 65+ age group also reports the
+highest percentage of being ``very unlikely'' to reduce hydro usage.
 
@@
 
-\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_age_plot.png}
-
-}
-
-\caption{\label{fig-six}Likelihood of Taking Climate Change Actions by
-Age Group. The stacked bar chart illustrates the percentage of
+\includegraphics[width=9in,height=\textheight]{../data/03-figures_data/likelihood_age_plot.png}
+
+}
+
+\caption{\label{fig-twenty}Likelihood of Taking Climate Change Actions
+by Age Group. The stacked bar chart illustrates the percentage of
 respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64,
@@
 
-Figure~\ref{fig-seven} displays how the likelihood of engaging in
+Figure~\ref{fig-twenty-one} displays how the likelihood of engaging in
 climate-friendly actions varies by educational attainment. The x-axis
 represents the proportion of respondents in each education category,
-while the y-axis lists the educational levels, from ``Prefer not to
-answer'' to ``Postgrad.'' Each action is shown across separate facets,
+while the y-axis lists the educational levels, from low to high
+educational attainment. Each action is shown across separate facets,
 revealing how education level correlates with engagement in each
@@
 
-\subsubsection{Trends in Education Attainment and Climate-Friendly
-Actions}\label{trends-in-education-attainment-and-climate-friendly-actions}
-
-Individuals with higher education levels generally show a higher
-likelihood of engaging in climate-friendly actions. This trend is
-evident across all behaviors, with respondents possessing undergraduate
-or postgraduate degrees more likely to adopt electric vehicles or
-purchase green products.
-
-\paragraph{Electric/Hybrid Vehicle
-Adoption}\label{electrichybrid-vehicle-adoption}
-
-Postgraduate degree holders are the most likely to have adopted or
-consider adopting electric or hybrid vehicles. In contrast, respondents
-with lower education levels, such as those with high school or less, are
-more likely to report being ``Very unlikely'' or ``Somewhat unlikely''
-to adopt these vehicles.
-
-\paragraph{Minimizing Car Use}\label{minimizing-car-use-1}
-
-Higher education levels correlate with a greater likelihood of
-minimizing car use, though the trend is less pronounced for individuals
-with lower education levels.
-
-\paragraph{Reducing Hydro Usage}\label{reducing-hydro-usage-1}
-
-While education has a smaller impact on reducing hydro usage compared to
-other actions, those with higher education levels are still more likely
-to engage in this behavior.
-
-\paragraph{Purchasing Green Products and Reducing
-Waste}\label{purchasing-green-products-and-reducing-waste}
-
-Purchasing green products and reducing waste are more common among
-individuals with postsecondary education, especially those with
-undergraduate or postgraduate degrees. In contrast, individuals with
-lower education levels report more moderate engagement with these
-actions.
-
-\subsubsection{Adopting Meat
-Alternatives}\label{adopting-meat-alternatives}
-
-Higher education is associated with greater adoption of meat
-alternatives. This is particularly true for those with undergraduate or
-postgraduate education, while fewer respondents with lower education
-levels report engaging in this behavior.
-
-\subsubsection{Walking or Cycling Short
-Distances}\label{walking-or-cycling-short-distances}
-
-Walking or cycling short distances is a behavior that is relatively
-common across all education levels, though individuals with higher
-education levels show slightly higher engagement.
-
-\subsubsection{Sorting Waste Correctly}\label{sorting-waste-correctly}
-
-Sorting waste correctly is one of the most consistently adopted
-behaviors across all education levels, with a relatively small
-proportion of respondents indicating they are unlikely to engage in this
-action. However, individuals with higher education are still more likely
-to fall in the ``Already doing this'' category.
+\subsubsection{Transportation Actions}\label{transportation-actions-2}
+
+In the category of transportation actions, the likelihood of adopting
+electric or hybrid vehicles does not significantly vary across age
+groups, but older individuals, particularly those aged 65+, are more
+likely to report being ``very unlikely'' to adopt this action. When
+considering minimizing car use, responses show relatively consistent
+engagement across all age groups, with similar percentages already
+engaging in this action. However, older age groups, particularly those
+aged 45-54 and 65+, are more likely to report being ``very unlikely'' to
+minimize their car use. For walking or cycling shorter distances, the
+trend is fairly consistent across age groups, with all groups showing
+similar levels of adoption, except for those aged 25-34, who report
+slightly lower engagement. Older age groups, particularly individuals
+aged 65+, are also more likely to report being ``very unlikely'' to
+engage in walking or cycling for short distances.
+
+\subsubsection{Waste and Product
+Actions}\label{waste-and-product-actions-2}
+
+Regarding purchasing green products, individuals aged 35 and older show
+higher levels of engagement, with a significant proportion already
+purchasing or expressing strong intentions to do so. Conversely,
+individuals aged 45 and older exhibit lower likelihoods, with a higher
+percentage reporting being ``very unlikely'' to adopt this behavior. For
+reducing waste, older age groups (35 and above) are more likely to have
+already taken action or express high intentions to do so. However, the
+45-54 age group stands out as the least likely to engage in this action.
+Sorting waste correctly is a behavior that is overwhelmingly practiced
+across all age groups, with at least 75\% of individuals from every age
+category reporting that they are already doing it or are very likely to
+do so. The percentage of individuals reporting being ``very unlikely''
+to sort waste correctly is minimal across all age groups.
+
+\subsubsection{Home and Lifestyle
+Changes}\label{home-and-lifestyle-changes-2}
+
+For making home improvements to increase energy efficiency, individuals
+in the 35-54 age range are the most likely to report having already made
+improvements or being very likely to do so. In general, at least half of
+the sample across all age groups reports that they are already engaged
+in or very likely to make energy-efficient home improvements, although
+younger individuals (15-24) are less likely to take this action. When it
+comes to adopting meat alternatives, individuals aged 35 and above are
+more likely to reduce meat consumption with plant-based alternatives,
+while those aged 15-24 are the least likely to engage in this behavior.
+For reducing hydro usage, older age groups, particularly those aged 65+,
+report the highest rates of already engaging in or being very likely to
+engage in this action. However, the 65+ age group also reports the
+highest percentage of being ``very unlikely'' to reduce hydro usage.
 
@@
 
-\captionsetup{labelsep=none}\includegraphics[width=6in,height=\textheight]{../data/03-figures_data/likelihood_education_plot.png}
-
-}
-
-\caption{\label{fig-seven}}
+\captionsetup{labelsep=none}\includegraphics[width=9in,height=\textheight]{../data/03-figures_data/likelihood_education_plot.png}
+
+}
+
+\caption{\label{fig-twenty-one}}
 
@@
 
-\subsection{Overall Summary of
-Results:}\label{overall-summary-of-results}
-
-The results indicate that both age and education significantly influence
-the likelihood of engaging in climate-related actions. Younger
-respondents tend to be more likely to adopt behaviors such as consuming
-meat alternatives and minimizing car use, while older individuals are
-more inclined to engage in actions that require larger investments or
-long-term commitments, such as reducing hydro usage and investing in
-energy-efficient home improvements. Higher educational attainment is
-also strongly linked to a greater likelihood of engaging in
-climate-friendly behaviors, particularly those that involve financial
-investment, like adopting electric vehicles and consuming meat
-alternatives. However, simpler actions such as sorting waste correctly
-are more widely reported across all education levels. These generational
-and educational differences highlight the importance of factors such as
-income, lifestyle, and environmental awareness in shaping individuals'
-climate-related behaviors. In light of these findings, it is crucial to
-consider demographic factors when designing policies or campaigns aimed
-at encouraging climate action, as different age and education groups
-exhibit varied levels of engagement with both simple and more complex
-sustainable practices.
-
-\section{Discussion}\label{discussion}
+\subsection{Discussion}\label{sec-discussion}
+
+\subsection{Overview of Climate Change
+Perspectives}\label{overview-of-climate-change-perspectives}
+
+This paper explored how various demographic factors---such as age,
+education, and climate change knowledge---affect individuals' engagement
+in climate-friendly behaviors. Through a comprehensive analysis of
+survey data from 2018 and 2021, we uncovered surprising patterns and
+deeper insights into the influences that drive people to adopt more
+sustainable actions. By investigating the interplay of these factors, we
+aimed to shed light on how societal changes, particularly in the context
+of climate action, reflect evolving values and behaviors.
+
+\subsection{What We Learn About the
+World}\label{what-we-learn-about-the-world}
 
@@
 
-The findings indicate that younger individuals are more likely to engage
-in climate-friendly actions perceived as low-cost and easier to
-implement, such as consuming meat alternatives and reducing car usage.
-The model results show that these behaviors have relatively higher
-predicted likelihoods among younger participants, aligning with existing
-research on generational differences in environmental attitudes. This
-trend may be driven by heightened environmental awareness and increased
-exposure to climate change discussions among younger generations, often
-through social media and educational initiatives. These results suggest
-that lifestyle factors and generational attitudes significantly shape
-behavioral patterns, with younger individuals gravitating toward actions
-that are both socially encouraged and accessible.
+Initially, we anticipated that younger individuals would lead the way in
+adopting climate-friendly actions. While younger people did excel in
+behaviors like walking or cycling and adopting meat alternatives, the
+older demographic demonstrated more significant commitment to long-term
+sustainable actions, such as making energy-efficient home improvements
+and reducing waste. This unexpected finding revealed that age influences
+sustainability in complex ways: younger people may embrace immediate,
+accessible actions, while older individuals engage in more
+transformative, lasting efforts. This highlights that climate action is
+a multi-generational effort, with each age group contributing in its own
+way.
 
@@
 
-Education significantly influences individuals' likelihood of engaging
-in more substantial climate-friendly behaviors. Our models demonstrate
-that individuals with higher educational attainment are more likely to
-adopt behaviors requiring greater financial or logistical investment,
-such as purchasing electric vehicles or making energy-efficient home
-improvements. The accuracy of the models predicting these behaviors is
-relatively lower than for simpler actions, suggesting that education is
-an important but not sole determinant. This relationship between
-education and sustainability underscores the importance of knowledge and
-informed decision-making in supporting climate-friendly actions,
-particularly those with long-term environmental benefits. The data
-suggests that higher education increases both environmental awareness
-and the capacity to implement financially demanding sustainable
-practices, which are often inaccessible to those with lower educational
-levels.
+We initially hypothesized that higher education levels would lead to
+greater engagement in climate-friendly behaviors, and the data largely
+supported this. Individuals with higher educational attainment were more
+likely to adopt green products and engage in waste reduction. However,
+some behaviors, such as reducing meat consumption, were less influenced
+by education and more affected by lifestyle preferences and cultural
+norms. Education acts as a strong catalyst for sustainability, but it
+works in conjunction with other factors, such as age and socio-economic
+status, to shape climate action. This reminds us that while education is
+a powerful tool for promoting sustainable behaviors, it is not the only
+factor at play.
 
@@
 
-Self-reported knowledge of climate change also plays a role in the
-likelihood of adopting sustainable behaviors. Our analysis shows that
-individuals with greater awareness are more proactive in making
-environmentally conscious choices, particularly for actions like
-reducing waste and conserving energy. However, the model accuracy for
-some knowledge-based behaviors remains moderate, highlighting a gap
-between awareness and action. This suggests that while raising awareness
-is critical, it must be paired with policies that reduce structural
-barriers to adopting more expensive or long-term sustainable actions.
-For example, financial incentives or subsidies for purchasing
-energy-efficient appliances could bridge this gap, ensuring individuals
-are both informed and able to make practical changes.
-
-\subsection{Limitations}\label{limitations}
-
-One significant limitation of this study is its reliance on
-self-reported survey data, which is inherently prone to biases such as
-social desirability bias and recall errors. Respondents may overestimate
-their environmental knowledge or exaggerate their participation in
-climate-friendly behaviors to present themselves in a favorable light.
-This introduces uncertainty into the accuracy of the models, as the
-input data may not fully reflect actual behaviors or knowledge levels.
-Additionally, self-reported data often lacks the granularity needed to
-explore complex interactions between socio-economic factors, such as
-income and household size, which can significantly influence sustainable
-actions.
-
-Another limitation arises from the use of summary data from the 2018 and
-2021 surveys instead of individual-level data. While the summary
-statistics provided valuable insights into broad demographic trends,
-they limited the study's ability to explore more nuanced patterns and
-interactions. For example, the summary data showed differences in
-education and age trends between 2018 and 2021, but without
-individual-level data, it was difficult to determine the direct effect
-of socio-economic factors on climate action likelihood. Future studies
-with access to raw, individual-level data could offer more precise
-estimates and a deeper understanding of these dynamics.
-
-\subsection{Challenges with Survey
-Data}\label{challenges-with-survey-data}
-
-Survey data presents additional challenges, such as non-response bias,
-where certain demographic groups may be underrepresented, leading to
-skewed results. Additionally, the framing of survey questions can
-influence how respondents perceive and answer them, introducing further
-variability in the data. The inability to verify self-reported behaviors
-also limits the reliability of the conclusions drawn from such datasets.
-Despite these challenges, surveys remain a valuable tool for capturing
-perceptions and self-reported behaviors, but their findings should be
-interpreted with caution and, when possible, supplemented with objective
-data sources.
+To effectively encourage individuals to take climate action, it's
+crucial to consider the most popular and impactful methods of
+communication. Based on the findings from both 2018 and 2021, the most
+common methods for engaging individuals in climate-friendly behavior are
+ad campaigns, city newsletters/emails, and the official torontoca
+website. However, there has been a notable shift towards more diverse,
+digitally-focused strategies. Social media platforms, particularly
+Instagram and Twitter, have seen a significant increase in usage since
+2018. These platforms allow for more dynamic, engaging, and personalized
+communication, which can be particularly effective for reaching younger
+demographics. Smith and Brown (Smith and Brown 2023) discuss how digital
+media can drive climate action by engaging youth through interactive and
+tailored content, offering an effective way to reach younger individuals
+who are more digitally engaged. Traditional methods, such as newsletters
+and brochures, continue to play a role but are becoming less dominant.
+To maximize engagement, a multi-channel approach that blends digital and
+traditional communication methods will likely resonate best with the
+broadest audience, particularly when targeting specific age groups and
+education levels.
+
+\subsection{Weaknesses of the Study}\label{weaknesses-of-the-study}
+
+One limitation of this study is its reliance on self-reported survey
+data, which can be biased by social desirability or recall errors.
+Respondents may overestimate their commitment to sustainability or
+exaggerate their behaviors to align with societal expectations.
+Additionally, the use of summary data instead of individual-level data
+constrained our ability to explore complex interactions between
+socio-economic factors and climate behaviors. Future studies that
+utilize individual-level data and more objective measures, such as
+energy consumption records, would provide a clearer picture of the
+drivers behind climate action.
+
+Survey data also presents challenges related to non-response bias, where
+certain demographic groups may be underrepresented, skewing results.
+Additionally, the framing of questions can influence responses, which
+could introduce variability in the data. The inability to verify
+self-reported behaviors further limits the reliability of the
+conclusions drawn from such datasets. Despite these challenges, surveys
+remain a valuable tool for understanding attitudes and behaviors, but
+their findings should be interpreted with caution and complemented with
+more direct forms of data collection.
 
@@
 
-Future research should aim to identify the specific barriers preventing
-certain demographic groups from adopting climate-friendly behaviors.
-This could involve examining factors such as income, access to
-resources, and perceived obstacles to sustainable practices.
-Additionally, targeted interventions, such as financial subsidies,
-public awareness campaigns, or infrastructure improvements, could make
-sustainable actions more accessible and affordable. Longitudinal studies
-would be particularly valuable for tracking how awareness of climate
-change influences sustained behavioral changes over time. Comparing
-individual-level data across different years could also provide insights
-into the long-term impact of educational and policy interventions on
-climate-friendly behaviors.
-
-Lastly, integrating objective data, such as energy consumption records
-or transportation usage statistics, could validate and enhance the
-accuracy of survey-based findings. This combined approach would offer a
-more comprehensive understanding of how demographic and socio-economic
-factors influence the adoption of sustainable actions, ultimately
-informing more effective climate policies and interventions.
+To build on these findings, future research should focus on identifying
+the barriers that prevent certain groups from engaging in
+climate-friendly actions. By examining factors such as income, access to
+resources, and perceived obstacles to sustainability, we can tailor
+interventions to address specific needs. For example, financial
+incentives or public infrastructure improvements could make sustainable
+behaviors more accessible and feasible for low-income individuals.
+Longitudinal studies will also help track how climate awareness
+influences sustained behavioral changes over time, offering insights
+into the effectiveness of educational and policy interventions.
+
+Lastly, incorporating objective data such as energy usage and
+transportation patterns could complement self-reported behaviors and
+validate the findings. This integrated approach would provide a more
+comprehensive understanding of how demographic factors shape sustainable
+actions, ultimately informing more effective climate policies.
 
@@
 
-This study provides valuable insights into the demographic factors that
-influence individuals' likelihood to engage in climate-friendly
-behaviors, particularly age, education, and climate change knowledge.
-Younger individuals and those with higher levels of education are more
-likely to adopt sustainable behaviors, particularly those that require
-greater financial investment or long-term commitment. However, barriers
-such as financial constraints and access to resources remain significant
-challenges. Addressing these barriers through targeted policies and
-interventions could help make sustainable behaviors more accessible and
-the norm across all demographic groups. Future research should explore
-the underlying reasons for resistance to adopting climate-friendly
-behaviors and how external factors can help overcome these challenges to
-achieve widespread climate action.
+This paper examined how age, education, and climate-friendly behaviors
+intersect, revealing that while younger individuals engage in more
+immediate actions like walking and adopting meat alternatives, older
+individuals tend to adopt long-term sustainable practices such as
+energy-efficient home improvements and waste reduction. Education plays
+a significant role in fostering sustainable behavior, though it works
+alongside other factors like income and lifestyle. The rise of digital
+media, especially social platforms, is crucial for engaging younger
+generations in climate action. Despite challenges such as biases in
+self-reported data, the study highlights the need for targeted
+strategies and multi-channel communication to drive climate action
+across diverse groups.
 
@@
 
-\section{Appendix}\label{sec-appendix}
+\subsection{Appendix}\label{sec-appendix}
 
@@
 
+\bibitem[\citeproctext]{ref-partykit}
+Hothorn, Torsten, and Achim Zeileis. 2024. \emph{Partykit: A Toolkit for
+Recursive Partytioning}.
+\url{https://cran.r-project.org/package=partykit}.
+
 \bibitem[\citeproctext]{ref-IPCC2023}
@@
 
+\bibitem[\citeproctext]{ref-tinytable}
+Mikolas, Tomas. 2024. \emph{Tinytable: Create Compact Tables for
+Analysis and Reporting}.
+\url{https://CRAN.R-project.org/package=tinytable}.
+
 \bibitem[\citeproctext]{ref-opendatatoronto}
@@
 
-\bibitem[\citeproctext]{ref-Schultz2002}
-Schultz, P. W. 2002. {``Knowledge, Information, and Household Recycling:
-Examining the Knowledge-Behavior Relationship.''} \emph{Environment and
-Behavior} 34 (3): 344--72.
-\url{https://doi.org/10.1177/001391602400773004}.
-
-\bibitem[\citeproctext]{ref-Steg2014}
-Steg, van den Berg, L. 2014. {``Environmental Psychology: An
-Introduction.''} \emph{Psychology Press}.
-\url{https://doi.org/10.4324/9780203383453}.
-
-\bibitem[\citeproctext]{ref-Stern2000}
-Stern, P. C. 2000. {``Toward a Coherent Theory of Environmentally
-Significant Behavior.''} \emph{Journal of Social Issues} 56 (3):
-407--24. \url{https://doi.org/10.1111/0022-4537.00175}.
+\bibitem[\citeproctext]{ref-arrow}
+Richardson, Neal et al. 2024. \emph{Arrow: Interface to the Apache Arrow
+Columnar Format}. \url{https://CRAN.R-project.org/package=arrow}.
+
+\bibitem[\citeproctext]{ref-Smith2023}
+Smith, J., and A. Brown. 2023. {``The Role of Digital Media in Promoting
+Climate Action Among Youth: A Case Study.''} \emph{Journal of
+Environmental Communication} 15 (3): 45--58.
+
+\bibitem[\citeproctext]{ref-rpart}
+Therneau, Terry, and Beth Atkinson. 2024. \emph{Rpart: Recursive
+Partitioning and Regression Trees}.
+\url{https://cran.r-project.org/package=rpart}.
+
+\bibitem[\citeproctext]{ref-openxlsx}
+Walker, Alexander et al. 2024. \emph{Openxlsx: Read, Write, and Edit
+Xlsx Files}. \url{https://CRAN.R-project.org/package=openxlsx}.
+
+\bibitem[\citeproctext]{ref-forcats}
+Wickham, Hadley. 2024a. \emph{Forcats: Tools for Working with
+Categorical Variables (Factors)}.
+\url{https://CRAN.R-project.org/package=forcats}.
+
+\bibitem[\citeproctext]{ref-ggplot2}
+Wickham, Hadley et al. 2024a. \emph{Ggplot2: Create Elegant Data
+Visualisations Using the Grammar of Graphics}.
+\url{https://CRAN.R-project.org/package=ggplot2}.
+
+\bibitem[\citeproctext]{ref-httr}
+Wickham, Hadley. 2024b. \emph{Httr: Tools for Working with URLs and
+HTTP}. \url{https://CRAN.R-project.org/package=httr}.
+
+\bibitem[\citeproctext]{ref-stringr}
+---------. 2024c. \emph{Stringr: Simple, Consistent Wrappers for Common
+String Operations}. \url{https://CRAN.R-project.org/package=stringr}.
+
+\bibitem[\citeproctext]{ref-testthat}
+Wickham, Hadley et al. 2024b. \emph{Testthat: Unit Testing for r}.
+\url{https://CRAN.R-project.org/package=testthat}.
 
@@
 
+\bibitem[\citeproctext]{ref-tidyr}
+Wickham, Hadley, Lionel Henry, et al. 2024. \emph{Tidyr: Tidy Messy
+Data}. \url{https://CRAN.R-project.org/package=tidyr}.
+
 \bibitem[\citeproctext]{ref-readr}
@@
 
+\bibitem[\citeproctext]{ref-knitr}
+Xie, Yihui. 2024. \emph{Knitr: A General-Purpose Package for Dynamic
+Report Generation in r}. \url{https://CRAN.R-project.org/package=knitr}.
+
+\bibitem[\citeproctext]{ref-kableExtra}
+Zhu, Hao. 2024. \emph{kableExtra: Construct Complex Table with 'Kable'
+and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
+
 \end{CSLReferences}

### 2024-12-14 paper/climate_change.qmd
last pushing attempt to render

--- 2024-12-14 paper/climate_change.qmd
@@
 
-# Results
+# Results {#sec-results}
 
@@
 #| message: false
-#| label: fig-nineteen
-#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
-The accuracy values reflect how closely the model predictions align with the actual observed data.
-Higher accuracy values indicate better model performance.
+#| results: hide
+#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education. See Table @fig-nineteen for details."
+#| fig-names: model_accuracies
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-12-14 paper/climate_change.tex
last pushing attempt to render

@@
 }
-\subsection{Introduction}\label{introduction}
+\section{Introduction}\label{introduction}
 
@@
 
-\subsection{Data}\label{sec-data}
+\section{Data}\label{sec-data}
 
@@
 
-\subsubsection{Software and R-packages}\label{software-and-r-packages}
+\subsection{Software and R-packages}\label{software-and-r-packages}
 
@@
 
-\subsubsection{Methodology}\label{methodology}
-
-\paragraph{Data Collection}\label{data-collection}
+\subsection{Methodology}\label{methodology}
+
+\subsubsection{Data Collection}\label{data-collection}
 
@@
 
-\paragraph{Data Analysis}\label{data-analysis}
+\subsubsection{Data Analysis}\label{data-analysis}
 
@@
 
-\subsubsection{Features}\label{features}
-
-\paragraph{Age}\label{age}
-
-\subparagraph{Individual 2018}\label{individual-2018}
+\subsection{Features}\label{features}
+
+\subsubsection{Age}\label{age}
+
+\paragraph{Individual 2018}\label{individual-2018}
 
@@
 
-\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}
 
@@
 
-\paragraph{Education}\label{education}
-
-\subparagraph{Individual 2018}\label{individual-2018-1}
+\subsubsection{Education}\label{education}
+
+\paragraph{Individual 2018}\label{individual-2018-1}
 
@@
 
-\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}
 
@@
 
-\paragraph{Extent Feel Informed}\label{extent-feel-informed}
-
-\subparagraph{Individual 2018}\label{individual-2018-2}
+\subsubsection{Extent Feel Informed}\label{extent-feel-informed}
+
+\paragraph{Individual 2018}\label{individual-2018-2}
 
@@
 
-\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}
 
@@
 
-\paragraph{Best Method of Delivery}\label{best-method-of-delivery}
-
-\subparagraph{Individual 2018}\label{individual-2018-3}
+\subsubsection{Best Method of Delivery}\label{best-method-of-delivery}
+
+\paragraph{Individual 2018}\label{individual-2018-3}
 
@@
 
-\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}
+\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}
 
@@
 
-\paragraph{Likelihood Taking Action}\label{likelihood-taking-action}
+\subsubsection{Likelihood Taking Action}\label{likelihood-taking-action}
 
@@
 
-\subsection{Model}\label{sec-model}
+\section{Model}\label{sec-model}
 
@@
 
-\subsection{Results}\label{sec-results}
+\section{Results}\label{sec-results}
 
@@
 
-\subsection{Discussion}\label{sec-discussion}
+\section{Discussion}\label{sec-discussion}
 
@@
 
-\subsection{Appendix}\label{sec-appendix}
+\section{Appendix}\label{sec-appendix}
 

### 2024-12-14 paper/climate_change.qmd
cant render because offig-nineteen

@@
 ## Model Summary Table
-@fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education.
+fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education.
 A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation.
@@
 #| results: hide
-#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education. See Table @fig-nineteen for details."
-#| fig-names: model_accuracies
+# #| label: fig-nineteen
+#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
 

### 2024-12-14 paper/climate_change.qmd
finally rendered! must fix cross referencing and display figure sizes next

@@
     toc: true
-number-sections: true
+    number_sections: true
+    toc_depth: 2   # Optional: to control how deep the TOC goes (e.g., section and subsection)
 bibliography: references.bib
@@
 #### Individual 2018
-@fig-one presents the age distribution of survey respondents in 2018.
+fig-one presents the age distribution of survey respondents in 2018.
 The histogram shows the frequency of respondents across age groups, with age intervals on the x-axis and the number of respondents on the y-axis.
@@
 #| message: false
-#| label: fig-one
+##| label: fig-one
 #| fig-cap: "Distribution of age given the 2018 survey respondents. The mean and median of the sample is indicated with dashed and dotted lines respectively."
@@
 #### Comparison 2018 to 2021
-@fig-two compares the age distributions between 2018 and 2021.
+fig-two compares the age distributions between 2018 and 2021.
 The main difference is an increase in respondents aged 18-23 in 2021, with other age groups remaining relatively stable.
@@
 #| message: false
-#| label: fig-two
+##| label: fig-two
 #| fig-cap: "This table highlights the age distribution of survey respondents in 2018 and 2021."
@@
 #### Individual 2018
-@fig-three shows the distribution of respondents by their highest level of education attained in 2018.
+fig-three shows the distribution of respondents by their highest level of education attained in 2018.
 The most common education levels are "Completed undergraduate degree" and "Postgraduate/professional school," indicating a well-educated respondent population.
@@
 #| message: false
-#| label: fig-three
+##| label: fig-three
 #| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."
@@
 #### Comparison 2018 to 2021
-@fig-four compares the education levels of respondents in 2018 and 2021.
+fig-four compares the education levels of respondents in 2018 and 2021.
 The two surveys used different education categories, making direct comparisons challenging.
@@
 #| message: false
-#| label: fig-four
-#| fig-cap: This table highlights the education distribution of survey respondents in 2018 and 2021."
+##| label: fig-four
+#| fig-cap: "This table highlights the education distribution of survey respondents in 2018 and 2021."
 
@@
 #### Individual 2018
-@fig-five depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
+fig-five depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
 The majority of participants identified as "Very informed," making this the most prevalent category by a significant margin.
@@
 #| message: false
-#| label: fig-five
-#| fig-cap: The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents.
+##| label: fig-five
+#| fig-cap: "The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents."
 
@@
 #### Comparison 2018 to 2021
-@fig-six illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
+fig-six illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
 In 2018, the large marjority of individuals say they are very informed with 60 percent and the follwoign category is not very informed with 27 percent.
@@
 #| message: false
-#| label: fig-six
+##| label: fig-six
 #| fig-cap: "This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021."
@@
 #### Individual 2018
-@fig-seven, shows 2018 survey results for the preferred method for receiving climate change information.
+fig-seven, shows 2018 survey results for the preferred method for receiving climate change information.
 Advertising campaigns emerged as the most popular choice, selected by approximately 55 percent of respondents, followed closely by newsletters with 52 percent and the Toronto.ca website with 46 percent.
@@
 #| message: false
-#| label: fig-seven
-#| fig-cap: The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action.
+##| label: fig-seven
+#| fig-cap: "The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action."
 
@@
 #### Comparison 2018 to 2021
-@fig-eight compares the preferred methods of delivering climate change information between the 2018 and 2021 surveys.
+fig-eight compares the preferred methods of delivering climate change information between the 2018 and 2021 surveys.
 While the top three methods namely advertising campaigns, newsletters, and the Toronto.ca website remained consistent across both years, there were notable shifts in preferences.
@@
 #| message: false
-#| label: fig-eight
+##| label: fig-eight
 #| fig-cap: "This table highlights the prefered method of communication of survey respondents in 2018 and 2021."
@@
 ```
+
 ### Likelihood Taking Action 
-@fig-nine illustrates the self-reported likelihood of individuals taking various actions to minimize environmental impacts.
+fig-nine illustrates the self-reported likelihood of individuals taking various actions to minimize environmental impacts.
 The x-axis displays nine different climate actions, while the y-axis represents the percentage of individuals corresponding to each likelihood level.
@@
 #| message: false
-#| label: fig-nine
-#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.
+##| label: fig-nine
+#| fig-cap: "The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change."
 
@@
 #### Likelihood of switching to an electric or hybrid vehicle
-@fig-ten reveals that education is the primary predictor for the likelihood of switching to an electric or hybrid vehicle.
+fig-ten reveals that education is the primary predictor for the likelihood of switching to an electric or hybrid vehicle.
 Individuals with "Some Community/Trade School" or "Some University" education are "Very likely" to invest, though with moderate variability (error rate 63.8%).
@@
 #| message: false
-#| label: fig-ten
-#| fig-cap: Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education.
+##| label: fig-ten
+#| fig-cap: "Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education."
 
@@
 #### Likelihood of minimizing car use
-@fig-eleven shows that the likelihood of minimizing car use is consistent across the sample, with a high error rate (61.9%).
+fig-eleven shows that the likelihood of minimizing car use is consistent across the sample, with a high error rate (61.9%).
 The model classifies all individuals into the "Already doing this or have done this" category, indicating widespread adoption of this behavior, regardless of age or education
@@
 #| message: false
-#| label: fig-eleven
-#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.
+##| label: fig-eleven
+#| fig-cap: "Probability tree for likelihood of minimizing car use, predicted by age and education."
 
@@
 #### Likelihood of walking or cycling shorter distances
-@fig-twelve indicates that education is the primary factor influencing short-distance walking or cycling.
+fig-twelve indicates that education is the primary factor influencing short-distance walking or cycling.
 Those with higher education (postgraduate, undergraduate, or some university) are more likely to engage in this behavior, with an error rate of 51.9%.
@@
 #| message: false
-#| label: fig-twelve
-#| fig-cap: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
+##| label: fig-twelve
+#| fig-cap: "Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education."
 
@@
 #### Likelihood of purchasing green products
-@fig-thirteen reveals that age is the initial split for green product purchasing behavior.
+fig-thirteen reveals that age is the initial split for green product purchasing behavior.
 Younger individuals (under 38 years) are more likely to purchase green products, with an error rate of 51.9%.
@@
 #| message: false
-#| label: fig-thirteen
-#| fig-cap: Probability tree for likelihood of purchasing green products, predicted by age and education.
+##| label: fig-thirteen
+#| fig-cap: "Probability tree for likelihood of purchasing green products, predicted by age and education."
 
@@
 #### Likelihood of reducing waste by repurposing used product
-@fig-fourteen shows that age is the primary factor for waste reduction behaviors.
+fig-fourteen shows that age is the primary factor for waste reduction behaviors.
 Younger individuals (under 35 years) are more likely to repurpose waste, with an error rate of 57.1%.
@@
 #| message: false
-#| label: fig-fourteen
-#| fig-cap: Probability tree for likelihood of reducing waste, predicted by age and education.
+##| label: fig-fourteen
+#| fig-cap: "Probability tree for likelihood of reducing waste, predicted by age and education."
 
@@
 #### Likelihood of sorting waste correctly
-@fig-fifteen identifies education as the primary factor for sorting waste.
+fig-fifteen identifies education as the primary factor for sorting waste.
 Those with higher education (at least community/trade school or postgraduate) are more likely to sort waste correctly, with an error rate of 37.3%.
@@
 #| message: false
-#| label: fig-fifteen
-#| fig-cap: Probability tree for likelihood of sorting waste correctly, predicted by age and education.
+##| label: fig-fifteen
+#| fig-cap: "Probability tree for likelihood of sorting waste correctly, predicted by age and education."
 
@@
 #### Likelihood of making home improvements
-@fig-sixteen shows that age is the key predictor for home improvement behavior.
+fig-sixteen shows that age is the key predictor for home improvement behavior.
 Individuals aged 36 years and older are predominantly classified as "Already doing this or have done this," with an error rate of 59.6%.
@@
 #| message: false
-#| label: fig-sixteen
-#| fig-cap: Probability tree for likelihood of making home improvements predicted by age and education.
+##| label: fig-sixteen
+#| fig-cap: "Probability tree for likelihood of making home improvements predicted by age and education."
 
@@
 #### Likelihood of adopting meat alternatives
-@fig-seventeen demonstrates that age is the primary factor for adopting meat alternatives.
+fig-seventeen demonstrates that age is the primary factor for adopting meat alternatives.
 Younger individuals (under 35 years) are more likely to adopt meat alternatives, with an error rate of 44%.
@@
 #| message: false
-#| label: fig-seventeen
-#| fig-cap: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
+##| label: fig-seventeen
+#| fig-cap: "Probability tree for likelihood of adopting meat alternatives, predicted by age and education."
 
@@
 #### Likelihood of reducing hydro usage
-@fig-eighteen reveals that age is the primary predictor influencing hydro usage reduction.
+fig-eighteen reveals that age is the primary predictor influencing hydro usage reduction.
 Younger individuals (under 35 years) are "Very likely" to reduce hydro usage, with an error rate of 60.9%.
@@
 #| message: false
-#| label: fig-eighteen
-#| fig-cap: Probability tree for likelihood of reducing hydro usage, predicted by age and education.
+##| label: fig-eighteen
+#| fig-cap: "Probability tree for likelihood of reducing hydro usage, predicted by age and education."
 
@@
 #| message: false
-#| results: hide
-# #| label: fig-nineteen
-#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
+#| results: asis
+##| label: fig-nineteen
+#| fig-cap: "This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education."
 
@@
 # Check data to ensure it loaded and rounded correctly
-print(model_accuracies)
+#print(model_accuracies)
+
+# Render the table
+knitr::kable(model_accuracies, format = "latex", booktabs = TRUE)
 
@@
 ## Likelihood taking action by age
-@fig-twenty shows the relationship between age and the likelihood of engaging in various climate-related actions.
+fig-twenty shows the relationship between age and the likelihood of engaging in various climate-related actions.
 The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely".
@@
 #| message: false
-#| label: fig-twenty
-#| fig-cap: Likelihood of Taking Climate Change Actions by Age Group.
-The stacked bar chart illustrates the percentage of respondents across six age groups (15-24, 25-34, 35-44, 45-54, 55-64, 65+) in terms of their self-reported likelihood to engage in nine distinct climate-related actions.
-Each color represents a different level of likelihood, from "Already doing this or have done this" to "Very unlikely." The black dashed trend line highlights how the likelihood of action changes across age groups, providing insights into generational differences in climate-related behavior.
+##| label: fig-twenty
+#| fig-cap: "Likelihood of Taking Climate Change Actions by Age Group."
 
@@
 ## Likelihood taking action by education 
-@fig-twenty-one displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
+fig-twenty-one displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
 The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from low to high educational attainment.
@@
 #| message: false
-#| label: fig-twenty-one
+##| label: fig-twenty-one
+#| fig-cap: "Likelihood of Taking Climate Change Actions by Education Level."
 
@@
 ## What We Learn About the World
-## Age and Climate-Friendly Behaviors {#sec-first-point}
+## Age and Climate-Friendly Behaviors
 Initially, we anticipated that younger individuals would lead the way in adopting climate-friendly actions.
@@
 
-## The Role of Education in Sustainable Actions {#sec-second-point}
+## The Role of Education in Sustainable Actions
 We initially hypothesized that higher education levels would lead to greater engagement in climate-friendly behaviors, and the data largely supported this.
@@
 
-## The Influence of Climate Change Knowledge {#sec-third-point}
+## The Influence of Climate Change Knowledge
 To effectively encourage individuals to take climate action, it's crucial to consider the most popular and impactful methods of communication.
@@
 
-# Idealized methodology {#sec-idealized-meth}
+# Idealized methodology 
 ## Survey objectives

### 2024-12-14 paper/climate_change.qmd
edit YAML

@@
     number_sections: true
-    toc_depth: 2   # Optional: to control how deep the TOC goes (e.g., section and subsection)
 bibliography: references.bib

### 2024-12-14 paper/climate_change.qmd
nice rending in data section

@@
 
-The remainder of this paper is structured as follows: @sec-data describes the data and methodology used for analysis, @sec-model outlines the statistical model used to assess the effects of age and education on behavior adoption, @sec-results presents the key findings, and @sec-discussion explores the implications of these results, addresses limitations, and suggests directions for future research.
-Finally, @sec-conclusion summarizes the main takeaways and offers recommendations for enhancing climate action engagement.
-Additional methodological details and the data cleaning process are provided in @sec-appendix.
+The remainder of this paper is structured as follows: The `data section` describes the data and methodology used for analysis, the `model section` outlines the statistical model used to assess the effects of age and education on behavior adoption, the `results section` presents the key findings, and teh `discussion section` explores the implications of these results, addresses limitations, and suggests directions for future research.
+Finally, the `conclusion section` summarizes the main takeaways and offers recommendations for enhancing climate action engagement.
+Additional methodological details and the data cleaning process are provided in the `appendix section`.
 
-# Data {#sec-data}
+# Data 
 The primary data source for this project is the Climate Perception Study dataset, provided by the City of Toronto via the Open Data Toronto platform [@climateperceptionstudy].
@@
 
-In the download script, `httr`[@httr] retrieved files from `Open Data Toronto` [@opendatatoronto], while`readxl` [@readxl] read Excel files, and `openxlsx` [@openxlsx] created structured Excel workbooks.
+In the download script, `httr` [@httr] retrieved files from `Open Data Toronto` [@opendatatoronto], while `readxl` [@readxl] read Excel files, and `openxlsx` [@openxlsx] created structured Excel workbooks.
 The `arrow` package [@arrow] optimized data storage and was used in the simulation and cleaning scripts to save datasets as Parquet files.
@@
 #### Individual 2018
-fig-one presents the age distribution of survey respondents in 2018.
+Figure 1 presents the age distribution of survey respondents in 2018.
 The histogram shows the frequency of respondents across age groups, with age intervals on the x-axis and the number of respondents on the y-axis.
@@
 #| message: false
-##| label: fig-one
 #| fig-cap: "Distribution of age given the 2018 survey respondents. The mean and median of the sample is indicated with dashed and dotted lines respectively."
@@
 ```
+
 \newpage
@@
 #### Comparison 2018 to 2021
-fig-two compares the age distributions between 2018 and 2021.
+Table 1 compares the age distributions between 2018 and 2021.
 The main difference is an increase in respondents aged 18-23 in 2021, with other age groups remaining relatively stable.
@@
 #| message: false
-##| label: fig-two
-#| fig-cap: "This table highlights the age distribution of survey respondents in 2018 and 2021."
+#| fig-pos: "H"  # Force figure placement here
 
@@
 
-# Print the cleaned table (using kable for styling)
+# Render the table with a manually added caption
 age_summary_combined %>%
-  kbl() %>%
+  kbl(caption = "This table highlights the age distribution of survey respondents in 2018 and 2021.") %>%
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
@@
 #### Individual 2018
-fig-three shows the distribution of respondents by their highest level of education attained in 2018.
+@fig-educ shows the distribution of respondents by their highest level of education attained in 2018.
 The most common education levels are "Completed undergraduate degree" and "Postgraduate/professional school," indicating a well-educated respondent population.
@@
 #| message: false
-##| label: fig-three
+#| label: fig-educ
 #| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."
@@
 knitr::include_graphics(here("data/03-figures_data", "educ_individual_plot.png"))
-
 ```
 
+\newpage
+
 #### Comparison 2018 to 2021
-fig-four compares the education levels of respondents in 2018 and 2021.
+Table 2 compares the education levels of respondents in 2018 and 2021.
 The two surveys used different education categories, making direct comparisons challenging.
@@
 #| message: false
-##| label: fig-four
-#| fig-cap: "This table highlights the education distribution of survey respondents in 2018 and 2021."
+#| fig-cap: "Table 2: This table highlights the education distribution of survey respondents in 2018 and 2021."
 
@@
 library(tinytable)
+library(kableExtra)
+library(here)
 
@@
 
-# Convert the data frame to tinytable
-education_summary_combined_tiny <- tt(education_summary_combined)
+# Render the table with adjusted font size and column width
+education_summary_combined %>%
+  kable() %>%
+  kable_styling(full_width = TRUE, position = "center") %>%
+  column_spec(1, width = "10em") %>%
+  column_spec(3, width = "10em") %>%
+  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
+  # Add resizebox to scale the table down to fit within the page
+  row_spec(0, bold = TRUE) %>%
+  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE)
 
 # Print the tinytable
-education_summary_combined_tiny
+#education_summary_combined
 
@@
 #### Individual 2018
-fig-five depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
+Figure 3 depicts the distribution of self-reported climate change knowledge among survey respondents in 2018.
 The majority of participants identified as "Very informed," making this the most prevalent category by a significant margin.
@@
 #| message: false
-##| label: fig-five
-#| fig-cap: "The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents."
 
@@
 #### Comparison 2018 to 2021
-fig-six illustrates the self-reported level of extent inviduals feel informed about climate change and climate action for 2018 and 2021.
-In 2018, the large marjority of individuals say they are very informed with 60 percent and the follwoign category is not very informed with 27 percent.
-In 2021, The majority of inividuals also say they are very informed but to a lesser degree with 48 percent and this is closely followed by only a little informed with 37 percent.
-There is a trend that invidiusls in 2018 reported greater levels of knowldege about climate change whereas 2021 illstrates a more even split between very informed and only little informed, portraying that fewer individuals have adequate knowledge about climate change.
+Table 3 illustrates the self-reported level of extent individuals feel informed about climate change and climate action for 2018 and 2021.
+In 2018, the large majority of individuals say they are very informed with 60 percent and the following category is not very informed with 27 percent.
+In 2021, The majority of individuals also say they are very informed but to a lesser degree with 48 percent and this is closely followed by only a little informed with 37 percent.
+There is a trend that individuals in 2018 reported greater levels of knowledge about climate change whereas 2021 illustrates a more even split between very informed and only little informed, portraying that fewer individuals have adequate knowledge about climate change.
 
@@
 #| message: false
-##| label: fig-six
-#| fig-cap: "This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021."
 
@@
 informed_summary_combined %>%
-  kbl() %>%
+  kbl(caption = "This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021") %>%
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
@@
 
+\newpage
+
 ### Best Method of Delivery
 #### Individual 2018
-fig-seven, shows 2018 survey results for the preferred method for receiving climate change information.
+Figure 4 shows 2018 survey results for the preferred method for receiving climate change information.
 Advertising campaigns emerged as the most popular choice, selected by approximately 55 percent of respondents, followed closely by newsletters with 52 percent and the Toronto.ca website with 46 percent.

### 2024-12-14 scripts/05-exploratory_data_analysis.R

@@ -28,6 +28,7 @@ individual_18 <- read_parquet(here("data/02-analysis_data/twenty_eighteen_indivi
 # Calculate mean and median of age
 mean_age <- mean(individual_18$age, na.rm = TRUE)
 median_age <- median(individual_18$age, na.rm = TRUE)
+
 # Create a histogram to show the distribution of age with mean and median lines
 age_individual_plot <- ggplot(individual_18, aes(x = age)) + 
   geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) + 
@@ -37,9 +38,8 @@ age_individual_plot <- ggplot(individual_18, aes(x = age)) +
              show.legend = TRUE) +  # Median line
   labs(
     title = "Age Distribution of Survey Respondents (2018)",
-    x = "Age",
-    y = "Frequency",
-    caption = "Blue dashed line = Mean | Green dotted line = Median"  # Legend explanation
+    x = "Age (years)",
+    y = "Frequency"
   ) + 
   theme_minimal() +
   scale_x_continuous(
@@ -53,7 +53,7 @@ print(age_individual_plot)
 ggsave(
   filename = here("data/03-figures_data", "age_individual_plot.png"),  # Specify the correct path and filename
   plot = age_individual_plot,
-  width = 6, height = 4
+  width = 5, height = 2.5
 )
 
 
@@ -106,7 +106,7 @@ print(educ_individual_plot)
 ggsave(
   filename = here("data/03-figures_data", "educ_individual_plot.png"),  # Saving as a PNG file
   plot = educ_individual_plot,
-  width = 6, height = 4
+  width = 5, height = 3.5
 )
 
 
@@ -120,13 +120,15 @@ informed_18_plot <- individual_18 %>%
                                                       "Very informed", 
                                                       "Not very informed", 
                                                       "Not at all informed")))
+
 # Create the plot with adjusted y-axis range
 informed_18_plot <- ggplot(informed_18_plot, aes(x = extent_consider_informed, fill = extent_consider_informed)) +
   geom_bar(color = "black", alpha = 0.7) + 
   labs(
-    title = "Distribution of Self-Reported Climate Change Knowledge (2018)",
+    title = "Distribution of Self-Reported Climate Change Knowledge",
     x = "Extent Informed about Climate Change",
-    y = "Frequency"
+    y = "Frequency",
[…]

### 2024-12-15 paper/climate_change.qmd
slight adjustments for rendering

@@
 #### Individual 2018
-@fig-educ shows the distribution of respondents by their highest level of education attained in 2018.
+Figure 2 shows the distribution of respondents by their highest level of education attained in 2018.
 The most common education levels are "Completed undergraduate degree" and "Postgraduate/professional school," indicating a well-educated respondent population.
@@
 #| message: false
-#| label: fig-educ
-#| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."
 
@@
 ```
+
+Figure 3: The histogram shows the distribution of self-reported climate change knowledge among 2018 survey respondents.
+This distribution provides insights into public awareness and the extent to which individuals feel informed about climate change.
+
 #### Comparison 2018 to 2021
@@
 There is a trend that individuals in 2018 reported greater levels of knowledge about climate change whereas 2021 illustrates a more even split between very informed and only little informed, portraying that fewer individuals have adequate knowledge about climate change.
+
+Table 3: This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021.
 
@@
 informed_summary_combined %>%
-  kbl(caption = "This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021") %>%
+  kbl() %>%
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
@@
 ```
-
-\newpage
 
@@
 #### Comparison 2018 to 2021
-fig-eight compares the preferred methods of delivering climate change information between the 2018 and 2021 surveys.
+Table 4 compares the preferred methods of delivering climate change information between the 2018 and 2021 surveys.
 While the top three methods namely advertising campaigns, newsletters, and the Toronto.ca website remained consistent across both years, there were notable shifts in preferences.
@@
 #| message: false
-##| label: fig-eight
-#| fig-cap: "This table highlights the prefered method of communication of survey respondents in 2018 and 2021."
 
@@
 communication_summary_combined %>%
-  kbl() %>%
+  kbl(caption = "This table illustrates the prefered method of communication of survey respondents in 2018 and 2021") %>%
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
@@
 
+\newpage
+
 ### Likelihood Taking Action 
-fig-nine illustrates the self-reported likelihood of individuals taking various actions to minimize environmental impacts.
+Figure 5 illustrates the self-reported likelihood of individuals taking various actions to minimize environmental impacts.
 The x-axis displays nine different climate actions, while the y-axis represents the percentage of individuals corresponding to each likelihood level.
@@
 #| message: false
-##| label: fig-nine
-#| fig-cap: "The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change."
 
@@
 #### Likelihood of switching to an electric or hybrid vehicle
-fig-ten reveals that education is the primary predictor for the likelihood of switching to an electric or hybrid vehicle.
+Figure 6 reveals that education is the primary predictor for the likelihood of switching to an electric or hybrid vehicle.
 Individuals with "Some Community/Trade School" or "Some University" education are "Very likely" to invest, though with moderate variability (error rate 63.8%).
@@
 #| message: false
-##| label: fig-ten
-#| fig-cap: "Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 6: Probability tree for likelihood of investing in an electric or hybrid vehicle, predicted by age and education
+
 #### Likelihood of minimizing car use
-fig-eleven shows that the likelihood of minimizing car use is consistent across the sample, with a high error rate (61.9%).
+Figure `7` shows that the likelihood of minimizing car use is consistent across the sample, with a high error rate (61.9%).
 The model classifies all individuals into the "Already doing this or have done this" category, indicating widespread adoption of this behavior, regardless of age or education
@@
 #| message: false
-##| label: fig-eleven
-#| fig-cap: "Probability tree for likelihood of minimizing car use, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 7: Probability tree for likelihood of minimizing car use, predicted by age and education.
+
 #### Likelihood of walking or cycling shorter distances
-fig-twelve indicates that education is the primary factor influencing short-distance walking or cycling.
+Figure `8` indicates that education is the primary factor influencing short-distance walking or cycling.
 Those with higher education (postgraduate, undergraduate, or some university) are more likely to engage in this behavior, with an error rate of 51.9%.
@@
 #| message: false
-##| label: fig-twelve
-#| fig-cap: "Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 ```
+Figure 8: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
 
@@
 #### Likelihood of purchasing green products
-fig-thirteen reveals that age is the initial split for green product purchasing behavior.
+Figure `9` reveals that age is the initial split for green product purchasing behavior.
 Younger individuals (under 38 years) are more likely to purchase green products, with an error rate of 51.9%.
@@
 #| message: false
-##| label: fig-thirteen
-#| fig-cap: "Probability tree for likelihood of purchasing green products, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+FIgure 9: Probability tree for likelihood of purchasing green products, predicted by age and education
+
 #### Likelihood of reducing waste by repurposing used product
-fig-fourteen shows that age is the primary factor for waste reduction behaviors.
+Figure `10` shows that age is the primary factor for waste reduction behaviors.
 Younger individuals (under 35 years) are more likely to repurpose waste, with an error rate of 57.1%.
@@
 #| message: false
-##| label: fig-fourteen
-#| fig-cap: "Probability tree for likelihood of reducing waste, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 10: Probability tree for likelihood of reducing waste, predicted by age and education.
+
 #### Likelihood of sorting waste correctly
-fig-fifteen identifies education as the primary factor for sorting waste.
+Figure `11` identifies education as the primary factor for sorting waste.
 Those with higher education (at least community/trade school or postgraduate) are more likely to sort waste correctly, with an error rate of 37.3%.
@@
 #| message: false
-##| label: fig-fifteen
-#| fig-cap: "Probability tree for likelihood of sorting waste correctly, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 11: Probability tree for likelihood of sorting waste correctly, predicted by age and education
+
 ### Home and Lifestyle Changes
 #### Likelihood of making home improvements
-fig-sixteen shows that age is the key predictor for home improvement behavior.
+Figure `12` shows that age is the key predictor for home improvement behavior.
 Individuals aged 36 years and older are predominantly classified as "Already doing this or have done this," with an error rate of 59.6%.
@@
 #| message: false
-##| label: fig-sixteen
-#| fig-cap: "Probability tree for likelihood of making home improvements predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 12: Probability tree for likelihood of making home improvements predicted by age and education.
+
 #### Likelihood of adopting meat alternatives
-fig-seventeen demonstrates that age is the primary factor for adopting meat alternatives.
+Figure `13` demonstrates that age is the primary factor for adopting meat alternatives.
 Younger individuals (under 35 years) are more likely to adopt meat alternatives, with an error rate of 44%.
@@
 #| message: false
-##| label: fig-seventeen
-#| fig-cap: "Probability tree for likelihood of adopting meat alternatives, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 13: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
+
 #### Likelihood of reducing hydro usage
-fig-eighteen reveals that age is the primary predictor influencing hydro usage reduction.
+Figure `14` reveals that age is the primary predictor influencing hydro usage reduction.
 Younger individuals (under 35 years) are "Very likely" to reduce hydro usage, with an error rate of 60.9%.
@@
 #| message: false
-##| label: fig-eighteen
-#| fig-cap: "Probability tree for likelihood of reducing hydro usage, predicted by age and education."
+#| out.width: "100%"
+#| out.height: "auto"  # Maintain aspect ratio
 
@@
 
+Figure 14: Probability tree for likelihood of reducing hydro usage, predicted by age and education.
+
 # Results {#sec-results}
@@
 ## Model Summary Table
-fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education.
+Table `5` presents the accuracy of models predicting climate-friendly actions based on age and education.
 A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation.
@@
 #| results: asis
-##| label: fig-nineteen
-#| fig-cap: "This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education."
+#| fig-cap: "Table 5: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education."
 
@@
 ## Likelihood taking action by age
-fig-twenty shows the relationship between age and the likelihood of engaging in various climate-related actions.
+Figure `15` shows the relationship between age and the likelihood of engaging in various climate-related actions.
 The x-axis represents the age groups, and the y-axis indicates the percentage of respondents reporting different likelihood levels, from "Already doing this" to "Very unlikely".
@@
 Conversely, older individuals, especially those aged 65+, are more likely to report being "very unlikely" to engage in walking or cycling for short distances.
+
+\newpage
 
@@
 #| message: false
-##| label: fig-twenty
-#| fig-cap: "Likelihood of Taking Climate Change Actions by Age Group."
+#| out.width: "200%"
+#| out.height: "auto"
 
@@
 
+Figure 15: The facet of stacked bar charts allows for comparison of which climate-friendly actions are most practiced amongts different age categories.
+
 ## Likelihood taking action by education 
-fig-twenty-one displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
+Figure `16` displays how the likelihood of engaging in climate-friendly actions varies by educational attainment.
 The x-axis represents the proportion of respondents in each education category, while the y-axis lists the educational levels, from low to high educational attainment.
@@
 #| message: false
-##| label: fig-twenty-one
-#| fig-cap: "Likelihood of Taking Climate Change Actions by Education Level."
+#| out.width: "200%"
+#| out.height: "auto"
 
@@
 ```
+
+Figure 16: The facet of stacked bar charts allows for comparison of which climate-friendly actions are most practiced amongts different education attainments.
 

### 2024-12-15 scripts/05-exploratory_data_analysis.R

@@ -76,7 +76,8 @@ educ_individual_plot <- ggplot(individual_18, aes(x = highest_level_educ, fill =
   labs(
     title = "Education Distribution of Survey Respondents (2018)",
     x = "Education Level",
-    y = "Frequency"
+    y = "Frequency",
+    caption = "Figure 2: The histogram shows the distribution of education levels of 2018 survey respondents."
   ) + 
   theme_minimal() +
   scale_x_discrete(
@@ -106,7 +107,7 @@ print(educ_individual_plot)
 ggsave(
   filename = here("data/03-figures_data", "educ_individual_plot.png"),  # Saving as a PNG file
   plot = educ_individual_plot,
-  width = 5, height = 3.5
+  width = 6, height = 4
 )
 
 
@@ -127,8 +128,7 @@ informed_18_plot <- ggplot(informed_18_plot, aes(x = extent_consider_informed, f
   labs(
     title = "Distribution of Self-Reported Climate Change Knowledge",
     x = "Extent Informed about Climate Change",
-    y = "Frequency",
-    caption = "Figure 3: The histogram shows the distribution of self-reported climate change knowledge\namong 2018 survey respondents. This distribution provides insights into public awareness\nand the extent to which individuals feel informed about climate change."
+    y = "Frequency"
   ) + 
   theme_minimal() +
   scale_x_discrete(
@@ -186,6 +186,7 @@ likelihood_data <- individual_18 %>%
                                         "Somewhat likely", 
                                         "Somewhat unlikely", 
                                         "Very unlikely")))
+
 # Calculate percentages
 likelihood_18_plot_percent <- likelihood_data %>%
   group_by(action, likelihood) %>%
@@ -196,28 +197,48 @@ likelihood_18_plot_percent <- likelihood_data %>%
 # Create the likelihood plot
 likelihood_18_plot <- ggplot(likelihood_18_plot_percent, aes(x = action, fill = likelihood, y = percentage)) +
   geom_bar(stat = "identity", position = "stack") +
-  labs(title = "Likelihood of Taking Climate Change Actions",
-       x = "Actions", y = "Percentage", fill = "Likelihood") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_fill_manual(
-    values = c("Already doing this or have done this" = "forestgreen", 
[…]

### 2024-12-15 scripts/06-model_data.R

@@ -51,10 +51,10 @@ generate_model <- function(target_var, train_data, test_data, model_name) {
   png_file_path <- file.path(here::here("models/"), paste0(model_name, "_tree.png"))
   
   # Adjust PNG size to avoid cutting off the tree
-  png(png_file_path, width = 3200, height = 1500, res = 150)  # Increase size and resolution
+  png(png_file_path, width = 4800, height = 2400, res = 300)  # Larger size and higher resolution
   
   # Plot the decision tree and save the plot as a .png
-  plot(as.party(tree), gp = gpar(cex = 1), type = "simple")
+  plot(as.party(tree), gp = gpar(cex = 1.5), type = "simple")  # Adjust font size for better visibility
   
   # Close the device after saving the plot
   dev.off()
@@ -69,6 +69,7 @@ generate_model <- function(target_var, train_data, test_data, model_name) {
   accuracy <- sum(diag(confusion_matrix)) / sum(confusion_matrix) * 100
   return(accuracy)
 }
+
 
 #### Loop to create models for different target variables ####
 # Create a data frame to store the model names and their corresponding accuracies
@@ -121,4 +122,5 @@ print(model_results)
 
 # Save the results as a CSV in the correct location
 write_csv(model_results, here::here("models/model_accuracies.csv"))
+
 

### 2024-12-15 paper/climate_change.qmd
final touches rending

@@
 
-\newpage
-
 #### Comparison 2018 to 2021
@@
 This suggests that the 2021 survey may have captured a broader range of educational backgrounds, providing a more well-rounded representation of Toronto’s population.
+
+\newpage
 
@@
 
+\newpage
+
 Table 3: This table highlights the extent feel informed distribution of survey respondents in 2018 and 2021.
@@
 #| message: false
-##| label: fig-seven
-#| fig-cap: "The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action."
 
@@
 ```
+
+Figure 4: The stacked bar plot illustrates the preferred methods of communication for receiving information about climate change and climate action.
 
@@
 communication_summary_combined %>%
-  kbl(caption = "This table illustrates the prefered method of communication of survey respondents in 2018 and 2021") %>%
+  kbl() %>%
   kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
@@
 
-\newpage
+Table 4: This table illustrates the preferred method of communication of survey respondents in 2018 and 2021
 
@@
 
+\newpage
+
 #### Likelihood of walking or cycling shorter distances
@@
 Figure 8: Probability tree for likelihood of walking or cycling shorter distances, predicted by age and education.
+
+\newpage
 
@@
 
-FIgure 9: Probability tree for likelihood of purchasing green products, predicted by age and education
+Figure 9: Probability tree for likelihood of purchasing green products, predicted by age and education
+
+\newpage
 
@@
 
+\newpage
+
 #### Likelihood of sorting waste correctly
@@
 Figure 11: Probability tree for likelihood of sorting waste correctly, predicted by age and education
+
+\newpage
 
@@
 
+\newpage
+
 #### Likelihood of adopting meat alternatives
@@
 Figure 13: Probability tree for likelihood of adopting meat alternatives, predicted by age and education.
+
+\newpage
 
@@
 #| message: false
-#| out.width: "200%"
+#| out.width: "100%"
 #| out.height: "auto"
@@
 ## What We Learn About the World
-## Age and Climate-Friendly Behaviors
+### Age and Climate-Friendly Behaviors
 Initially, we anticipated that younger individuals would lead the way in adopting climate-friendly actions.
@@
 
-## The Role of Education in Sustainable Actions
+### The Role of Education in Sustainable Actions
 We initially hypothesized that higher education levels would lead to greater engagement in climate-friendly behaviors, and the data largely supported this.
@@
 
-## The Influence of Climate Change Knowledge
+### The Influence of Climate Change Knowledge
 To effectively encourage individuals to take climate action, it's crucial to consider the most popular and impactful methods of communication.
@@
 
-# Weighting and Data adjustments
+## Weighting and Data adjustments
 The data collected will be weighted to account for any imbalances in demographic representation within the sample.
@@
 Correspondence will not be shared with any external parties.
+
 -    I consent.
 
-**Demographic Information: **
-1. Whats your age? 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, 65+, Prefer not to say
+**Demographic Information:**
+
+1. What's your age? 12-17, 18-24, 25-34, 35-44, 45-54, 55-64, 65+, Prefer not to say
+
 2.
 What is the highest level of education that you've completed?
-Some high school, High school diploma, Diploma / post secondary certificate (college, trade school).
-Bachelor's degree, Master's degree, Doctorate degree.
+Some high school, High school diploma, Diploma / post-secondary certificate (college, trade school), Bachelor's degree, Master's degree, Doctorate degree.
 
 **Climate Change knowledge and Awareness:**
+
 3. How would you rate your knowledge of the causes of climate change? Very informed, Somewhat informed, Neutral, Somewhat Uninformed, Very uninformed.
+
 4. How confident are you in your understanding of how to mitigate climate change through individual actions? Very confident, Confident, Neutral, Somewhat confident, Not confident.
@@
 **Climate-Friendly Action: **
+
 5.
@@
 Reduce personal vehicle use (e.g., carpooling, using public transport, biking or walking shorter distances), Use / install energy-efficient appliances / devices (e.g., LED bulbs, smart thermostats), Eat a plant-based diet or reduce meat consumption, Recycle and compost, Purchase eco-friendly products (e.g., sustainable clothing, eco-conscious brands), Use renewable energy sources (e.g., solar panels, wind energy), None of the above, Other.
+
 6. How often do you consider the environmental impact of your purchases? Always, Often, Sometimes, Rarely, Never
@@
 **Barriers to Sustainable Actions: **
+
 7.
@@
 (Select all that apply) Cost of sustainable products or services, Lack of time, Lack of knowledge about how to make sustainable choices, Convenience (e.g., environmentally harmful options are more accessible), Skepticism about the effectiveness of individual actions, No barriers (I already engage in sustainable behaviors), Other (please specify)
+
 8. Do you feel that climate-friendly behaviors are affordable for people in your community? Yes, No, Not sure
+
 9.
@@
 (Select all that apply) I do not believe my individual actions will make a difference, I find it too difficult to make sustainable choices in my daily life, It is too expensive to adopt sustainable behaviors, I don’t know where to start or how to make a meaningful impact, Sustainable products or services are not easily available in my area, I do not feel that climate change directly affects me or my community, I am unsure about what actions are most effective in reducing climate change, I am not sure how to balance sustainable actions with my current lifestyle
+
 10.
@@
 (Select up to three) Lower cost of sustainable products or services, More convenient access to sustainable options, Clearer information on how individual actions can make a difference, More education or awareness about climate change, Incentives (e.g., government subsidies, rewards) to take action, More social pressure or norms encouraging sustainable behavior, Other (please specify)
+
 11.
@@
 Government, Environmental NGOs, Local community organizations, Media (TV, online news), Social media influencers/bloggers, Scientists, I do not trust any of these sources
+
 12.
@@
 Yes, No, Not sure
+
 13. How strongly do you agree with the following statement: "Taking climate-friendly actions is a personal responsibility." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
+
 14.
 How strongly do you agree with the following statement: "The government or businesses should take more responsibility for addressing climate change than individuals." Strongly disagree, Disagree, Neutral, Agree, Strongly agree
+
 15.
@@
 **Education and Information: **
+
 16. How effective do you think current school programs are in educating students about climate change? Very ineffective, Somewhat ineffective, Neutral, Somewhat effective, Very effective
+
 17.
@@
 **General Perception: **
+
 18. Do you believe that individual actions can make a significant difference in combating climate change? Yes, No, Not sure
@@
 
-## Simlation Process {sec-simulation-process}
+## Simlation Process
 For the purposes of this study, I simulated data to investigate various factors related to climate change behaviors, including demographics, education levels, awareness of climate change causes, and preferences for communication methods.
@@
 
-## Data cleaning {#sec-data-cleaning}
+## Data cleaning
 

### 2024-12-15 scripts/05-exploratory_data_analysis.R

@@ -304,8 +304,7 @@ communication_18_plot <- ggplot(data_summary, aes(x = reorder(delivery_method, p
     title = "Preferred Methods of Communication for Climate Change and Climate Action Information",
     x = "Delivery Method",
     y = "Percentage of Responses",
-    fill = "Delivery Method",
-    caption = "Figure 4: The stacked bar plot illustrates the preferred methods of communication for receiving\ninformation about climate change and climate action."
+    fill = "Delivery Method"
   ) +
   theme_minimal() +
   theme(

### 2024-12-15 other/datasheet/datasheet_template.qmd
update datasheet

@@
 ---
-title: "Datasheet for Climate Change Perspectives Dataset"
+title: "Datasheet for Climate Change Dataset"
 author: 
@@
 2. **How many instances are there in total (of each type, if appropriate)?**
-    - The dataset contains 500 instances, each corresponding to a single participant’s responses.
+    - The 2018 dataset contains 404 instances whereas the 2021 dataset contains 1400 instances, each corresponding to a single participant’s responses.
 
@@
 This does not include intentionally removed information, but might include, for example, redacted text.**
-    - There is some missing data for specific questions related to income, as some respondents chose not to provide this information.
+    - There is some missing data for specific questions related to education, as some respondents chose not to provide this information.
 
@@
 8. **Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.**
-    - The dataset is split into 80% training and 20% testing for machine learning tasks.
+    - It not known based on the dataset itsef howevery we split the data into 80% training and 20% testing for machine learning tasks (to generate the models).
 
 9. **Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.**
-    - There may be minor errors in the self-reported data, such as inconsistent responses or missing values.
+    - There are minor errors in the self-reported data, such as inconsistent responses. There is also instances where individuals did not respond such as stating their education level.
 
@@
 If so, please describe how these sub-populations are identified and provide a description of their respective distributions within the dataset.**
-    - Yes, the dataset identifies sub-populations by age, education level, and income group, with the following distributions: 30% aged 18-35, 40% aged 36-50, and 30% aged 51-65; education levels range from high school to postgraduate education.
+    - Yes, the dataset identifies sub-populations by age and education level.
+Age is split into 18-35, 36-50, 51-65 and 65+.
+Education levels range from high school to postgraduate education however the specific categories vary between the 2018 and 2021 survey.
 
@@
 How were these mechanisms or procedures validated?*
-    - The data was collected using an online survey platform.
-The survey was designed using Qualtrics and distributed via email and social media channels.
-The platform ensures that responses are stored securely and collected without bias.
+    - The 2018 survey data was collected through online interviews that lasted approximately ten minues.
+Quotas were set by region, age and gender ensuring sampling only those 18 years and older.
+The 2021 survey data was collected online and over the phone.
 
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-    - The dataset used a probabilistic sampling strategy with an oversampling of higher-education respondents to better capture differences in behavior based on education level.
+    - N/A
 
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-    - The data collection was managed by the researcher, with assistance from a small group of volunteers from local environmental organizations. No monetary compensation was provided.
+    - The data collection was managed by the researcher, the specifics are unknown.
 
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-    - Data was collected over a 2-month period, from May to June 2024. The data accurately reflects participants' attitudes and behaviors regarding climate action at that time.
+    - The 2018 survey data was collected between October 11 and October 18, 2018. The 2021 survey data does not specify the timeframe of collection.
 
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-    - Yes, the research was reviewed and approved by the University of Toronto’s Research Ethics Board (REB). Ethical approval documentation is available upon request.
+    - No, there is no mention of ethical review.
 
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-    - Yes, a data protection impact analysis was conducted.
-The analysis concluded that the data collection process adequately protected participants' privacy while enabling meaningful research outcomes.
+    - No, there is no mention of conduction of a data protection impact analysis.
 
 12. *Any other comments?*
-    - The ethical guidelines of the study ensured that the research process was transparent and respectful of participant privacy.
+    - N/A
 
@@
 If not, you may skip the remaining questions in this section.*
-    - The data was cleaned to remove duplicate entries and handle missing values for certain demographic questions. Missing values for income were imputed based on similar demographic profiles.
+    - The data was cleaned to keep missing values and rename variables more meaningful descriptions.
 
@@
 If so, please provide a link or other access point to the "raw" data.*
-    - Yes, the raw data has been saved in a separate file and can be accessed upon request.
+    - Yes, the raw data has been saved in a separate file and can be accessed in the download script.
 
@@
 4. *Any other comments?*
-    - The data cleaning process aimed to ensure that the dataset was as accurate and representative as possible, while maintaining participant confidentiality.
+    - N/A
 
@@
     - The dataset offers a rich resource for studying the intersection of demographics and climate behavior, with potential for comparative studies in other urban areas.
+
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
 	- N/A
+
 6. *Any other comments?*
@@
 If so, please provide a description.*
-	- Yes, the dataset may be distributed to third parties for academic research, policy analysis, or public service projects related to climate change behavior or urban studies.
-Distribution will be carefully managed to maintain privacy and confidentiality.
+	- No, the dataset will not be distributed to third parties unless requested for academic research, policy analysis, or public service projects related to climate change behavior.
+The dataset is however accessibly via GitHub.
+
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- The dataset will be distributed via GitHub and is accessible to anyone with the link.
-It will not have a DOI at this time, but plans for future DOI assignment are being considered for formal publication.
+	- The dataset would be distributed via GitHub and is accessible to anyone with the link.
+
 3. *When will the dataset be distributed?*
-	- The dataset is available for distribution immediately. However, it may be updated periodically as new data becomes available or improvements are made.
+	- The dataset is available for distribution immediately.
+
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- The dataset will be distributed under a Creative Commons Attribution-ShareAlike license (CC BY-SA), which allows for modification, distribution, and sharing of the dataset with proper attribution.
-No fees are associated with the use of this dataset.
-Licensing terms are available on the GitHub repository
+	- No, the dataset will not be distributed under a copyright or other IP license nor others similar.
+
 5.
@@
 	- No third-party restrictions have been imposed on the dataset, but users are reminded to respect confidentiality and ethical guidelines regarding sensitive demographic data.
+
 6.
@@
 	- No export controls or regulatory restrictions apply to this dataset at the moment.
+
 7. *Any other comments?*
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- The dataset will be hosted on GitHub and maintained by the project team, which includes data scientists and urban studies researchers.
+	- The dataset will be hosted on GitHub and maintained by the Open Data Toronto project team, which includes data scientists and urban studies researchers.
+
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- The dataset owner can be contacted via email at lexiknight@example.com for inquiries related to the dataset.
+	- The dataset owner can be contacted at Opendatatoronto.ca
 3. *Is there an erratum? If so, please provide a link or other access point.*
 	- There is no erratum currently. If errors are identified, they will be documented and corrected in subsequent versions of the dataset.
+
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- The dataset will be updated annually to reflect new data or to correct any errors. Updates will be communicated via GitHub, with a changelog provided for transparency.
+	- The dataset will be updated annually to reflect new data or to correct any errors. Updates will be communicated via Open Data Toronto.
+
 5.
@@
 Data will be retained for a maximum of five years, after which it will be deleted unless otherwise required by law or for ongoing research purposes.
+
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
 	- Older versions of the dataset will be archived for historical reference. Users will be notified via GitHub whenever a new version is released, with clear indication of any major changes or updates.
+
 7.
@@
 Contributions will be reviewed by the dataset maintainers for accuracy and relevance before being merged into the main repository.
+
 8. *Any other comments?*
-	- The maintenance of this dataset is a collaborative process, and the project team welcomes feedback and contributions from the broader community to ensure its continued growth and accuracy.
+	- N/A
